### 2023-08-13 paper.tex
init

%  LaTeX support: latex@mdpi.com 
%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.

%=================================================================
\documentclass[mathematics,article,submit,moreauthors]{Definitions/mdpi}

%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, adolescents, aerobiology, aerospace, agriculture, agriengineering, agrochemicals, agronomy, ai, air, algorithms, allergies, alloys, analytica, analytics, anatomia, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arm, arthropoda, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, cyber, dairy, data, ddc, dentistry, dermato, dermatopathology, designs, devices, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, future, futureinternet, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, grasses, gucdd, hazardousmatters, healthcare, hearts, hemato, hematolrep, heritage, higheredu, highthroughput, histories, horticulturae, hospitals, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijpb, ijtm, ijtpp, ime, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jcto, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jvd, jzbg, kidneydial, kinasesphosphatases, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing,\gdef\@continuouspages{yes}} nanomaterials, ncrna, ndt, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, %%nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, %oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology,\gdef\@ISSN{2813-0618}\gdef\@continuous pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, platforms, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, receptors, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, sclerosis, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, spectroscj, sports, standards, stats, std, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, targets, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, virtualworlds, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis 
% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal. Changing "submit" to "accept" before posting will remove line numbers.

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by: 
% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. Remove "pdftex" for (1) compiling with LaTeX & dvi2pdf (if eps figures are used) or for (2) compiling with XeLaTeX.

%=================================================================
% MDPI internal commands - do not modify
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2023}
\copyrightyear{2023}
%\externaleditor{Academic Editor: Firstname Lastname}
\datereceived{ } 
\daterevised{ } % Comment out if no revised date
\dateaccepted{ } 
\datepublished{ } 
%\datecorrected{} % For corrected papers: "Corrected: XXX" date in the original paper.
%\dateretracted{} % For corrected papers: "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%\pdfoutput=1 % Uncommented for upload to arXiv.org

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, float, amsmath, amssymb, lineno, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, colortbl, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, array, tabularx, pbox, ragged2e, tocloft, marginnote, marginfix, enotez, amsthm, natbib, hyperref, cleveref, scrextend, url, geometry, newfloat, caption, draftwatermark, seqsplit
% cleveref: load \crefname definitions after \begin{document}

%=================================================================
% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
%\Title{Expansive Information Injection with Large Language Models for Multi-Span Question Answering }
\Title{Empowering Multi-Span Question Answering with Expansive Information Injection using Large Language Models}

% MDPI internal command: Title for citation in the left column
\TitleCitation{Title}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0002-2206-1926} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Zhiyi Luo $^{1}$\orcidA{}, Yingying Zhang$^{1}$ and Shuyun Luo $^{1,}$*}

%\longauthorlist{yes}

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Zhiyi Luo, Yingying Zhang and Shuyun Luo}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Luo, Z.; Zhang, Y.; Luo, S.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad School of Computer Science and Technology and the Key Laboratory of Intelligent Textile and Flexible Interconnection of Zhejiang Province, Zhejiang Sci-Tech University, Hangzhou, China; luozhiyi@zstu.edu.cn
%$^{2}$ \quad Affiliation 2; e-mail@e-mail.com
}

% Contact information of the corresponding author
\corres{Correspondence: shuyunluo@zstu.edu.cn;}

% Current address and/or shared authorship
%\firstnote{Current address: Affiliation 3.} 
%\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

%\simplesumm{} % Simple summary

%\conference{} % An extended version of a conference paper

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{Retrieval-based question answering in the automotive domain requires a model to comprehend and articulate relevant domain knowledge, accurately understand user intent, and effectively match the required information. Typically, these systems employ a encoder-retriever architecture. However, existing encoders, which rely on pretrained language models, suffer from limited specialization, insufficient awareness of domain knowledge, and biases in user intent understanding. To overcome these limitations, this paper constructs a Chinese corpus specifically tailored for the automotive domain, comprising question-answer pairs, document collections, and multitask annotated data. Subsequently, a pretraining-multitask fine-tuning framework based on masked language models is introduced to integrate domain knowledge as well as enhance semantic representations, thereby yielding benefits for downstream applications. To evaluate system performance, an evaluation dataset is created using ChatGPT, and a novel retrieval task evaluation metric called Mean Linear Window Rank (MLWR) is proposed. Experimental results demonstrate that the proposed system (based on $\text{BERT}_{base}$), achieves accuracies of 77.5\% and 84.75\% for Hit@1 and Hit@3 respectively, in the automotive domain retrieval-based question answering task. Additionally, the MLWR reaches 87.71\%. Compared to a system utilizing a general encoder, the proposed multitask fine-tuning strategy shows improvements of 12.5\%, 12.5\%, and 28.16\% for Hit@1, Hit@3, and MLWR, respectively. Furthermore, when compared to the best single-task fine-tuning strategy, the enhancements amount to 0.5\%, 1.25\%, and 0.95\% for Hit@1, Hit@3, and MLWR, respectively.}

% Keywords
\keyword{deep learning; pretrained language model; retrieval-based question answering; multitask learning; fine-tuning}

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Diversity
%\LSID{\url{http://}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data
%\dataset{DOI number or link to the deposited data set if the data set is published separately. If the data set shall be published as a supplement to this paper, this field will be filled by the journal editors. In this case, please submit the data set as a supplement.}
%\datasetlicense{License under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins
%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Encyclopedia
%\encyclopediadef{For entry manuscripts only: please provide a brief overview of the entry title instead of an abstract.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Advances in Respiratory Medicine
%\addhighlights{yes}
%\renewcommand{\addhighlights}{%

%\noindent This is an obligatory section in “Advances in Respiratory Medicine”, whose goal is to increase the discoverability and readability of the article via search engines and other scholars. Highlights should not be a copy of the abstract, but a simple text allowing the reader to quickly and simplified find out what the article is about and what can be cited from it. Each of these parts should be devoted up to 2~bullet points.\vspace{3pt}\\
%\textbf{What are the main findings?}
% \begin{itemize}[labelsep=2.5mm,topsep=-3pt]
% \item First bullet.
% \item Second bullet.
% \end{itemize}\vspace{3pt}
%\textbf{What is the implication of the main finding?}
% \begin{itemize}[labelsep=2.5mm,topsep=-3pt]
% \item First bullet.
% \item Second bullet.
% \end{itemize}
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\1}[1]{\mathds{1}\left[#1\right]}

\newcommand{\secref}[1]{Section \ref{#1}}
\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\eqnref}[1]{Eq. (\ref{#1})}
\newcommand{\exref}[1]{Example \ref{#1}}
\newcommand{\algoref}[1]{Algorithm \ref{#1}}
\newcommand{\tableref}[1]{Table \ref{#1}}

\usepackage{color}
\usepackage[utf8]{inputenc}
\usepackage{xeCJK}
\setCJKmainfont{STKaiti}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
\label{sec:intro}

In summary, the main contributions in this paper are as follows:
\begin{itemize}
	\item We construct Chinese question and answer corpora, document corpora, and multi-task annotated corpora specifically tailored to the automotive domain.
	\item We propose a joint learning framework with a pretraining-multitask fine-tuning architecture to incorporate domain knowledge and conduct a comparative analysis of the contributions of various auxiliary task objectives to model performance.
	\item We create an evaluation dataset based on ChatGPT using a semi-automated approach, along with the introduction of the MLWR metric for evaluation.
\end{itemize}

%The introduction should briefly place the study in a broad context and highlight why it is important. It should define the purpose of the work and its significance. The current state of the research field should be reviewed carefully and key publications cited. Please highlight controversial and diverging hypotheses when necessary. Finally, briefly mention the main aim of the work and highlight the principal conclusions. As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research. Citing a journal paper \cite{ref-journal}. Now citing a book reference \cite{ref-book1,ref-book2} or other reference types \cite{ref-unpublish,ref-communication,ref-proceeding}. Please use the command \citep{ref-thesis,ref-url} for the following MDPI journals, which use author--date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, Journal of Intelligence, Journalism and Media, JRFM, Languages, Laws, Religions, Risks, Social Sciences, Literature.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Related Work}
\label{sec:related}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Our Approach}

\begin{figure}[H]
	\includegraphics[width=14.0cm]{overview}
	\caption{An overview of our retrieval-based QA system. \textbf{(a) Step 1}: Automotive Corpus Construction. \textbf{(b) Step 2}: The encoder module under a pretraining-multitask fine-tuning framework. \textbf{(c) Step 3}: The retriever module based on Faiss library.}
	\label{fig:overview}
\end{figure}   
\unskip

\subsection{Corpus Construction}
\label{sec:corpus_construction}
We construct a QA dataset specific to the automotive domain by gathering question-answer pairs from authoritative resources, including professional databases, websites and other relevant resources. This dataset comprises a total of 7,157 question-answer pairs, with each pair consisting of a question and its corresponding answer. \tableref{tab:base_corpus} provides an illustrative example of the dataset.

\begin{table}[H] 
	\caption{The constructed Chinese QA corpus in automotive domain.} \label{tab:base_corpus}
	\newcolumntype{C}{>{\centering\arraybackslash}X}
	\begin{tabularx}{\textwidth}{C}
		\toprule
		\textbf{An Example of QA pairs}	\\
		\midrule
		\{ ``id'': 0,~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \\
		``question'': ``WEY是什么品牌的车?'',~~~~~~~~~~~~~~~~~~~~~~ \\
		~~~~~~~~~~ ({\color{blue} Which automobile brand is WEY?}) \\ 
		``answer'': ``WEY是长城汽车旗下的高端品牌…'', ~~~~~~~\\
		 ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~({\color{blue} WEY is a high-end brand under Great Wall Motors…}) \\
		\}~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
%		\midrule
%		Entry 1		\\
%		Entry 2	Dat \textsuperscript{1}\\
		\bottomrule
	\end{tabularx}
%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
\end{table}

\begin{table}[H] 
	\caption{The constructed Chinese QA corpus in automotive domain.} \label{tab:annotated_corpus}
	\newcolumntype{C}{>{\centering\arraybackslash}X}
	\begin{tabularx}{\textwidth}{p{2cm}L} 
		\toprule
		\textbf{Name}  & \textbf{Data Format}	\\
		\midrule
		MLM Corpus  & \textbf{[MASK][MASK]}车队首次在1994年的JGTC第四站比\textbf{[MASK]}中亮相，获得了资格赛第二名的位置。{\color{blue} (The [MASK] team made its debut in the fourth round of the JGTC  in 1994, securing the second position in the qualifying [MASK].) } \\
		\midrule
		NSP Corpus  & \textbf{Sentence1}: 上世纪90年代，TRD为丰田TOM'S车队打造了Supra赛车。{\color{blue} (In the 1990s, TRD built Supra race cars for the Toyota TOM'S team.) }
		\textbf{Sentence2}: 丰田车队首次在1994年的JGTC第四站比赛中亮相，获得了资格赛第二名的位置。{\color{blue} (The Toyota team made its debut in the fourth round of the JGTC  in 1994, securing the second position in the qualifying race.)} ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\textbf{Label}: continuous (1)\\
		\midrule
		STS Corpus & \textbf{Sentence1}: 丰田车队首次在1994年的JGTC第四站比赛中亮相，获得了资格赛第二名的位置。{\color{blue} (The Toyota team made its debut in the fourth round of the JGTC  in 1994, securing the second position in the qualifying race.)}
		\textbf{Sentence2}: 在1994年的JGTC第四站比赛中，丰田车队首次参赛，并在资格赛中获得了第二名的成绩。{\color{blue} (In 1994, during the fourth round of the JGTC, the Toyota team made its debut and secured a second-place finish in the qualifying race.)} ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \textbf{Label}: similar (1) ~~~~~~~~		\\
		\midrule
		TE Corpus  &  \textbf{Sentence1}: 一个年轻的黑人正试图向另外两个人解释一些事情。{\color{blue} (A young black person is trying to explain something to two other individuals.)}
		\textbf{Sentence2}: 一位年轻的黑人男子正在和另外两位说话。{\color{blue} (A young black man is talking to two other people.)} ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \textbf{Label}: entailment (0) ~~~~~		\\
		\bottomrule
	\end{tabularx}
	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
\end{table}

\section{Experiments}
In this section, we first create an evaluation dataset for the automotive domain. Next, we introduce evaluation metrics utilized in our experiments. Finally, we conduct a comparative analysis against competing models to substantiate the effectiveness of our system.

\subsection{Evaluation Dataset}
Firstly, we create a retrieval corpus (shown in \tableref{tab:question_set}) utilizing the question set outlined  in \secref{sec:corpus_construction}. 
Then, we randomly sample 100 questions from the retrieval corpus. These selected questions are then subjected to synonymous rephrasing using ChatGPT, which ultimately leads to the creation of the evaluation dataset (shown in \tableref{tab:eval_dataset}).

\begin{table}[H] 
	\caption{The retrieval corpus consisted of all questions in QA dataset.} \label{tab:question_set}
	\newcolumntype{C}{>{\centering\arraybackslash}X}
	\begin{tabularx}{\textwidth}{C}
		\toprule
		\textbf{Questions}	\\
		\midrule
		\{ 未来车门会是什么样？\} \\({\color{blue} What will the car doors of the future look like?})\\
		\midrule
		\{ WEY是什么品牌的车？\} \\({\color{blue} Which automobile brand is WEY?}) \\ \midrule
		\{ 长安沃尔沃和吉利沃尔沃有什么区别？\} \\ ({\color{blue} What is the difference between Changan Volvo and Geely Volvo?})\\
		%		\midrule
		%		Entry 1		\\
		%		Entry 2	Dat \textsuperscript{1}\\
		\bottomrule
	\end{tabularx}
	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
\end{table}

Specifically, we transform the rephrasing task description and the question text into prompts, which are fed into ChatGPT to generate the rephrased results. These results are then subject to manual screening to create the final evaluation dataset. The prompts are designed following specific principles: (1) Role assignment: ChatGPT assumes the role of an automotive engineer, for instance, with a prompt like ``Imagine you are an automotive engineer''. (2) Rephrasing task description: a detailed explanation of the rephrasing task requirements is provided, such as ``You will receive a text related to the automotive domain and your task is to rewrite it, ensuring that the length remains similar to the original while preserving its meaning''. (3) Result requirements: the desired outcomes of ChatGPT's generation are described, for example, with a prompt like ``Please provide 6 rephrased results for each data point and rank them in descending order based on their quality''. Subsequently, human annotators manually review the rephrased results generated by ChatGPT, carefully examining each question's rephrased versions, and selecting the top 4 synonyms with the highest quality. This process yields a dataset comprising 400 user queries, as depicted in Table 4. Each query corresponds to a question in the {\em queries} field and has a corresponding reference question in the retrieval corpus, indicated by the {\em reference} field. This user query dataset is utilized to evaluate the performance of the retrieval-based question answering model.

\begin{table}[H] 
	\caption{The evaluation dataset in our experiments.} \label{tab:eval_dataset}
	\newcolumntype{C}{>{\centering\arraybackslash}X}
	\begin{tabularx}{\textwidth}{L}
	\toprule
		\textbf{An illustration Example}	\\
		\midrule
		\{ ``reference'': ``长安cs75plus车型热销背后的几点思考'',~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \\
		~~~~~~~~~~~~~~~~~~~({\color{blue} Some thoughts behind the hot sales of the Changan CS75 Plus model.}) \\ 
		~~~``queries'': [\\
		~~~~~~``长安cs75plus车型热销背后原因解析'', \\
		~~~~~~~({\color{blue} Analysis of the reasons behind the high sales of the Changan CS75 Plus model.}) \\ 
		~~~~~~``购买长安cs75plus车型的几点原因'', \\
		~~~~~~ ({\color{blue} Several reasons for purchasing the Changan CS75 Plus model.}) \\ 
		~~~~~~``长安cs75plus车型为什么能够热销，列出几点原因'', \\
		~~~~~~~({\color{blue} Please list a few reasons to explain why the Changan CS75 Plus model sells well.}) \\ 
		~~~~~~~``长安cs75plus车型，热销背后的原因思考'',~~~~ \\
		~~~~~~ ({\color{blue} Reflection on the reasons behind the popularity of the Changan CS75 Plus model.}) \\ 
		~~~~] ~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
		\}~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
		\bottomrule
	\end{tabularx}
	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
\end{table}

\subsection{Evaluation Metrics}
\label{sec:metrics}
The hit rate at K (Hit@K) is a widely used evaluation metric for assessing the performance of retrieval systems. It measures the capability to rank the correct target of user queries among the top K retrieval results. When conducting Hit@K for evaluation, a query is considered a hit if the true target is included in the top K retrieval results; otherwise, it is categorized as a miss. In our experiments, we utilize Hit@1, Hit@3, and Hit@5 as evaluation metrics for the retrieval model. Formally, the Hit@K is computed as:
\begin{linenomath}
	\begin{equation}\label{eq:hit}
		Hit@K = \frac{N_K}{|\mathcal{Q}|}, 
	\end{equation}
\end{linenomath}
where $N_K$ represents the total number of hits for $N$ retrieval tasks, and $|\mathcal{Q}|$ is the total number of true targets across all queries.

While Hit@K is a straightforward metric, it solely focuses on the top-ranked results, disregarding other potentially valuable outcomes. To account for the ranking of all results, we utilize the Mean Reciprocal Rank (MRR) as an evaluation metric. MRR is computed as follows:
\begin{linenomath}
	\begin{equation}\label{eq:mrr}
		MRR = \frac{1}{|S|}\sum_{i=1}^{|S|}\frac{1}{r_i}, 
	\end{equation}
\end{linenomath}
where $|S|$ represents the total number of queries, and $r_i$ denotes the ranking of the true target corresponding to the $i$-th query in the retrieved  results.

In addition, we present a novel evaluation metric designed based on real user behavior. Considering that the result page of the QA system  has the capability to display multiple results, the difference between the top-ranked and fifth-ranked feedback results holds minimal significance in terms of user experience. However, the MRR metric assigns a score difference of 0.8 between the first and fifth ranks (with a maximum score of 1). 
Moreover, considering that users typically limit their exploration to the initial pages of retrieval results, if a rank exceeds a certain threshold, it indicates a failure of the query sample to produce the correct result within the system. Despite a low ranking, MRR still provides a positive evaluation score when used for assessment. To address these concerns, we propose a new evaluation metric called Mean Linear Window Rank (MLWR). MLWR linearly adjusts the impact of ranking on the evaluation metric and incorporates a window size to exclude query samples with rankings beyond the predefined window. This approach better aligns with the user experience requirements of the system and provides a comprehensive assessment of retrieval system performance. Formally, MLWR is computed as follows:
\begin{linenomath}
	\begin{equation}\label{eq:mlwr}
		MLWR = \sum_{i=1}^{|S|}\frac{\max\{0, N-r_i+1\}}{N\times |S|}, 
	\end{equation}
\end{linenomath}
where $|S|$ represents the total number of samples, $r_i$ denotes the ranking of the true target corresponding to the $i$-th query in the retrieved  results, and $N$ is the window size.

\subsection{Comparison Results}
In this section, we compare the performance of pretrained models, single-task fine-tuned models, and multitask fine-tuned models on the automotive domain QA retrieval task. By thoroughly examining the experimental results, we identify the most effective multitask fine-tuning strategy.

\begin{table}[H] 
	\caption{Comparison of Hit@K, MRR, MLWR using single-task fine-tuning models based on $\text{BERT}_{base}$.} \label{tab:single}
	\newcolumntype{C}{>{\centering\arraybackslash}X}
	\begin{tabularx}{\textwidth}{p{1.5cm}CCCCCCCCCC}
		\toprule
		\multirow{2}{*}{\textbf{Model}} & \multicolumn{2}{c}{Hit@1(\%)} & \multicolumn{2}{c}{Hit@3(\%)} & \multicolumn{2}{c}{Hit@5(\%)} & \multicolumn{2}{c}{MRR(\%)} & \multicolumn{2}{c}{MLWR(\%)} \\
		\cline{2-11} 
		\addlinespace
		& CLS           & MEAN          & CLS           & MEAN          & CLS           & MEAN          & CLS          & MEAN         & CLS           & MEAN         \\
		\midrule
		$\text{BERT}_{base}$   & 30.00         & 64.50         & 39.50         & 72.25         & 43.25         & 77.25         & 36.57        & 70.21        & 47.37         & 79.97   \\ 
%		BERT   & 30.00         & 64.50         & 39.50         & 72.25         & 43.25         & 77.25         & 36.57        & 70.21        & 47.37         & 79.97        \\
		FT-MLM & 47.25         & 77.00         & 55.50         & 83.50         & 57.00         & 85.75         & 52.19        & 80.94        & 58.96         & 86.76        \\
		FT-STS & 13.00         & 60.25         & 18.50         & 71.25         & 22.25         & 74.75         & 17.73        & 66.58        & 26.21         & 76.19        \\
		FT-TE  & 5.00          & 24.75         & 8.50          & 30.25         & 9.00          & 32.75         & 7.27         & 28.89        & 10.73         & 35.41        \\
		FT-NSP & 14.75         & 59.00         & 14.75         & 67.75         & 20.75         & 71.00         & 18.53        & 64.53        & 24.56         & 73.29  \\ 
%		$\text{BERT}_{large}$   & 26.50         & 64.50         & 39.50         & 72.25         & 43.25         & 77.25         & 36.57        & 70.21        & 47.37         & 79.97   \\ 
		\bottomrule
	\end{tabularx}
	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
\end{table}

\begin{table}[H] 
	\caption{Comparison of Hit@K, MRR, MLWR using multitask fine-tuning models based on $\text{BERT}_{base}$.} \label{tab:multi}
	\newcolumntype{C}{>{\centering\arraybackslash}X}
	\begin{tabularx}{\textwidth}{p{3.0cm}CCCCCC}
	\toprule
	\multicolumn{1}{c}{Model}                & Hit@1(\%) & Hit@3(\%) & Hit@5(\%) & MRR(\%) & MLWR(\%) \\
	\midrule
	STS+MLM {[}CLS{]}  & 74.25     & 84.00     & 85.25     & 79.54   & 87.12    \\
	NSP+MLM {[}CLS{]}  & 8.25      & 15.00     & 18.75     & 13.08   & 21.65    \\
	STS+MLM {[}MEAN{]} & 77.50     & 84.75     & 87.00     & 81.60   & 87.71    \\
	NSP+MLM {[}MEAN{]} & 73.25     & 78.75     & 80.50     & 76.77   & 82.17   \\
	\bottomrule
	\end{tabularx}
	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
\end{table}

\begin{table}[H] 
	\caption{Comparison of Hit@K, MRR, MLWR using the best single-task and multitask fine-tuning models based on $\text{BERT}_{large}$ and $\text{RoBERTa}$.} \label{tab:sup}
	\newcolumntype{C}{>{\centering\arraybackslash}X}
	\begin{tabularx}{\textwidth}{p{1.5cm}CCCCCCCCCC}
		\toprule
		\multirow{2}{*}{\textbf{Model}} & \multicolumn{2}{c}{Hit@1(\%)} & \multicolumn{2}{c}{Hit@3(\%)} & \multicolumn{2}{c}{Hit@5(\%)} & \multicolumn{2}{c}{MRR(\%)} & \multicolumn{2}{c}{MLWR(\%)} \\
		\cline{2-11} 
		\addlinespace
		& CLS           & MEAN          & CLS           & MEAN          & CLS           & MEAN          & CLS          & MEAN         & CLS           & MEAN         \\
		\toprule
		$\text{BERT}_{large}$   & 26.50         & 64.50         & 39.50         & 72.25         & 43.25         & 77.25         & 36.57        & 70.21        & 47.37         & 79.97   \\ 
		FT-MLM & 29.25         & 76.75         & 36.50         & 82.00         & 39.50         & 85.25        & 33.88        & 80.42        & 41.56        & 86.19        \\
		MLM+STS & 18.50        & 78.00        & 22.20         & 83.50        & 23.50         & 85.75         & 21.13       & 81.67     & 25.16       & 88.42      \\ \toprule[0.2mm]
		$\text{RoBERTa}$   & 69.00         & 73.00         & 77.75      & 79.50        & 79.25        & 82.75        & 74.16        & 77.41       & 81.59         & 84.61   \\ 
		FT-MLM & 73.25        & 75.75        & 79.25        & 81.75        & 83.25         & 84.00         &  77.63        & 79.79        & 85.31         & 86.81        \\
		MLM+STS & 37.50         & 78.75        & 48.25         & 84.50       & 51.75        & 87.75         & 44.46     & 82.50       & 55.16         & 88.79       \\
		\bottomrule[0.2mm]
	\end{tabularx}
	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
\end{table}

To illustrate the generalization capability of our framework in mitigating bias within pretrained models, we extend our evaluation beyond the BERT-base model to also include the BERT-large and RoBERTa models. As shown in \tableref{tab:sup}, our framework exhibits effective generalization   across a variety of pretrained models. It is worth nothing that RoBERTa, which is solely pretrained using the MLM task, demonstrates good performance with the CLS encoding, achieving a Hit@1 score of 69\%. However, in pretraining models such as BERT-base and BERT-large, the CLS representation primarily learns from the NSP task, resulting in sub-optimal performance when directly utilizing the  CLS encoding. These findings highlight the negative impact of the NSP task as a training objective on QA tasks, while emphasizing the benefits of the MLM task as a training objective for downstream QA tasks.

%Furthermore, in order to showcase the effectiveness of the retriever module in our proposed system, we compare its performance using different indexing structures as described in Section 3.2. Specifically, we evaluate the retriever module using brute force, IndexPQ index, IndexHNSWFlat, and IndexFlatL2. 
%As shown in 
\subsection{Case Study}
In this section,  we conduct a case study to qualitatively analyze competing models. 
\tableref{tab:case} presents the results obtained when inputting an example user query, 
namely ``如何对高尔夫7系列车型进行自我检修？'' ({\color{blue} How to perform self-maintenance on Volkswagen Golf7 series?}), and showcases the responses retrieved by the competing models utilizing $\text{BERT}_{base}$ in proposed framework.
The baseline BERT model provides a historical overview of the 7th Generation Volkswagen Golf, while the single-task FT-MLM model compares the 308S and Golf 7 models. However, neither of these models is capable of providing an accurate answer to the query. In contrast, the STS+MLM joint fine-tuning model effectively responds with the precise and specific steps to perform maintenance on the FAW-Volkswagen Golf7, thereby correctly addressing the query.
The STS+MLM joint model demonstrates its effectiveness in capturing the query intentions, surpassing other competing models in terms of qualitative performance.

\begin{table}[H] 
	\caption{Retrieved answers from baseline $\text{BERT}_{base}$ model, single-task FT-MLM model, and multitask STS+MLM model.} \label{tab:case}
	\newcolumntype{C}{>{\centering\arraybackslash}X}
	\begin{tabularx}{\textwidth}{cp{10cm}}
		\toprule
		\multicolumn{2}{p{12cm}}{\hangindent=2.2cm \hangafter=1 \textbf{Input Query}: ``如何对高尔夫7系列车型进行自我检修？'' ({\color{blue} How to perform self-maintenance on Volkswagen Golf7 series?})}   \\
		\midrule
		\textbf{Model} & \textbf{Retrieved answers} \\ \midrule
		$\text{BERT}_{base}$  &  1. 高尔夫Mk1：1974年5月，第一代高尔夫... 2. 高尔夫Mk2:1983年8月，大众推出第二代... ({\color{blue} 1. Golf Mk1: In May 1974, the first generation Golf was introduced..  2. Golf Mk2: In August 1983, Volkswagen unveiled the second generation...})  \\\midrule
		FT-MTM  &       1. 动力组合对比：高尔夫一共有三种排量...	 2. 质保政策对比：高尔夫官方保修周期为3年或者...
		  ({\color{blue} 1. Powertrain Comparison: The Golf is available in three different engine displacements... 2. Warranty Policy Comparison: The official warranty period for the Golf is 3 years or...})   \\ \midrule
		MLM+STS  &   1. 更换4.5升5w40美孚全合成机油、博世机滤、博世空气滤芯、博世空调滤芯、博世汽油滤芯、3m燃油添加剂、免拆三元催化清洗剂
2. 动平衡、更换原厂轮毂盖
		 ({\color{blue} 1. Replace 4.5 liters of 5w40 Mobil fully synthetic engine oil, Bosch oil filter, Bosch air filter, Bosch cabin air filter, Bosch fuel filter, 3M fuel additive, and non-dismantle catalytic converter cleaner.  2. Dynamic balancing and replace original wheel hub covers. }) \\
		\bottomrule
	\end{tabularx}
	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
\end{table}

\section{Conclusion}
In this paper, we first focus on constructing QA corpora, document sets, and multitask fine-tuning datasets specifically tailored to the automotive domain. Then, we propose a pretraining-multitask fine-tuning learning framework to develop an encoder model that incorporates domain knowledge, enhancing the semantic representation of texts and enabling effective retrieval QA applications. The experimental results reveal that within the multitask fine-tuning framework (based on $\text{BERT}_{base}$), the joint fine-tuned model MLM+STS achieves the highest performance. It attains Hit@1 and Hit@3 accuracies of 77.5\% and 84.75\%, respectively, along with an MLWR of 87.71\%. These outcomes signify substantial improvements of 12.5, 12.5, and 28.16 percentage points, respectively, compared to the baseline BERT model. Additionally, when compared to the best-performing single-task fine-tuned model, FT-MLM, the observed enhancements amount to 0.5, 1.25, and 0.95 percentage points, respectively.

%All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, etc.

%\section{Discussion}
%
%Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses. The findings and their implications should be discussed in the broadest context possible. Future research directions may also be highlighted.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Conclusions}
%
%This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
%\supplementary{The following supporting information can be downloaded at:  \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.}

% Only for journal Methods and Protocols:
% If you wish to submit a video article, please do so with any other supplementary material.
% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title. A supporting video article is available at doi: link.}

% Only for journal Hardware:
% If you wish to submit a video article, please do so with any other supplementary material.
% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.\vspace{6pt}\\
%\begin{tabularx}{\textwidth}{lll}
%\toprule
%\textbf{Name} & \textbf{Type} & \textbf{Description} \\
%\midrule
%S1 & Python script (.py) & Script of python source code used in XX \\
%S2 & Text (.txt) & Script of modelling code used to make Figure X \\
%S3 & Text (.txt) & Raw data from experiment X \\
%S4 & Video (.mp4) & Video demonstrating the hardware in use \\
%... & ... & ... \\
%\bottomrule
%\end{tabularx}
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided. The following statements should be used ``Conceptualization, X.X. and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y. and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing---original draft preparation, X.X.; writing---review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y. All authors have read and agreed to the published version of the manuscript.'', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation. Authorship must be limited to those who have contributed substantially to the work~reported.}

\funding{ This research was supported by the Natural Science Foundation of Zhejiang Province, China (Grant No. LQ22F020027) and the Key Research and Development Program of Zhejiang Province, China (2023C01041).}

%\acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections. This may include administrative and technical support, or donations in kind (e.g., materials used for experiments).}

\conflictsofinterest{The authors declare no conflict of interest.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Only for journal Encyclopedia
%\entrylink{The Link to this entry published on the encyclopedia platform.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{adjustwidth}{-\extralength}{0cm}
%\printendnotes[custom] % Un-comment to print a list of endnotes

\reftitle{References}

% Please provide either the correct journal abbreviation (e.g. according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% References, variant A: external bibliography
%=====================================
%\bibliography{your_external_BibTeX_file}

%=====================================
% References, variant B: internal bibliography
%=====================================
\begin{thebibliography}{999}
	% Reference 1
	\bibitem[Gupta(2005)]{asq-system}
	Gupta, N.; Tur, G.; Hakkani-Tur, D.; et al. The AT\&T spoken language understanding system. {\em IEEE Transactions on Audio, Speech, and Language Processing}, {\bf 2005}, {\em 14(1)}, 213-222.
	\bibitem[Ferrucci(2010)]{watson}
	Ferrucci, D.G.; Brown, E.; Chu-Carroll, J.; Fan, J.; Gondek, D.; Kalyanpur, A.A.; Lally, A.; Murdock, J.W.; Nyberg, E.; Prager, J.; Schlaefer, N.; Welty, C. Building Watson: An Overview of the DeepQA Project. {\em AI Magazine} {\bf 2010}, {\em 31(3)}, 59--79.
	\bibitem[Qu(2018)]{odqa2018}
	Qu, C.; Yang, L.; Qiu, M.H. Open domain question answering using early fusion of knowledge bases and text. Available online: https://doi.org/10.48550/arXiv.1809.00782. (accessed on 19-05-2023).
	\bibitem[Vaswani(2017)]{transformers2017}
	Vaswani, A.; Shazeer, N.; Parmar, N.; Uszkoreit, J.; Jones, L.; Gomez, A.N.; Polosukhin, I. Attention Is All You Need. In Proceedings of Advances in Neural Information Processing Systems(ANIPS), California, USA, 2017; 5998-6008.
	\bibitem[Devlin(2019)]{bert2019}
	Devlin, J.; Chang, M.W.; Lee, K.; Toutanova, K. BERT: Pre-training of Deep Bidirectional Transformers for Language Understanding. In Proceedings of the Conference of the North American Chapter of the Association for Computational Linguistics: Human Language Technologies (NAACL-HLT), Minneapolis, 2019; 4171-4186.
	\bibitem[Radford(2018)]{gpt}
	Radford, A.; Narasimhan, K.; Salimans, T.; Sutskever, I. Improving Language Understanding by Generative Pre-Training. Available online: https://cdn.openai.com/research-covers/language-unsupervised/language\_understanding\_paper.pdf. (accessed on 19-05-2023).
	\bibitem[Radford(2020)]{gpt2}
	Radford, A.; Wu, J.; Child, R.; Luan, D.; Amodei, D.; Sutskever, I. Language Models are Unsupervised Multitask Learners. Available online: https://cdn.openai.com/better-language-models/language\_models\_are\_unsupervised\_multitask\_learners.\\pdf. (accessed on 19-05-2023).
	\bibitem[Brown(2020)]{gpt3}
	Brown, T.; Mann, B.; Ryder, N.; et al. Language models are few-shot learners. In proceedings of Advances in Neural Information Processing Systems, Virtual-only Conference, 2020, 33: 1877-1901.
	\bibitem[Rajpurkar(2016)]{squad}
	Rajpurkar, P.; Zhang, J.; Lopyrev, K.; Liang, P. Squad: 100,000+ questions for machine comprehension of text. In Proceedings of the Conference on Empirical Methods in Natural Language Processing(EMNLP), Austin, Texas, USA, 2016, 2383-2392.
	\bibitem[Rajpurkar(2018)]{squad2.0}
	Rajpurkar, P.; Jia, R.; Liang, P. Know what you don’t know: Unanswerable questions for squad. In Proceedings of the 56th Annual Meeting of the Association for Computational Linguistics (Volume 2: Short Papers), Melbourne, Australia, 2018, 784–789.
	\bibitem[Li(2022)]{multispanqa}
	Li, H.; Tomko, M.; Vasardani, M.; Baldwin, T. MultiSpanQA: A dataset for multi-span question answering. In Proceedings of the Conference of the North American Chapter of the Association for Computational Linguistics: Human Language Technologies (NAACL-HLT), Seattle, Washington, 2022, 1250–1260.
	\bibitem[Yang(2019)]{bertserini}
	Yang, Wei; et al. End-to-end open-domain question answering with bertserini. Available online: https://doi.org/10.48550/ar-\\Xiv.1902.01718. (accessed on 19-05-2023).
	\bibitem[Zhang(2022)]{qa-survey}
	Zhang, Q.; Chen, S.S.; Xu, D.K.; Cao, Q.Q.; Chen, X.J.; Cohn, T.; Fang, M. A Survey for Efficient Open Domain Question Answering. Available Online: https://arxiv.org/abs/2211.07886. (accessed on 19-05-2023).
	\bibitem[Jones(1972)]{tf-idf}
	Jones, S.K. A statistical interpretation of term specificity and its application in retrieval. {\em Journal of Documentation} {\bf 1972}, {\em 28(1)}, 11--21.
%	\bibitem[Lin(2017)]{multichannel}
%	Lin, B. Y.; Xu, F. F.; Luo, Z.; et al. Multi-channel bilstm-crf model for emerging named entity recognition in social media. In Proceedings of the 3rd Workshop on Noisy User-generated Text, Copenhagen, Denmark, 2017, 160-165.
	\bibitem[Baldwin(2015)]{hand-crafted-features}
	Baldwin, T.; Marneffe M.C.; Han, B.; et al. Shared tasks of the 2015 workshop on noisy user-generated text: Twitter lexical normalization and named entity recognition. In Proceedings of the workshop on noisy user-generated text, Beijing, China, 2015, 126-135.
	\bibitem[Derczynski(2015)]{tweet}
	Derczynski, L.; Maynard, D.; Rizzo, G.; et al. Analysis of named entity recognition and linking for tweets. {\em Information Processing \& Management} {\bf 2015}, {\em 51(2)}, 32-49.
	\bibitem[Mikolov(2013)]{word2vec}
	Mikolov, T.; Chen, K.; Corrado, G.; Dean, J. Efficient estimation of word representations in vector space. Available online: https://arxiv.org/abs/1301.3781. (accessed on 19-05-2023).
%	\bibitem[Le(2014)]{word2vec2}
%	Le, Q.; Mikolov, T. Distributed representations of sentences and documents. In Proceedings of the 31st International Conference on Machine Learning (ICML), Beijing, China, 2014; 1188-1196.
	\bibitem[Harris(1954)]{distributed-hypothesis}
	Harris, Z.S. Distributional structure. {\em Journal of Documentation} {\bf 1954}, {\em 10(2-3)}, 146--162.
	\bibitem[Le(2014)]{glove}
	Pennington, J.; Socher, R.; Manning, C.D. GloVe: Global Vectors for Word Representation. In Proceedings of the 2014 conference on empirical methods in natural language processing (EMNLP),  Maryland, USA, 2014; 1532-1543.
	\bibitem[Vaswani(2017)]{cove}
	McCann, B.; Bradbury, J.; Xiong, C.; Socher, R. Learned in translation: Contextualized word vectors. In Proceedings of Advances in Neural Information Processing Systems(NIPS), California, USA, 2017; 6297-6308.
	\bibitem[Peters(2018)]{elmo}
	Peters, M.E.; Neumann, M.; Iyyer, M.; Gardner, M.; Clark, C.; Lee, K.; Zettlemoyer, L. Deep contextualized word representations. In Proceedings of the 2018 Conference of the North American Chapter of the Association for Computational Linguistics: Human Language Technologies, New Orleans, USA, 2018; 2227-2237.
	\bibitem[Devika(2021)]{app1}
	Devika, R.; Vairavasundaram, S.; Mahenthar, C.S.J.; et al. A Deep Learning Model Based on BERT and Sentence Transformer for Semantic Keyphrase Extraction on Big Social Data. In  IEEE Access \textbf{2021}, 9, 165252-165261.
	\bibitem[Natarajan(2022)]{app2}
	Natarajan, B.; Rajalakshmi, E.; Elakkiya, R; et al. Development of an End-to-End Deep Learning Framework for Sign Language Recognition, Translation, and Video Generation. In IEEE Access \textbf{2022}, 10, 104358-104374.
	\bibitem[Bentley(1975)]{kd-tree}
	Bentley, J.L. Multidimensional binary search trees used for associative searching. {\em Communications of the ACM} {\bf 1975}, {\em 18(9)}, 509-517.
	\bibitem[Liu(2006)]{ball-tree}
	Liu, T.; Moore, A.W.; Gray, A.; New algorithms for efficient high-dimensional nonparametric classification. {\em JMLR} {\bf 2006}, 7, 1135–1158.
	\bibitem[Omohundro(1989)]{ball-tree2}
	Omohundro SM. Five balltree construction algorithms. Berkeley, California, USA: International Computer Science Institute, 1989.
	\bibitem[Friedman(1977)]{knn-graph}
	Friedman, J.H.; Bentley, J.L.; Finkel, R.A. An algorithm for finding best matches in logarithmic expected time. {\em ACM Transactions on Mathematical Software} {\bf 1977}, {\em 3(3)}, 209-226.
	\bibitem[Jégou(2011)]{pq}
	Jégou, H.; Douze, M.; Schmid, C. Product quantization for nearest neighbor search. {\em IEEE Transactions on Pattern Analysis and Machine Intelligence} {\bf 2011}, {\em 33(1)}, 117-128.
	\bibitem[20Indyk(1998)]{lsh}
	Indyk, P.; Motwani, R. Approximate nearest neighbors: towards removing the curse of dimensionality. In Proceedings of the Thirtieth Annual ACM Symposium on Theory of Computing, New York, USA, 1998; 604-613.
	\bibitem[21Malkov(2018)]{hnsw}
	Malkov, Y.A.; Yashunin, D.A. Efficient and robust approximate nearest neighbor search using Hierarchical Navigable Small World graphs. Available online: https://arxiv.org/abs/1603.09320. (accessed on 19-05-2023).
	\bibitem[Jégou(2010)]{pns}
	Jégou, H.; Perronnin, F.; Douze, M.; Sánchez, J.; Pérez, P.; Schmid, C. Aggregating local descriptors into a compact image representation. In Proceedings of the 2010 IEEE Computer Society Conference on Computer Vision and Pattern Recognition, San Francisco, USA, 2010; 3304-3311.
	\bibitem[Wang(2019)]{haq}
	Wang, K.; Liu, Z.; Lin, Y.; Lin, W.; Han, S. HAQ: Hardware-Aware Automated Quantization with Mixed Precision. In Proceedings of  the IEEE Computer Society Conference on Computer Vision and Pattern Recognition, Los Angeles, USA, 2019; 1669-1678.	
	\bibitem[Johnson(2011)]{faiss}
	Johnson, J.; Douze, M.; Jégou, H. Billion-scale similarity search with GPUs. {\em IEEE Transactions on Big Data} {\bf 2019}, {\em 7(3)}, 535-547.	
%	\bibitem[Zhu(2015)]{}
%	Zhu, Y.K.; Kiros, R.; Zemel, R.; Salakhutdinov, R.; Urtasun, R.; Torralba, A.; Fidler, S. Aligning books and movies: Towards story-like visual explanations by watching movies and reading books. In Proceedings of the IEEE International Conference on Computer Vision, Santiago, Republic of Chile, 2015; 19-27.
	\bibitem[Liu(2019)]{roberta}
	Liu, Y.; Ott, M.; Goyal, N.; Du, J.; Joshi, M.; Chen, D. RoBERTa: A Robustly Optimized BERT Pretraining Approach. Available online: https://arxiv.org/abs/1603.09320. (accessed on 19-05-2023).
	\bibitem[Johnson(2020)]{spanbert}
	Clark, C.; Lee, K.; Chang, M.W.; Kwiatkowski, T.; Collins, M.; Toutanova, K. SpanBERT: Improving Pre-training by Representing and Predicting Spans. {\em Transactions of the Association for Computational Linguistics} {\bf 2020}, {\em 8}, 64-77.
	%	% Reference 2
%	\bibitem[Author2(year)]{ref-book1}
%	Author~2, L. The title of the cited contribution. In {\em The Book Title}; Editor 1, F., Editor 2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
%	% Reference 3
%	\bibitem[Author3(year)]{ref-book2}
%	Author 1, A.; Author 2, B. \textit{Book Title}, 3rd ed.; Publisher: Publisher Location, Country, 2008; pp. 154--196.
%	% Reference 4
%	\bibitem[Author4(year)]{ref-unpublish}
%	Author 1, A.B.; Author 2, C. Title of Unpublished Work. \textit{Abbreviated Journal Name} year, \textit{phrase indicating stage of publication (submitted; accepted; in press)}.
%	% Reference 5
%	\bibitem[Author5(year)]{ref-communication}
%	Author 1, A.B. (University, City, State, Country); Author 2, C. (Institute, City, State, Country). Personal communication, 2012.
%	% Reference 6
%	\bibitem[Author6(year)]{ref-proceeding}
%	Author 1, A.B.; Author 2, C.D.; Author 3, E.F. Title of presentation. In Proceedings of the Name of the Conference, Location of Conference, Country, Date of Conference (Day Month Year); Abstract Number (optional), Pagination (optional).
%	% Reference 7
%	\bibitem[Author7(year)]{ref-thesis}
%	Author 1, A.B. Title of Thesis. Level of Thesis, Degree-Granting University, Location of University, Date of Completion.
%	% Reference 8
%	\bibitem[Author8(year)]{ref-url}
%	Title of Site. Available online: URL (accessed on Day Month Year).
\end{thebibliography}
% Reference 2
%\bibitem[Author2(year)]{ref-book1}
%Author~2, L. The title of the cited contribution. In {\em The Book Title}; Editor 1, F., Editor 2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
%% Reference 3
%\bibitem[Author3(year)]{ref-book2}
%Author 1, A.; Author 2, B. \textit{Book Title}, 3rd ed.; Publisher: Publisher Location, Country, 2008; pp. 154--196.
%% Reference 4
%\bibitem[Author4(year)]{ref-unpublish}
%Author 1, A.B.; Author 2, C. Title of Unpublished Work. \textit{Abbreviated Journal Name} year, \textit{phrase indicating stage of publication (submitted; accepted; in press)}.
%% Reference 5
%\bibitem[Author5(year)]{ref-communication}
%Author 1, A.B. (University, City, State, Country); Author 2, C. (Institute, City, State, Country). Personal communication, 2012.
%% Reference 6
%\bibitem[Author6(year)]{ref-proceeding}
%Author 1, A.B.; Author 2, C.D.; Author 3, E.F. Title of presentation. In Proceedings of the Name of the Conference, Location of Conference, Country, Date of Conference (Day Month Year); Abstract Number (optional), Pagination (optional).
%% Reference 7
%\bibitem[Author7(year)]{ref-thesis}
%Author 1, A.B. Title of Thesis. Level of Thesis, Degree-Granting University, Location of University, Date of Completion.
%% Reference 8
%\bibitem[Author8(year)]{ref-url}
%Title of Site. Available online: URL (accessed on Day Month Year).

% If authors have biography, please use the format below
%\section*{Short Biography of Authors}
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author1.pdf}}}
%{\textbf{Firstname Lastname} Biography of first author}
%
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author2.jpg}}}
%{\textbf{Firstname Lastname} Biography of second author}

% For the MDPI journals use author-date citation, please follow the formatting guidelines on http://www.mdpi.com/authors/references
% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p. 328; \citeyear{ref-journal-3b}, p.475). This produces: Wong (1999, p. 328; 2000, p. 475)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% for journal Sci
%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\PublishersNote{}
\end{adjustwidth}
\end{document}

### 2023-08-14 paper.tex
Add files via upload
The main experimental data has been added to the end of the document 'paper.tex'.

@@
+% !TeX program = xelatex 
 %  LaTeX support: latex@mdpi.com 
@@
 \subsection{Comparison Results}
+
 In this section, we compare the performance of pretrained models, single-task fine-tuned models, and multitask fine-tuned models on the automotive domain QA retrieval task.
@@
 \PublishersNote{}
+
+\begin{table}[H] 
+	\caption{Approach performance on complete MultiSpanQA valid set based on $\text{BERT}_{base}$.} \label{tab:single}
+	\newcolumntype{C}{>{\centering\arraybackslash}X}
+	\begin{tabularx}{\textwidth}{p{1.5cm}CCCCCCCC}
+		\toprule
+		\multirow{2}{*}{\textbf{Model}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match}  \\
+		\cline{2-7} 
+		\addlinespace
+		& P           & R          & F           & P          & R           & F           \\
+		\midrule
+		Tase   & 60.28         & 55.59         & 65.83         & 78.16         & 78.27         & 78.06         \\ 
+		Liquid & 61.44         & 58.39         & 64.84         & 78.56         & 78.65         & 78.46         \\
+		C-rand & 63.05         & 58.51         & 68.34         & 79.42         & 78.70         & 80.14         \\
+		ER-EEins  & 63.93          & 60.22         & 68.13          & 77.50         & 77.07          & 77.94         \\
+		C-ER-EE & 62.90          & 61.02        & 64.89          & 76.72         & 78.56          & 74.97         \\
+		Bagging & 64.44          & 61.63        & 67.50          & 79.52         & 80.49          & 78.57         \\
+		\bottomrule
+	\end{tabularx}
+	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
+\end{table}
+
+\begin{table}[H] 
+	\caption{Approach performance on complete MultiSpanQA valid set based on $\text{RoBERTa}_{base}$.} \label{tab:single}
+	\newcolumntype{C}{>{\centering\arraybackslash}X}
+	\begin{tabularx}{\textwidth}{p{1.5cm}CCCCCCC}
+		\toprule
+		\multirow{2}{*}{\textbf{Model}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match}  \\
+		\cline{2-7} 
+		\addlinespace
+		& P & R & F & P & R & F \\
+		\midrule
+		Tase & 68.00 & 65.06 & 71.22 & 83.13 & 83.05 & 83.22 \\ 
+		Liquid & 68.33 & 66.68 & 70.07 & 82.71 & 82.45 & 82.98 \\
+		C-rand & 70.35 & 67.35 & 73.63 & 84.06 & 83.38 & 84.76 \\
+		ER-EEins & 69.15 & 67.81 & 70.54 & 82.85 & 83.90 & 81.83 \\
+		C-ER-EE & 70.44 & 67.813 & 73.26 & 82.80 & 82.45 & 83.15 \\
+		Bagging & 70.86 & 69.03 & 72.79 & 84.82 & 85.53 & 84.12 \\
+		\bottomrule
+	\end{tabularx}
+	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
+\end{table}
+
+\begin{table}[ht]
+	\caption{Model performance on complete MultiSpanQA valid Subset with different answer types based on $\text{BERT}_{base}$.}
+	\label{tab:single}
+	\newcolumntype{C}{>{\centering\arraybackslash}X}
+	\begin{tabularx}{\textwidth}{Cp{1.5cm}CCCCCCC}
+		\toprule
+		\multirow{2}{*}{\textbf{Type}} & \multirow{2}{*}{\textbf{Model}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match} \\
+		\cmidrule{3-8} 
+		& & P & R & F & P & R & F \\
+		\midrule
+		\multirow{6}{*}{DESC} & Tase & 32.76 & 27.33 & 40.87 & 64.46 & 68.61 & 60.79 \\ 
+		& Liquid & 36.69 & 31.10 & 44.71 & 66.05 & 65.95 & 66.15 \\
+		& C-rand & 38.74 & 32.89 & 47.12 & 68.31 & 70.32 & 66.42 \\
+		& ER-EEins & 44.69 & 40.71 & 49.52 & 63.12 & 67.16 & 59.53 \\
+		& C-ER-EE & 40.63 & 38.30 & 43.27 & 64.25 & 71.15 & 58.57 \\
+		& Bagging & 39.91 & 36.69 & 43.75 & 66.70 & 73.68 & 60.93 \\
+		\midrule
+		\multirow{6}{*}{NUM} & Tase & 33.33 & 30.23 & 37.14 & 60.98 & 71.99 & 52.89 \\ 
+		& Liquid & 34.33 & 31.25 & 38.10 & 60.68 & 68.15 & 54.69 \\
+		& C-rand & 35.96 & 33.33 & 39.05 & 64.47 & 71.56 & 58.65 \\
+		& ER-EEins & 36.20 & 34.48 & 38.10 & 59.02 & 65.63 & 53.62 \\
+		& C-ER-EE & 36.71 & 37.25 & 36.19 & 57.09 & 69.04 & 48.67 \\
+		& Bagging & 35.94 & 34.82 & 37.14 & 60.73 & 71.15 & 52.97 \\
+		\midrule
+		\multirow{6}{*}{HUM} & Tase & 70.68 & 67.64 & 74.00 & 83.09 & 83.93 & 82.28 \\ 
+		& Liquid & 72.59 & 71.35 & 73.88 & 84.16 & 85.77 & 82.61 \\
+		& C-rand & 73.80 & 71.17 & 76.63 & 84.36 & 85.30 & 83.43 \\
+		& ER-EEins & 73.61 & 70.63 & 76.86 & 82.75 & 82.64 & 82.85 \\
+		& C-ER-EE & 73.43 & 72.33 & 74.57 & 82.33 & 84.13 & 80.61 \\
+		& Bagging & 75.22 & 73.66 & 76.86 & 84.56 & 86.36 & 82.83 \\
+		\midrule
+		\multirow{6}{*}{LOC} & Tase & 59.52 & 54.65 & 65.34 & 78.91 & 76.57 & 81.40 \\ 
+		& Liquid & 60.75 & 57.58 & 64.29 & 79.03 & 77.85 & 80.25 \\
+		& C-rand & 63.07 & 57.68 & 69.58 & 80.58 & 76.73 & 84.85 \\
+		& ER-EEins & 62.36 & 57.79 & 67.72 & 80.13 & 77.03 & 83.48 \\
+		& C-ER-EE & 61.54 & 57.14 & 66.67 & 78.30 & 76.18 & 80.55 \\
+		& Bagging & 64.36 & 60.47 & 68.78 & 80.92 & 78.29 & 83.72 \\
+		\midrule
+		\multirow{6}{*}{ENTY} & Tase & 63.17 & 57.93 & 69.45 & 78.95 & 76.32 & 81.77 \\ 
+		& Liquid & 60.89 & 59.08 & 62.82 & 78.29 & 76.07 & 80.64 \\
+		& C-rand & 61.68 & 56.63 & 67.72 & 77.60 & 74.07 & 81.48 \\
+		& ER-EEins & 62.12 & 58.00 & 66.86 & 75.64 & 73.46 & 77.95 \\
+		& C-ER-EE & 59.63 & 59.04 & 60.23 & 73.74 & 75.03 & 72.50 \\
+		& Bagging & 61.98 & 58.42 & 65.99 & 78.34 & 76.22 & 80.59 \\
+		\midrule
+		\multirow{6}{*}{All Entities} & Tase & 66.30 & 62.21 & 70.96 & 81.16 & 80.37 & 81.96 \\ 
+		& Liquid & 67.17 & 65.25 & 69.21 & 81.66 & 81.69 & 81.63 \\
+		& C-rand & 68.47 & 64.44 & 73.03 & 81.93 & 80.57 & 83.34 \\
+		& ER-EEins & 68.36 & 64.64 & 72.53 & 80.55 & 79.21 & 81.93 \\
+		& C-ER-EE & 67.54 & 65.60 & 69.59 & 79.49 & 80.16 & 78.83 \\
+		& Bagging & 69.65 & 66.94 & 72.59 & 82.31 & 82.07 & 82.55 \\
+		\bottomrule
+	\end{tabularx}
+\end{table}
+
+\begin{table}[ht]
+	\caption{Model performance on complete MultiSpanQA valid Subset with different answer types based on $\text{RoBERTa}_{base}$.}
+	\label{tab:single}
+	\newcolumntype{C}{>{\centering\arraybackslash}X}
+	\begin{tabularx}{\textwidth}{Cp{1.5cm}CCCCCCC}
+		\toprule
+		\multirow{2}{*}{\textbf{Type}} & \multirow{2}{*}{\textbf{Model}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match} \\
+		\cmidrule{3-8} 
+		& & P & R & F & P & R & F \\
+		\midrule
+		\multirow{6}{*}{DESC} & Tase & 45.53 & 40.84 & 51.44 & 75.44 & 76.61 & 74.31 \\ 
+		& Liquid & 48.68 & 44.76 & 53.37 & 73.27 & 71.57 & 75.04 \\
+		& C-rand & 49.02 & 44.66 & 54.33 & 76.33 & 77.85 & 74.86 \\
+		& ER-EEins & 50.99 & 46.96 & 55.77 & 76.87 & 78.07 & 75.71 \\
+		& C-ER-EE & 49.24 & 44.71 & 54.81 & 71.87 & 73.03 & 70.74 \\
+		& Bagging & 47.70 & 43.78 & 52.40 & 77.43 & 80.63 & 74.47 \\
+		\midrule
+		\multirow{6}{*}{NUM} & Tase & 46.23 & 45.79 & 46.67 & 71.89 & 78.42 & 66.36 \\ 
+		& Liquid & 40.19 & 39.45 & 40.95 & 67.56 & 72.28 & 63.42 \\
+		& C-rand & 50.69 & 49.11 & 52.38 & 72.86 & 80.22 & 66.74 \\
+		& ER-EEin & 42.40 & 41.07 & 43.81 & 66.67 & 73.51 & 61.00 \\
+		& C-ER-EE & 45.58 & 44.55 & 46.67 & 65.86 & 73.19 & 59.87 \\
+		& Bagging & 44.65 & 43.64 & 45.71 & 70.11 & 78.49 & 63.35 \\
+		\midrule
+		\multirow{6}{*}{HUM} & Tase & 76.40 & 74.14 & 78.81 & 86.83 & 87.67 & 86.00 \\ 
+		& Liquid & 76.70 & 76.30 & 77.09 & 85.85 & 87.16 & 84.59 \\
+		& C-rand & 78.36 & 76.00 & 80.87 & 87.41 & 87.30 & 87.53 \\
+		& ER-EEins & 77.11 & 76.12 & 78.12 & 86.44 & 87.56 & 85.35 \\
+		& C-ER-EE & 78.42 & 77.37 & 79.50 & 85.88 & 87.49 & 86.28 \\
+		& Bagging & 78.51 & 77.33 & 79.73 & 87.90 & 88.66 & 87.15 \\
+		\midrule
+		\multirow{6}{*}{LOC} & Tase & 64.85 & 60.93 & 69.31 & 81.73 & 79.37 & 84.23 \\ 
+		& Liquid & 68.51 & 65.38 & 71.96 & 85.48 & 82.58 & 88.58 \\
+		& C-rand & 66.25 & 62.18 & 70.90 & 83.11 & 79.33 & 87.26 \\
+		& ER-EEins & 68.48 & 67.18 & 69.84 & 83.09 & 82.45 & 83.73 \\
+		& C-ER-EE & 69.03 & 66.10 & 72.22 & 83.88 & 81.97 & 85.88 \\
+		& Bagging & 69.47 & 66.91 & 72.22 & 84.44 & 82.77 & 86.19 \\
+		\midrule
+		\multirow{6}{*}{ENTY} & Tase & 71.63 & 69.86 & 73.49 & 83.54 & 81.62 & 85.55 \\ 
+		& Liquid & 68.57 & 67.99 & 69.16 & 82.37 & 81.27 & 83.49 \\
+		& C-rand & 74.54 & 72.80 & 76.37 & 84.68 & 83.00 & 86.44 \\
+		& ER-EEins & 69.87 & 70.59 & 69.16 & 82.19 & 83.58 & 80.84 \\
+		& C-ER-EE & 73.37 & 69.41 & 77.81 & 83.33 & 80.13 & 86.79 \\
+		& Bagging & 76.26 & 76.15 & 76.37 & 86.35 & 86.39 & 86.30 \\
+		\bottomrule
+	\end{tabularx}
+\end{table}
+
 \end{adjustwidth}

### 2023-08-25 paper.tex
Add files via upload

--- 2023-08-13 paper.tex
@@
 \section{Experiments}
-In this section, we first create an evaluation dataset for the automotive domain.
-Next, we introduce evaluation metrics utilized in our experiments.
-Finally, we conduct a comparative analysis against competing models to substantiate the effectiveness of our system.
+In this section, we compare our information augmentation approach with multiple strong baseline on multi-span question answering.
+We first introduce the datasets and experiment setup, then show the experimental results and analysis for different model.
 
 \subsection{Evaluation Dataset}
-Firstly, we create a retrieval corpus (shown in \tableref{tab:question_set}) utilizing the question set outlined  in \secref{sec:corpus_construction}. 
-Then, we randomly sample 100 questions from the retrieval corpus.
-These selected questions are then subjected to synonymous rephrasing using ChatGPT, which ultimately leads to the creation of the evaluation dataset (shown in \tableref{tab:eval_dataset}).
+\label{sec:datasets}
+	 We conducted experiments on MultiSpanQA(Li et al., 2022), a recently introduced Reading Comprehension dataset designed for multi-span question answering.
+This dataset comprises 6.5K multi-span examples in which the questions represent user queries issued to the Google search engine, and the contexts are extracted from the English Wikipedia.
+It's worth noting that there is a expand variant of MultiSpanQA known as MultispanQA(expand), which intakes single-span and answerable questions.
+However, we did not perform a comparison with the expanded dataset due to its relatively lower proportion of multi-span QA pairs.
+
+\subsection{Experimental Setup}
+	For all competing models and our model, we use the HuggingFace implementation of $\text{BERT}_{base}$ or $\text{RoBERTa}_{base}$ as the \textit{encoder} with $\textit{max\_len}$ = 512.
+We set the initial learning rate as $3 \times 10^{-5}$ and  $\textit{batch\_size}$ = 4, and use the BERTAdam optimizer with a weight decay of 0.01.
+Our approach does not involve tuning the parameters on the validation set.
+Instead, we rely on the model checkpoints obtained after 5 epochs.
+Next, we introduce the comparison model and evaluation metrics in our experiments.
+
+	\subsubsection{\textit{Model Under Comparison}}
+	\label{sec:baselines}
+	We introduce two comstracting models approaches to multi-span answer extraction : \textbf{TASE} (Segal et al., 2020) and \textbf{LIQUID}(Lee et al., 2023).
+TASE utilizes a tag-based span extraction model which identifies multi-span answers though the assigning a tag to every input token with BIO tagging scheme.
+On the other hand, LIQUID serves as a framework for generating multi-span QA datasets to improve model performance.
+
+	To enhance the context with auxiliary information, we employ two distinct   approaches: \textbf{$\text{AUG}_{c}$} and \textbf{$\text{AUG}_{eree}$}, where \textbf{AUG} is our automatic data augmentation framework,and the suffix indicates which kind of information is injected into the context.
+\textbf{$\text{AUG}_{C}$} enriches the context with continue writing, while \textbf{$\text{AUG}_{EREE}$} supplements context with entities information including explanation and relationship analysis.
+	Specifically, we leverage ChatGPT as a knowledge source to linearize the relevant information from large language models.
+in texts format and seamlessly integrate into the original contexts, thus reinforces the information of model inputs.
+
+	\subsubsection{\textit{Evaluation Metrics}}
+	\label{sec:metrics}
+	We use two automatic metrics for evaluation: Exact Match and Overlap F1 score.
+	\begin{itemize}
+		\item \textbf{Exact Match}. An exact match occurs when a predicted span fully matches one of the ground-truth
+		answer spans. We calculate the micro-average precision, recall and f1 score for the extract match
+		metric.
+
+		\item \textbf{Overlap F1 score}. Overlap F1 score is the macro-average f1 score, where the f1 score for each
+		example is computed by treating the prediction and gold as a bag of tokens.
+	\end{itemize}
+
+\subsection{Experimental Results and Analysis}
+	In this section, we compare $\text{AUG}$ with all competing models described above \textcolor{red}{both quantitatively and qualitatively}.
+
+	\subsubsection{\textit{Comparison Results}}
+	We evaluate our model as well as baselines 
+	\(( Section ~\ref{sec:baselines} )\) on the development splits of multi-span datasets \(( Section  ~\ref{sec:datasets})\) using automatic metrics \(( Section ~\ref{sec:datasets})\).
+The comparison results are shown in Table \ref{tab:bertall}, Table \ref{tab:robertaall}.
 
 	\begin{table}[H] 
-	\caption{The retrieval corpus consisted of all questions in QA dataset.} \label{tab:question_set}
+		\caption{Approach performance on complete MultiSpanQA valid set based on $\text{BERT}_{base}$.} 
+		\label{tab:bertall}
 		\newcolumntype{C}{>{\centering\arraybackslash}X}
-	\begin{tabularx}{\textwidth}{C}
+		\begin{tabularx}{\textwidth}{p{1.5cm}CCCCCCCC}
 			\toprule
-		\textbf{Questions}	\\
+			\multirow{2}{*}{\textbf{Model}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match}  \\
+			\cline{2-7} 
+			\addlinespace
+			& F\((\%)\)           & P\((\%)\)          & R\((\%)\)           & F\((\%)\)          & P\((\%)\)           & R\((\%)\)           \\
 			\midrule
-		\{ 未来车门会是什么样？\} \\({\color{blue} What will the car doors of the future look like?})\\
-		\midrule
-		\{ WEY是什么品牌的车？\} \\({\color{blue} Which automobile brand is WEY?}) \\ \midrule
-		\{ 长安沃尔沃和吉利沃尔沃有什么区别？\} \\ ({\color{blue} What is the difference between Changan Volvo and Geely Volvo?})\\
-		%		\midrule
-		%		Entry 1		\\
-		%		Entry 2	Dat \textsuperscript{1}\\
-		\bottomrule
-	\end{tabularx}
-	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
-\end{table}
-
-Specifically, we transform the rephrasing task description and the question text into prompts, which are fed into ChatGPT to generate the rephrased results.
-These results are then subject to manual screening to create the final evaluation dataset.
-The prompts are designed following specific principles: (1) Role assignment: ChatGPT assumes the role of an automotive engineer, for instance, with a prompt like ``Imagine you are an automotive engineer''.
-(2) Rephrasing task description: a detailed explanation of the rephrasing task requirements is provided, such as ``You will receive a text related to the automotive domain and your task is to rewrite it, ensuring that the length remains similar to the original while preserving its meaning''.
-(3) Result requirements: the desired outcomes of ChatGPT's generation are described, for example, with a prompt like ``Please provide 6 rephrased results for each data point and rank them in descending order based on their quality''.
-Subsequently, human annotators manually review the rephrased results generated by ChatGPT, carefully examining each question's rephrased versions, and selecting the top 4 synonyms with the highest quality.
-This process yields a dataset comprising 400 user queries, as depicted in Table 4.
-Each query corresponds to a question in the {\em queries} field and has a corresponding reference question in the retrieval corpus, indicated by the {\em reference} field.
-This user query dataset is utilized to evaluate the performance of the retrieval-based question answering model.
-
-\begin{table}[H] 
-	\caption{The evaluation dataset in our experiments.} \label{tab:eval_dataset}
-	\newcolumntype{C}{>{\centering\arraybackslash}X}
-	\begin{tabularx}{\textwidth}{L}
-	\toprule
-		\textbf{An illustration Example}	\\
-		\midrule
-		\{ ``reference'': ``长安cs75plus车型热销背后的几点思考'',~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \\
-		~~~~~~~~~~~~~~~~~~~({\color{blue} Some thoughts behind the hot sales of the Changan CS75 Plus model.}) \\ 
-		~~~``queries'': [\\
-		~~~~~~``长安cs75plus车型热销背后原因解析'', \\
-		~~~~~~~({\color{blue} Analysis of the reasons behind the high sales of the Changan CS75 Plus model.}) \\ 
-		~~~~~~``购买长安cs75plus车型的几点原因'', \\
-		~~~~~~ ({\color{blue} Several reasons for purchasing the Changan CS75 Plus model.}) \\ 
-		~~~~~~``长安cs75plus车型为什么能够热销，列出几点原因'', \\
-		~~~~~~~({\color{blue} Please list a few reasons to explain why the Changan CS75 Plus model sells well.}) \\ 
-		~~~~~~~``长安cs75plus车型，热销背后的原因思考'',~~~~ \\
-		~~~~~~ ({\color{blue} Reflection on the reasons behind the popularity of the Changan CS75 Plus model.}) \\ 
-		~~~~] ~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
-		\}~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
-		\bottomrule
-	\end{tabularx}
-	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
-\end{table}
-
-\subsection{Evaluation Metrics}
-\label{sec:metrics}
-The hit rate at K (Hit@K) is a widely used evaluation metric for assessing the performance of retrieval systems.
-It measures the capability to rank the correct target of user queries among the top K retrieval results.
-When conducting Hit@K for evaluation, a query is considered a hit if the true target is included in the top K retrieval results; otherwise, it is categorized as a miss.
-In our experiments, we utilize Hit@1, Hit@3, and Hit@5 as evaluation metrics for the retrieval model.
-Formally, the Hit@K is computed as:
-\begin{linenomath}
-	\begin{equation}\label{eq:hit}
-		Hit@K = \frac{N_K}{|\mathcal{Q}|}, 
-	\end{equation}
-\end{linenomath}
-where $N_K$ represents the total number of hits for $N$ retrieval tasks, and $|\mathcal{Q}|$ is the total number of true targets across all queries.
-
-While Hit@K is a straightforward metric, it solely focuses on the top-ranked results, disregarding other potentially valuable outcomes.
-To account for the ranking of all results, we utilize the Mean Reciprocal Rank (MRR) as an evaluation metric.
-MRR is computed as follows:
-\begin{linenomath}
-	\begin{equation}\label{eq:mrr}
-		MRR = \frac{1}{|S|}\sum_{i=1}^{|S|}\frac{1}{r_i}, 
-	\end{equation}
-\end{linenomath}
-where $|S|$ represents the total number of queries, and $r_i$ denotes the ranking of the true target corresponding to the $i$-th query in the retrieved  results.
-
-In addition, we present a novel evaluation metric designed based on real user behavior.
-Considering that the result page of the QA system  has the capability to display multiple results, the difference between the top-ranked and fifth-ranked feedback results holds minimal significance in terms of user experience.
-However, the MRR metric assigns a score difference of 0.8 between the first and fifth ranks (with a maximum score of 1).
-Moreover, considering that users typically limit their exploration to the initial pages of retrieval results, if a rank exceeds a certain threshold, it indicates a failure of the query sample to produce the correct result within the system.
-Despite a low ranking, MRR still provides a positive evaluation score when used for assessment.
-To address these concerns, we propose a new evaluation metric called Mean Linear Window Rank (MLWR).
-MLWR linearly adjusts the impact of ranking on the evaluation metric and incorporates a window size to exclude query samples with rankings beyond the predefined window.
-This approach better aligns with the user experience requirements of the system and provides a comprehensive assessment of retrieval system performance.
-Formally, MLWR is computed as follows:
-\begin{linenomath}
-	\begin{equation}\label{eq:mlwr}
-		MLWR = \sum_{i=1}^{|S|}\frac{\max\{0, N-r_i+1\}}{N\times |S|}, 
-	\end{equation}
-\end{linenomath}
-where $|S|$ represents the total number of samples, $r_i$ denotes the ranking of the true target corresponding to the $i$-th query in the retrieved  results, and $N$ is the window size.
-
-\subsection{Comparison Results}
-In this section, we compare the performance of pretrained models, single-task fine-tuned models, and multitask fine-tuned models on the automotive domain QA retrieval task.
-By thoroughly examining the experimental results, we identify the most effective multitask fine-tuning strategy.
-
-\begin{table}[H] 
-	\caption{Comparison of Hit@K, MRR, MLWR using single-task fine-tuning models based on $\text{BERT}_{base}$.} \label{tab:single}
-	\newcolumntype{C}{>{\centering\arraybackslash}X}
-	\begin{tabularx}{\textwidth}{p{1.5cm}CCCCCCCCCC}
-		\toprule
-		\multirow{2}{*}{\textbf{Model}} & \multicolumn{2}{c}{Hit@1(\%)} & \multicolumn{2}{c}{Hit@3(\%)} & \multicolumn{2}{c}{Hit@5(\%)} & \multicolumn{2}{c}{MRR(\%)} & \multicolumn{2}{c}{MLWR(\%)} \\
-		\cline{2-11} 
-		\addlinespace
-		& CLS           & MEAN          & CLS           & MEAN          & CLS           & MEAN          & CLS          & MEAN         & CLS           & MEAN         \\
-		\midrule
-		$\text{BERT}_{base}$   & 30.00         & 64.50         & 39.50         & 72.25         & 43.25         & 77.25         & 36.57        & 70.21        & 47.37         & 79.97   \\ 
-%		BERT   & 30.00         & 64.50         & 39.50         & 72.25         & 43.25         & 77.25         & 36.57        & 70.21        & 47.37         & 79.97        \\
-		FT-MLM & 47.25         & 77.00         & 55.50         & 83.50         & 57.00         & 85.75         & 52.19        & 80.94        & 58.96         & 86.76        \\
-		FT-STS & 13.00         & 60.25         & 18.50         & 71.25         & 22.25         & 74.75         & 17.73        & 66.58        & 26.21         & 76.19        \\
-		FT-TE  & 5.00          & 24.75         & 8.50          & 30.25         & 9.00          & 32.75         & 7.27         & 28.89        & 10.73         & 35.41        \\
-		FT-NSP & 14.75         & 59.00         & 14.75         & 67.75         & 20.75         & 71.00         & 18.53        & 64.53        & 24.56         & 73.29  \\ 
-%		$\text{BERT}_{large}$   & 26.50         & 64.50         & 39.50         & 72.25         & 43.25         & 77.25         & 36.57        & 70.21        & 47.37         & 79.97   \\ 
+			TASE   & 60.28         & 55.59         & 65.83         & 78.16         & 78.27         & 78.06         \\ 
+			LIQUID & 61.44         & 58.39         & 64.84         & 78.56         & 78.65         & 78.46         \\
+			$\text{AUG}_{c}$ & 63.05         & 58.51         & 68.34         & 79.42         & 78.70         & 80.14         \\
+			$\text{AUG}_{eree}$  & 63.93          & 60.22         & 68.13          & 77.50         & 77.07          & 77.94         \\
+			$\text{AUG}_{ereec}$ & 62.90          & 61.02        & 64.89          & 76.72         & 78.56          & 74.97         \\
+			Bagging & 64.44          & 61.63        & 67.50          & 79.52         & 80.49          & 78.57         \\
 			\bottomrule
@@
 	\begin{table}[H] 
-	\caption{Comparison of Hit@K, MRR, MLWR using multitask fine-tuning models based on $\text{BERT}_{base}$.} \label{tab:multi}
+		\caption{Approach performance on complete MultiSpanQA valid set based on $\text{RoBERTa}_{base}$.} 
+		\label{tab:robertaall}
 		\newcolumntype{C}{>{\centering\arraybackslash}X}
-	\begin{tabularx}{\textwidth}{p{3.0cm}CCCCCC}
+		\begin{tabularx}{\textwidth}{p{1.5cm}CCCCCCC}
 			\toprule
-	\multicolumn{1}{c}{Model}                & Hit@1(\%) & Hit@3(\%) & Hit@5(\%) & MRR(\%) & MLWR(\%) \\
+			\multirow{2}{*}{\textbf{Model}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match}  \\
+			\cline{2-7} 
+			\addlinespace
+			& F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
 			\midrule
-	STS+MLM {[}CLS{]}  & 74.25     & 84.00     & 85.25     & 79.54   & 87.12    \\
-	NSP+MLM {[}CLS{]}  & 8.25      & 15.00     & 18.75     & 13.08   & 21.65    \\
-	STS+MLM {[}MEAN{]} & 77.50     & 84.75     & 87.00     & 81.60   & 87.71    \\
-	NSP+MLM {[}MEAN{]} & 73.25     & 78.75     & 80.50     & 76.77   & 82.17   \\
+			TASE & 68.00 & 65.06 & 71.22 & 83.13 & 83.05 & 83.22 \\ 
+			LIQUID & 68.33 & 66.68 & 70.07 & 82.71 & 82.45 & 82.98 \\
+			$\text{AUG}_{c}$ & 70.35 & 67.35 & 73.63 & 84.06 & 83.38 & 84.76 \\
+			$\text{AUG}_{eree}$ & 69.15 & 67.81 & 70.54 & 82.85 & 83.90 & 81.83 \\
+			$\text{AUG}_{ereec}$ & 70.44 & 67.813 & 73.26 & 82.80 & 82.45 & 83.15 \\
+			Bagging & 70.86 & 69.03 & 72.79 & 84.82 & 85.53 & 84.12 \\
 			\bottomrule
@@
 
-\begin{table}[H] 
-	\caption{Comparison of Hit@K, MRR, MLWR using the best single-task and multitask fine-tuning models based on $\text{BERT}_{large}$ and $\text{RoBERTa}$.} \label{tab:sup}
+\subsubsection{\textit{Discussion}}
+
+	\begin{table}[ht]
+		\caption{Model performance on complete MultiSpanQA valid Subset with different answer types based on $\text{BERT}_{base}$.}
+		\label{tab:bertsub}
 		\newcolumntype{C}{>{\centering\arraybackslash}X}
-	\begin{tabularx}{\textwidth}{p{1.5cm}CCCCCCCCCC}
+		\begin{tabularx}{\textwidth}{Cp{1.5cm}CCCCCCC}
 			\toprule
-		\multirow{2}{*}{\textbf{Model}} & \multicolumn{2}{c}{Hit@1(\%)} & \multicolumn{2}{c}{Hit@3(\%)} & \multicolumn{2}{c}{Hit@5(\%)} & \multicolumn{2}{c}{MRR(\%)} & \multicolumn{2}{c}{MLWR(\%)} \\
-		\cline{2-11} 
-		\addlinespace
-		& CLS           & MEAN          & CLS           & MEAN          & CLS           & MEAN          & CLS          & MEAN         & CLS           & MEAN         \\
-		\toprule
-		$\text{BERT}_{large}$   & 26.50         & 64.50         & 39.50         & 72.25         & 43.25         & 77.25         & 36.57        & 70.21        & 47.37         & 79.97   \\ 
-		FT-MLM & 29.25         & 76.75         & 36.50         & 82.00         & 39.50         & 85.25        & 33.88        & 80.42        & 41.56        & 86.19        \\
-		MLM+STS & 18.50        & 78.00        & 22.20         & 83.50        & 23.50         & 85.75         & 21.13       & 81.67     & 25.16       & 88.42      \\ \toprule[0.2mm]
-		$\text{RoBERTa}$   & 69.00         & 73.00         & 77.75      & 79.50        & 79.25        & 82.75        & 74.16        & 77.41       & 81.59         & 84.61   \\ 
-		FT-MLM & 73.25        & 75.75        & 79.25        & 81.75        & 83.25         & 84.00         &  77.63        & 79.79        & 85.31         & 86.81        \\
-		MLM+STS & 37.50         & 78.75        & 48.25         & 84.50       & 51.75        & 87.75         & 44.46     & 82.50       & 55.16         & 88.79       \\
-		\bottomrule[0.2mm]
+			\multirow{2}{*}{\textbf{Type}} & \multirow{2}{*}{\textbf{Model}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match} \\
+			\cmidrule{3-8} 
+			& & F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
+			\midrule
+			\multirow{6}{*}{DESC} & TASE & 32.76 & 27.33 & 40.87 & 64.46 & 68.61 & 60.79 \\ 
+			& LIQUID & 36.69 & 31.10 & 44.71 & 66.05 & 65.95 & 66.15 \\
+			& $\text{AUG}_{c}$ & 38.74 & 32.89 & 47.12 & 68.31 & 70.32 & 66.42 \\
+			& $\text{AUG}_{eree}$ & 44.69 & 40.71 & 49.52 & 63.12 & 67.16 & 59.53 \\
+			& $\text{AUG}_{ereec}$ & 40.63 & 38.30 & 43.27 & 64.25 & 71.15 & 58.57 \\
+			& Bagging & 39.91 & 36.69 & 43.75 & 66.70 & 73.68 & 60.93 \\
+			\midrule
+			\multirow{6}{*}{NUM} & TASE & 33.33 & 30.23 & 37.14 & 60.98 & 71.99 & 52.89 \\ 
+			& LIQUID & 34.33 & 31.25 & 38.10 & 60.68 & 68.15 & 54.69 \\
+			& $\text{AUG}_{c}$ & 35.96 & 33.33 & 39.05 & 64.47 & 71.56 & 58.65 \\
+			& $\text{AUG}_{eree}$ & 36.20 & 34.48 & 38.10 & 59.02 & 65.63 & 53.62 \\
+			& $\text{AUG}_{ereec}$ & 36.71 & 37.25 & 36.19 & 57.09 & 69.04 & 48.67 \\
+			& Bagging & 35.94 & 34.82 & 37.14 & 60.73 & 71.15 & 52.97 \\
+			\midrule
+			\multirow{6}{*}{ENTYS} & TASE & 66.30 & 62.21 & 70.96 & 81.16 & 80.37 & 81.96 \\ 
+			& LIQUID & 67.17 & 65.25 & 69.21 & 81.66 & 81.69 & 81.63 \\
+			& $\text{AUG}_{c}$ & 68.47 & 64.44 & 73.03 & 81.93 & 80.57 & 83.34 \\
+			& $\text{AUG}_{eree}$ & 68.36 & 64.64 & 72.53 & 80.55 & 79.21 & 81.93 \\
+			& $\text{AUG}_{ereec}$ & 67.54 & 65.60 & 69.59 & 79.49 & 80.16 & 78.83 \\
+			& Bagging & 69.65 & 66.94 & 72.59 & 82.31 & 82.07 & 82.55 \\
+			\bottomrule
 		\end{tabularx}
-	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
 	\end{table}
 
-To illustrate the generalization capability of our framework in mitigating bias within pretrained models, we extend our evaluation beyond the BERT-base model to also include the BERT-large and RoBERTa models.
-As shown in \tableref{tab:sup}, our framework exhibits effective generalization   across a variety of pretrained models.
-It is worth nothing that RoBERTa, which is solely pretrained using the MLM task, demonstrates good performance with the CLS encoding, achieving a Hit@1 score of 69\%.
-However, in pretraining models such as BERT-base and BERT-large, the CLS representation primarily learns from the NSP task, resulting in sub-optimal performance when directly utilizing the  CLS encoding.
-These findings highlight the negative impact of the NSP task as a training objective on QA tasks, while emphasizing the benefits of the MLM task as a training objective for downstream QA tasks.
-
-%Furthermore, in order to showcase the effectiveness of the retriever module in our proposed system, we compare its performance using different indexing structures as described in Section 3.2.
-Specifically, we evaluate the retriever module using brute force, IndexPQ index, IndexHNSWFlat, and IndexFlatL2.
-%As shown in 
-\subsection{Case Study}
-In this section,  we conduct a case study to qualitatively analyze competing models. 
-\tableref{tab:case} presents the results obtained when inputting an example user query, 
-namely ``如何对高尔夫7系列车型进行自我检修？'' ({\color{blue} How to perform self-maintenance on Volkswagen Golf7 series?}), and showcases the responses retrieved by the competing models utilizing $\text{BERT}_{base}$ in proposed framework.
-The baseline BERT model provides a historical overview of the 7th Generation Volkswagen Golf, while the single-task FT-MLM model compares the 308S and Golf 7 models.
-However, neither of these models is capable of providing an accurate answer to the query.
-In contrast, the STS+MLM joint fine-tuning model effectively responds with the precise and specific steps to perform maintenance on the FAW-Volkswagen Golf7, thereby correctly addressing the query.
-The STS+MLM joint model demonstrates its effectiveness in capturing the query intentions, surpassing other competing models in terms of qualitative performance.
-
-\begin{table}[H] 
-	\caption{Retrieved answers from baseline $\text{BERT}_{base}$ model, single-task FT-MLM model, and multitask STS+MLM model.} \label{tab:case}
+	\begin{table}[ht]
+		\caption{Model performance on complete MultiSpanQA valid Subset with different answer types based on $\text{RoBERTa}_{base}$.}
+		\label{tab:robertasub}
 		\newcolumntype{C}{>{\centering\arraybackslash}X}
-	\begin{tabularx}{\textwidth}{cp{10cm}}
+		\begin{tabularx}{\textwidth}{Cp{1.5cm}CCCCCCC}
 			\toprule
-		\multicolumn{2}{p{12cm}}{\hangindent=2.2cm \hangafter=1 \textbf{Input Query}: ``如何对高尔夫7系列车型进行自我检修？'' ({\color{blue} How to perform self-maintenance on Volkswagen Golf7 series?})}   \\
+			\multirow{2}{*}{\textbf{Type}} & \multirow{2}{*}{\textbf{Model}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match} \\
+			\cmidrule{3-8} 
+			& & F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
 			\midrule
-		\textbf{Model} & \textbf{Retrieved answers} \\ \midrule
-		$\text{BERT}_{base}$  &  1.
-高尔夫Mk1：1974年5月，第一代高尔夫...
-2.
-高尔夫Mk2:1983年8月，大众推出第二代...
-({\color{blue} 1.
-Golf Mk1: In May 1974, the first generation Golf was introduced..
-2.
-Golf Mk2: In August 1983, Volkswagen unveiled the second generation...})  \\\midrule
-		FT-MTM  &       1. 动力组合对比：高尔夫一共有三种排量...	 2. 质保政策对比：高尔夫官方保修周期为3年或者...
-		  ({\color{blue} 1.
-Powertrain Comparison: The Golf is available in three different engine displacements...
-2.
-Warranty Policy Comparison: The official warranty period for the Golf is 3 years or...})   \\ \midrule
-		MLM+STS  &   1. 更换4.5升5w40美孚全合成机油、博世机滤、博世空气滤芯、博世空调滤芯、博世汽油滤芯、3m燃油添加剂、免拆三元催化清洗剂
-2. 动平衡、更换原厂轮毂盖
-		 ({\color{blue} 1.
-Replace 4.5 liters of 5w40 Mobil fully synthetic engine oil, Bosch oil filter, Bosch air filter, Bosch cabin air filter, Bosch fuel filter, 3M fuel additive, and non-dismantle catalytic converter cleaner.
-2.
-Dynamic balancing and replace original wheel hub covers.
-}) \\
+			\multirow{6}{*}{DESC} & TASE & 45.53 & 40.84 & 51.44 & 75.44 & 76.61 & 74.31 \\ 
+			& LIQUID & 48.68 & 44.76 & 53.37 & 73.27 & 71.57 & 75.04 \\
+			& $\text{AUG}_{c}$ & 49.02 & 44.66 & 54.33 & 76.33 & 77.85 & 74.86 \\
+			& $\text{AUG}_{eree}$ & 50.99 & 46.96 & 55.77 & 76.87 & 78.07 & 75.71 \\
+			& $\text{AUG}_{ereec}$ & 49.24 & 44.71 & 54.81 & 71.87 & 73.03 & 70.74 \\
+			& Bagging & 47.70 & 43.78 & 52.40 & 77.43 & 80.63 & 74.47 \\
+			\midrule
+			\multirow{6}{*}{NUM} & TASE & 46.23 & 45.79 & 46.67 & 71.89 & 78.42 & 66.36 \\ 
+			& LIQUID & 40.19 & 39.45 & 40.95 & 67.56 & 72.28 & 63.42 \\
+			& $\text{AUG}_{c}$ & 50.69 & 49.11 & 52.38 & 72.86 & 80.22 & 66.74 \\
+			& $\text{AUG}_{eree}$ & 42.40 & 41.07 & 43.81 & 66.67 & 73.51 & 61.00 \\
+			& $\text{AUG}_{ereec}$ & 45.58 & 44.55 & 46.67 & 65.86 & 73.19 & 59.87 \\
+			& Bagging & 44.65 & 43.64 & 45.71 & 70.11 & 78.49 & 63.35 \\
+			\midrule
+			\multirow{6}{*}{ENTYS} & TASE & 72.57 & 69.94 & 75.41 & 84.90 & 84.32 & 85.48 \\ 
+			& LIQUID & 72.95 & 71.77 & 74.16 & 85.02 & 84.75 & 85.29 \\
+			& $\text{AUG}_{c}$ & 74.59 & 71.87 & 77.53 & 85.79 & 84.40 & 87.23 \\
+			& $\text{AUG}_{eree}$ & 73.50 & 72.81 & 74.22 & 84.74 & 85.49 & 83.99 \\
+			& $\text{AUG}_{ereec}$ & 75.04 & 72.81 & 77.41 & 85.37 & 84.46 & 86.29 \\
+			& Bagging & 75.85 & 74.52 & 77.22 & 86.73 & 86.73 & 86.74 \\
 			\bottomrule
 		\end{tabularx}
-	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
 	\end{table}
@@
 \section{Conclusion}
-In this paper, we first focus on constructing QA corpora, document sets, and multitask fine-tuning datasets specifically tailored to the automotive domain.
-Then, we propose a pretraining-multitask fine-tuning learning framework to develop an encoder model that incorporates domain knowledge, enhancing the semantic representation of texts and enabling effective retrieval QA applications.
-The experimental results reveal that within the multitask fine-tuning framework (based on $\text{BERT}_{base}$), the joint fine-tuned model MLM+STS achieves the highest performance.
-It attains Hit@1 and Hit@3 accuracies of 77.5\% and 84.75\%, respectively, along with an MLWR of 87.71\%.
-These outcomes signify substantial improvements of 12.5, 12.5, and 28.16 percentage points, respectively, compared to the baseline BERT model.
-Additionally, when compared to the best-performing single-task fine-tuned model, FT-MLM, the observed enhancements amount to 0.5, 1.25, and 0.95 percentage points, respectively.
 
@@
 \PublishersNote{}
+
 \end{adjustwidth}

### 2023-08-28 paper.tex
Add files via upload

@@
 \begin{itemize}
-	\item We construct Chinese question and answer corpora, document corpora, and multi-task annotated corpora specifically tailored to the automotive domain.
-	\item We propose a joint learning framework with a pretraining-multitask fine-tuning architecture to incorporate domain knowledge and conduct a comparative analysis of the contributions of various auxiliary task objectives to model performance.
-	\item We create an evaluation dataset based on ChatGPT using a semi-automated approach, along with the introduction of the MLWR metric for evaluation.
+	\item We employs a automatic data augmentation framework using Large Language Model \((LLM)\) as a knowledge source and a extra content supplement to linearize relevant information and possible continuation from LLM as texts, then inject them into original contexts.
+
+	\item We develop a series of prompt templates designed for interacting with ChatGPT to acquire comprehensive explanations of numerous entities.
+These templates ensure that the formats of the responses provided by ChatGPT are highly parseable and well-structured."
 \end{itemize}
@@
 	\includegraphics[width=14.0cm]{overview}
-	\caption{An overview of our retrieval-based QA system.
-\textbf{(a) Step 1}: Automotive Corpus Construction.
-\textbf{(b) Step 2}: The encoder module under a pretraining-multitask fine-tuning framework.
-\textbf{(c) Step 3}: The retriever module based on Faiss library.}
+	\caption{An overview of our automatic information augmentation framework.
+\textbf{(a) Step 1}: Interact with ChatGPT to Get Auxiliary Information.
+\textbf{(b) Step 2}: Distilling the Information and Injecting Them into Context \textbf{(c) Step 3}: Input the Augmented Context into Tagging Model}
 	\label{fig:overview}
@@
 	\end{table}
+	Table~\ref{tab:bertall} and Table~\ref{tab:robertaall} illustrate the performance comparison between the proposed approaches, $\text{AUG}_{c}$ and $\text{AUG}_{eree}$, and several strong baselines, including the previous state-of-the-art model LIQUID.
+These comparisons are conducted using both the $\text{BERT}_{base}$ and $\text{RoBERTa}_{base}$ encoders, and regard multi-span question answering as a \textit{BIO} sequence tagging task to predict each token whether it is a part or begin of an answer.
+	Notably,$\text{AUG}_{c}$ exhibit superior performance across the evaluate dataset on all metrics.
+However, on Partial Match scores, $\text{AUG}_{eree}$ demonstrates slightly lower performance compared to TASE, and especially lower than LIQUID when employing the $\text{BERT}_{base}$ encoder.
+	Importantly, the performance of $\text{AUG}_{c}$ consistently outperforms LIQUID and TASE on all metrics and encoders, irrespective of the encoder setting.
+	These results demonstrate the effectiveness of our proposed framework, as well as the efficacy of the information augmentation strategy.
+
+	To be more specific,
 

### 2023-08-29 paper.tex
Add files via upload

@@
 
-	To be more specific,
+	To be more specific, Table~\ref{tab:bertall} shows comparisons of metrics among all competing models backed by $\text{BERT}_{base}$.
+We can see that our proposed framework, $\text{AUG}$, consistently outperforms all other baselines across multispanQA dataset.
+Baked by $\text{BERT}_{base}$, $\text{AUG}_{c}$ achieves EM and Overlap F1 scores of 63.05 and 79.42, respectively.
+Moreover, when equipped with entities' information, $\text{AUG}_{eree}$  achieves even higher EM F1 scores of 63.93 but relatively lower Overlap F1 of 77.50 on the same datasets and encoder.
+	These results showcase substantial improvements over the previous state-of-the-art model, LIQUID, with EM F1 score enhancements ranging from 1.61 to 2.49 percents across validation datasets.
+Additionally, when utilizing $\text{RoBERTa}_{base}$ instead of $\text{BERT}_{base}$, $\text{AUG}_{c}$ achieves EM and Overlap F1 scores of 70.35 and 69.15 respectively on the same datasets.These scores represent EM and Overlap F1 improvements of 2.02 and 0.93 compared to the previous setup.
+Totally the results, shown in Table~\ref{tab:robertaall} demonstrate similar trends to $\text{BERT}_{base}$.
 

### 2023-09-02 paper.tex
Add files via upload

--- 2023-08-28 paper.tex
@@
 
-	To be more specific,
+	To be more specific, Table~\ref{tab:bertall} shows comparisons of metrics among all competing models 100 backed by $\text{BERT}_{base}$.
+We can see that our proposed framework, AUG, consistently outperforms all other baselines across multispanQA dataset.
+Backed by $\text{BERT}_{base}$, $\text{AUG}_{c}$ achieves EM and Overlap F1 scores of 63.05 and 79.42, respectively.
+Moreover, when equipped with entities’ information,  $\text{AUG}_{eree}$ achieves even higher EM F1 scores of 63.93 but relatively lower Overlap F1 of 77.50 than baselines on the same encoder.
+These results showcase substantial improvements over the previous state-of-the-art model, LIQUID, with EM F1 score enhancements ranging from 1.61 to 2.49 percents across validation datasets.
+
+	Additionally, when utilizing $\text{RoBERTa}_{base}$ instead of $\text{BERT}_{base}$, $\text{AUG}_{c}$ achieves EM and Overlap F1 scores of 70.35 and 84.06 respectively on the same datasets.
+These scores represent EM and Overlap F1 improvements of 2.02 and 0.93 compared to the previous setup.
+For  $\text{AUG}_{eree}$, the EM F1 score represents an enhancement of 0.82, with the EM and Overlap F1 values of 69.16 and 82.85 respectively.
+Notably, the partial metrics also indicate lower values compared to TASE and LIQUID, in line with the result supported by $\text{BERT}_{base}$.
+This is because augmenting the model with entity information, including definition and relationship knowledge, strengthens its ability to capture and understand entity concepts, which leads the model to prefer complete entity spans as answers rather than partial entity span, and therefore a  decrease in the partial recall and ultimately a lower partial F1 scores and a higher EM F1.
+
+	Totally, the result, displayed in Table~\ref{tab:robertaall} demonstrates the same trends to Table~\ref{tab:bertall}.
+And the outcome highlights robustness in effectively generalizing across different datasets without requiring hyperparameter re-tuning.
 

### 2023-09-09 paper.tex
Add files via upload

@@
 \usepackage{xeCJK}
-\setCJKmainfont{STKaiti}
 
@@
 \end{figure}   
-\unskip
+%\unskip
 
@@
 \tableref{tab:base_corpus} provides an illustrative example of the dataset.
-
-\begin{table}[H] 
-	\caption{The constructed Chinese QA corpus in automotive domain.} \label{tab:base_corpus}
-	\newcolumntype{C}{>{\centering\arraybackslash}X}
-	\begin{tabularx}{\textwidth}{C}
-		\toprule
-		\textbf{An Example of QA pairs}	\\
-		\midrule
-		\{ ``id'': 0,~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \\
-		``question'': ``WEY是什么品牌的车?'',~~~~~~~~~~~~~~~~~~~~~~ \\
-		~~~~~~~~~~ ({\color{blue} Which automobile brand is WEY?}) \\ 
-		``answer'': ``WEY是长城汽车旗下的高端品牌…'', ~~~~~~~\\
-		 ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~({\color{blue} WEY is a high-end brand under Great Wall Motors…}) \\
-		\}~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\\
-%		\midrule
-%		Entry 1		\\
-%		Entry 2	Dat \textsuperscript{1}\\
-		\bottomrule
-	\end{tabularx}
-%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
-\end{table}
-
-\begin{table}[H] 
-	\caption{The constructed Chinese QA corpus in automotive domain.} \label{tab:annotated_corpus}
-	\newcolumntype{C}{>{\centering\arraybackslash}X}
-	\begin{tabularx}{\textwidth}{p{2cm}L} 
-		\toprule
-		\textbf{Name}  & \textbf{Data Format}	\\
-		\midrule
-		MLM Corpus  & \textbf{[MASK][MASK]}车队首次在1994年的JGTC第四站比\textbf{[MASK]}中亮相，获得了资格赛第二名的位置。{\color{blue} (The [MASK] team made its debut in the fourth round of the JGTC  in 1994, securing the second position in the qualifying [MASK].) } \\
-		\midrule
-		NSP Corpus  & \textbf{Sentence1}: 上世纪90年代，TRD为丰田TOM'S车队打造了Supra赛车。{\color{blue} (In the 1990s, TRD built Supra race cars for the Toyota TOM'S team.) }
-		\textbf{Sentence2}: 丰田车队首次在1994年的JGTC第四站比赛中亮相，获得了资格赛第二名的位置。{\color{blue} (The Toyota team made its debut in the fourth round of the JGTC  in 1994, securing the second position in the qualifying race.)} ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\textbf{Label}: continuous (1)\\
-		\midrule
-		STS Corpus & \textbf{Sentence1}: 丰田车队首次在1994年的JGTC第四站比赛中亮相，获得了资格赛第二名的位置。{\color{blue} (The Toyota team made its debut in the fourth round of the JGTC  in 1994, securing the second position in the qualifying race.)}
-		\textbf{Sentence2}: 在1994年的JGTC第四站比赛中，丰田车队首次参赛，并在资格赛中获得了第二名的成绩。{\color{blue} (In 1994, during the fourth round of the JGTC, the Toyota team made its debut and secured a second-place finish in the qualifying race.)} ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \textbf{Label}: similar (1) ~~~~~~~~		\\
-		\midrule
-		TE Corpus  &  \textbf{Sentence1}: 一个年轻的黑人正试图向另外两个人解释一些事情。{\color{blue} (A young black person is trying to explain something to two other individuals.)}
-		\textbf{Sentence2}: 一位年轻的黑人男子正在和另外两位说话。{\color{blue} (A young black man is talking to two other people.)} ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ \textbf{Label}: entailment (0) ~~~~~		\\
-		\bottomrule
-	\end{tabularx}
-	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
-\end{table}
 
@@
 \subsection{Experimental Results and Analysis}
-	In this section, we compare $\text{AUG}$ with all competing models described above \textcolor{red}{both quantitatively and qualitatively}.
+	In this section, we compare $\text{AUG}$ with all competing models described above quantitatively.
 
@@
 			$\text{AUG}_{eree}$ & 69.15 & 67.81 & 70.54 & 82.85 & 83.90 & 81.83 \\
-			$\text{AUG}_{ereec}$ & 70.44 & 67.813 & 73.26 & 82.80 & 82.45 & 83.15 \\
+			$\text{AUG}_{ereec}$ & 70.44 & 67.83 & 73.26 & 82.80 & 82.45 & 83.15 \\
 			Bagging & 70.86 & 69.03 & 72.79 & 84.82 & 85.53 & 84.12 \\
@@
 \subsubsection{\textit{Discussion}}
+	Besides, Table~\ref{tab:bertall} and Table~\ref{tab:robertaall} also discuss the performance of different augmentation integrated strategies, including the results-bagging methods whose outputs are voting results of $\text{AUG}_{c}$, $\text{AUG}_{eree}$ as well as LIQUID, and the input-fusion model $\text{AUG}_{ceree}$ who injects all kinds of information above into input contexts.
+
+	In detail, with EM f1 scores of 62.90 and 64.44 in Table~\ref{tab:bertall} and 70.44 and 70.86 in Table~\ref{tab:robertaall}, both the $\text{AUG}_{ceree}$ and Bagging methods consistently surpass TASE and LIQUID, which exhibits robust effectiveness of information injection strategies.
+However, there is a little decrease caused by fusing all auxiliary information when contrast with single information augmentation strategies and the bagging method.
+This may be due to the likelihood that incorporating all of the augmentation information into the model inputs will confuse the model by introducing excessive auxiliary knowledge and underrepresented original context proportion.
+Therefore it may be more useful that adding limit information into context, and using result-bagging method, a multi-model voting to bringing all information into model with an indirect way.
+
+	From the Partial Match perspective, $\text{AUG}_{ceree}$ and the Bagging method achieve 76.72 and 79.52 in Table~\ref{tab:bertall}, and 82.80 and 84.82 in Table~\ref{tab:robertaall}.
+In accordance with Exact Match metrics, Bagging demonstrate a overall superior performance.
+Meanwhile overlap f1 score of $\text{AUG}_{eree}$ is inferior to TASE but superior to LIQUID ,with relatively higher precision and relativelv higher recall, which  is comparable to all single augmented models such as $\text{AUG}_{eree}$.
+And its weak performance on overlap f1 also reveals complete entities preference of this information injection approach.
+
+	In addition, we	categorized the data in MultispanQA into DESC, NUM, ENTYS in terms of answer types, and compared the performance of each of the model mentioned above in each breakdown category.
+Specifically,  Table~\ref{tab:bertsub} and Table~\ref{tab:robertasub} present the results backed by  $\text{BERT}_{base}$ and $\text{RoBERTa}_{base}$, respectively.
+As shown in Tables~\ref{tab:bertsub},Table~\ref{tab:robertasub}, our proposed models display superior performance in DESC and ENTYS categories answer extraction, which to some extent indicates the enhancement of models' knowledge at entity and description levels.
 
@@
 		\end{tabularx}
+	\end{table}
+
+\subsubsection{\textit{Ablation Experiment}}
+
+\begin{table}[H] 
+	\caption{$\text{AUG}_{c}$'s performance with different information injection proportion on complete MultiSpanQA valid set based on $\text{BERT}_{base}$.} 
+	\label{tab:different_ratio}
+	\newcolumntype{C}{>{\centering\arraybackslash}X}
+	\begin{tabularx}{\textwidth}{p{1.7cm}CCCCCCC}
+		\toprule
+		\multirow{2}{*}{\textbf{Proportion}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match}  \\
+		\cline{2-7} 
+		\addlinespace
+		& F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
+		\midrule
+		0.90 & 56.60 & 54.27 & 59.13 & 71.79 & 73.90 & 71.79 \\ 
+		0.70 & 56.36 & 63.11 & 63.11 & 75.87 & 77.25 & 74.54 \\
+		0.50 & 57.92 & 52.82 & 64.10 & 76.82 & 76.78 & 76.86 \\
+		0.40 & 58.48 & 53.99 & 63.79 & 77.35 & 77.58 & 77.13 \\
+		0.10 & 53.18 & 64.48 & 77.02 & 77.02 & 77.02 & 77.02 \\
+		\bottomrule
+	\end{tabularx}      
+	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
 \end{table}

### 2023-09-30 paper.tex
Add files via upload

@@
 \label{sec:corpus_construction}
-We construct a QA dataset specific to the automotive domain by gathering question-answer pairs from authoritative resources, including professional databases, websites and other relevant resources.
-This dataset comprises a total of 7,157 question-answer pairs, with each pair consisting of a question and its corresponding answer.
-\tableref{tab:base_corpus} provides an illustrative example of the dataset.
 
@@
 \subsubsection{\textit{Ablation Experiment}}
+	At the end of this section, we conducted ablations on our approach to confirm the effectiveness of selecting the information injection proportion.
+For each QA data, we randomly split the original context and the auxiliary text, then concatenated them into a final augmented context with a specific proportion to ensure that the new input length meets $\textit{max\_len}$, which has a crucial impact on our approach.
+In practice, we determined the final text splicing ratio by calculating the ratio of the average length of the source text to the added information, which for the $\text{AUG}_{c}$ is 0.86.
+
+	Specifically, Table~\ref{tab:different_ratio_bert} and Table~\ref{tab:different_ratio_roberta} displays $\text{AUG}_{c}$'s performance with differential proportion to concatenate original contexts and continuation, on complete MultispanQA valid set,backed by $\text{BERT}_{base}$ and $\text{RoBERTa}_{base}$ respectively.
+We choose five proportions for information integration, which determine how much auxiliary information would be inject into each overflowed text segment.
+The results presented in tables indicate that using the ratio of their average lengths as the proportion of the overflow text composed of original text and auxiliary information is an effective approach.
+In detail, $\text{AUG}_{c}$,equipping with $\text{BERT}_{base}$, achieves an Exact Match F1 scores improvements of at least 4.57 compared to other proportions and an overlap F1 scores improvements of at least 2.07.
+In line with Table~\ref{tab:different_ratio_bert}, when $\text{AUG}_{c}$ equips with $\text{Roberta}_{base}$, it achieves an improvement of Exact Match F1 scores of 0.55 but an decrease of Overlap F1 scores of 0.17.
 
 \begin{table}[H] 
-	\caption{$\text{AUG}_{c}$'s performance with different information injection proportion on complete MultiSpanQA valid set based on $\text{BERT}_{base}$.} 
-	\label{tab:different_ratio}
+	\caption{Ablations of $\text{AUG}_{c}$ on different proportion for information concatenation, based on $\text{BERT}_{base}$.} 
+	\label{tab:different_ratio_bert}
 	\newcolumntype{C}{>{\centering\arraybackslash}X}
@@
 		\midrule
-		0.90 & 56.60 & 54.27 & 59.13 & 71.79 & 73.90 & 71.79 \\ 
-		0.70 & 56.36 & 63.11 & 63.11 & 75.87 & 77.25 & 74.54 \\
-		0.50 & 57.92 & 52.82 & 64.10 & 76.82 & 76.78 & 76.86 \\
-		0.40 & 58.48 & 53.99 & 63.79 & 77.35 & 77.58 & 77.13 \\
-		0.10 & 53.18 & 64.48 & 77.02 & 77.02 & 77.02 & 77.02 \\
+		0.90 & 58.55 & 57.69 & 59.44 & 71.88 & 74.30 & 69.61 \\ 
+		0.70 & 61.70 & 59.03 & 64.63 & 76.58 & 77.84 & 75.36 \\
+		0.50 & 61.22 & 57.37 & 65.62 & 77.38 & 77.61 & 77.16 \\
+		0.40 & 61.36 & 56.50 & 67.13 & 78.26 & 77.57 & 78.96 \\
+		0.10 & 61.41 & 56.36 & 67.45 & 78.94 & 78.45 & 79.44 \\
+		0.14 & 63.05 & 58.51 & 68.34 & 79.42 & 78.70 & 80.14 \\
+		\bottomrule
+	\end{tabularx}      
+	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
+\end{table}
+
+\begin{table}[H] 
+	\caption{Ablations of $\text{AUG}_{c}$ on different proportion for information concatenation, based on $\text{BERT}_{base}$.} 
+	\label{tab:different_ratio_roberta}
+	\newcolumntype{C}{>{\centering\arraybackslash}X}
+	\begin{tabularx}{\textwidth}{p{1.7cm}CCCCCCC}
+		\toprule
+		\multirow{2}{*}{\textbf{Proportion}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match}  \\
+		\cline{2-7} 
+		\addlinespace
+		& F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
+		\midrule
+		0.90 & 58.13 & 56.92 & 59.39 & 71.70 & 73.49 & 69.98 \\ 
+		0.70 & 66.97 & 65.42 & 68.60 & 80.05 & 80.80 & 79.32 \\
+		0.50 & 68.94 & 67.23 & 70.75 & 82.43 & 83.23 & 81.64 \\
+		0.40 & 68.95 & 66.11 & 71.06 & 83.71 & 83.71 & 81.71 \\
+		0.10 & 69.80 & 66.47 & 73.47 & 84.23 & 83.49 & 84.99 \\
+		0.86 & 70.35 & 67.35 & 73.63 & 84.06 & 83.38 & 84.76 \\
 		\bottomrule

### 2023-09-30 paper.tex
Add files via upload

@@
 	\item We develop a series of prompt templates designed for interacting with ChatGPT to acquire comprehensive explanations of numerous entities.
-These templates ensure that the formats of the responses provided by ChatGPT are highly parseable and well-structured."
+These templates ensure that the formats of the responses provided by ChatGPT are highly parseable and well-structured.
+
+	\item We propose a new calculation method for the overlap F1 score in multi-span QA task.
+This method can alleviate the issue of lower scores in situations where the model decomposes the answer into multiple complete spans, but the answer’s spans are still entirely correct.
+This approach provides a more accurate reflection of the model’s performance in handling complex multi-span answers.
 \end{itemize}
@@
 \end{figure}
+
 %\unskip
+	Existing extractive multi-span question answering models exhibit subpar performance in handling ambiguous words, complex proper nouns (such as film and song titles), numerical values, and long descriptive answers.
+The main reasons for these shortcomings can be categorized into three aspects:
+	\begin{enumerate}
+		\item Ambiguous Words: The real world is replete with words that have a single form but multiple meanings, which heavily depend on the context.
+For instance, the word "Cameron" could refer to a famous director or a former British Prime Minister, depending on the context.
+The specific meanings of such words often appear infrequently in training corpora, making them difficult to learn.
+		\item Numerical Values: In contrast to ambiguous words, numerical values have a single meaning but can be represented in various forms.
+For example, "22.5 billion years" can also be expressed as "cosmic years".
+		\item Multi-span Answers: In extractive multi-span question answering tasks, the model needs to grasp the overall relationship of multi-span answers in the context, such as parallelism and progression.
+		These challenges require the model to possess a high level of comprehensive understanding ability and knowledge about language and the world.
+	\end{enumerate}
+
+	Leveraging large language models to parse question-answering data and inject auxiliary knowledge into the model can promote the integration of the model's latent world knowledge and specific domain knowledge in the paragraph, thereby enhancing the model's performance.
+Overall, we use GPT-3.5-turbo to generate entity annotations, entity association analysis, and content continuation for each question-answering paragraph as auxiliary information for the model:
+	\begin{enumerate}
+		\item Context Supplementary: By inserting explanations of entities in the form of annotations after the main entities or concept words in the question and paragraph, this method helps the model capture the actual meaning of ambiguous words in specific contexts.
+It provides direct information prompts for low-frequency meanings or low-frequency words, achieving entity or concept alignment in the question-answering system.
+		\item Context Enrichment: By integrating entity association analysis and content continuation with the original question-answering text to form new paragraphs based on knowledge enhancement, this method captures the inherent associations between words or entity concepts with the same meaning but different forms.
+On one hand, it parses the logical relationships between other entities using entity relationship analysis.
+On the other hand, it extends the original paragraph information using content continuation, introducing more external knowledge while helping the model understand the overall content direction of the paragraph, thereby enhancing the model's comprehension ability.
+	\end{enumerate}
 
@@
 And its weak performance on overlap f1 also reveals complete entities preference of this information injection approach.
-
+	z
 	In addition, we	categorized the data in MultispanQA into DESC, NUM, ENTYS in terms of answer types, and compared the performance of each of the model mentioned above in each breakdown category.
@@
 As shown in Tables~\ref{tab:bertsub},Table~\ref{tab:robertasub}, our proposed models display superior performance in DESC and ENTYS categories answer extraction, which to some extent indicates the enhancement of models' knowledge at entity and description levels.
+
+	\textcolor{red}{please supplements new overlap calculation method in tase-zh}
 

### 2023-09-30 paper.tex
Add files via upload

@@
 	\begin{figure}[H]
-	\includegraphics[width=14.0cm]{overview}
+	\centering
+	\includegraphics[width=14.0cm]{overview.png}
 	\caption{An overview of our automatic information augmentation framework.
@@
 The main reasons for these shortcomings can be categorized into three aspects:
-	\begin{enumerate}
+	\begin{itemize}
 		\item Ambiguous Words: The real world is replete with words that have a single form but multiple meanings, which heavily depend on the context.
@@
 		These challenges require the model to possess a high level of comprehensive understanding ability and knowledge about language and the world.
-	\end{enumerate}
+	\end{itemize}
 
 	Leveraging large language models to parse question-answering data and inject auxiliary knowledge into the model can promote the integration of the model's latent world knowledge and specific domain knowledge in the paragraph, thereby enhancing the model's performance.
-Overall, we use GPT-3.5-turbo to generate entity annotations, entity association analysis, and content continuation for each question-answering paragraph as auxiliary information for the model:
-	\begin{enumerate}
+Thus, we use GPT-3.5-turbo to generate entity annotations, entity association analysis, and content continuation for each question-answering paragraph as auxiliary information for the model:
+	\begin{itemize}
 		\item Context Supplementary: By inserting explanations of entities in the form of annotations after the main entities or concept words in the question and paragraph, this method helps the model capture the actual meaning of ambiguous words in specific contexts.
@@
 On the other hand, it extends the original paragraph information using content continuation, introducing more external knowledge while helping the model understand the overall content direction of the paragraph, thereby enhancing the model's comprehension ability.
-	\end{enumerate}
+	\end{itemize}
 
-\subsection{Corpus Construction}
-\label{sec:corpus_construction}
+	Overall,we design an automated knowledge enhancement method for multi-span question answering tasks, which interacts with large language models based on templates.
+This method is applicable to all question answering models or frameworks.
+It is universally applicable to any other downstream tasks that contain paragraph data, without the need for any complex calculations.
+In the following sections, we will provide a detailed introduction to each specific module of this process.
+
+\subsection{Construction of Prompt Template}
+\label{sec:prompt_construction}
+	\begin{figure}[H]
+		\centering
+		\includegraphics[width=14.5cm]{Prompts_construction.png}
+		\caption{Prompt Templates and it's Construction}
+		\label{fig:prompt_template}
+	\end{figure}
+
+\subsection{Information Injection}
+\label{sec:information_injection}
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=10cm]{EntityInsert.png}
+	\caption{The Process of Inserting Entity Explanation into Context}
+	\label{fig:entity_insertion}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=10cm]{RandomConcat.png}
+	\caption{The Process of Concatenation of Original Context and Auxiliary Information}
+	\label{fig:random_concatenate}
+\end{figure}
+
+\subsection{Information Integration}
+\label{sec:information_integration}
 

### 2023-10-01 manuscript.tex
kbs

%% 
%% Copyright 2019-2021 Elsevier Ltd
%% 
%% This file is part of the 'CAS Bundle'.
%% --------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'CAS Bundle' is
%% given in the file `manifest.txt'.
%% 
%% Template article for cas-sc documentclass for 
%% single column output.

\documentclass[a4paper]{cas-sc}

% If the frontmatter runs over more than one page
% use the longmktitle option.

%\documentclass[a4paper,fleqn,longmktitle]{cas-sc}

%\usepackage[numbers]{natbib}
\usepackage[authoryear]{natbib}
%\usepackage[authoryear,longnamesfirst]{natbib}
\usepackage{dsfont}
\usepackage{array}
\usepackage{float}
\usepackage{placeins}
\usepackage{makecell} % add by shuyun
%\usepackage[utf8]{inputenc}
\usepackage{lineno,hyperref}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[small]{caption}
\usepackage{subcaption}
\usepackage{array}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{diagbox}
\usepackage{mathrsfs}
\usepackage{color}
\usepackage{booktabs}
\usepackage{soul}
\usepackage{mathspec}
\usepackage{xeCJK}
\setCJKmainfont{STKaiti}

%\setCJKmainfont[Mapping=tex-text]{STKaiti}
\usepackage[ruled, linesnumbered, vlined]{algorithm2e}

%\linenumbers

%%%Author macros
\def\tsc#1{\csdef{#1}{\textsc{\lowercase{#1}}\xspace}}
\tsc{WGM}
\tsc{QE}
%%%

% Uncomment and use as if needed
%\newtheorem{theorem}{Theorem}
%\newtheorem{lemma}[theorem]{Lemma}
%\newdefinition{rmk}{Remark}
%\newproof{pf}{Proof}
%\newproof{pot}{Proof of Theorem \ref{thm}}

\newcommand{\1}[1]{\mathds{1}\left[#1\right]}
\renewcommand{\floatpagefraction}{0.8}

\newcommand{\secref}[1]{Section \ref{#1}}
\newcommand{\figref}[1]{Figure \ref{#1}}
\newcommand{\eqnref}[1]{Eq. (\ref{#1})}
\newcommand{\exref}[1]{Example \ref{#1}}
\newcommand{\algoref}[1]{Algorithm \ref{#1}}
\newcommand{\tableref}[1]{Table \ref{#1}}
\newcommand{\socvec}{SocVec}
\newcommand{\argmin}{\operatornamewithlimits{argmin}}
\newcommand{\argmax}{\operatornamewithlimits{argmax}}
\newtheorem{example}{Example}
\newtheorem{lemma}{Lemma}
\newtheorem{definition}{Definition}
\newcommand{\cut}[1]{}
\newcommand{\ZY}[1]{\textcolor{red}{Zhiyi: #1}}

\begin{document}
	\let\WriteBookmarks\relax
	\def\floatpagepagefraction{1}
	\def\textpagefraction{.001}

	% Short title
	\shorttitle{A Token-based Transition-Aware Joint Framework for Multi-Span Question Answering}

	% Short author
	\shortauthors{Z. Luo et al.}

	% Main title of the paper
	\title{A Token-based Transition-Aware Joint Framework for Multi-Span Question Answering}

	\author{Zhiyi Luo}[type=editor,auid=000,bioid=1,orcid=0000-0002-2206-1926]
	%\cormark[1]
	\ead{luozhiyi@zstu.edu.cn}
	\ead[url]{http://zhiyiluo.site}
	%\credit{Conceptualization of this study, Methodology, Software}

	\author{Yingying Zhang}
	\ead{272831920@qq.com}

	\author{Shuyun Luo}
	\ead{shuyunluo@zstu.edu.cn}
	\cormark[1]
	\cortext[mycorrespondingauthor]{Corresponding author}

	\address[mymainaddress]{School of Computer Science and Technology and the Key Laboratory of Intelligent Textile and Flexible Interconnection of Zhejiang Province, Zhejiang Sci-Tech University}
	\address[mysecondaryaddress]{No. 928, No. 2 street, Baiyang street, Qiantang New District, Hangzhou 310018, China}

	% % Here goes the abstract
	\begin{abstract}
		Multi-span question answering has gained prominence as it aligns more closely with real-world user requirements compared to single-span question answering. The utilization of pretrained language models has shown promise in improving multi-span question answering, particularly for factoid questions that necessitate entity-based answers. However, existing methods tend to overlook critical information regarding answer span boundaries, resulting in limited accuracy when generating descriptive answers. To address this limitation, we propose TOAST, a novel joint learning framework specialized in token-based neighboring transitions that capture answer span boundaries through adjacent word relations. Our approach extracts high-quality multi-span answers and is general-purpose, applicable to both alphabet languages like English and logographic languages like Chinese. Furthermore, we introduce CLEAN, a comprehensive open-domain Chinese multi-span question answering dataset, which includes a substantial number of descriptive questions. 
		Extensive experiments demonstrate the superior performance of TOAST over previous top-performing QA models in terms of both EM F1 and overlapped F1 scores. Specifically, the TOAST models, leveraging  $\text{BERT}_{base}$ and $\text{RoBERTa}_{base}$, achieve substantial  improvements in EM F1 scores, with increments of 3.03/2.13, 4.82/3.73, and 16.26/11.53, across three publicly available datasets, respectively.

	\end{abstract}
	% 
	% Use if graphical abstract is present
	%\begin{graphicalabstract}
	%\includegraphics{}
	%\end{graphicalabstract}
	% 
	% Research highlights
	%\begin{highlights}
	%\item The paper proposes a novel joint learning framework called TOAST, which specializes in token-based neighboring transitions to capture the boundary information of answer spans through adjacent word relations for multi-span question answering.
	%\item TOAST extracts high-quality multi-span answers and is general-purpose, applicable to both alphabet languages like English and logographic languages like Chinese.
	%\item The paper creates a new Chinese reading comprehension dataset, consisting of both single-span and multi-span answers, with a broad-coverage of types of open-domain questions and demonstrates that incorporating the span boundary information via the awareness of adjacent word relations improves strong baselines on three multi-span question answering datasets.
	%\end{highlights}

	% Keywords
	% Each keyword is seperated by \sep
	\begin{keywords}
		Reading comprehension \sep Multi-span question answering \sep  Pretrained language models \sep Multitask learning  \sep Chinese datasets 
	\end{keywords}
	%Reading comprehension \sep
	%\sep Neural networks
	% \keywords{multi-span question answering, reading comprehension, chinese datasets, joint learning, neural networks}
	\maketitle

%	\input{intro}
\section{Introduction}
\label{sec:introduction}

Extractive question answering, also commonly referred as the task of reading comprehension, which aims to answer a user's question by finding short text segments (i.e., {\em spans}) from the given context, has been actively studied and achieved rapid progress in recent years.
Benefiting from the sophisticated industrial search engines and the vast amount of text collections on the web, 
high-quality contexts relevant to the user questions can be effectively retrieved to construct the datasets.
As a result, the answers directly drawn from the high-quality contexts are expressive enough.
Hence, existing datasets and models~\citep{DBLP:conf/emnlp/DasigiLMSG19,li2022multispanqa,lee2023liquid,DBLP:journals/ipm/Liu0GC23}, cast reading comprehension as an \emph{extractive} task that is easy to learn.

Most previous work~\citep{rajpurkar2016squad,rajpurkar2018know,yang2018hotpotqa,zaheer2020big} restricts the answer extracted from the context to a single text span 
which can only satisfy limited real-world open-domain questions. 
For example, as shown in \tableref{tab:intro} (the left example), the complete answer to a question could consist of a series of non-contiguous spans, 
or even the question itself could have multiple intents, 
where the answer to each intent is composed of one or more spans drawn from the input.
Hence, the models of multi-span question answering have significant utility to users. 
Recently, ~\cite{segal2020simple} cast the multi-span extraction as a sequence tagging task, 
predicting whether each token is part of an answer. 
~\cite{li2022multispanqa} captured the global information by integrating two sub-tasks of predicting the number of spans to extract and the answer structure annotated in their proposed dataset. 
Benefiting from nowadays pretrained models (e.g., BERT~\citep{kenton2019bert}, RoBERTa~\citep{liu2019roberta}), 
the above neural approaches 
have achieved promising performance on answer span extraction,  
especially for factoid questions where the expected answers are \emph{entities} (e.g., \emph{Person} and \emph{Location}).

However, existing systems fail to carefully consider span boundaries according to the information need of the question, 
and thus have very limited capabilities of 
precisely drawing a \emph{description} answer, for example, 
the answer spans of ``饮食护理(diet and care)'' and  ``适当地带它们出去运动一下(take them out for some exercises)''
as shown in \tableref{tab:intro}, from the input.
Moreover,  in the construction of existing datasets, 
user question candidates are constrained 
by the organization way of the document collection 
where the relevant contexts are retrieved from. 
For example, Wikipedia, the most widely used document collection 
for context retrieval, organizes articles using entities.
The problem is that a \emph{semantic gap} exists between the real context of what users want to ask and the entity-based articles (i.e. single Wiki page). 
Backed by the document collection of Wikipedia, 
existing datasets include most types of the factoid questions,
whereas they exclude many questions that can not be answered from a single 
article of an entity.
% =====  draw a figure here ====
\begin{table}[width=\textwidth,cols=4,pos=h]
	%	\centering
	\caption{Examples of questions and answers.}
	\begin{tabular*}{\tblwidth}{c|c|c} \hline
		Dataset   & CLEAN   &  MultiSpanQA \\ \hline
		Question  &  {\makecell[l]{
				如何养好约克夏犬?
				\\ (How to raise a Yorkshire terrier?)}} & Who wrote the song if you could see me now? \\ \hline
		Context  & {\makecell[l]{想要养好约克夏对于它们的{\color{blue}饮食护理}都要做好，\\
				由于它们所需的运动量并不是特别大，所以一般\\
				在家里就可以，不过还是要{\color{blue}适当地带它们出去运}\\
				{\color{blue}动一下}，这样它们能够生长的更好。\\
				(...
				must do a good job in their {\color{blue}diet and care.}\\
				... but it is still necessary to
				{\color{blue}take them out for}\\
				{\color{blue}some exercise} so that they can grow better.)}} 
		&  {\makecell[l]{
				``If You Could See Me Now'' is a 1946 jazz\\
				standard, composed by {\color{blue}Tadd Dameron}. He\\
				wrote it especially for vocalist Sarah\\
				Vaughan, a frequent collaborator. Lyrics\\
				were written by {\color{blue}Carl Sigman} and it became\\
				one of her signature songs, inducted into\\
				the Grammy Hall of Fame in 1998.}}
		\\ \hline
		Answer & {\makecell[l]{Segment1:饮食护理(diet and care)\\Segment2:适当地带它们出去运动一下\\(take them out for some exercise)}} &
		{\makecell[l]{Segment1: Tadd Dameron\\
				Segment2: Carl Sigman}}\\ \hline
	\end{tabular*}
	\label{tab:intro}
\end{table}

Following the above observations, we in this paper propose a novel approach to explicitly model the implicit \emph{neighboring transitions} 
via the adjacent word (or token) relations, 
which are both semantically and syntactically informative for span boundaries identification. 
This approach captures the intuition that the span boundary is produced in-between adjacent words. 
We indicate neighboring transitions in-between
as five types of relations.
Then, we jointly learn the sequence tagging task 
together with the  adjacent word relation classification task 
evolved from the span boundary identification, 
considering whether each token is part of an answer 
and which span each token belongs to accordingly. 
With the awareness of adjacent word relations, 
we incorporate the information of span boundaries in a multi-task learning manner.
Furthermore, in order to ameliorate the observed limitation of previous datasets, 
which including more real-world open-domain questions, 
we create a new dataset (in Chinese) in a more natural manner, 
extracting question-context pairs from a large-scale knowledge Q\&A sharing platform (i.e., BaiduZhidao\footnote{https://zhidao.baidu.com/}) instead of Wikipedia.

In summary, the main contributions in this paper are as follows:
\begin{itemize}
	\item We create a new reading comprehension dataset named CLEAN~\footnote{We intend to make CLEAN 1.0 dataset publicly avaiable at http://zhiyiluo.site/misc/clean\_v1.0\_sample.json for future work in this research area.} that consists of both single-span and multi-span answers, covering a wide range of open-domain question topics. 
	CLEAN overcomes the constraints imposed by previous datasets by incorporating carefully crafted long answers as contexts, effectively bridging the semantic gap with the insights provided by respondents. 
	\item We propose a novel approach for multi-span reading comprehension,  where we explore implicit neighboring transitions using adjacent word relations, effectively capturing both semantic and syntactic information pertaining to the boundaries of answer spans.

	\item We demonstrate that incorporating the span boundary information via the awareness of adjacent word relations improves strong baselines on three multi-span question answering datasets (both English and Chinese).
\end{itemize}

%	\input{method}
%\section{Tasks and Datasets}
\section{Preliminary}
\label{sec:preliminary}
% 1.30  10:20 - 13:00  0.5页
In this section, we present the problem statement and then introduce the datasets. 
%\subsection{Task}
%\label{sec:tasks}
%Information retrieval based question answering (IR-based QA) systems consist of two components: \emph{retriever}  and  \emph{reader}. 
%The reading comprehension (RC) task focuses more on building the \emph{reader} model since the construction of the RC dataset already utilizes the \emph{retriever} component  explicitly or implicitly.
%Thus, we formulate the problem of multi-span question answering as a task of multi-span extraction on the basis of the RC datasets. The objective of the task is to extract one or more answer spans based on the input question and context.
\subsection{Problem Statement}
\label{sec:problem}
We formulate the problem of multi-span question answering as a task of multi-span extraction on the basis of the reading comprehension (RC) datasets. The objective of the task is to extract one or more answer spans based on the input question and context.

Formally, given an input question represented as a sequence of words 
$q=(q_1, q_2, ..., q_n) \in \mathcal{V}$, and an input context $c$, associating to $q$, 
which is also represented as a sequence of words $c=(c_1, c_2, ..., c_m)\in \mathcal{V}$, where $\mathcal{V}$ refers to the vocabulary, 
the objective of the system is to extract one or more spans as the answer $a$, 
say $l$ spans, $a = [a_1, a_2, ..., a_l]$ from the context $c$,
where the $i$-th span $a_i$ is a sequence of words $a_i=(c_{i_s}, c_{i_s+1}, ..., c_{i_e})$, 
ranging from the start position $i_s$ to its end position $i_e$. Note that the extracted answer spans should be neither duplicated nor overlap with each other. That means, for any $i, j$ where $i$ < $j$, $i_e < j_s$ holds. 
%Following previous studies, we regard the problem as a sequence tagging task.
%We also build an auxiliary task incorporating token-based transition knowledge to capture 
%the information of span boundaries, and jointly learn the sequence tagging task as well as the transition classification task.

Evaluation are exact match and partial match with any of the reference answer strings after minor normalization such as lowercasing, following evaluation scripts from~\cite{li2022multispanqa}.

\subsection{Datasets}
\label{sec:predata}
In this work, we conduct the experiments on three RC datasets, ranging from two English datasets and one proposed Chinese dataset for multi-span question answering.

The latest dataset, MultiSpanQA, focus on multi-span questions, which is derived from Natural Question (NQ) ~\citep{DBLP:journals/tacl/KwiatkowskiPRCP19}, a large-scale open domain QA dataset. It also has an expanded variant by introducing single-span and unanswerable questions, namely MultiSpanQA (expand).

In MultiSpanQA and MultiSpanQA (expand), the questions are derived from real queries issued to the Google search engine. Each question is paired with a context extracted from a retrieved Wikipedia page. However, it is important to acknowledge that Wikipedia pages are structured around entities, which may not fully align with the intentions of real-world open-domain questions, especially those that are non-factoid in nature. This entity-centric organization of Wikipedia pages introduces a semantic gap between the content and the intended meaning of real-world open-domain questions.
As a result, existing RC datasets like MultiSpanQA are limited to questions  that primarily revolve around entities, allowing for the extraction of concise spans from a single Wikipedia page as answers.
Moreover, there is a noticeable scarcity of publicly available open-domain multi-span QA datasets in the Chinese language. Although recently proposed CMQA~\citep{DBLP:conf/coling/JuWZZ0022} is one such dataset, it primarily focuses on a new task of conditional question answering, which may not directly address the requirements of traditional question answering scenarios.

To ameliorate these limitations, we create a more realistic and challenging dataset, utilizing a large-scale Chinese online knowledge Q\&A sharing platform (i.e. BaiduZhidao) which is full of open-domain questions with crafted long answers from  public users. 
Over the course of two decades of crowd-sourcing efforts, the shared questions have covered  a broad range of subjects, including people, celestial bodies, flora and fauna, landmarks, etc. Firstly, we conduct a random crawl of one million questions across 29 popular subjects in the open domain. Next, we employ two key strategies to increase the proportion of multi-span answers relative to single-span answers: 1) selectively choosing questions that contain  keywords such as \emph{如何/怎样}(e.g. \emph{how}) or \emph{哪些}(e.g.\emph{ what/which ones}), as these types of questions typically require multipart descriptions; and 2) translating all the crawled questions into English and specifically targeting questions featuring plural nouns. 
Note that, a question may have a number of long answers created by different users, and we only consider those with more than 3 likes as potential candidates. Then, our annotators are educated to pick up high-quality contexts from the candidate answers for each question and identify one or more answer spans within the context that can effectively answer the given question. Finally, we obtain a diverse collection of multi-span answers in various formats.

In our proposed \textbf{C}hinese mu\textbf{L}ti-span qu\textbf{E}stion \textbf{AN}swering (or CLEAN) dataset, the context consists of meticulously constructed long answers that effectively bridge the semantic gap with the insights provided by respondents. This approach ensures that the question intents are appropriately addressed and breaks the constraints imposed by  previous datasets in terms of question selection. 
Table 1 (left) presents a specific example from the CLEAN dataset, where the question is obtained from BaiduZhidao, and the context is selected from the original long answers associated with that question. 
To make our dataset more general, as well as considering the versatility of questions, unlike MultiSpanQA, we only annotate the span of answer without the structure of the answer.

\section{Our Framework}
\label{sec:framework}
% 1.30  导言 15:00 - 15:30  0.2页
In this section, we first introduce a basic neural framework for multi-span question answering based on pretrained language models, which involves casting multi-span extraction as a sequence tagging task. We then propose a novel model called \textbf{TO}ken-b\textbf{AS}ed \textbf{T}ransition-aware 
(TOAST) for multi-span question answering that incorporates joint learning.

%In this section, we first introduce the basic neural framework on the basis of 
%pretrained models, casting multi-span extraction as a sequence tagging task.
%We then propose a novel joint learning 
%\textbf{TO}ken-b\textbf{AS}ed \textbf{T}ransition-aware 
%(or TOAST) model
%for multi-span question answering.

The architecture of TOAST is depicted in \figref{fig:toast}.
The \emph{Transition Identification} module demonstrates how span boundary identification can be transferred to a token-based transition classification task, while the  \emph{Transition Incorporation} module explains how we incorporate semantic and syntactic knowledge in adjacent word relations to improve the informativeness of the extraction. 
In addition to the sequence tagging task (Task 1 in \figref{fig:toast}), TOAST also includes an auxiliary task of transition classification (Task 2 in \figref{fig:toast}). We therefore present a multi-task learning strategy for TOAST. 
Finally, we present the joint decoding step, which leverages outputs from multiple tasks to improve performance.

\begin{figure*}[thb!]
	%	\small
	\centering
	\includegraphics[width=0.9\columnwidth]{framework.png}
	\caption{An illustration of TOAST framework architecture.}
	\label{fig:toast}
\end{figure*}
%at the inference time.
\subsection{A BERT-based Sequence Tagging Model}
\label{sec:basic}
Extracting a variable number of spans from an input text can be
commonly cast as a sequence tagging problem, 
which is suitable for answer extraction of multi-span questions.
Following the observation of ~\cite{li2022multispanqa}, 
we adopt the BIO
tagging scheme to mark answer spans in the context 
where words are tagged as either part of the answer (\textbf{B}egin, \textbf{I}nside) or not (\textbf{O}ther). 
Formally, BIO tagging scheme is represented by a tag set $\mathcal{T}=\{$ B, I, O$\}$.

\subsubsection{Encoder}
First, we encode the question and context with a pretrained 
language model, such as BERT and RoBERTa.
Generally, the encoder takes in the input text and encodes it into 
a series of contextualized hidden representations.
Specifically, the BERT-style encoder takes in a
$[CLS] $ token, followed by
the concatenation of a question $q=(q_1, q_2, ..., q_n)$ and its context $c=(c_1, c_2, ..., c_m)$ with $[SEP]$  token,
as the input sequence $([CLS], q_1, q_2, ..., q_n, $ $[SEP], $ $c_1, c_2, ..., c_m)$.
We use $x=(x_1, x_2, ..., x_L)$ as a more concise notation of the above sequence, 
where $L$ refers to the length of the input, 
that $L=n+m+2$ when ignoring padding tokens.
Then we send it through neural layers of the encoder to finally obtain hidden representations 
$\mathbf{H}=\left[\mathbf{h}_1, \mathbf{h}_2, ..., \mathbf{h}_{L}\right] 
\in \mathbb{R}^{L\times d_h}$,
where $d_h$ denotes the hidden-layer size, and $\mathbf{h}_i$ represents the hidden representation of the $i$-th input token. 
In the next step, output representations are sent into 
an FFN (Feed Forward Neural Network) layer, 
and computed the output logits as 
$\mathbf{O}_{tag}=FFN(\mathbf{H})\in\mathbb{R}^{L\times |\mathcal{T}|}$ for token-level tag prediction,  
where $\mathcal{T}$ denotes the tag set we described above.

\subsubsection{Training \& Decoding}
The task of token-level tag prediction that aims to assign a specific tag $t_i$ from the set $\mathcal{T}$ to each token $x_i$ in the input sequence $x$, is inherently a classification problem. In this regard,  we employ the widely adopted cross-entropy loss, which aggregates the negative logarithm of the predicted probability for the correct tag across all tokens in the training set. This loss penalizes the model heavily for confident yet incorrect predictions, prompting the model to adjust its parameters and minimize the loss. To optimize the answer span tagging model, we compute the cross-entropy loss, say $L_{tag}$, as follows:
\begin{equation}\label{eq:tag_loss}
	\centering
	%	\widetilde{
	L_{tag}=-\sum_{x\in D}\sum_{i=1}^{L(x)} \log (p(t_i | x_{i})) ,
\end{equation}
where $D$ is the training set, and $L(x)$ is the input length of $x$. 
At the decoding step, we predict the tag $\hat{t}_i$ for token $x_i$ as follows:
\begin{equation}\label{eq:ti1}
	\hat{t}_i=\argmax_{t\in \mathcal{T}} p(t | x_i).
\end{equation}
Then, we extract a successive sequence of 
B- and I-tagged tokens as an answer span. 
For example, the input sequence of context ``a b c d e f'' tagged as ``O B I O B O'' can be decoded into two 
answer spans of ``b c'' and ``e'' respectively. 
Note that we do a post-processing step to tag``O'' for all input tokens except for those from the context, 
which means we only draw answer spans from the input context.

\subsection{Token-based Transition Awareness}
\label{sec:aware}
One limitation of the baseline framework is that 
it often breaks a complete answer span into 
many meaningless splits, 
which is especially serious for those description answer spans.
This reflects that the model lacks specific knowledge to indicate span boundaries accurately. 
A context or long answer for a multi-span question contains a variable number of answer spans corresponding to one or more user intents. 
Therefore, semantic meanings and syntactic patterns transit quickly  
across words (or tokens), the minimal text unit.
Following the above observation, 
we propose a novel approach to capture such token-based neighboring transitions, 
then come up with an auxiliary task and  joint learning strategy to incorporate such knowledge into our framework.

\subsubsection{Transition Identification}
In our approach, neighboring transitions are represented as five types of \emph{relations} in-between adjacent words by exploring whether a span transition happens across the adjacent words. 
More specifically, for each adjacent word pair in the input, say $x_{i-1}$ and $x_{i}$, 
8 possible tagging cases exist under the BIO tagging scheme,
denoted as ($t_{i-1}$, $t_{i}$), where $t_{i}\in \mathcal{T}$ is the ground truth tag of $x_i$.
As shown in \tableref{tab:relation}, 
we summarize five relations in-between adjacent words $(x_{i-1}, x_{i})$ according to their tags $(t_{i-1}, t_{i})$, each of which corresponds to a type of span transition. 
For example, an inter-span transition (defined as \emph{Inter} relation) happens when an adjacent word pair is tagged as (B, B) or (I, B), which means $x_{i-1}$ and $x_{i}$ are both part of the answer while belong to two consecutive but different answer spans.
The relation of \emph{NONE} indicates that there is no span transition in-between $x_{i-1}$ and $x_{i}$.
Note that $x_{i}$ could be either a context word (e.g., $c_i$) or a question word (e.g., $q_i$) as well as a special token (e.g., [CLS] and [SEP].
The NONE relation holds if any word in $(x_{i-1}, x_{i})$ is a non-context word or both $x_{i-1}$ and $x_{i}$ are context words, but neither is part of the answer.
To further illustrate the types of relations, we provide an example from the MSQA dataset in~\tableref{tab:relation}. 
The question ``When are the Winter Olympics and where are they'' has two intents: querying the time and location of the Winter Olympics. The  \textit{Inter} relation between the terms ``2018'' and ``in'' indicates a semantic transition from time to location. By exploring every neighboring transition modeled by the defined set of relations between adjacent words, our approach effectively captures semantically and syntactically span-based transitions. 
Next, we present how to encode span-transition knowledge via adjacent word relations in \tableref{tab:relation} and incorporate such knowledge into our framework.

\begin{table}[width=\textwidth,cols=4,pos=h]
	\centering
	% 	\begin{center}
	\caption{The definition of adjacent word relations.}
	\label{tab:relation}
	% 	\begin{tabular}{lcc}
	\begin{tabular*}{\tblwidth}{lllc}%{@{}LCC@{}}
		\hline 
		Tag Pair  ~$(t_{i-1}, t_{i})$ 
		& Span Transition &  Relation Name &  MSQA Example \\
		\hline
		(O, O)
		&  NONE &  NONE  &   \raisebox{-0.3\totalheight}{\includegraphics[width=0.51\textwidth]{relation_a}} \\
		(O, B) 
		&  Other $\rightarrow$ Span1 &   In relation & \raisebox{-0.4\totalheight}{~~~~~~~~~~~~~~~~~\includegraphics[width=0.4\textwidth]{relation_b}} \\
		(B, I), (I, I)  
		& Span1 $\rightarrow$ Span1 &  Intra relation & \raisebox{-0.5\totalheight}{\includegraphics[width=0.51\textwidth]{relation_c}}  \\
		(B, B), (I, B)  
		& Span1 $\rightarrow$ Span2 &  Inter relation & \raisebox{-0.6\totalheight}{~~~~~~~~~~~~~~~~~~~~~~\includegraphics[width=0.4\textwidth]{relation_d}} \\
		(B, O), (I, O) 
		& Span1 $\rightarrow$ Other  &  Out relation &
		% \raisebox{-0.5\totalheight}{Span 1: between 9 and 25 February 2018 \\ Span 2: in Pyeongchang County , Gangwon Province , South Korea} \\
		\raisebox{-0.5\totalheight}{\includegraphics[width=0.51\textwidth]{relation_e}} 
		\\
		% 		\raisebox{-0.5\totalheight}{\includegraphics[width=0.6\textwidth]{relation_e}} \\
		\hline
	\end{tabular*}
	%\end{center}
\end{table}

\subsubsection{Transition Incorporation}
After transition identification, each adjacent word pair $(x_{i-1}, x_{i})$ has been associated with a relation $r_i \in \mathcal{R}$, where $\mathcal{R}$ is the set of adjacent word relations. As defined in  \tableref{tab:relation}, $\mathcal{R} = \{NONE, In, Intra, Inter, Out\}$. Then, we equip our model with 
token-based transition knowledge though relational transformations.
More specifically, for each $(x_{i-1}, r_i, x_i)$ triple, 
that $r_i$ associates to a relational matrix $\mathbf{W}^{r_i}\in \mathbb{R}^{d_h\times 2d_h}$,
we compute the enhanced contextualized representation of $x_i$
with the awareness of span transitions as follows: 
\begin{equation}\label{eq:matrix}
	\mathbf{u_i}=\mathbf{W}^{r_i} \left[ \mathbf{h}_{i-1}; \mathbf{h}_i \right], 
\end{equation}
where $\mathbf{h_i}$ is the output representation of token $x_i$ 
from the encoder described in \secref{sec:basic}, 
$\mathbf{u_i}$ is its enhanced representation, 
%and $[\mathbf{h}_{i-1}; \mathbf{h}_i]$ denotes the concatenation of $\mathbf{h}_{i-1}$ and $\mathbf{h}_i$.
and $[;]$ is vector concatenation across row.
Then, we send the enhanced representations $\mathbf{U} = [\mathbf{u}_1, \mathbf{u}_2, ..., \mathbf{u}_L] \in \mathbb{R}^{L\times d_h}$ into a FNN layer and compute the output logits as:
\begin{equation}\label{eq:enhanced}
	\mathbf{\widetilde{O}}_{tag}=FNN(\mathbf{U})\in \mathbb{R}^{L\times|\mathcal{T}|},
\end{equation}
where $[, ]$ is vector concatenation aross column, and 
the implicit multiplicaiton is matrix multiplication.
We make up a fake token $x_0$ as the prior word of $x_1$, that $(x_0, NONE, x_1)$ holds, and $\mathbf{h}_0$ is set to be a vector full of zeros. Hence, each input token $x_i$ can be paired with its prior token $x_{i-1}$ as an adjacent word pair indicating with a relation $r_i$, where $i$ ranges from $1$ to $L$.

We argue that the awareness of span-based transition which intuitively modeled by adjacent word relations bring extra information for span identification%both semantically and syntactically
, thus facilitate the multi-span extraction task.
The proposed incorporation method is natural and straightforward, 
and we will demonstrate its effectiveness in our experiments
(See \secref{sec:experiments}).

\subsection{Multi-task Learning}
\label{sec:multitask}
To aware the knowledge of span-based transition, 
we need to construct a series of relations $(r_1, r_2, ..., r_L)$ from the input sequence $(x_1, x_2, ..., x_L)$, where $r_i$ indicates the adjacent word relation in-between the adjacent word pair $(x_{i-1}, x_i)$.
%At the training step, 
For the training data, each input token $x_i$ is annotated with a ground truth tag $t_i$, thus we can draw relation $r_i$  from the tag pair $(t_{i-1}, t_i)$ according to \tableref{tab:relation}.
While it is not true for the test data, 
we can not harvest accurate adjacent word relations directly.
Thus, on the basis of previous sequence tagging model, 
we build a multi-task learning framework by introducing an auxiliary task of token-based transition classification.
This relation classifier of the auxiliary task shares the BERT-style encoder with previous tagging model with a new, unshared FNN layer upon. The output logits of relation classifier are computed as: 
\begin{equation}\label{eq:aux_logits}
	%	\widetilde{
	\mathbf{O}_{rel}=FNN([ \mathbf{H}_{prev}; \mathbf{H} ]) \in \mathbb{R}^{L \times |\mathcal{R}|},
\end{equation}
where $\mathbf{H}_{prev}=[\mathbf{h}_0, \mathbf{h}_1, ..., \mathbf{h}_{L-1}]\in \mathbb{R}^{L\times d_h}$ denotes representations of the prior token sequence $(x_0, x_1, ..., x_{L-1})$ with respect to the input sequnce $(x_1, x_2, ..., x_L)$.
For the auxiliary task, we use cross-entropy loss to train the relation classifier, which reflects the awareness of span-based transition. 
More specifically, the above loss $L_{rel}$ is computed as:
\begin{equation}\label{eq:rel_loss}
	%	\widetilde{
	L_{rel}=- \sum_{x\in D}\sum_{i=1}^{L(x)} \log (p(r_i | x_{i-1}, x_{i})) ,
\end{equation}
where $D$ refers to the training data, and $L(x)$ denotes the length of input sequence $x$. 
To jointly learn shared parameters in the encoder as well as leverage the representation of token-based transition knowledge, we use a combinartorial loss as follows:
\begin{equation}\label{eq:loss}
	%	\widetilde{
	%	L= L_{tag} + \lambda L_{rel}.  %,
	L = L_{tag} + L_{rel}.  %,
\end{equation}

In summary, 
the strategy of our multi-task learning framework is that, 
given an input sequence, we first predict the token-based transitions in each position, 
then leverage the predicted transitions to calculate the enhanced token representation following \eqnref{eq:enhanced}, 
finally optimize the proposed combinartorial loss in \eqnref{eq:loss} to update joint model parameters together.

\subsection{Decoding}
\label{sec:decoding}
Next, we present two decoding strategies for our joint framework.
As described above, we jointly train two tasks (i. e, sequence tagging and transition classification) in our framework, then predict the adjacent token-based transitions and the token tags respectively.
Intuitively,  
we can decode the answer spans from tags predicted by the enhanced sequence tagging model of our framework directly, 
similar to the decoding algorithm described in \secref{sec:basic}.
Formally, we decode tag $\hat{t}_i$ of $x_i$ as follows:
\begin{equation}\label{eq:t_i1}
	\hat{t}_i = \argmax_{t\in \mathcal{T}} p(t | x_i, \mathcal{M}_{tag}),
\end{equation}
where $\mathcal{M}_{tag}$ represents the token-based transition aware tagging model (see \secref{sec:aware}). 
As we will see in \secref{sec:experiments}, this enhanced tagging model outperforms the baseline model marginally.

While the predicted tags implicitly incorporate the knowledge of token-based transitions, we propose to explicitly combine the predictions from the enhanced tagging model $\mathcal{M}_{tag}$ with those from the transition classifier $\mathcal{M}_{rel}$ at decoding time. We score the potential tag $t$ of a token $x_i$, considering not only $x_i$ but also its prior token $x_{i-1}$ through the predicted transition $r_i$ in-between.

To be more specific, we jointly decode the tag $t_i$ of $x_i$ as  follows:
\begin{equation}\label{eq:t_i}
	\hat{t}_i = \argmax_{t\in \mathcal{T}} \widetilde{S}(t | x_{i-1}, x_i, \hat{t}_{i-1}, \mathcal{M}_{joint}),
\end{equation}
where $\widetilde{S}$ denotes the scoring function that intakes the predicted transition between $x_{i-1}$ and $x_i$.
Therefore, $\widetilde{S}(t  | x_{i-1}, x_i, \hat{t}_{i-1}, \mathcal{M}_{joint})$ is computed as: 
\begin{equation}\label{eq:decoding}
	\begin{split}
		\widetilde{S}(& t | x_{i-1}, x_i, \hat{t}_{i-1},  \mathcal{M}_{joint})  = S(t|x_i, \mathcal{M}_{tag}) +  S(\hat{r}_i | x_{i-1}, x_i, \hat{t}_{i-1}, t, \mathcal{M}_{rel})\\
		& = S(t|x_i, \mathcal{M}_{tag}) + \mathds{1}(\hat{t}_{i-1} \in \text{First}(\hat{r}_i)) S({\hat{r}_i}| x_i, x_{i-1}, \mathcal{M}_{rel})^{\frac{1}{2}}\cdot \mathds{1}(t \in \text{Second}(\hat{r}_i)) S({\hat{r}_i}| x_i, x_{i-1}, \mathcal{M}_{rel})^{\frac{1}{2}}\\
		& = S(t|x_i, \mathcal{M}_{tag}) + \mathds{1}(\hat{t}_{i-1} \in \text{First}(\hat{r}_i)) \cdot \mathds{1}(t \in \text{Second}(\hat{r}_i)) \cdot  S({\hat{r}_i}| x_i, x_{i-1}, \mathcal{M}_{rel}),
	\end{split}
\end{equation}
where $S$ refers to the probability score, $\mathds{1}$ denotes the indicator function, $\text{First}(r)$ represents 
a set of tags consisting of the distinct first elements of all tag pairs mapped from $r$ according to \tableref{tab:relation}, and $\text{Second}$ operates like $\text{First}$ except that $\text{Second}$ collects the second elements. 
For example, \emph{Inter} can be mapped into two kinds of tag pairs (B, B) and (B, I), then 
$\text{First}(\emph{\text{Inter}})$ is the set $\{\text{B}\}$ and   $\text{Second}(\emph{\text{Inter}})$ is the set $\{\text{B}, \text{I}\}$.
Note that, $\hat{r}_i$ in \eqnref{eq:decoding} is the optimal transition relation predicted by $\mathcal{M}_{tag}$ which is computed as: 
\begin{equation}\label{eq:r_i}
	\hat{r}_i = \argmax_{r_i\in \mathcal{R}} p(r_i | x_{i-1}, x_i, \mathcal{M}_{rel}).
\end{equation}

%	\input{experiments}
\section{Experiments}
\label{sec:experiments} %preamble 16:10 - 16:40
In this section, we compare TOAST with multiple strong baselines on multi-span question answering. 
We first introduce the datasets and experimental setup, 
then show the experimental results and analysis for different models.

%To show the generalization ability of TOAST

\subsection{Dataset Description} 
\label{sec:dataset}
% 17:30 - 20:00  0.4页 
% MultiSpanQA  MultiSpanQA (expanded)  0.2页
We conduct the experiments  on three RC datasets, including
two English datasets, namely MultiSpanQA and its variant MultiSpanQA (expand), as well as one Chinese dataset, namely CLEAN (ours).
\tableref{tab:datasets} shows an overview statistics of those datasets.
To examine the performance of different models on various question types, 
we categorize the samples into two types: \emph{description} and \emph{entity}, 
based on the expected answer type. \tableref{tab:answer_types} illustrates the breakdown of these types along with an example for each answer type class.
Note that, MSQA is short for MultiSpanQA, and MSQA-Exp is short for the expansion of MultiSpanQA.

%\subsubsection*{QUOREF}
%%%%%%%%
%Quoref~\cite{DBLP:conf/emnlp/DasigiLMSG19} contains over 21K examples, where each example is a triple of (question, context, answer). 
%The contexts consist of 4.7K paragraphs  from English Wikipedia, from each paragraph a number of questions requiring coreferential reasoning are derived. Quoref contains both single-span and multi-span questions, whose answers are spans and sets of spans, respectively.
%%%%%%%%%%%%%
%4.7K paragraphs where the answer to a single-span question is a single span, and the answer to a multi-span question is a set of spans. English Wikipedia. 
%Quoref, an earlier RC dataset which contains multi-span questions models the answers 
\subsubsection*{MultiSpanQA} 
MultiSpanQA~\citep{li2022multispanqa}, a recently proposed dataset for multi-span question answering, consists of 6.5K multi-span examples, where the questions are user queries issued to Google search engine and the contexts are extracted from English Wikipedia. 
\subsubsection*{MultiSpanQA (expand)}
MultiSpanQA(expand)~\citep{li2022multispanqa}, an expanded variant of MultiSpanQA, intakes single-span and unanswerable questions, and consists of 19K examples in total.
\subsubsection*{CLEAN}
We propose CLEAN harvesting from a Chinese online knowledge Q\&A sharing platform (i.e., BaiduZhidao), 
which consists of 9,063 examples in total, including over 4.2K multi-span examples. 
CLEAN contains 3,077 distinct open-domain user questions, and each question is annotated with a number of contexts from its associated long answers. To be more specific, we recruit three annotators to extract answer spans from given contexts, and retained only those examples that achieved a Fleiss' Kappa score greater than 0.5. Our results indicate a high level of inner-annotator agreement, with a Fleiss' Kappa score of 0.739, suggesting that the annotations are consistent and reliable.

\begin{table}[width=.7\textwidth,cols=4,pos=h]
	\caption{Dataset statistics.}
	\label{tab:datasets}
	\begin{tabular*}{\tblwidth}{lccc}
		\toprule
		Dataset 
		& Language &  \#Examples & \#Multi-span Examples \\
		\hline
		% 		QUOREF~\cite{DBLP:conf/emnlp/DasigiLMSG19}
		% 		&  English &  21,817  & 2,207 \\
		MSQA~\cite{li2022multispanqa}
		&  English  & 6,536   & 6,536  \\
		MSQAExp~\cite{li2022multispanqa}
		&  English  & 19,608   & 6,536  \\
		CLEAN (ours)
		& Chinese &  9,063  & 4,204  \\
		\bottomrule
	\end{tabular*}
\end{table}

\begin{table}[width=.7\textwidth,cols=4,pos=h]
	\caption{Proportion and examples of answer types in MSQA and CLEAN Datasets.}
	\label{tab:answer_types}
	\begin{tabular*}{\tblwidth}{llcp{8cm}}
		\toprule
		\textbf{Dataset} & \textbf{Answer Type} & \textbf{\%} & \textbf{Example} \\
		\midrule
		\multirow{3}{*}{MSQA} & Description & 16.40 & \emph{other gases} \\
		& Entity & 76.30 & \emph{Vermont} \\
		& \emph{Numeric} & 7.30 & \emph{9,677 ft} \\
		\midrule
		\multirow{3}{*}{CLEAN} & Description & 76.54 & \emph{长满了尖锐的刺 (full of sharp thorns)} \\
		& Entity & 18.00 & \emph{北京市 (Beijing)}  \\
		& Numeric & 5.46 & \emph{1006万人 (10.06 million people)} \\
		\bottomrule
	\end{tabular*}
\end{table}

%Our results demonstrate a high level of inner-annotator agreement, as indicated by a Fleiss' Kappa score of 0.739. This high score strengthens the validity of subsequent analyses, as it suggests that the annotations are consistent and reliable. 
%Our results demonstrate a high level of inner-annotator agreement, as indicated by a Fleiss' Kappa score of 0.739 suggesting that the annotations are consistent and reliable. 
%We  ask 3 annotators to extract answer spans from contexts, and remain those examples with Fleiss Kappa greater than 0.5. Finally, CLEAN demonstrates a high level of inner-annotator agreement, as evidenced by a Fleiss' Kappa score of 0.739.
%Te sample 208 examples from  CLEAN The inner-annotator agreement of each   \ZY{加一个一致性}
% 弄一个数据集的表格 解释 QUAREF, MultiSpanQA, CLEAN的区别
% 分别给出例子

%\example{xx}
% CLEAN 总共有9063条数据 即(question, context, answers) triples
% 其中包括3077个unique的questions 平均每个问题有 9063/3077个有效回答
% 4204 个multi-span examples
% 1588 个multi-span questions
% \begin{table}[h]
%	\caption{Proportion and examples of answer types in MSQA and CLEAN.}
%	\label{tab:answer_types}
%	\begin{tabular*}{\tblwidth}{lcc}
%		\toprule
%		Answer type 
%		& \% &  Example  \\
%		\hline
%		MSQA
%		&  English  & 6,536   & 6,536  \\
%		MSQAExp~\cite{li2022multispanqa}
%		&  English  & 19,608   & 6,536  \\
%		CLEAN (ours)
%		& Chinese &  9,063  & 4,204  \\
%		\bottomrule
%	\end{tabular*}
%\end{table}

\subsection{Experimental Setup}
\label{sec:setup}
% 22:00 - 22:30 preamble 
For all competing models and our models, we use the HuggingFace implementation of $\text{BERT}_{base}$ or $\text{RoBERTa}_{base}$ as the \emph{encoder} with $max\_len=512$. 
Specifically, for TOAST models, we initialize the learning rate to $3e-5$ and set the batch size to $32$, then use the BERTAdam optimizer with a weight decay of 0.01. 
Our approach does not involve tuning the parameters on the validation set. Instead, we rely on using the model checkpoints obtained after 50 epochs.
As for the other competing models, we follow the configurations as originally reported  in~\citep{segal2020simple,li2022multispanqa,lee2023liquid} accordingly. 
%with a linear warm-up at first 200 steps.
Next, we introduce the comparison models and the evaluation metrics in our experiments. 
\subsubsection{Models Under Comparison}
\label{sec:baselines}
% 6:00 - 8:00  0.4页
We introduce four competing models for multi-span answer extraction. These are \textbf{SSE}~\citep{DBLP:conf/naacl/DevlinCLT19}, \textbf{TASE}~\citep{segal2020simple}, \textbf{SNP-TASE}~\citep{li2022multispanqa} and \textbf{LIQUID}~\citep{lee2023liquid}.

\textbf{SSE} is a traditional single-span extraction  model which formulates the answer extraction task by span labeling, i.e., identifying in the context a span (a continuous string of text) that constitutes an answer.  SSE builds a learnable linear layer upon the encoder which is used to predict the start and end position of the span. We adapt SSE for multi-span question answering, that considers the first span of a multi-span answer as the ground truth at the training step.

\textbf{TASE} is a tag-based span extraction model which identifies the multi-span answer by assigning a tag to every input token with BIO tagging scheme.
Following~\cite{li2022multispanqa}, we build a strong baseline upon TASE, integrating with span number prediction and structure prediction, namely \textbf{SNP-TASE}.

The most recent framework, \textbf{LIQUID}~\citep{lee2023liquid}, employs question generation as a form of data augmentation to enhance answer extraction performance, differing from the conventional emphasis on the exploration of model architectures.

According to the different strategies of decoding,
we propose two models, $\textbf{TOAST}_{tag}$ and $\textbf{TOAST}_{joint}$, on the basis of our framework, where
\textbf{TOAST} is our joint learning framework, and the respective suffix designates the module from which predictions are used at decoding step.
$\textbf{TOAST}_{tag}$ predicts a tag for every token using the predictions of $\mathcal{M}_{tag}$ (see \eqnref{eq:t_i1}), while $\textbf{TOAST}_{joint}$  leverages predictions from both $\mathcal{M}_{tag}$ and $\mathcal{M}_{rel}$ explicitly (see \eqnref{eq:t_i}).
%\begin{itemize}
%	\item[] \textbf{TOAST} 
%\end{itemize}
\subsubsection{Evaluation Metrics}
\label{sec:metrics}
% 9:30 - 11:30  0.4页
% 人工判断标准   因为
We evaluate the performance of our methods by automatic metrics and human evaluation.
% Exact Match

\textbf{Automatic Metrics.}  We use two automatic metrics for evaluation: Exact Match and F1 score. 
%The exact match metric  and F1 score.  Following Segal et al.~\cite{segal2020simple} and Li et al.~\cite{li2022multispanqa}, we use Exact Match (EM) on question-level and span-level as well as Partial Match (PM) scores as the automatic metrics for multi-span question answering evaluation. 
\begin{itemize}
	\item \textbf{Exact Match}. An exact match occurs when a predicted span fully matches one of the ground-truth answer spans. We calculate the micro-average precision, recall and f1 score for the extract match metric. 
	%	For each example, we iterate over  the predicted spans given by the model for evaluation, and an exact match occurs when the predicted span exactly matches one of the ground-truth spans for that example.
	\item \textbf{Overlap F1 score}. Overlap F1 score is the macro-average f1 score, where the f1 score for each example is computed by treating the prediction and gold as a bag of tokens.
\end{itemize}
The exact match shows the quality of predictions straightforwardly. However, counting the number of exact matches makes the score discrete and coarse. Besides, it penalizes the partial matched prediction too much. The overlap F1 score considers the overlap between the prediction and gold and thus can be used as a complementary metric to the exact match metric.
%\textbf{Exact Match} 
%
%\textbf{Partial Match}
% F1 score 
%In QA, it's computed over the individual words in the prediction against those in the True Answer. The number of shared words between the prediction and the truth is the basis of the F1 score: precision is the ratio of the number of shared words to the total number of words in the prediction, and recall is the ratio of the number of shared words to the total number of words in the ground truth.
%https://github.com/eladsegal/tag-based-multi-span-extraction/blob/master/predictions/quoref_predictions.jsonl

\textbf{Human Evaluation.} We randomly select 50 samples from each dataset and average the scores of two human annotators who are proficient in English and Chinese.
%We ask annotators to give a score on each predicted span of one sample, ranging from 1 to 5, then average the scores of each span as the final score of this sample.
%We ask the annotators to score each predicted span for a sample on a five-scale scores, ranging from 1 to 5, according to its quality, and then average the scores for each span as the final score for that sample.
We ask the annotators to score each sample under 3 span-level aspects (completeness, correctness and distinctness) and the overall quality:
\begin{itemize}
	\item \textbf{Completeness} is to measure the semantic completeness of a given predicted span. If the span expresses the meaning completely, it will receive a high rate on the completeness.
	\item \textbf{Correctness} is to measure the content correctness of a given predicted span. If the span answers the user question correctly, it will receive a high rate on the correctness.
	\item \textbf{Distinctness} is to measure the content distinctness of a given predicted span against other predictions. If the span distinguishes from others semantically, it will receive a high rate on the distinctness. 
	\item \textbf{Overall} is to measure the overall quality of the predictions from a model for each sample.
\end{itemize}
For a given sample, each aspect is judged as a five-scale scores, 
ranging from 1 (Poor) to 5 (Excellent) depending on its quality.
For each span-level aspect, we score every predicted span and then average the scores across all predicated spans for evaluation.
In addition, for each sample we use the averaged overall scores from three annotators to present the overall quality of the predictions of that sample.
%For a given sample and aspect, we score each predicted span on a five-scale scores, ranging from 1 to 5, according to its quality, and then average the scores of all predicted spans respectively to evaluate that sample on the given aspect.

% 整几个方面

%For each sample, we ask an annotator scores for each predicted span with three-scale 
\subsection{Experimental Results and Analysis}
\label{sec:evaluation}
% 13:00 - 17:00 做各种实验
% encoder: RoBERTa large
In this section, we compare TOAST with all competing models described above both quantitatively and qualitatively.

\subsubsection{Comparison Results}
\label{sec:comparison}
We evaluate our model as well as baselines (\secref{sec:baselines}) on the development splits of four datasets (\secref{sec:dataset}) using both automatic metrics and human evaluation metrics (\secref{sec:metrics}). 
The comparison results are shown in \tableref{tab:exact_match} (exact match), \tableref{tab:overlapped} (overlap) and \figref{fig:human_eval} (human evaluation).

\begin{table}[width=\textwidth,cols=4,pos=h]
	%	\centering
	\caption{The Exact Match results for all competing models, including micro-average precision (P), recall (R) and f1 score (F1). }
	\label{tab:exact_match}
	\begin{tabular*}{\tblwidth}{@{}p{2.2cm}p{1.0cm}p{1.0cm}p{1.0cm}cp{1.0cm}p{1.0cm}p{1.0cm}cp{1.0cm}p{1.0cm}p{1.0cm}@{}}
		\toprule[0.3mm]
		\multicolumn{1}{l}{}  & \multicolumn{3}{c}{MSQA}  & \multicolumn{1}{l}{}  & \multicolumn{3}{c}{MSQA-Exp} & \multicolumn{1}{l}{} & \multicolumn{3}{c}{CLEAN} \\ 
		\cline{2-4} \cline{6-8} \cline{10-12}
		%		\midrule
		\addlinespace
		& P(\%)  & R(\%)  & F1(\%)  &  ~& P(\%)    & R(\%)   & F1(\%)  & ~ & P(\%)   & R(\%)  & F1(\%)  \\
		%		\cline{2-4} \cline{6-8} \cline{10-12}
		%		\midrule
		\toprule[0.3mm]
		$\left[\text{BERT}_{base}\right]$ & & & & & & & & & \\ \midrule
		SSE              & 52.53 & 17.95  & 26.76  & & 32.21    & 19.61   & 24.38  &  & 22.02   & 21.19  & 21.60  \\
		TASE                 & 54.16  & 63.63  & 58.52  & & 51.01    & 59.12   & 54.77  &  & 28.73   & 49.39  & 36.33  \\
		SNP-TASE              & 58.12  & 60.50 & 59.28 &  & 58.32   & 60.34 & 59.31  & & -   & -  & -  \\
		LIQUID  & 55.67  &66.24  & 60.50 &  & 55.56   & 61.49  & 58.37 &  & 41.04  & 47.95  & 44.23 \\
		$\text{TOAST}_{tag}$           & 60.10  & 66.61  & 63.19  &  & 59.47    & 61.98   &  60.70  &  & 57.95   & 62.31  & 60.05  \\
		$\text{TOAST}_{joint}$          & \textbf{60.55}  & \textbf{66.82}  & \textbf{63.53}  & & \textbf{60.97}    & \textbf{65.57}   & \textbf{63.19}   & &  \textbf{58.48}  & \textbf{62.64}   & \textbf{60.49}  \\ 
		%		\midrule
		\toprule[0.3mm]
		%		\toprule
		$\left[\text{RoBERTa}_{base}\right]$  & & & &  & & & & & & & \\ \midrule
		SSE                & 55.13  & 18.84  & 
		28.08  & & 33.18    & 20.20   & 25.12  &  & 23.41   & 22.74  & 23.07  \\
		TASE                  & 63.91  & 69.13  & 66.42  & & 64.17    &  68.20   & 66.12  &  & 33.62   & 51.05  & 40.54  \\
		SNP-TASE             & 61.43  & 67.30  & 64.23  & & 32.85    & 22.41   & 26.64  &  & -   & -  & -  \\
		LIQUID  & 66.14  & 72.16  & 69.02 & & 63.80    & 66.21   & 64.98  &  & 47.75   & 56.20  & 51.63  \\
		$\text{TOAST}_{tag}$    & 68.15   & 73.57  &  70.76  & & 66.90   & 68.23   & 67.56  &  & 61.04   & 64.32  & 62.64  \\
		$\text{TOAST}_{joint}$         &\textbf{68.61}  & \textbf{73.89}  & \textbf{71.15} &  & \textbf{68.41 } & \textbf{69.01}   & \textbf{68.71}  & & \textbf{61.86}  & \textbf{64.52}  & \textbf{63.16}  \\ \bottomrule
	\end{tabular*}
\end{table}

\begin{table}[width=\textwidth,cols=4,pos=h]
	%	\centering
	\caption{The Overlapped results for all competing models, including macro-average precision (P), recall (R) and f1 score (F1). }
	\label{tab:overlapped}
	\begin{tabular*}{\tblwidth}{@{}p{2.2cm}p{1.0cm}p{1.0cm}p{1.0cm}cp{1.0cm}p{1.0cm}p{1.0cm}cp{1.0cm}p{1.0cm}p{1.0cm}@{}}
		\toprule[0.3mm]
		\multicolumn{1}{l}{}  & \multicolumn{3}{c}{MSQA}  & \multicolumn{1}{l}{}  & \multicolumn{3}{c}{MSQA-Exp} & \multicolumn{1}{l}{} & \multicolumn{3}{c}{CLEAN} \\ 
		\cline{2-4} \cline{6-8} \cline{10-12}
		\addlinespace
		& P(\%)  & R(\%)  & F1(\%)  &  ~& P(\%)    & R(\%)   & F1(\%)  & ~ & P(\%)   & R(\%)  & F1(\%)  \\
		\toprule
		$\left[\text{BERT}_{base}\right]$ & & & & & & & & & \\ \midrule
		SSE                   & 72.44  &48.05 & 57.77 & & 46.23    & 42.02   & 44.03  & & 65.90   & 67.19  & 66.54  \\
		TASE                  & 77.34 & 77.25  & 77.30 & & 70.39   & 70.03   & 70.21  & & 67.48   & 74.02  & 70.60  \\
		SNP-TASE           &  79.56  & 73.23 & 73.23  & & 74.05    & 68.06   & 70.47 &   & -   & -  & - \\
		LIQUID   & 78.60 & 79.80 & 79.20  & & 72.65  & 71.91  & 72.29 &  & 70.91  & 67.82  & 69.33  \\
		$\text{TOAST}_{tag}$          & 79.48 &  78.78  &  79.12 &  & 73.47    & 71.37   & 72.40 &  & \textbf{82.32}   & 79.41  & 80.84  \\
		$\text{TOAST}_{joint}$        & \textbf{79.88}& \textbf{79.72}  & \textbf{79.80}  & & \textbf{78.49}    & \textbf{76.87}   & \textbf{77.65}   & & 82.16   & \textbf{79.83}  & \textbf{80.98}  \\ 
		%		\midrule
		\toprule[0.25mm]
		$\left[\text{RoBERTa}_{base}\right]$ & & & & & & & & & & & \\ \midrule
		SSE              & 75.65  & 49.25  & 59.66  & & 48.53    &  43.48   & 45.87   & & 66.24  & 67.25  & 66.74 \\
		TASE                & 82.56    & 81.73   & 82.14  & & 78.94    & \textbf{78.81  } & 78.88 &  & 70.81  & 75.68  & 73.16  \\
		SNP-TASE              & 80.72  & 79.83  & 80.27  & & 47.79    & 27.10   & 34.59   & & -   & -  & -  \\
		LIQUID  & 80.90  & 81.50  & 81.20  & &  78.31   & 76.14  & 77.21  & & 75.60  & 74.96  &  75.28  \\
		$\text{TOAST}_{tag}$            & 83.76  & 84.27  & 84.01  & & 79.64   & 77.72   & 78.67  & & 83.77   & 80.58  & 82.15  \\
		$\text{TOAST}_{joint}$    & \textbf{84.06}  & \textbf{84.40}  & \textbf{84.23}  & & \textbf{80.65}    & 78.47  & \textbf{79.54}  & & \textbf{83.81}  & \textbf{80.79}  & \textbf{82.27}  \\ 
		\bottomrule[0.25mm]
	\end{tabular*}
\end{table}

\tableref{tab:exact_match} and \tableref{tab:overlapped} illustrate the performance comparison between the proposed models, $\text{TOAST}_{tag}$ and $\text{TOAST}_{joint}$, and  several strong baselines, including the previous state-of-the-art model LIQUID.
These comparisons are conducted using both the $\text{BERT}_{base}$  and $\text{RoBERTa}_{base}$ encoders. Notably, $\text{TOAST}_{tag}$ exhibits superior performance in EM F1 across all three datasets. However, when employing the $\text{BERT}_{base}$ encoder on the MSQA dataset, $\text{TOAST}_{tag}$ demonstrates slightly lower performance in overlapped F1 compared to LIQUID. Importantly, the performance of $\text{TOAST}_{joint}$ consistently outperforms LIQUID on all three datasets, irrespective of the encoder setting. These results demonstrate the effectiveness of our proposed framework, as well as the efficacy of the joint decoding strategy.
%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%
%dev_precision: 65.31 | dev_recall: 71.22 | dev_f1 = 68.14| dev_macro_precision = 83.38| dev_macro_recall = 82.80| dev_macro_avg_f1 = 83.09
To be more specific, \tableref{tab:exact_match} shows the comparisons of exact match scores among all competing models. We can see that our proposed framework, TOAST, consistently outperforms all other baselines across multiple multi-span question answering datasets. Backed by $\text{BERT}_{base}$,    $\text{TOAST}_{tag}$ achieves EM F1 scores of 63.19 and, 60.70 and 60.05 on the datasets of MSQA, MSQA-Exp and CLEAN, respectively. Moreover, when equipped with the joint decoding strategy, $\text{TOAST}_{joint}$ achieves even higher EM F1 scores of 63.53 and, 63.19 and 60.49 on the same datasets.
These results showcase substantial improvements over the previous state-of-the-art model, LIQUID, with EM F1 score enhancements ranging from 3.03 to 16.26 across various datasets.
Additionally, when utilizing $\text{RoBERTa}_{base}$ instead of  $\text{BERT}_{base}$, $\text{TOAST}_{joint}$ 
achieves EM F1 scores of 71.15, 68.68 and 63.16 on the respective datasets. These scores represent EM F1 improvements of 7.62, 5.49 and 2.67 compared to the previous setup.

The overlapped F1 results shown in \tableref{tab:overlapped} demonstrate similar trends to the EM F1 results. In comparison to the state-of-the-art (SOTA) model LIQUID, $\text{TOAST}_{joint}$ achieves improvements in overlapped F1 scores.
Specifically, when using  $\text{BERT}_{base}$, the improvements are 0.6, 5.36,  11.65 on the MSQA, MSQA-Exp and CLEAN datasets, respectively. Similarly, when employing $\text{RoBERTa}_{base}$, the improvements of 3.03, 2.33, and 6.99 are observed on the same datasets.
When augmenting TOAST with joint decoding, we observed further performance  improvements on both BERT-based and RoBERTa-based encoders. This outcome highlights the effectiveness of the joint decoding strategy, which explicitly combines predictions from multitask modules.
%Moreover, our proposed model demonstrates robustness in effectively generalizing across different datasets without requiring hyperparameter re-tuning. 
%In contrast, SNP-TASE faces challenges in achieving such generalization.
%While SNP-TASE demonstrates satisfactory performance when utilizing the $\text{BERT}_{base}$ encoder, its effectiveness significantly declines when transitioning to the $\text{RoBERTa}_{base}$ encoder. 
%\textcolor{blue}{
Moreover, our proposed model demonstrates robustness in effectively generalizing across different datasets without requiring hyperparameter re-tuning. In contrast, SNP-TASE faces challenge in achieving such generalization. While SNP-TASE demonstrates satisfactory performance when utilizing the $\text{RoBERTa}_{base}$ encoder on MSQA dataset, its effectiveness significantly declines when transitioning to MSQA-Exp dataset with the same hyperparameter configuration. Specifically, SNP-TASE achieves an EM F1 score of approximately 27, which is considerably lower compared to other competing models. These results suggest the potential need for hyperparameter re-tuning when applying the SNP-TASE model to different datasets.
To ensure a fair comparison with other competing models that did not undergo this re-tuning process, we report the raw results of the SNP-TASE model without any adjustments.
%}

% 
%As shown in \tableref{tab:exact_match} and \tableref{tab:overlapped},
%when utilizing the $\text{BERT}_{base}$ encoder, $\text{TOAST}_{tag}$ demonstrates superior performance compared to the previous state-of-the-art model, LIQUID, across all three datasets. 
%However, with the $\text{RoBERTa}_{base}$ encoder, $\text{TOAST}_{tag}$ exhibits slightly lower performance than LIQUID. It is worth nothing that the performance of $\text{TOAST}_{joint}$ surpasses that of  LIQUID on all three datasets, consistently outperforming it across both the $\text{BERT}_{base}$ and $\text{RoBERTa}_{base}$ encoder settings, which shows the effectiveness of our proposed framework as well as of joint decoding strategy.

% 1. joint decoding 策略有效
% 2. 我们最好的模型比之前SOTA提高了xx xx xx
% 
%We can see that our proposed framework TOAST  outperforms all the other baselines on all multi-span question answering datasets, except Quoref, under both automatic metrics and human evaluation metrics.

%%%%%%%%%%%%

%%%%%%%%%%
%Our proposed framework, TOAST, exhibits superior performance compared to all other baselines across multiple multi-span question answering datasets, with the exception of Quoref, as demonstrated by both automatic metrics and human evaluation. This discrepancy can potentially be attributed to the Quoref dataset's emphasis on evaluating coreference resolution capabilities.
%Additionally, when augmenting TOAST with joint decoding, referred to as $\text{TOAST}_{joint}$, we observed further improvements in performance on both BERT-based and RoBERTa-based encoders. This outcome highlights the effectiveness of the joint decoding strategy, which explicitly combines predictions from multitask modules.
%%%%%%%%%%%%%%%
%In addition, $\text{TOAST}_{joint}$, the TOAST framework equipped with joint decoding, outperforms vanilla TOAST on both BERT-based and RoBERTa-based encoders
%by xx percent
%,  showing the effectiveness of the joint decoding strategy that explicitly combines the predictions from multitask modules.

%%%%%%%%%%%%%%%%%%%%Table 6
%\begin{table}[bth!]
%	\centering
%	\caption{The human evaluation results for all competing models, including the span-level evaluation (completeness, correctness, distinctness), and the question-level evaluation (overall quality). }
%	\label{tab:human}
%	\begin{tabular*}{\tblwidth}{@{}lcccccccccccc@{}}
%		\toprule
%		\multicolumn{1}{l}{} & \multicolumn{3}{c}{Span-level Evaluation} & \multicolumn{1}{c}{Question-level Evaluation} \\ \midrule
%		& Completeness (1-5)   & Correctness (1-5) & Distinctness (1-5) & Overall (1-5)  \\
%		\midrule
%		SSE                  & 00.00   & 00.00   & 00.00  & 00.00  \\
%		TASE                 & 00.00   & 00.00   & 00.00  & 00.00  \\
%		SNP-TASE             & 00.00   & 00.00   & 00.00  & 00.00 \\
%		LIQUID             & -   & -   & -  & - \\
%		$\text{TOAST}_{tag}$          & 00.00   & 00.00   & 00.00  & 00.00  \\
%		$\text{TOAST}_{joint}$        & 00.00   & 00.00   & 00.00  & 00.00  \\ \bottomrule
%	\end{tabular*}
%\end{table}
%%%%%%%%%%%%%%%%%%%%%%%

In addition, \figref{fig:human_eval} presents the comparison results of human evaluation on the overall quality of the complete answer, as well as three aspects at the span-level: completeness, correctness and distinctness. 
Specifically, \figref{fig:bert_msqa}  and \figref{fig:roberta_msqa} illustrate the comparisons on the MSQA dataset using $\text{BERT}_{base}$ and $\text{RoBERTa}_{base}$, respectively.
Similarly, \figref{fig:bert_clean} and \figref{fig:roberta_clean} depict the comparisons on the CLEAN dataset. As shown in \figref{fig:human_eval}, the competing models demonstrate superior performance in terms of \emph{completeness} and \emph{distinctness} when extracting spans from the MSQA dataset compared to the CLEAN dataset. This observation can be attributed to the prevalence of entity-type questions in the MSQA dataset (see \tableref{tab:answer_types}), which are typically shorter and relatively easier to extract completely using tagging models.

\begin{figure*}[!ht]
	\centering
	\begin{subfigure}{.49\textwidth}
		\centering
		\includegraphics[width=0.99\linewidth]{bert_msqa}
		\caption{Comparisons on MSQA based on $\text{BERT}_{base}$}
		\label{fig:bert_msqa}
	\end{subfigure}%
	\begin{subfigure}{.49\textwidth}
		\centering
		\includegraphics[width=0.99\linewidth]{roberta_msqa}
		\caption{Comparisons on MSQA based on $\text{RoBERTa}_{base}$}
		\label{fig:roberta_msqa}
	\end{subfigure}%

	\begin{subfigure}{.49\textwidth}
		\centering
		\includegraphics[width=0.99\linewidth]{bert_clean}
		\caption{Comparisons on CLEAN based on $\text{BERT}_{base}$}
		\label{fig:bert_clean}
	\end{subfigure}%
	\begin{subfigure}{.49\textwidth}
		\centering
		\includegraphics[width=0.99\linewidth]{roberta_clean}
		\caption{Comparisons on CLEAN based on $\text{RoBERTa}_{base}$}
		\label{fig:roberta_clean}
	\end{subfigure}%

	\caption{Human evaluations on MSQA and CLEAN datasets. }
	\label{fig:human_eval}
\end{figure*}

Our proposed models, $\text{TOAST}_{tag}$ and $\text{TOAST}_{joint}$, demonstrate an overall superior performance in the human evaluation.
Specifically, concerning the MSQA dataset, TOAST outperforms the strong baselines TASE and LIQUID in terms of the span correctness and the overall answer quality (see \figref{fig:bert_msqa} and \figref{fig:roberta_msqa}). However, it shows a slight decline in the completeness and distinctiveness aspects of spans when using $\text{RoBERTa}_{base}$ (see  \figref{fig:roberta_msqa}). 
We observe that the LIQUID model tends to extract keywords from reference spans of the description type, leading to the fragmentation of answer spans into multiple shorter spans, such as single-word nouns. While these shorter spans are more likely to achieve enhanced completeness and distinctiveness at the span level, but this does not necessarily imply that LIQUID is more effective. In fact, $\text{TOAST}_{joint}$ consistently outperforms them in terms of span correctness and the overall quality. 
On the other hand, in the comparison of different models on the CLEAN dataset,
the TOAST models demonstrate marginal improvements across all aspects  compared to the competing models. 
%This is because that most of questions in CLEAN dataset are description type (see Table 4). 
Specifically, the $\text{TOAST}_{joint}$ model using $\text{RoBERTa}_{base}$ achieves the highest overall score of 4.34 (ranging from 1 to 5), representing a 0.56 score improvement over the TASE model. Similarly, the $\text{TOAST}_{joint}$ model using $\text{BERT}_{base}$ achieves an overall score of 4.3 which demonstrates a 0.46 score improvement  over the TASE model.
At the span level, $\text{TOAST}_{joint}$ using $\text{RoBERTa}_{base}$ exhibit enhancements of 0.64, 0.52, and 0.54 scores of in terms of completeness, distinctness and correctness, respectively. Additionally, $\text{TOAST}_{joint}$ using  $\text{BERT}_{base}$ demonstrates improvements of 0.26, 0.2, and 0.38 scores in these respective aspects.

\subsubsection{Case Studies}
\label{sec:case}
Next, we perform case studies to examine the impact of our proposed methods on answer extraction. 
The case studies utilize running examples from the MSQA and CLEAN datasets, which are presented in \tableref{tab:msqa_case} and \tableref{tab:clean_case}, respectively. 
In the context, the gold answer spans are annotated in blue color to facilitate identification.

\begin{table}[width=\textwidth,cols=3,pos=h]
	\small
	\caption{The case studies from the MSQA dataset.}
	\label{tab:msqa_case}
	\begin{tabular}{p{21em}|c|cp{22em}}
		\hline
		\multicolumn{1}{c|}{Example} & Model & Extracted Answer \\ 
		\hline
		\multirow{5}{*}[2pt]{\begin{tabular}{@{}p{21em}@{}}
				\textbf{Question}: what is the proximal attachment of the flexor carpi ulnaris in humans \\
				\textbf{Context}: The flexor carpi ulnaris muscle (or FCU) is a muscle of the human forearm that acts to flex and adduct (medial deviation) the hand. The flexor carpi ulnaris muscle arises from two heads, the {\color{blue}humeral} and {\color{blue}ulnar} heads, which are connected by a tendinous arch beneath which the ulnar nerve and artery pass. \\
				\textbf{Gold Answer}: 
				[``{\color{blue}humeral}'', ``{\color{blue}ulnar}'']
		\end{tabular}}
		&SSE &  \begin{tabular}{p{22.5em}} \vskip -1mm 
			[``{\color{blue} humeral} and {\color{blue} ulnar} , connected by a tendinous arch''] \vskip -1mm
		\end{tabular} \\
		\cline{2-3}
		& TASE & \begin{tabular}{p{22.5em}} 
			\vskip -1mm	
			[``medial deviation'', ``the hand''] \vskip -1mm
		\end{tabular} \\
		\cline{2-3}
		& LIQUID & \begin{tabular}{p{22.5em}} \vskip -1mm
			[``flex'', ``medial deviation'', ``the hand'', ``tendinous''] \vskip -1mm
		\end{tabular}  \\
		\cline{2-3}
		& $\text{TOAST}_{tag}$ & \begin{tabular}{p{22.5em}}  \vskip -1mm 
			[``hand'', ``{\color{blue}humeral}'', ``{\color{blue}ulnar}'']  \vskip -1mm
		\end{tabular} \\
		\cline{2-3}
		& $\text{TOAST}_{joint}$ & \begin{tabular}{p{22.5em}} \vskip -1mm
			[``{\color{blue}humeral}'', ``{\color{blue}ulnar}''] \vskip -1mm
		\end{tabular} \\
		\cline{2-3}
		\hline
		\multirow{5}{*}[2pt]{\begin{tabular}{@{}p{21em}@{}}
				\textbf{Question}: popular styles of music in the middle ages \\ 
				\textbf{Context}: Medieval music consists of songs , instrumental pieces ... Medieval music was an era of Western music, including {\color{blue}liturgical music} (also known as sacred) used for the church, and {\color{blue} secular music}, non-religious music. Medieval music includes solely vocal music, such as {\color{blue} Gregorian chant} and {\color{blue} choral music} (music for a group of singers), solely instrumental music ... practice era , a period of shared music writing practices ... \\
				\textbf{Gold Answer}: 
				[``{\color{blue}liturgical music}'', ``{\color{blue}secular music}'', ``{\color{blue}Gregorian chant}'', ``{\color{blue}choral music}'']
		\end{tabular}}
		&SSE &  \begin{tabular}{p{22.5em}} \vskip -1mm 
			[``{\color{blue} Gregorian chant} and {\color{blue} choral music}''] \vskip -1mm
		\end{tabular} \\
		\cline{2-3}
		& TASE & \begin{tabular}{p{22.5em}} 
			\vskip -1mm	
			[``{\color{blue}secular music}'', ``{\color{blue}Gregorian chant}'', ``{\color{blue}choral music}'', ``Baroque'', ``Classical music'', ``Romantic music'']  
			\vskip -1mm
		\end{tabular} \\
		\cline{2-3}
		& LIQUID & \begin{tabular}{p{22.5em}} \vskip -1mm
			[``Baroque'', ``Classical music'', ``Romantic''] \vskip -1mm
		\end{tabular}  \\
		\cline{2-3}
		& $\text{TOAST}_{tag}$ & \begin{tabular}{p{22.5em}}  \vskip -1mm 
			[``{\color{blue}liturgical music}'', ``{\color{blue}secular music}'', ``{\color{blue}Gregorian chant}'', ``{\color{blue}choral music}'']
			\vskip -1mm
		\end{tabular} \\
		\cline{2-3}
		& $\text{TOAST}_{joint}$ & \begin{tabular}{p{22.5em}} \vskip -1mm [``{\color{blue}liturgical music}'', ``{\color{blue}secular music}'', ``{\color{blue}Gregorian chant}'', ``{\color{blue}choral music}'']
			\vskip -1mm
		\end{tabular} \\
		\cline{2-3}
		\hline
		\multirow{5}{*}[6pt]{\begin{tabular}{@{}p{21em}@{}}
				\textbf{Question}: how long does it take for the milky way to rotate \\
				\textbf{Context}: The galactic year, also known as a cosmic year, is the duration of time required for the Sun to orbit once around the center of the Milky Way Galaxy. Estimates of the length of one orbit range from 225 to 250 million terrestrial years. The Solar System is traveling at an average speed of 828,000 km / h (230 km / s) or 514,000 mph (143 mi / s) within its trajectory around the galactic center, a speed at which an object could circumnavigate the Earth 's equator in 2 minutes and 54 seconds; ... \\
				\textbf{Gold Answer}: 
				%				[``{\color{blue}galactic year}'', ``{\color{blue}cosmic year}''] 
				Unanswerable \vskip 2mm
		\end{tabular}}
		&SSE &  \begin{tabular}{p{22.5em}} \vskip -1mm 
			[``2 minutes and 54 seconds''] \vskip -1mm
		\end{tabular} \\
		\cline{2-3}
		& TASE & \begin{tabular}{p{22.5em}} 
			\vskip -1mm	
			[``galactic year'', ``million'', ``years'', ``km / h'', ``514,000 mph'', ``2 minutes and 54 seconds''] \vskip -1mm
		\end{tabular} \\
		\cline{2-3}
		& LIQUID & \begin{tabular}{p{22.5em}} \vskip -1mm
			[``828,000 km / h'', ``514,000 mph (143 mi / s)'', ``2 minutes and 54 seconds''] \vskip -1mm
		\end{tabular}  \\
		\cline{2-3}
		& $\text{TOAST}_{tag}$ & \begin{tabular}{p{22.5em}}  \vskip -1mm 
			[``828,000 km / h'', ``514,000 mph (143 mi / s) '', ``2 minutes and 54 seconds'']  \vskip -1mm
		\end{tabular} \\
		\cline{2-3}
		& $\text{TOAST}_{joint}$ & \begin{tabular}{p{22.5em}} \vskip -1mm
			[``828,000 km / h'', ``514,000 mph (143 mi / s) '', ``2 minutes and 54 seconds''] \vskip -1mm
		\end{tabular} \\
		\cline{2-3}
		\hline
	\end{tabular}
\end{table}

\begin{table}[width=\textwidth,cols=4,pos=htp]	\caption{The case studies from the CLEAN dataset.}
	\label{tab:clean_case}
	\begin{tabular}{p{23em}|c|cp{20em}}
		\hline
		\multicolumn{1}{c|}{Example} & Model & Extracted Answer \\ 
		\hline
		\multirow{5}{*}[-2pt]{\begin{tabular}{@{}p{22em}@{}}
				\textbf{Question}: 甘肃省哪些城市经济比较发达 \\ (Which cities in Gansu Province have relatively developed economies) \\
				\vskip -1mm
				\textbf{Context}: 论GDP人均，{\color{blue}嘉峪关}，{\color{blue}金昌} \\ \quad \quad \quad \quad ~论GDP总量{\color{blue}兰州} ，{\color{blue}庆阳} \\ (In terms of per capita GDP, {\color{blue}Jiayuguan} and {\color{blue}Jinchang}. In terms of total GDP, {\color{blue}Lanzhou} and {\color{blue}Qingyang}.) \\
				\vskip -1mm
				\textbf{Gold Answer}: 
				[``{\color{blue}嘉峪关}'', ``{\color{blue}金昌}'', ``{\color{blue}兰州}'', ``{\color{blue}庆阳}'']  \vskip -1mm \quad \\
		\end{tabular}}
		&SSE &  \begin{tabular}{p{19em}} \vskip -1mm 
			[``{\color{blue}嘉峪关}，{\color{blue}金昌}''] \vskip -1mm
		\end{tabular} \\
		\cline{2-3}
		& TASE & \begin{tabular}{p{19em}} 
			\vskip -1mm	
			[``{\color{blue}兰州}''，``{\color{blue}庆阳}'']  \vskip -1mm
		\end{tabular} \\
		\cline{2-3}
		&LIQUID &  \begin{tabular}{p{19em}} \vskip -1mm 
			[``{\color{blue}嘉峪关}，{\color{blue}金昌}''] \vskip -1mm
		\end{tabular} \\
		\cline{2-3}
		& $\text{TOAST}_{tag}$ & \begin{tabular}{p{19em}}  \vskip -1mm 
			[``{\color{blue}嘉峪关}'', ``{\color{blue}金昌}'', ``{\color{blue}兰州}'', ``{\color{blue}庆阳}'']  \vskip -1mm
		\end{tabular} \\
		\cline{2-3}
		& $\text{TOAST}_{joint}$ & \begin{tabular}{p{19em}} \vskip -1mm
			[``{\color{blue}嘉峪关}'', ``{\color{blue}金昌}'', ``{\color{blue}兰州}'', ``{\color{blue}庆阳}''] \vskip -1mm
		\end{tabular} \\
		\cline{2-3}
		\hline
		\multirow{5}{*}[-2pt]{\begin{tabular}{@{}p{22em}@{}}
				\vskip -4mm
				\textbf{Question}: 细菌和古细菌有什么区别\\ (What are the differences between bacteria and archaea)  \\
				\vskip -1mm
				\textbf{Context}: 在细胞结构和代谢上，古菌在很多方面接近其它原核生物 ... {\color{blue}古菌}还具有一些其它特征。与大多数细菌不同，它们{\color{blue}只有一层细胞膜而缺少肽聚糖细胞壁}。而且，绝大多数{\color{blue}细菌和真核生物的细胞膜中的脂类主要由甘油酯组成}，而{\color{blue}古菌的膜脂由甘油醚构成} ... \\ (In terms of cellular structure and metabolism, ... {\color{blue}Archaea} also possess some other characteristics. Unlike most bacteria, they {\color{blue}only have a single layer of cell membrane and lack peptidogly can cell walls}. Additionally, while the cell membranes of most {\color{blue}bacteria and eukaryotes are predominantly composed of glycerol esters}, {\color{blue}the membrane lipids of archaea are composed of glycerol ethers}...) \\ 
				\vskip -1mm
				\textbf{Gold Answer}: 
				[``{\color{blue}古菌}'', ``{\color{blue}只有一层细胞膜而缺少肽聚糖细胞壁}'', ``{\color{blue}细菌和真核生物的细胞膜中的脂类主要由甘油酯 组成}'', ``{\color{blue}古菌的膜脂由甘油醚构成}'']
		\end{tabular}}
		&SSE &  \begin{tabular}{p{19em}} \vskip -1mm 
			[``在细胞结构和代谢上，古菌在很多方面接近其它原核生物 ...'']\vskip -0.1mm
		\end{tabular} \\ 
		\cline{2-3}
		& TASE & \begin{tabular}{p{19em}} 
			\vskip -0.1mm	
			[``大多数细菌'', ``同'', ``它们'', ``{\color{blue}只有一层细胞膜而缺少肽聚糖细胞壁}'', ``绝大多数细菌和真核生物'', ``{\color{blue}细胞膜中}'', ``{\color{blue}脂类主要由甘油酯组成}，而{\color{blue}古菌} '', ``{\color{blue}膜脂由甘油醚构成}'']
			\vskip -0.1mm
		\end{tabular} \\
		\cline{2-3}
		&LIQUID &  \begin{tabular}{p{19em}} \vskip -0.5mm 
			[``{\color{blue}只有一层细胞膜而缺少肽聚糖细胞壁}，{\color{blue}绝大多数细菌和真核生物的细胞膜中的脂类主要由甘油酯组成},{\color{blue}而古菌的膜脂由甘油醚构成}''] \vskip -0.1mm
		\end{tabular} \\
		\cline{2-3}
		& $\text{TOAST}_{tag}$ & \begin{tabular}{p{19em}}  \vskip -0.5mm 
			[``{\color{blue}只有一层细胞膜而缺少肽聚糖细胞壁}'', ``{\color{blue}细菌和真核生物的细胞膜中的脂类主要由甘油酯组成}'', ``{\color{blue}古菌的膜脂由甘油醚构成}'']
			\vskip -0.1mm
		\end{tabular} \\
		\cline{2-3}
		& $\text{TOAST}_{joint}$ & \begin{tabular}{p{19em}} \vskip -1mm [``{\color{blue}只有一层细胞膜而缺少肽聚糖细胞壁}'', ``{\color{blue}细菌和真核生物的细胞膜中的脂类主要由甘油酯组成}'', ``{\color{blue}古菌的膜脂由甘油醚构成}'']
			\vskip -0.3mm
		\end{tabular} \\
		\cline{2-3}
		\hline
		\multirow{5}{*}[-2pt]{\begin{tabular}{@{}p{22em}@{}}
				\vskip -1mm
				\textbf{Question}: 宿州学院的特色专业是什么\\ (What are the characteristic majors of Suzhou University)  \\
				\vskip -1mm
				\textbf{Context}: {\color{blue}会计}或{\color{blue}英语}吧，西校区{\color{blue}人力资源管理}，{\color{blue}地理科学}不错\\ ({\color{blue}Accounting} or {\color{blue}English}, {\color{blue}human resource management} at West Campus, good in {\color{blue}geography science}) \\ 
				\vskip -1mm
				\textbf{Gold Answer}: 
				[``{\color{blue}会计}'', ``{\color{blue}英语}'', ``{\color{blue}人力资源管理}'', ``{\color{blue}地理科学}'']
		\end{tabular}}
		&SSE &  \begin{tabular}{p{19em}} \vskip -1mm 
			[``{\color{blue}会计}或{\color{blue}英语}''] \vskip -0.5mm
		\end{tabular} \\
		\cline{2-3}
		& TASE & \begin{tabular}{p{19em}} 
			\vskip -0.5mm	
			[``{\color{blue}会计}或{\color{blue}英语}'', ``人'',``{\color{blue}管理}'' ,`` 地'',`` 科学'']
			\vskip -0.01mm
		\end{tabular} \\
		\cline{2-3}
		&LIQUID &  \begin{tabular}{p{19em}}
			\vskip -1mm 
			[``{\color{blue}会计}或{\color{blue}英语}''] \vskip -0.5mm
		\end{tabular} \\
		\cline{2-3}
		& $\text{TOAST}_{tag}$ & \begin{tabular}{p{19em}}  \vskip -1mm 
			[``{\color{blue}会计}'',``{\color{blue}英语}'', ``人'']
			\vskip -0.5mm
		\end{tabular} \\
		\cline{2-3}
		& $\text{TOAST}_{joint}$ & \begin{tabular}{p{19em}} \vskip -1mm [``{\color{blue}会计}'', ``人'']
			\vskip -0.5mm
		\end{tabular} \\
		\cline{2-3}
		\hline
	\end{tabular}
\end{table}

In \tableref{tab:msqa_case}, the first example inquires about the proximal attachment of the flexor carpi ulnaris. TASE and LIQUID primarily focus on the flexion  and adduction functions of the flexor carpi ulnaris muscle. In constract, TOAST models accurately identify that the muscle originates from the humeral and ulnar heads, which are its true proximal attachments.  
The second example explores the prevalent music styles during the Middle Ages. TASE and LIQUID mistakenly categorize the style of composers (e.g. Baroque) as  music styles, whereas TOAST models correctly identify all popular music styles.
These cases exemplify the effectiveness of TOAST in comprehending the query intention and semantics of the associated context. 
The third example, which seeks to determine the duration of the Milky Way's rotation, presents a failure case for TOAST. The given context introduces the concept of a galactic year as a measure of time for Milky Way rotation. However, the provided information is insufficient to answer the question. Instead of refusing to answer, we observe that the TASE model extracts the concept of a "galactic year," albeit with multiple broken spans. Both LIQUID and TOAST models extract information related to the traveling speed of the Solar System and the time it takes to circumnavigate the Earth's equator at this speed, which pertain to the Solar System rather than the Milky Way. Thus, TOAST and other competing models may struggle to handle cases with intricate semantic relations.

Likewise, the examples in \tableref{tab:clean_case} from the CLEAN dataset demonstrate similar trends.
TOAST models excel in accurately and comprehensively extracting description answers from the given contexts. For instance, in the second example from \tableref{tab:clean_case}, the TASE model tends to fragment the description answer into multiple incomplete spans, whereas TOAST models capture the boundary information of the long description span, thus precisely extracting the entire answer span. 
The running examples from both datasets emphasize the effectiveness of the proposed model.

%	\input{related}
\section{Related Work}
\label{sec:related}
In this section, we briefly summarize previous works that are relevant to extractive reading comprehension (RC) datasets and various modeling approaches employed for extractive RC tasks.
\subsection{Extractive RC Datasets}
\label{sec:related_dataset}
\subsubsection{Single-Span RC Datasets}
Most existing RC datasets, such as SQuAD~\citep{rajpurkar2016squad}, SQuAD2.0~\citep{rajpurkar2018know}, SearchQA~\citep{DBLP:journals/corr/DunnSHGCC17}, HotpotQA~\citep{yang2018hotpotqa}, TriviaQA~\citep{DBLP:conf/acl/JoshiCWZ17} and QuAC~\citep{DBLP:conf/emnlp/ChoiHIYYCLZ18}, contain only single-span questions whose answers are limited to a single text span from the provided context, referred as single-span RC datasets. 
SQuAD consists of passages from Wikipedia as contexts and associated questions whose answers are spans from the passage. SQuAD 2.0 expands SQuAD by adding some questions that are designed to be unanswerable.
HotpotQA dataset extends the answer context from single passage to multiple passages. Since the RC datasets like SQuAD or HotpotQA are built by having humans read a given context, write questions and choose a specific answer span, the annotators may tend to make use of words from the answer text which potentially makes  their questions easier to answer.  
To address this concern, one possible solution is to create datasets where questions are not specifically designed with a context in mind. 
The TriviaQA dataset consists of questions authored by trivia enthusiasts, while the QuAC dataset prevents the annotators (who also serve as questioners) from seeing the full context.
However, all of these RC datasets primarily focus on single-span questions, which does not align with the distribution of real-world user questions. 
\subsubsection{Multi-Span RC Datasets}
The complete answer to a real-world user question could consist of multiple text spans. 
Furthermore, a user question can even have multiple intents, where the answer to each intent is composed of one or more spans. 
We refer to the datasets focus on such multi-span questions as multi-span RC datasets.
Natural Question~\citep{DBLP:journals/tacl/KwiatkowskiPRCP19} and Quoref~\citep{DBLP:conf/emnlp/DasigiLMSG19} both contain multi-span questions. 
The Natural Question dataset incorporates real anonymized queries to the Google search engine. 
Quoref is used to validate models with the ability to resolve co-reference among entities. %, which is not for general capability validation of models.
However, the proportion of multi-span answers in Natural Question and Quoref is relatively low, around 2\% and 10\% respectively. 
The DROP~\citep{DBLP:conf/naacl/DuaWDSS019} dataset which consists of complex questions on history and football games, requires discrete reasoning over the content of contexts, including  co-reference resolution and arithmetic operations, such as addition, sorting and counting. 
Although the questions could be multi-span, the answer spans are almost exclusively semantically homogeneous and related to numeric values. 
MASH-QA~\citep{DBLP:conf/aaai/PangLGXSC19} is a domain-specific dataset that extends the answer space to general text types in the healthcare domain.
Recently, \cite{li2022multispanqa} propose the MultiSpanQA dataset, which consists of open-domain multi-span questions. The MultiSpanQA dataset is derived from Natural Question, whose questions are real queries issued to the Google search engine. 
Each question is associated with a context extracted from a retrieved Wikipedia page.  
MultiSpanQA also has an expanded variant by introducing single-span and unanswerable questions, namely MultiSpanQA (expand).

The above datasets are all in English. The TyDi QA dataset~\citep{DBLP:journals/tacl/ClarkPNCGCK20} offers question-answer pairs in 11 typologically diverse languages, including Arabic, Bengali, Kiswahili, Russian and Thai.  
The various languages in the dataset bring up new challenges such as morphological variation and word segmentation.
To address the scarcity of Arabic datasets for the RC task, the QRCD dataset~\citep{DBLP:journals/ipm/MalhasE22} provides valuable resources. 
Additionally, the CMQA dataset~\citep{DBLP:conf/coling/JuWZZ0022} introduces a new annotate scheme that labels both fine-grained answers and conditions  as well as the hierarchical relations in-between.
% requires models to extract  conditions and hierarchical relations for multi-span answers. 
CMQA is the first public multi-span QA dataset in Chinese, 
however it formulates a new task of conditional question answering.
%However, the multi-span Chinese RC datasets 
To ameliorate the situation of the lack of Chinese multi-span RC datasets, we propose a Chinese multi-span question answering dataset (CLEAN), which consists of multi-span questions in open domain and supports to cast RC as answer extraction task.

%Dasigi et al. propose Quoref~\cite{DBLP:conf/emnlp/DasigiLMSG19}

%\subsection{Neural-based RC Models}
\subsection{Neural Models for RC}
\label{sec:related_models}
Research in reading comprehension grows rapidly, and many successful neural-based RC models have been proposed in this area. 
%As discussed in \secref{sec:related_dataset}, the extractive RC datasets support to cast RC as answer extraction task.
Typically, neural  models~\citep{DBLP:conf/aaai/PangLGXSC19,DBLP:conf/iclr/Wang017a,DBLP:conf/iclr/XiongZS17} for RC are composed of two components, a context encoder and an answer decoder. 
The context encoder is used to encode the information of questions, contexts and their interactions in-between. Then, the answer decoder aims to generate the answer texts based on outputs of the context encoder. 
To make the answer decoder compatible with the answer extraction task, 
Pointer Network~\citep{DBLP:conf/nips/VinyalsFJ15} model has been adopted to
% tackle the problem that 
%generates answer texts from contexts. 
copy tokens from the given contexts as answers~\citep{DBLP:conf/acl/KadlecSBK16,DBLP:conf/emnlp/TrischlerYYBSS16}.
\cite{DBLP:conf/iclr/Wang017a} proposed a boundary model, which utilized Pointer Network to predict the start and end indices for an answer span.
%\ZY{single token - single span - multispan}
%Boundary Model
\cite{DBLP:conf/iclr/SeoKFH17} proposed an alternative way for the implementation of answer decoder, that built neural position classifiers upon the encoder outputs, predicting the start and end indices of the answer span in the context.

% neural layer unifies the components of encoder and decoder together that 
Recently, the RC models upgrade the context encoder using pre-trained language models (PrLMs)~\citep{radford2018improving,kenton2019bert,liu2019roberta,lee2020biobert,gu2021domain} 
%such as GPT~\citep{radford2018improving}, BERT~\citep{kenton2019bert} and RoBERTa~\citep{liu2019roberta}
, benefiting from the invention of Transformer~\citep{vaswani2017attention} blocks.
%Benefiting from nowadays pretrained language models (PrLMs) based on Transformer~\cite{vaswani2017attention} blocks, recent RC models upgrades the context encoder using PrLMs such as BERT. 
%the context encoder and answer decoder can be unified into a standard algorithm that utilize PrLMs such as BERT to encode inputs, then predict the start position and end position for the answer span.
\cite{DBLP:conf/naacl/DevlinCLT19}  proposed a standard extractive model for  single-span RC that utilizes BERT to encode inputs, then builds position classifiers to predict where the answer span starts and ends.
However, the answer decoder, whether implemented with Pointer Network or position classifiers, predicts start and end position independently, thus can not distinguish the different answer spans properly.
%Pang et al. proposed HAS-QA~\cite{} which built the conditional pointer network and aggregators to model multiple answer spans.
~\cite{DBLP:conf/emnlp/ZhuAJ0R20} proposed MultiCo which used a contextualized sentence selection method to capture the relevance among multiple sentence-based answer spans in order to form an answer with multiple sentences.
%However, such single-span extractive model is not suitable for multi-span RC task which can be formulated as multi-span extraction.
These models are not well adapted to multi-span RC which can be formulated as more flexible task of multi-span extraction where each span can be a word, phrase, sentence or any continuous string of text.

%the start position and end position of the answer span. 
%PrLMs unify the context encoder and answer decoder as a standard algorithm, that  
%\subsubsection{Single-span Models}
%~\citep{yoon2022,DBLP:journals/corr/abs-2302-01691} 
Extracting a variable number of spans from an input text can be commonly cast as a sequence tagging problem.
\cite{segal2020simple} proposed using a sequence tagging model for multi-span extraction, which predicts whether each token is part of an answer. \cite{yoon2022} employed a similar sequence tagging approach to address extractive question answering~\citep{DBLP:journals/bmcbi/NaseemDKK22}  in the biomedical domain.
\cite{li2022multispanqa} also adopted the tagging model architecture, integrating two sub-tasks: predicting the number of spans to extract and annotating the answer structure within their proposed dataset to capture global information.
ADRAV~\citep{hu2023biomedical} proposed a dynamic routing and answer voting method to further make full use of the hidden layer knowledge of pre-trained models.
More recently, LIQUID~\citep{lee2023liquid} was introduced to  automatically generate list-style QA pairs from unlabeled corpora. LIQUID extracted named entities from the summarized text as candidate answers and incorporated synthetic data in the tagging model. 
These methods harness the extensive factual knowledge embedded in powerful contextualized encoders (PrLMs) or synthesized data that resolves around named entities. 
As a result, they have demonstrated promising performance in extracting  multi-span answers, particularly for factoid questions where the answers correspond entities.
%Benefiting from the rich factual knowledge implied in the powerful contextualized encoders (PrLMs) or synthesized data centered around name entities, these methods have achieved promising performance on multi-span answer extraction, especially for factoid questions where the answers are entities.
%These methods have been achieved promising performance on multi-span answer extraction, especially for factoid questions whose answers are entities, benefiting from the rich factoid knowledge implied in the powerful context encoder like PrLMs.
However, these methods do not take into account the information of span boundaries in terms of the questions, and thus have very limited capabilities of precisely drawing a description answer. 
%However, for these methodswhich are implied in the powerful context encoder like PrLMs, they are failed to care span boundaries .
Compared to these approaches, TOAST incorporates the semantic and syntactic information of span boundaries by explicitly modeling the implicit neighboring transitions in-between the adjacent tokens or words, which benefits the span boundary identification.

%	\input{conclusion}
\section{Implications}
Our main aim in this study is to address the problem of multi-span question answering, that has widespread implications for real-life applications such as virtual assistants. Although existing reading comprehension (RC) datasets and models have demonstrated effectiveness in answering factoid questions, they encounter difficulties when it comes to handling the complexities inherent in descriptive questions.

We propose the TOAST framework, which is designed for the extraction of multi-span answers, and complement it with a newly created RC dataset named CLEAN that encompasses a significant number of descriptive questions. In \secref{sec:evaluation}, we demonstrate the effectiveness of the components integrated within TOAST. A key insight in the extraction of multi-span answers lies in the value placed on boundary knowledge, particularly through token-based neighboring transitions. 
To capture this information, we employ an auxiliary task that incorporates token-based transition knowledge, enabling us to jointly learn the sequence tagging task and the transition classification task.
Additionally, we further demonstrate the usefulness of the joint decoding strategy in TOAST, which not only implicitly integrates neighboring transition knowledge but also explicitly combines predictions from the enhanced tagging model.

\section{Conclusion}
\label{sec:conclusion}
In this paper, we propose a joint learning framework named TOAST, which specializes in token-based neighboring transitions to capture the boundary information of answer spans through adjacent word relations for multi-span question answering. Our approach extracts high-quality multi-span answers and is applicable to both alphabet languages like English and logographic languages like Chinese. Furthermore, we introduce an open-domain Chinese multi-span question answering dataset, named CLEAN, that incorporates crafted long answers as contexts. CLEAN effectively bridges the semantic gap by leveraging insights from public contributors, addressing the limitation of existing datasets. Results show that TOAST is more effective than a number of other strong baselines across three publicly available datasets.

	\section*{Acknowledgements}
	This research was supported by the Natural Science Foundation of Zhejiang Province, China (Grant No. LQ22F020027), Fundamental Research Funds of Zhejiang Sci-Tech University (Grant No. 23232138-Y), Liaoning Provincial Natural Science Foundation of China (Grant No. 2022-KF-21-01) and the Key Research and Development Program of Zhejiang Province, China (Grant No. 2023C01041 and 2022C01079).

	\bibliographystyle{cas-model2-names}
	% 
	\bibliography{refs}
\end{document}

### 2023-10-01 paper.tex
kbs

@@
 % !TeX program = xelatex 
-%  LaTeX support: latex@mdpi.com 
-%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.
+%% 
+%% Copyright 2019-2021 Elsevier Ltd
+%% 
+%% This file is part of the 'CAS Bundle'.
+%% --------------------------------------
+%% 
+%% It may be distributed under the conditions of the LaTeX Project Public
+%% License, either version 1.2 of this license or (at your option) any
+%% later version.  The latest version of this license is in
+%%    http://www.latex-project.org/lppl.txt
+%% and version 1.2 or later is part of all distributions of LaTeX
+%% version 1999/12/01 or later.
+%% 
+%% The list of all files belonging to the 'CAS Bundle' is
+%% given in the file `manifest.txt'.
+%% 
+%% Template article for cas-dc documentclass for 
+%% double column output.
 
-%=================================================================
-\documentclass[mathematics,article,submit,moreauthors]{Definitions/mdpi}
+\documentclass[a4paper,fleqn]{cas-dc}
 
-%--------------------
-% Class Options:
-%--------------------
-%----------
-% journal
-%----------
-% Choose between the following MDPI journals:
-% acoustics, actuators, addictions, admsci, adolescents, aerobiology, aerospace, agriculture, agriengineering, agrochemicals, agronomy, ai, air, algorithms, allergies, alloys, analytica, analytics, anatomia, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arm, arthropoda, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, cyber, dairy, data, ddc, dentistry, dermato, dermatopathology, designs, devices, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, future, futureinternet, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, grasses, gucdd, hazardousmatters, healthcare, hearts, hemato, hematolrep, heritage, higheredu, highthroughput, histories, horticulturae, hospitals, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijpb, ijtm, ijtpp, ime, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jcto, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jvd, jzbg, kidneydial, kinasesphosphatases, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing,\gdef\@continuouspages{yes}} nanomaterials, ncrna, ndt, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, %%nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, %oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology,\gdef\@ISSN{2813-0618}\gdef\@continuous pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, platforms, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, receptors, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, sclerosis, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, spectroscj, sports, standards, stats, std, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, targets, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, virtualworlds, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis
-% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal. Changing "submit" to "accept" before posting will remove line numbers.
+% If the frontmatter runs over more than one page
+% use the longmktitle option.
 
-%---------
-% article
-%---------
-% The default type of manuscript is "article", but can be replaced by: 
-% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
-% supfile = supplementary materials
+%\documentclass[a4paper,fleqn,longmktitle]{cas-dc}
 
-%----------
-% submit
-%----------
-% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted.
-This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information.
-Also, line numbering will be removed.
-Journal info and pagination for accepted papers will also be assigned by the Editorial Office.
+%\usepackage[numbers]{natbib}
+%\usepackage[authoryear]{natbib}
+\usepackage[authoryear,longnamesfirst]{natbib}
 
-%------------------
-% moreauthors
-%------------------
-% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.
+%\usepackage[numbers]{natbib}
+\usepackage[authoryear]{natbib}
+%\usepackage[authoryear,longnamesfirst]{natbib}
+\usepackage{dsfont}
+\usepackage{array}
+\usepackage{float}
+\usepackage{placeins}
+\usepackage{makecell} % add by shuyun
+%\usepackage[utf8]{inputenc}
+\usepackage{lineno,hyperref}
+\usepackage{amsmath}
+\usepackage{graphicx}
+\usepackage[small]{caption}
+\usepackage{subcaption}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{multicol}
+\usepackage{diagbox}
+\usepackage{mathrsfs}
+\usepackage{color}
+\usepackage{booktabs}
+\usepackage{soul}
+\usepackage{mathspec}
+\usepackage{xeCJK}
+\setCJKmainfont{STKaiti}
 
-%---------
-% pdftex
-%---------
-% The option pdftex is for use with pdfLaTeX. Remove "pdftex" for (1) compiling with LaTeX & dvi2pdf (if eps figures are used) or for (2) compiling with XeLaTeX.
+%\setCJKmainfont[Mapping=tex-text]{STKaiti}
+\usepackage[ruled, linesnumbered, vlined]{algorithm2e}
 
-%=================================================================
-% MDPI internal commands - do not modify
-\firstpage{1} 
-\makeatletter 
-\setcounter{page}{\@firstpage} 
-\makeatother
-\pubvolume{1}
-\issuenum{1}
-\articlenumber{0}
-\pubyear{2023}
-\copyrightyear{2023}
-%\externaleditor{Academic Editor: Firstname Lastname}
-\datereceived{ } 
-\daterevised{ } % Comment out if no revised date
-\dateaccepted{ } 
-\datepublished{ } 
-%\datecorrected{} % For corrected papers: "Corrected: XXX" date in the original paper.
-%\dateretracted{} % For corrected papers: "Retracted: XXX" date in the original paper.
-\hreflink{https://doi.org/} % If needed use \linebreak
-%\doinum{}
-%\pdfoutput=1 % Uncommented for upload to arXiv.org
+%\linenumbers
+%%%Author macros
+\def\tsc#1{\csdef{#1}{\textsc{\lowercase{#1}}\xspace}}
+\tsc{WGM}
+\tsc{QE}
 
-%=================================================================
-% Add packages and commands here.
-The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, float, amsmath, amssymb, lineno, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, colortbl, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, array, tabularx, pbox, ragged2e, tocloft, marginnote, marginfix, enotez, amsthm, natbib, hyperref, cleveref, scrextend, url, geometry, newfloat, caption, draftwatermark, seqsplit
-% cleveref: load \crefname definitions after \begin{document}
+\newcommand{\1}[1]{\mathds{1}\left[#1\right]}
+\renewcommand{\floatpagefraction}{0.8}
 
-%=================================================================
-% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
-%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).
+\newcommand{\secref}[1]{Section \ref{#1}}
+\newcommand{\figref}[1]{Figure \ref{#1}}
+\newcommand{\eqnref}[1]{Eq. (\ref{#1})}
+\newcommand{\exref}[1]{Example \ref{#1}}
+\newcommand{\algoref}[1]{Algorithm \ref{#1}}
+\newcommand{\tableref}[1]{Table \ref{#1}}
+\newcommand{\socvec}{SocVec}
+\newcommand{\argmin}{\operatornamewithlimits{argmin}}
+\newcommand{\argmax}{\operatornamewithlimits{argmax}}
+\newtheorem{example}{Example}
+\newtheorem{lemma}{Lemma}
+\newtheorem{definition}{Definition}
+\newcommand{\cut}[1]{}
+\newcommand{\ZY}[1]{\textcolor{red}{Zhiyi: #1}}
 
-%=================================================================
-% Full title of the paper (Capitalized)
-%\Title{Expansive Information Injection with Large Language Models for Multi-Span Question Answering }
-\Title{Empowering Multi-Span Question Answering with Expansive Information Injection using Large Language Models}
+\begin{document}
+\let\WriteBookmarks\relax
+\def\floatpagepagefraction{1}
+\def\textpagefraction{.001}
 
-% MDPI internal command: Title for citation in the left column
-\TitleCitation{Title}
+% Short title
+\shorttitle{A Token-based Transition-Aware Joint Framework for Multi-Span Question Answering}
 
-% Author Orchid ID: enter ID or remove command
-\newcommand{\orcidauthorA}{0000-0002-2206-1926} % Add \orcidA{} behind the author's name
-%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name
+% Short author
+\shortauthors{Z. Luo et al.}
 
-% Authors, for the paper (add full first names)
-\Author{Zhiyi Luo $^{1}$\orcidA{}, Yingying Zhang$^{1}$ and Shuyun Luo $^{1,}$*}
+% Main title of the paper
+\title{Empowering Multi-Span Question Answering with Expansive Information Injection using Large Language Models}
 
-%\longauthorlist{yes}
+\author{Zhiyi Luo}[type=editor,auid=000,bioid=1,orcid=0000-0002-2206-1926]
+%\cormark[1]
+\ead{luozhiyi@zstu.edu.cn}
+\ead[url]{http://zhiyiluo.site}
+%\credit{Conceptualization of this study, Methodology, Software}
 
-% MDPI internal command: Authors, for metadata in PDF
-\AuthorNames{Zhiyi Luo, Yingying Zhang and Shuyun Luo}
+\author{Yingying Zhang}
+\ead{272831920@qq.com}
 
-% MDPI internal command: Authors, for citation in the left column
-\AuthorCitation{Luo, Z.; Zhang, Y.; Luo, S.}
-% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.
+\author{Shuyun Luo}
+\ead{shuyunluo@zstu.edu.cn}
+\cormark[1]
+\cortext[mycorrespondingauthor]{Corresponding author}
 
-% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
-\address{%
-$^{1}$ \quad School of Computer Science and Technology and the Key Laboratory of Intelligent Textile and Flexible Interconnection of Zhejiang Province, Zhejiang Sci-Tech University, Hangzhou, China; luozhiyi@zstu.edu.cn
-%$^{2}$ \quad Affiliation 2; e-mail@e-mail.com
-}
+\address[mymainaddress]{School of Computer Science and Technology and the Key Laboratory of Intelligent Textile and Flexible Interconnection of Zhejiang Province, Zhejiang Sci-Tech University}
+\address[mysecondaryaddress]{No. 928, No. 2 street, Baiyang street, Qiantang New District, Hangzhou 310018, China}
 
-% Contact information of the corresponding author
-\corres{Correspondence: shuyunluo@zstu.edu.cn;}
+%\Title{Empowering Multi-Span Question Answering with Expansive Information Injection using Large Language Models}
+%
+%% MDPI internal command: Title for citation in the left column
+%\TitleCitation{Title}
+%
+%% Author Orchid ID: enter ID or remove command
+%\newcommand{\orcidauthorA}{0000-0002-2206-1926} % Add \orcidA{} behind the author's name
+%%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name
+%
+%
+%% Authors, for the paper (add full first names)
+%\Author{Zhiyi Luo $^{1}$\orcidA{}, Yingying Zhang$^{1}$ and Shuyun Luo $^{1,}$*}
+%
+%%\longauthorlist{yes}
+%
+%% MDPI internal command: Authors, for metadata in PDF
+%\AuthorNames{Zhiyi Luo, Yingying Zhang and Shuyun Luo}
+%
+%% MDPI internal command: Authors, for citation in the left column
+%\AuthorCitation{Luo, Z.; Zhang, Y.; Luo, S.}
+%% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.
+%
+%% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
+%\address{%
+%$^{1}$ \quad School of Computer Science and Technology and the Key Laboratory of Intelligent Textile and Flexible Interconnection of Zhejiang Province, Zhejiang Sci-Tech University, Hangzhou, China; luozhiyi@zstu.edu.cn
+%%$^{2}$ \quad Affiliation 2; e-mail@e-mail.com
+%}
+%
+%% Contact information of the corresponding author
+%\corres{Correspondence: shuyunluo@zstu.edu.cn;}
 
@@
 
-% Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{Retrieval-based question answering in the automotive domain requires a model to comprehend and articulate relevant domain knowledge, accurately understand user intent, and effectively match the required information.
-Typically, these systems employ a encoder-retriever architecture.
-However, existing encoders, which rely on pretrained language models, suffer from limited specialization, insufficient awareness of domain knowledge, and biases in user intent understanding.
-To overcome these limitations, this paper constructs a Chinese corpus specifically tailored for the automotive domain, comprising question-answer pairs, document collections, and multitask annotated data.
-Subsequently, a pretraining-multitask fine-tuning framework based on masked language models is introduced to integrate domain knowledge as well as enhance semantic representations, thereby yielding benefits for downstream applications.
-To evaluate system performance, an evaluation dataset is created using ChatGPT, and a novel retrieval task evaluation metric called Mean Linear Window Rank (MLWR) is proposed.
-Experimental results demonstrate that the proposed system (based on $\text{BERT}_{base}$), achieves accuracies of 77.5\% and 84.75\% for Hit@1 and Hit@3 respectively, in the automotive domain retrieval-based question answering task.
-Additionally, the MLWR reaches 87.71\%.
-Compared to a system utilizing a general encoder, the proposed multitask fine-tuning strategy shows improvements of 12.5\%, 12.5\%, and 28.16\% for Hit@1, Hit@3, and MLWR, respectively.
-Furthermore, when compared to the best single-task fine-tuning strategy, the enhancements amount to 0.5\%, 1.25\%, and 0.95\% for Hit@1, Hit@3, and MLWR, respectively.}
+% % Here goes the abstract
+\begin{abstract}
+	Multi-span question answering has gained prominence as it aligns more closely with real-world user requirements compared to single-span question answering.
+The utilization of pretrained language models has shown promise in improving multi-span question answering, particularly for factoid questions that necessitate entity-based answers.
+However, existing methods tend to overlook critical information regarding answer span boundaries, resulting in limited accuracy when generating descriptive answers.
+To address this limitation, we propose TOAST, a novel joint learning framework specialized in token-based neighboring transitions that capture answer span boundaries through adjacent word relations.
+Our approach extracts high-quality multi-span answers and is general-purpose, applicable to both alphabet languages like English and logographic languages like Chinese.
+Furthermore, we introduce CLEAN, a comprehensive open-domain Chinese multi-span question answering dataset, which includes a substantial number of descriptive questions.
+	Extensive experiments demonstrate the superior performance of TOAST over previous top-performing QA models in terms of both EM F1 and overlapped F1 scores.
+Specifically, the TOAST models, leveraging  $\text{BERT}_{base}$ and $\text{RoBERTa}_{base}$, achieve substantial  improvements in EM F1 scores, with increments of 3.03/2.13, 4.82/3.73, and 16.26/11.53, across three publicly available datasets, respectively.
+\end{abstract}
 
 % Keywords
-\keyword{deep learning; pretrained language model; retrieval-based question answering; multitask learning; fine-tuning}
-
-% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
-%\PACS{J0101}
-%\MSC{}
-%\JEL{}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Diversity
-%\LSID{\url{http://}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Applied Sciences
-%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Data
-%\dataset{DOI number or link to the deposited data set if the data set is published separately.
-If the data set shall be published as a supplement to this paper, this field will be filled by the journal editors.
-In this case, please submit the data set as a supplement.}
-%\datasetlicense{License under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Toxins
-%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Encyclopedia
-%\encyclopediadef{For entry manuscripts only: please provide a brief overview of the entry title instead of an abstract.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Only for the journal Advances in Respiratory Medicine
-%\addhighlights{yes}
-%\renewcommand{\addhighlights}{%
-
-%\noindent This is an obligatory section in “Advances in Respiratory Medicine”, whose goal is to increase the discoverability and readability of the article via search engines and other scholars.
-Highlights should not be a copy of the abstract, but a simple text allowing the reader to quickly and simplified find out what the article is about and what can be cited from it.
-Each of these parts should be devoted up to 2~bullet points.\vspace{3pt}\\
-%\textbf{What are the main findings?}
-% \begin{itemize}[labelsep=2.5mm,topsep=-3pt]
-% \item First bullet.
-% \item Second bullet.
-% \end{itemize}\vspace{3pt}
-%\textbf{What is the implication of the main finding?}
-% \begin{itemize}[labelsep=2.5mm,topsep=-3pt]
-% \item First bullet.
-% \item Second bullet.
-% \end{itemize}
-%}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\newcommand{\1}[1]{\mathds{1}\left[#1\right]}
-
-\newcommand{\secref}[1]{Section \ref{#1}}
-\newcommand{\figref}[1]{Figure \ref{#1}}
-\newcommand{\eqnref}[1]{Eq. (\ref{#1})}
-\newcommand{\exref}[1]{Example \ref{#1}}
-\newcommand{\algoref}[1]{Algorithm \ref{#1}}
-\newcommand{\tableref}[1]{Table \ref{#1}}
-
-\usepackage{color}
-\usepackage[utf8]{inputenc}
-\usepackage{xeCJK}
-
-\begin{document}
+\begin{keywords}
+	Reading comprehension \sep Multi-span question answering \sep  Pretrained language models \sep Multitask learning  \sep Chinese datasets 
+\end{keywords}
 
@@
 
-	\begin{figure}[H]
+	\begin{figure}[h]
 	\centering
@@
 \label{sec:prompt_construction}
-	\begin{figure}[H]
+	\begin{figure}[h]
 		\centering
@@
 \label{sec:information_injection}
-\begin{figure}[H]
+\begin{figure}[h]
 	\centering
@@
 
-\begin{figure}[H]
+\begin{figure}[h]
 	\centering
@@
 
-	\begin{table}[H] 
+	\begin{table}[width=\textwidth,cols=9,pos=h]  % 
 		\caption{Approach performance on complete MultiSpanQA valid set based on $\text{BERT}_{base}$.} 
 		\label{tab:bertall}
-		\newcolumntype{C}{>{\centering\arraybackslash}X}
-		\begin{tabularx}{\textwidth}{p{1.5cm}CCCCCCCC}
+		\begin{tabular*}{\textwidth}{p{1.5cm}cccccccc}
 			\toprule
@@
 			\bottomrule
-		\end{tabularx}
+		\end{tabular*}
 		%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
@@
 
-	\begin{table}[H] 
+	\begin{table}[width=\textwidth,cols=8,pos=h]  
 		\caption{Approach performance on complete MultiSpanQA valid set based on $\text{RoBERTa}_{base}$.} 
 		\label{tab:robertaall}
-		\newcolumntype{C}{>{\centering\arraybackslash}X}
-		\begin{tabularx}{\textwidth}{p{1.5cm}CCCCCCC}
+		\begin{tabular*}{\textwidth}{p{1.5cm}ccccccc}
 			\toprule
@@
 			\bottomrule
-		\end{tabularx}      
+		\end{tabular*}      
 		%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
@@
 		\label{tab:bertsub}
-		\newcolumntype{C}{>{\centering\arraybackslash}X}
-		\begin{tabularx}{\textwidth}{Cp{1.5cm}CCCCCCC}
+		\begin{tabular*}{\textwidth}{cp{1.5cm}ccccccc}
 			\toprule
@@
 			\bottomrule
-		\end{tabularx}
+		\end{tabular*}
 	\end{table}
@@
 		\label{tab:robertasub}
-		\newcolumntype{C}{>{\centering\arraybackslash}X}
-		\begin{tabularx}{\textwidth}{Cp{1.5cm}CCCCCCC}
+		\begin{tabular*}{\textwidth}{cp{1.5cm}ccccccc}
 			\toprule
@@
 
-\begin{table}[H] 
+\begin{table}[width=.6\textwidth,cols=8,pos=h]
 	\caption{Ablations of $\text{AUG}_{c}$ on different proportion for information concatenation, based on $\text{BERT}_{base}$.} 
 	\label{tab:different_ratio_bert}
-	\newcolumntype{C}{>{\centering\arraybackslash}X}
-	\begin{tabularx}{\textwidth}{p{1.7cm}CCCCCCC}
+	\begin{tabular*}{\tblwidth}{cccccccc}
+%	\begin{tabularx}{\textwidth}{p{1.7cm}ccccccc}
 		\toprule
@@
 		\bottomrule
-	\end{tabularx}      
+	\end{tabular*}
 	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
@@
 
-\begin{table}[H] 
-	\caption{Ablations of $\text{AUG}_{c}$ on different proportion for information concatenation, based on $\text{BERT}_{base}$.} 
-	\label{tab:different_ratio_roberta}
-	\newcolumntype{C}{>{\centering\arraybackslash}X}
-	\begin{tabularx}{\textwidth}{p{1.7cm}CCCCCCC}
-		\toprule
-		\multirow{2}{*}{\textbf{Proportion}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match}  \\
-		\cline{2-7} 
-		\addlinespace
-		& F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
-		\midrule
-		0.90 & 58.13 & 56.92 & 59.39 & 71.70 & 73.49 & 69.98 \\ 
-		0.70 & 66.97 & 65.42 & 68.60 & 80.05 & 80.80 & 79.32 \\
-		0.50 & 68.94 & 67.23 & 70.75 & 82.43 & 83.23 & 81.64 \\
-		0.40 & 68.95 & 66.11 & 71.06 & 83.71 & 83.71 & 81.71 \\
-		0.10 & 69.80 & 66.47 & 73.47 & 84.23 & 83.49 & 84.99 \\
-		0.86 & 70.35 & 67.35 & 73.63 & 84.06 & 83.38 & 84.76 \\
-		\bottomrule
-	\end{tabularx}      
-	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
-\end{table}
-
-\section{Conclusion}
+%\begin{table}[H] 
+%	\caption{Ablations of $\text{AUG}_{c}$ on different proportion for information concatenation, based on $\text{BERT}_{base}$.} 
+%	\label{tab:different_ratio_roberta}
+%	\newcolumntype{C}{>{\centering\arraybackslash}X}
+%	\begin{tabularx}{\textwidth}{p{1.7cm}CCCCCCC}
+%		\toprule
+%		\multirow{2}{*}{\textbf{Proportion}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match}  \\
+%		\cline{2-7} 
+%		\addlinespace
+%		& F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
+%		\midrule
+%		0.90 & 58.13 & 56.92 & 59.39 & 71.70 & 73.49 & 69.98 \\ 
+%		0.70 & 66.97 & 65.42 & 68.60 & 80.05 & 80.80 & 79.32 \\
+%		0.50 & 68.94 & 67.23 & 70.75 & 82.43 & 83.23 & 81.64 \\
+%		0.40 & 68.95 & 66.11 & 71.06 & 83.71 & 83.71 & 81.71 \\
+%		0.10 & 69.80 & 66.47 & 73.47 & 84.23 & 83.49 & 84.99 \\
+%		0.86 & 70.35 & 67.35 & 73.63 & 84.06 & 83.38 & 84.76 \\
+%		\bottomrule
+%	\end{tabularx}      
+%	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
+%\end{table}
+%
+%\section{Conclusion}
 
@@
 
-\funding{ This research was supported by the Natural Science Foundation of Zhejiang Province, China (Grant No.
-LQ22F020027) and the Key Research and Development Program of Zhejiang Province, China (2023C01041).}
-
-%\acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections.
-This may include administrative and technical support, or donations in kind (e.g., materials used for experiments).}
-
-\conflictsofinterest{The authors declare no conflict of interest.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% Only for journal Encyclopedia
-%\entrylink{The Link to this entry published on the encyclopedia platform.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{adjustwidth}{-\extralength}{0cm}
-%\printendnotes[custom] % Un-comment to print a list of endnotes
-
-\reftitle{References}
-
-% Please provide either the correct journal abbreviation (e.g.
-according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
-% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.
-
 %=====================================
@@
 
-%=====================================
-% References, variant B: internal bibliography
-%=====================================
-\begin{thebibliography}{999}
-	% Reference 1
-	\bibitem[Gupta(2005)]{asq-system}
-	Gupta, N.; Tur, G.; Hakkani-Tur, D.; et al. The AT\&T spoken language understanding system. {\em IEEE Transactions on Audio, Speech, and Language Processing}, {\bf 2005}, {\em 14(1)}, 213-222.
-	\bibitem[Ferrucci(2010)]{watson}
-	Ferrucci, D.G.; Brown, E.; Chu-Carroll, J.; Fan, J.; Gondek, D.; Kalyanpur, A.A.; Lally, A.; Murdock, J.W.; Nyberg, E.; Prager, J.; Schlaefer, N.; Welty, C.
-Building Watson: An Overview of the DeepQA Project.
-{\em AI Magazine} {\bf 2010}, {\em 31(3)}, 59--79.
-	\bibitem[Qu(2018)]{odqa2018}
-	Qu, C.; Yang, L.; Qiu, M.H. Open domain question answering using early fusion of knowledge bases and text. Available online: https://doi.org/10.48550/arXiv.1809.00782. (accessed on 19-05-2023).
-	\bibitem[Vaswani(2017)]{transformers2017}
-	Vaswani, A.; Shazeer, N.; Parmar, N.; Uszkoreit, J.; Jones, L.; Gomez, A.N.; Polosukhin, I.
-Attention Is All You Need.
-In Proceedings of Advances in Neural Information Processing Systems(ANIPS), California, USA, 2017; 5998-6008.
-	\bibitem[Devlin(2019)]{bert2019}
-	Devlin, J.; Chang, M.W.; Lee, K.; Toutanova, K.
-BERT: Pre-training of Deep Bidirectional Transformers for Language Understanding.
-In Proceedings of the Conference of the North American Chapter of the Association for Computational Linguistics: Human Language Technologies (NAACL-HLT), Minneapolis, 2019; 4171-4186.
-	\bibitem[Radford(2018)]{gpt}
-	Radford, A.; Narasimhan, K.; Salimans, T.; Sutskever, I.
-Improving Language Understanding by Generative Pre-Training.
-Available online: https://cdn.openai.com/research-covers/language-unsupervised/language\_understanding\_paper.pdf.
-(accessed on 19-05-2023).
-	\bibitem[Radford(2020)]{gpt2}
-	Radford, A.; Wu, J.; Child, R.; Luan, D.; Amodei, D.; Sutskever, I.
-Language Models are Unsupervised Multitask Learners.
-Available online: https://cdn.openai.com/better-language-models/language\_models\_are\_unsupervised\_multitask\_learners.\\pdf.
-(accessed on 19-05-2023).
-	\bibitem[Brown(2020)]{gpt3}
-	Brown, T.; Mann, B.; Ryder, N.; et al. Language models are few-shot learners. In proceedings of Advances in Neural Information Processing Systems, Virtual-only Conference, 2020, 33: 1877-1901.
-	\bibitem[Rajpurkar(2016)]{squad}
-	Rajpurkar, P.; Zhang, J.; Lopyrev, K.; Liang, P.
-Squad: 100,000+ questions for machine comprehension of text.
-In Proceedings of the Conference on Empirical Methods in Natural Language Processing(EMNLP), Austin, Texas, USA, 2016, 2383-2392.
-	\bibitem[Rajpurkar(2018)]{squad2.0}
-	Rajpurkar, P.; Jia, R.; Liang, P.
-Know what you don’t know: Unanswerable questions for squad.
-In Proceedings of the 56th Annual Meeting of the Association for Computational Linguistics (Volume 2: Short Papers), Melbourne, Australia, 2018, 784–789.
-	\bibitem[Li(2022)]{multispanqa}
-	Li, H.; Tomko, M.; Vasardani, M.; Baldwin, T.
-MultiSpanQA: A dataset for multi-span question answering.
-In Proceedings of the Conference of the North American Chapter of the Association for Computational Linguistics: Human Language Technologies (NAACL-HLT), Seattle, Washington, 2022, 1250–1260.
-	\bibitem[Yang(2019)]{bertserini}
-	Yang, Wei; et al. End-to-end open-domain question answering with bertserini. Available online: https://doi.org/10.48550/ar-\\Xiv.1902.01718. (accessed on 19-05-2023).
-	\bibitem[Zhang(2022)]{qa-survey}
-	Zhang, Q.; Chen, S.S.; Xu, D.K.; Cao, Q.Q.; Chen, X.J.; Cohn, T.; Fang, M.
-A Survey for Efficient Open Domain Question Answering.
-Available Online: https://arxiv.org/abs/2211.07886.
-(accessed on 19-05-2023).
-	\bibitem[Jones(1972)]{tf-idf}
-	Jones, S.K. A statistical interpretation of term specificity and its application in retrieval. {\em Journal of Documentation} {\bf 1972}, {\em 28(1)}, 11--21.
-%	\bibitem[Lin(2017)]{multichannel}
-%	Lin, B.
-Y.; Xu, F.
-F.; Luo, Z.; et al.
-Multi-channel bilstm-crf model for emerging named entity recognition in social media.
-In Proceedings of the 3rd Workshop on Noisy User-generated Text, Copenhagen, Denmark, 2017, 160-165.
-	\bibitem[Baldwin(2015)]{hand-crafted-features}
-	Baldwin, T.; Marneffe M.C.; Han, B.; et al.
-Shared tasks of the 2015 workshop on noisy user-generated text: Twitter lexical normalization and named entity recognition.
-In Proceedings of the workshop on noisy user-generated text, Beijing, China, 2015, 126-135.
-	\bibitem[Derczynski(2015)]{tweet}
-	Derczynski, L.; Maynard, D.; Rizzo, G.; et al. Analysis of named entity recognition and linking for tweets. {\em Information Processing \& Management} {\bf 2015}, {\em 51(2)}, 32-49.
-	\bibitem[Mikolov(2013)]{word2vec}
-	Mikolov, T.; Chen, K.; Corrado, G.; Dean, J. Efficient estimation of word representations in vector space. Available online: https://arxiv.org/abs/1301.3781. (accessed on 19-05-2023).
-%	\bibitem[Le(2014)]{word2vec2}
-%	Le, Q.; Mikolov, T. Distributed representations of sentences and documents. In Proceedings of the 31st International Conference on Machine Learning (ICML), Beijing, China, 2014; 1188-1196.
-	\bibitem[Harris(1954)]{distributed-hypothesis}
-	Harris, Z.S. Distributional structure. {\em Journal of Documentation} {\bf 1954}, {\em 10(2-3)}, 146--162.
-	\bibitem[Le(2014)]{glove}
-	Pennington, J.; Socher, R.; Manning, C.D.
-GloVe: Global Vectors for Word Representation.
-In Proceedings of the 2014 conference on empirical methods in natural language processing (EMNLP),  Maryland, USA, 2014; 1532-1543.
-	\bibitem[Vaswani(2017)]{cove}
-	McCann, B.; Bradbury, J.; Xiong, C.; Socher, R.
-Learned in translation: Contextualized word vectors.
-In Proceedings of Advances in Neural Information Processing Systems(NIPS), California, USA, 2017; 6297-6308.
-	\bibitem[Peters(2018)]{elmo}
-	Peters, M.E.; Neumann, M.; Iyyer, M.; Gardner, M.; Clark, C.; Lee, K.; Zettlemoyer, L.
-Deep contextualized word representations.
-In Proceedings of the 2018 Conference of the North American Chapter of the Association for Computational Linguistics: Human Language Technologies, New Orleans, USA, 2018; 2227-2237.
-	\bibitem[Devika(2021)]{app1}
-	Devika, R.; Vairavasundaram, S.; Mahenthar, C.S.J.; et al.
-A Deep Learning Model Based on BERT and Sentence Transformer for Semantic Keyphrase Extraction on Big Social Data.
-In  IEEE Access \textbf{2021}, 9, 165252-165261.
-	\bibitem[Natarajan(2022)]{app2}
-	Natarajan, B.; Rajalakshmi, E.; Elakkiya, R; et al.
-Development of an End-to-End Deep Learning Framework for Sign Language Recognition, Translation, and Video Generation.
-In IEEE Access \textbf{2022}, 10, 104358-104374.
-	\bibitem[Bentley(1975)]{kd-tree}
-	Bentley, J.L. Multidimensional binary search trees used for associative searching. {\em Communications of the ACM} {\bf 1975}, {\em 18(9)}, 509-517.
-	\bibitem[Liu(2006)]{ball-tree}
-	Liu, T.; Moore, A.W.; Gray, A.; New algorithms for efficient high-dimensional nonparametric classification. {\em JMLR} {\bf 2006}, 7, 1135–1158.
-	\bibitem[Omohundro(1989)]{ball-tree2}
-	Omohundro SM. Five balltree construction algorithms. Berkeley, California, USA: International Computer Science Institute, 1989.
-	\bibitem[Friedman(1977)]{knn-graph}
-	Friedman, J.H.; Bentley, J.L.; Finkel, R.A. An algorithm for finding best matches in logarithmic expected time. {\em ACM Transactions on Mathematical Software} {\bf 1977}, {\em 3(3)}, 209-226.
-	\bibitem[Jégou(2011)]{pq}
-	Jégou, H.; Douze, M.; Schmid, C. Product quantization for nearest neighbor search. {\em IEEE Transactions on Pattern Analysis and Machine Intelligence} {\bf 2011}, {\em 33(1)}, 117-128.
-	\bibitem[20Indyk(1998)]{lsh}
-	Indyk, P.; Motwani, R.
-Approximate nearest neighbors: towards removing the curse of dimensionality.
-In Proceedings of the Thirtieth Annual ACM Symposium on Theory of Computing, New York, USA, 1998; 604-613.
-	\bibitem[21Malkov(2018)]{hnsw}
-	Malkov, Y.A.; Yashunin, D.A.
-Efficient and robust approximate nearest neighbor search using Hierarchical Navigable Small World graphs.
-Available online: https://arxiv.org/abs/1603.09320.
-(accessed on 19-05-2023).
-	\bibitem[Jégou(2010)]{pns}
-	Jégou, H.; Perronnin, F.; Douze, M.; Sánchez, J.; Pérez, P.; Schmid, C.
-Aggregating local descriptors into a compact image representation.
-In Proceedings of the 2010 IEEE Computer Society Conference on Computer Vision and Pattern Recognition, San Francisco, USA, 2010; 3304-3311.
-	\bibitem[Wang(2019)]{haq}
-	Wang, K.; Liu, Z.; Lin, Y.; Lin, W.; Han, S.
-HAQ: Hardware-Aware Automated Quantization with Mixed Precision.
-In Proceedings of  the IEEE Computer Society Conference on Computer Vision and Pattern Recognition, Los Angeles, USA, 2019; 1669-1678.
-	\bibitem[Johnson(2011)]{faiss}
-	Johnson, J.; Douze, M.; Jégou, H. Billion-scale similarity search with GPUs. {\em IEEE Transactions on Big Data} {\bf 2019}, {\em 7(3)}, 535-547.	
-%	\bibitem[Zhu(2015)]{}
-%	Zhu, Y.K.; Kiros, R.; Zemel, R.; Salakhutdinov, R.; Urtasun, R.; Torralba, A.; Fidler, S.
-Aligning books and movies: Towards story-like visual explanations by watching movies and reading books.
-In Proceedings of the IEEE International Conference on Computer Vision, Santiago, Republic of Chile, 2015; 19-27.
-	\bibitem[Liu(2019)]{roberta}
-	Liu, Y.; Ott, M.; Goyal, N.; Du, J.; Joshi, M.; Chen, D. RoBERTa: A Robustly Optimized BERT Pretraining Approach. Available online: https://arxiv.org/abs/1603.09320. (accessed on 19-05-2023).
-	\bibitem[Johnson(2020)]{spanbert}
-	Clark, C.; Lee, K.; Chang, M.W.; Kwiatkowski, T.; Collins, M.; Toutanova, K.
-SpanBERT: Improving Pre-training by Representing and Predicting Spans.
-{\em Transactions of the Association for Computational Linguistics} {\bf 2020}, {\em 8}, 64-77.
-	%	% Reference 2
-%	\bibitem[Author2(year)]{ref-book1}
-%	Author~2, L. The title of the cited contribution. In {\em The Book Title}; Editor 1, F., Editor 2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
-%	% Reference 3
-%	\bibitem[Author3(year)]{ref-book2}
-%	Author 1, A.; Author 2, B. \textit{Book Title}, 3rd ed.; Publisher: Publisher Location, Country, 2008; pp. 154--196.
-%	% Reference 4
-%	\bibitem[Author4(year)]{ref-unpublish}
-%	Author 1, A.B.; Author 2, C. Title of Unpublished Work. \textit{Abbreviated Journal Name} year, \textit{phrase indicating stage of publication (submitted; accepted; in press)}.
-%	% Reference 5
-%	\bibitem[Author5(year)]{ref-communication}
-%	Author 1, A.B. (University, City, State, Country); Author 2, C. (Institute, City, State, Country). Personal communication, 2012.
-%	% Reference 6
-%	\bibitem[Author6(year)]{ref-proceeding}
-%	Author 1, A.B.; Author 2, C.D.; Author 3, E.F.
-Title of presentation.
-In Proceedings of the Name of the Conference, Location of Conference, Country, Date of Conference (Day Month Year); Abstract Number (optional), Pagination (optional).
-%	% Reference 7
-%	\bibitem[Author7(year)]{ref-thesis}
-%	Author 1, A.B. Title of Thesis. Level of Thesis, Degree-Granting University, Location of University, Date of Completion.
-%	% Reference 8
-%	\bibitem[Author8(year)]{ref-url}
-%	Title of Site. Available online: URL (accessed on Day Month Year).
-\end{thebibliography}
-% Reference 2
-%\bibitem[Author2(year)]{ref-book1}
-%Author~2, L. The title of the cited contribution. In {\em The Book Title}; Editor 1, F., Editor 2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
-%% Reference 3
-%\bibitem[Author3(year)]{ref-book2}
-%Author 1, A.; Author 2, B. \textit{Book Title}, 3rd ed.; Publisher: Publisher Location, Country, 2008; pp. 154--196.
-%% Reference 4
-%\bibitem[Author4(year)]{ref-unpublish}
-%Author 1, A.B.; Author 2, C. Title of Unpublished Work. \textit{Abbreviated Journal Name} year, \textit{phrase indicating stage of publication (submitted; accepted; in press)}.
-%% Reference 5
-%\bibitem[Author5(year)]{ref-communication}
-%Author 1, A.B. (University, City, State, Country); Author 2, C. (Institute, City, State, Country). Personal communication, 2012.
-%% Reference 6
-%\bibitem[Author6(year)]{ref-proceeding}
-%Author 1, A.B.; Author 2, C.D.; Author 3, E.F.
-Title of presentation.
-In Proceedings of the Name of the Conference, Location of Conference, Country, Date of Conference (Day Month Year); Abstract Number (optional), Pagination (optional).
-%% Reference 7
-%\bibitem[Author7(year)]{ref-thesis}
-%Author 1, A.B. Title of Thesis. Level of Thesis, Degree-Granting University, Location of University, Date of Completion.
-%% Reference 8
-%\bibitem[Author8(year)]{ref-url}
-%Title of Site. Available online: URL (accessed on Day Month Year).
+\section*{Acknowledgements}
+This research was supported by the Natural Science Foundation of Zhejiang Province, China (Grant No.
+LQ22F020027), Fundamental Research Funds of Zhejiang Sci-Tech University (Grant No.
+23232138-Y), Liaoning Provincial Natural Science Foundation of China (Grant No.
+2022-KF-21-01) and the Key Research and Development Program of Zhejiang Province, China (Grant No.
+2023C01041 and 2022C01079).
 
-% If authors have biography, please use the format below
-%\section*{Short Biography of Authors}
-%\bio
-%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author1.pdf}}}
-%{\textbf{Firstname Lastname} Biography of first author}
+\bibliographystyle{cas-model2-names}
 % 
-%\bio
-%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author2.jpg}}}
-%{\textbf{Firstname Lastname} Biography of second author}
-
-% For the MDPI journals use author-date citation, please follow the formatting guidelines on http://www.mdpi.com/authors/references
-% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
-% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p.
-328; \citeyear{ref-journal-3b}, p.475).
-This produces: Wong (1999, p.
-328; 2000, p.
-475)
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% for journal Sci
-%\reviewreports{\\
-%Reviewer 1 comments and authors’ response\\
-%Reviewer 2 comments and authors’ response\\
-%Reviewer 3 comments and authors’ response
-%}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\PublishersNote{}
-
-\end{adjustwidth}
+\bibliography{refs}
 \end{document}

### 2023-10-09 paper.tex
Add files via upload

@@
 \usepackage{xeCJK}
-\setCJKmainfont{STKaiti}
+%\setCJKmainfont{STKaiti}
 
@@
 \begin{document}
+	\begin{multicols}{2}
 \let\WriteBookmarks\relax
@@
 
-	\item We propose a new calculation method for the overlap F1 score in multi-span QA task.
-This method can alleviate the issue of lower scores in situations where the model decomposes the answer into multiple complete spans, but the answer’s spans are still entirely correct.
-This approach provides a more accurate reflection of the model’s performance in handling complex multi-span answers.
+	\item We propose a new calculation method for the overlap F1 score in multi-span QA task to alleviate the issue of lower scores in situations where the model decomposes the answer into multiple complete spans while the answer spans are still overall correct.The adjusted metrics provides a more accurate reflection of the model’s performance in handling complex multi-span answers.
 \end{itemize}
@@
 
-	\begin{figure}[h]
+	\begin{figure*}[h]
 	\centering
-	\includegraphics[width=14.0cm]{overview.png}
+	\includegraphics[width=18cm]{overview.png}
 	\caption{An overview of our automatic information augmentation framework.
@@
 	\label{fig:overview}
-	\end{figure}
+	\end{figure*}
 
@@
 The main reasons for these shortcomings can be categorized into three aspects:
-	\begin{itemize}
-		\item Ambiguous Words: The real world is replete with words that have a single form but multiple meanings, which heavily depend on the context.
-For instance, the word "Cameron" could refer to a famous director or a former British Prime Minister, depending on the context.
+
+	\textbf{Ambiguous Words}: The real world is replete with words that have a single form but multiple meanings, which heavily depend on the context.
+For instance, the word ``Cameron" could refer to a famous director or a former British Prime Minister, depending on the context.
 The specific meanings of such words often appear infrequently in training corpora, making them difficult to learn.
-		\item Numerical Values: In contrast to ambiguous words, numerical values have a single meaning but can be represented in various forms.
+
+	\textbf{Numerical Values}: In contrast to ambiguous words, numerical values have a single meaning but can be represented in various forms.
 For example, "22.5 billion years" can also be expressed as "cosmic years".
-		\item Multi-span Answers: In extractive multi-span question answering tasks, the model needs to grasp the overall relationship of multi-span answers in the context, such as parallelism and progression.
-		These challenges require the model to possess a high level of comprehensive understanding ability and knowledge about language and the world.
-	\end{itemize}
+
+	\textbf{Multi-span Answers}: In extractive multi-span question answering tasks, the model needs to grasp the overall relationship of multi-span answers in the context, such as parallelism and progression.These challenges require the model to possess a high level of comprehensive understanding ability and knowledge about language and the world.
 
@@
 Thus, we use GPT-3.5-turbo to generate entity annotations, entity association analysis, and content continuation for each question-answering paragraph as auxiliary information for the model:
-	\begin{itemize}
-		\item Context Supplementary: By inserting explanations of entities in the form of annotations after the main entities or concept words in the question and paragraph, this method helps the model capture the actual meaning of ambiguous words in specific contexts.
+
+	\textbf{Context Supplementary}: By inserting explanations of entities in the form of annotations after the main entities or concept words in the question and paragraph, this method helps the model capture the actual meaning of ambiguous words in specific contexts.
 It provides direct information prompts for low-frequency meanings or low-frequency words, achieving entity or concept alignment in the question-answering system.
-		\item Context Enrichment: By integrating entity association analysis and content continuation with the original question-answering text to form new paragraphs based on knowledge enhancement, this method captures the inherent associations between words or entity concepts with the same meaning but different forms.
+
+	\textbf{Context Enrichment}: By integrating entity association analysis and content continuation with the original question-answering text to form new paragraphs based on knowledge enhancement, this method captures the inherent associations between words or entity concepts with the same meaning but different forms.
 On one hand, it parses the logical relationships between other entities using entity relationship analysis.
 On the other hand, it extends the original paragraph information using content continuation, introducing more external knowledge while helping the model understand the overall content direction of the paragraph, thereby enhancing the model's comprehension ability.
-	\end{itemize}
 
@@
 \label{sec:prompt_construction}
-	\begin{figure}[h]
+	\begin{figure*}[h]
 		\centering
@@
 		\label{fig:prompt_template}
-	\end{figure}
+	\end{figure*}
 
@@
 \label{sec:information_injection}
-\begin{figure}[h]
+\begin{figure*}[h]
 	\centering
@@
 	\label{fig:entity_insertion}
-\end{figure}
+\end{figure*}
 
-\begin{figure}[h]
+\begin{figure*}[h]
 	\centering
@@
 	\label{fig:random_concatenate}
-\end{figure}
+\end{figure*}
 
@@
 
-	\begin{table}[width=\textwidth,cols=9,pos=h]  % 
+	\begin{table*}[width=\textwidth,cols=9,pos=h]  % 
 		\caption{Approach performance on complete MultiSpanQA valid set based on $\text{BERT}_{base}$.} 
 		\label{tab:bertall}
-		\begin{tabular*}{\textwidth}{p{1.5cm}cccccccc}
+		\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccccc}
 			\toprule
@@
 			$\text{AUG}_{ereec}$ & 62.90  & 61.02 & 64.89 & 76.72 & 78.56 & 74.97 \\
-			Bagging & 64.44          & 61.63        & 67.50          & 79.52         & 80.49          & 78.57         \\
+			Bagging & 64.44 & 61.63 & 67.50 & 79.5 & 80.49 & 78.57 \\
 			\bottomrule
@@
 		%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
-	\end{table}
+	\end{table*}
 
-	\begin{table}[width=\textwidth,cols=8,pos=h]  
+	\begin{table*}[width=\textwidth,cols=8,pos=h]  
 		\caption{Approach performance on complete MultiSpanQA valid set based on $\text{RoBERTa}_{base}$.} 
 		\label{tab:robertaall}
-		\begin{tabular*}{\textwidth}{p{1.5cm}ccccccc}
+		\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccccc}
 			\toprule
@@
 		%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
-	\end{table}
+	\end{table*}
 	Table~\ref{tab:bertall} and Table~\ref{tab:robertaall} illustrate the performance comparison between the proposed approaches, $\text{AUG}_{c}$ and $\text{AUG}_{eree}$, and several strong baselines, including the previous state-of-the-art model LIQUID.
@@
 
-	\begin{table}[ht]
+	\begin{table*}[ht]
 		\caption{Model performance on complete MultiSpanQA valid Subset with different answer types based on $\text{BERT}_{base}$.}
 		\label{tab:bertsub}
-		\begin{tabular*}{\textwidth}{cp{1.5cm}ccccccc}
+		\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccccc}
 			\toprule
@@
 		\end{tabular*}
-	\end{table}
+	\end{table*}
 
-	\begin{table}[ht]
+	\begin{table*}[ht]
 		\caption{Model performance on complete MultiSpanQA valid Subset with different answer types based on $\text{RoBERTa}_{base}$.}
 		\label{tab:robertasub}
-		\begin{tabular*}{\textwidth}{cp{1.5cm}ccccccc}
+		\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccccc}
 			\toprule
@@
 		\end{tabular*}
-	\end{table}
+	\end{table*}
 
@@
 
-\begin{table}[width=.6\textwidth,cols=8,pos=h]
+\begin{table*}[H] 
 	\caption{Ablations of $\text{AUG}_{c}$ on different proportion for information concatenation, based on $\text{BERT}_{base}$.} 
 	\label{tab:different_ratio_bert}
-	\begin{tabular*}{\tblwidth}{cccccccc}
-%	\begin{tabularx}{\textwidth}{p{1.7cm}ccccccc}
+	\newcolumntype{C}{>{\centering\arraybackslash}X}
+	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccccc}
 		\toprule
@@
 	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
-\end{table}
+\end{table*}
+
+\begin{table*}[H] 
+	\caption{Ablations of $\text{AUG}_{c}$ on different proportion for information concatenation, based on $\text{RoBERTa}_{base}$.} 
+	\label{tab:different_ratio_roberta}
+	\newcolumntype{C}{>{\centering\arraybackslash}X}
+	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccccc}
+		\toprule
+		\multirow{2}{*}{\textbf{Proportion}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match}  \\
+		\cline{2-7} 
+		\addlinespace
+		& F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
+		\midrule
+		0.90 & 58.13 & 56.92 & 59.39 & 71.70 & 73.49 & 69.98 \\ 
+		0.70 & 66.97 & 65.42 & 68.60 & 80.05 & 80.80 & 79.32 \\
+		0.50 & 68.94 & 67.23 & 70.75 & 82.43 & 83.23 & 81.64 \\
+		0.40 & 68.95 & 66.11 & 71.06 & 83.71 & 83.71 & 81.71 \\
+		0.10 & 69.80 & 66.47 & 73.47 & 84.23 & 83.49 & 84.99 \\
+		0.86 & 70.35 & 67.35 & 73.63 & 84.06 & 83.38 & 84.76 \\
+		\bottomrule
+	\end{tabular*}      
+	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
+\end{table*}
 
@@
 \bibliography{refs}
+\end{multicols}
 \end{document}

### 2023-10-10 paper.tex
Add files via upload

@@
 
-\documentclass[a4paper,fleqn]{cas-dc}
+\documentclass[a4paper,fleqn,twocolumn]{cas-dc}
 
@@
 \usepackage{xeCJK}
+%
+
 %\setCJKmainfont{STKaiti}
@@
 \begin{document}
-	\begin{multicols}{2}
+%	\begin{multicols}{2}
 \let\WriteBookmarks\relax
@@
 % Short title
-\shorttitle{A Token-based Transition-Aware Joint Framework for Multi-Span Question Answering}
+\shorttitle{Empowering Multi-Span Question Answering with Expansive Information Injection using Large Language Models}
 
@@
 % % Here goes the abstract
+\maketitle
+
 \begin{abstract}
@@
 	\item We employs a automatic data augmentation framework using Large Language Model \((LLM)\) as a knowledge source and a extra content supplement to linearize relevant information and possible continuation from LLM as texts, then inject them into original contexts.
-
 	\item We develop a series of prompt templates designed for interacting with ChatGPT to acquire comprehensive explanations of numerous entities.
 These templates ensure that the formats of the responses provided by ChatGPT are highly parseable and well-structured.
+	\item We propose a new calculation method for the overlap F1 score in multi-span QA task to alleviate the issue of lower scores in situations where the model decomposes the answer into multiple complete spans while the answer spans are still overall correct.The adjusted metrics provides a more accurate reflection of the model’s performance in handling complex multi-span answers.
 
-	\item We propose a new calculation method for the overlap F1 score in multi-span QA task to alleviate the issue of lower scores in situations where the model decomposes the answer into multiple complete spans while the answer spans are still overall correct.The adjusted metrics provides a more accurate reflection of the model’s performance in handling complex multi-span answers.
 \end{itemize}
@@
 \subsection{Construction of Prompt Template}
+
+	The quality and format of the content produced by LLMs depends greatly on the prompts.
+Hence, it is necessary to clarify the format and content requirements of the outputs in advance, and to refine the templates that meet the expectations through extensive evaluation.
+	For entity relationship parsing and textual continuation, it would be better to ensured that the the output is a natural paragraph, to facilitate the automatic splicing of the enriched knowledge with the initial paragraphs,which is consistent with encoder's natural input format.
+	Regarding knowledge of entity explanation, the inserted knowledge fusion method requires a parsable and structured outputs for automatic recognition and segmentation of entities and their explanations in post-processing, as well as inserting explanation behind the description of matched entity in initial context.
+
+	Concretely, by clearly specifying the form and requirements in the prompts, especially for entity relationship parsing and contextual continuation, which need to be formulated in the form of natural statements, the targeted enhanced knowledge can be obtained more easily.
+	Furthermore, to obtain well-structured results for complex model interactions, like entity explanations, we utilize a set of corresponding hint templates to construct the process, which has proven to be useful for interactions that require semi-structured answers through verification.
+
+	The template adopts a generalized structure, where the general requirement is first stated in a concise and natural way (e.g., "Please list all the entities mentioned below.").
+Secondly, the format and content requirements are detailed and subdivided by means of separate specific requirement sentences, using appropriate verbs and giving formatting paradigms where necessary to enable the larger model to better grasp the outcome requirements (e.g., "For each entity, provide a sentence structure in the form of "X is/means...").
+" sentence structure to provide a short explanation or definition, where X refers to the entity or concept appearing in the text.") Finally, the model is tested several times to see if there are any deviations in the understanding of the requirements and to modify or add clarifications to the requirements that are ambiguous to the model (e.g., adding at the end of the prompt, "Please return the answer in the following form, being careful not to repeat it: \textbackslash n\textbackslash nA is .....
+\textbackslash nB is ....") .
+In addition, when the prompt text is long, in order to avoid forgetting or confusing the requirements in the larger language model, specific requirements that do not perform well on the test can be re-emphasized in a separate paragraph distinct from the overall requirement.
+
 \label{sec:prompt_construction}
@@
 \bibliography{refs}
-\end{multicols}
+%\end{multicols}
 \end{document}

### 2023-10-10 paper.tex
Add files via upload

@@
 \subsection{Construction of Prompt Template}
+	\label{sec:prompt_construction}
+	\begin{figure*}[h]
+		\centering
+		\includegraphics[width=14.5cm]{Prompts_construction.png}
+		\caption{Prompt Templates and it's Construction}
+		\label{fig:prompt_template}
+	\end{figure*}
 
@@
 
-	The template adopts a generalized structure, where the general requirement is first stated in a concise and natural way (e.g., "Please list all the entities mentioned below.").
-Secondly, the format and content requirements are detailed and subdivided by means of separate specific requirement sentences, using appropriate verbs and giving formatting paradigms where necessary to enable the larger model to better grasp the outcome requirements (e.g., "For each entity, provide a sentence structure in the form of "X is/means...").
-" sentence structure to provide a short explanation or definition, where X refers to the entity or concept appearing in the text.") Finally, the model is tested several times to see if there are any deviations in the understanding of the requirements and to modify or add clarifications to the requirements that are ambiguous to the model (e.g., adding at the end of the prompt, "Please return the answer in the following form, being careful not to repeat it: \textbackslash n\textbackslash nA is .....
-\textbackslash nB is ....") .
-In addition, when the prompt text is long, in order to avoid forgetting or confusing the requirements in the larger language model, specific requirements that do not perform well on the test can be re-emphasized in a separate paragraph distinct from the overall requirement.
-
-\label{sec:prompt_construction}
-	\begin{figure*}[h]
-		\centering
-		\includegraphics[width=14.5cm]{Prompts_construction.png}
-		\caption{Prompt Templates and it's Construction}
-		\label{fig:prompt_template}
-	\end{figure*}
+	Eventually, the template is piloted to clarify any ambiguous requirements in the template to confirm an accurate understanding of the LLMs (e.g., adding at the end of the prompt, ``Please return the answer in the following form, being careful not to repeat it: \textbackslash n\textbackslash nA is .....")  In addition, to avoid omission or confusion of requirements due to the length of the prompt text, specific principles should be reiterate in a separate paragraph.
 
 \subsection{Information Injection}
+	For the entity interpretation data, the enhanced knowledge is injected into the original data (questions and paragraphs) by means of insertion interpretation.
+Specifically, the entity interpretation data is first parsed by an automated script, which on the one hand parses most of the sentence structures by regular expressions; on the other hand, for a small number of sentences that deviate from the template specification, the entities and their interpretations are identified by using the Semantic Dependency Analysis model in Spacy.
+After obtaining the ``Entity-Entity Interpretation" knowledge base for each QA data, the original data is scanned for questions and paragraphs, and the corresponding explanation is inserted as ``Entity (Entity and its Interpretation)" after each entity (if it is in the Entity and its Interpretation base of the data), and the corresponding explanation is enclosed in parentheses.
+The corresponding explanation is inserted after each entity (if it is in the database of entities and their explanations) in the form of ``Entity (Entity and its explanation)", and the inserted explanation of the entity is surrounded by parentheses to make sure that the augmented text injected with the knowledge is still a natural sentence or paragraph that flows smoothly (e.g., ``how long does it take for the milky way (Milky Way: The galaxy that contains our Solar System and is home to billions of stars.) to rotate?").
+
 	\label{sec:information_injection}
@@
 	\end{figure*}
+
+	For entity-relationship analysis and content continuation knowledge, the augmented knowledge is injected into the original paragraph using random slice splicing in proportion to its length.
+Firstly, the ratio of the length of the enhanced knowledge text to the original paragraph is calculated; secondly, in the input layer of the model, the original input data is sliced into text fragments with a length of 512*original length/(original length+enhanced text length), and the enhanced text is sliced into text fragments with a length of 512*enhanced text length/(original length+enhanced text length); then, randomly select the enhanced text fragments, and splice them Then randomly select the enhanced text fragment, splice it into the middle of each original text fragment, and finally input this long text into the model by sliding, in order to ensure that the original data can fully interact with the enhanced data in the bottom position of the model, as shown in Figure\ref{fig:random_concatenate}.
 

### 2023-10-10 paper.tex
Add files via upload

--- 2023-10-10 paper.tex
@@
 
-	The template adopts a generalized structure, where the general requirement is first stated in a concise and natural way (e.g., "Please list all the entities mentioned below.").
-Secondly, the format and content requirements are detailed and subdivided by means of separate specific requirement sentences, using appropriate verbs and giving formatting paradigms where necessary to enable the larger model to better grasp the outcome requirements (e.g., "For each entity, provide a sentence structure in the form of "X is/means...").
-" sentence structure to provide a short explanation or definition, where X refers to the entity or concept appearing in the text.") Finally, the model is tested several times to see if there are any deviations in the understanding of the requirements and to modify or add clarifications to the requirements that are ambiguous to the model (e.g., adding at the end of the prompt, "Please return the answer in the following form, being careful not to repeat it: \textbackslash n\textbackslash nA is .....
-\textbackslash nB is ....") .
-In addition, when the prompt text is long, in order to avoid forgetting or confusing the requirements in the larger language model, specific requirements that do not perform well on the test can be re-emphasized in a separate paragraph distinct from the overall requirement.
-
-\label{sec:prompt_construction}
-	\begin{figure*}[h]
-		\centering
-		\includegraphics[width=14.5cm]{Prompts_construction.png}
-		\caption{Prompt Templates and it's Construction}
-		\label{fig:prompt_template}
-	\end{figure*}
+	Eventually, the template is piloted to clarify any ambiguous requirements in the template to confirm an accurate understanding of the LLMs (e.g., adding at the end of the prompt, ``Please return the answer in the following form, being careful not to repeat it: \textbackslash n\textbackslash nA is .....")  In addition, to avoid omission or confusion of requirements due to the length of the prompt text, specific principles should be reiterate in a separate paragraph.
 
 \subsection{Information Injection}
+
+	To incorporate enhanced knowledge into the original data (comprising questions and paragraphs) pertaining to entity interpretation, a methodology involving the insertion of explanations is employed.
+Specifically, the process begins with the automated script parsing of entity interpretation data.
+This script, on one hand, utilizes regular expressions to analyze the structure of the majority of sentences, while on the other hand, for a limited subset of sentences that deviate from the template specifications, employs Spacy's Semantic Dependency Analysis model to identify entities and their corresponding interpretations.
+
+	Upon obtaining the ``Entity-Entity Interpretation" knowledge base for each question-and-answer data, a subsequent scan of the original context is conducted.
+For each entity that exists in the dataset's library of entities and their explanations, the corresponding explanation is inserted immediately following the entity, enclosed within parentheses.
+This meticulous approach ensures that the augmented text, enriched with knowledge, retains its natural sentence or paragraph flow.
+For instance, a resulting sentence might appear as follows: ``How long does it take for the Milky Way (Milky Way: The galaxy that contains our Solar System and is home to billions of stars.) to rotate?"
+
 	\label{sec:information_injection}
@@
 	\end{figure*}
+
+	For the incorporation of enhanced knowledge related to entity relationship analysis and content continuation, a method of random slicing and concatenation based on length ratios is employed to infuse the augmented knowledge into the original paragraphs.
+Initially, the ratio of the average length of the augmented knowledge text to that of the original paragraph is calculated.
+Subsequently, at the model's input layer, the original input data is segmented into text fragments of length of \textit{512 * average original length / (average original length + average augmented text length)}, and the augmented text is also segmented into text fragments of length of  \textit{512 * average augmented text length / (average original length + average augmented text length)}.
+Then, random selections of augmented text fragments are made and concatenated into the middle of each original text fragment.
+Finally, this concatenated longer text is fed into the model in a sliding manner to ensure comprehensive interaction between the original data and the augmented data at lower layers of the model, as illustrated in Process Figure~\ref{fig:random_concatenate}.
 

### 2023-10-11 paper.tex
Add files via upload

@@
 Then, random selections of augmented text fragments are made and concatenated into the middle of each original text fragment.
-Finally, this concatenated longer text is fed into the model in a sliding manner to ensure comprehensive interaction between the original data and the augmented data at lower layers of the model, as illustrated in Process Figure~\ref{fig:random_concatenate}.
+Finally, this concatenated longer text is fed into the model in a sliding manner to ensure comprehensive interaction between the original data and the augmented data at lower layers of the model, as illustrated in Figure~\ref{fig:random_concatenate}.
 
@@
 \label{sec:information_integration}
+	In addition to the aforementioned three types of information, we seek more valuable enhanced information by requesting summaries for each question-context pair from Large Language Models (LLMs).
+We then extract entities mentioned in the summaries to capture those highly relevant to the core context.
+Moreover, recognizing the intrinsic connection between entity explanation and entity relationship parsing, we categorize them as complementary information for context enrichment, with context continuation serving as supplementary information.
+This approach aims to augment the model's internal text-parsing knowledge with external world knowledge through enhanced information.
+
+	To further investigate the efficacy of multi-information integration, leveraging enhanced information derived from Large Language Models (LLMs), we employ two distinct approaches to combine entity knowledge and context continuity.
+The first approach involves the incorporation of all information within the original context, with each type of information undergoing individualized knowledge injection.
+The second approach, referred to as "bagging," treats models trained on diverse information sources as voters.
+For each query, we employ all model predictions for token-level BIO labeling within the context, determining the final prediction through a majority vote.
+In cases of tie-breaking, we prioritize the logits' magnitude to ascertain the ultimate prediction.
 

### 2023-10-16 paper.tex
Add files via upload

@@
 These templates ensure that the formats of the responses provided by ChatGPT are highly parseable and well-structured.
-	\item We propose a new calculation method for the overlap F1 score in multi-span QA task to alleviate the issue of lower scores in situations where the model decomposes the answer into multiple complete spans while the answer spans are still overall correct.The adjusted metrics provides a more accurate reflection of the model’s performance in handling complex multi-span answers.
 
@@
 Notably, the partial metrics also indicate lower values compared to TASE and LIQUID, in line with the result supported by $\text{BERT}_{base}$.
-This is because augmenting the model with entity information, including definition and relationship knowledge, strengthens its ability to capture and understand entity concepts, which leads the model to prefer complete entity spans as answers rather than partial entity span, and therefore a decrease in the partial recall and ultimately a lower partial F1 scores and a higher EM F1.
+This is because augmenting the model with entity information, including definition and relationship knowledge, strengthens its ability to capture and understand entity concepts, which leads the model to prefer complete entity spans or empty span set as answers rather than partial entity span, and therefore a decrease in the partial recall and ultimately a lower partial F1 scores and a higher EM F1.
+
+	To further substantiate our explanation for the suboptimal performance of our model on the Overlap F1 metric, we conducted a detailed examination of the predictions made by $\text{AUG}_{eree}$ and two baseline models on the validation dataset.
+In essence, we tallied the instances where these models predicted empty answers and recalculated their Overlap F1 scores on non-empty predictions.
+This allowed us to investigate whether the $\text{AUG}_{eree}$ model aligns with our hypothesis, which posits that its extensive learning of entity knowledge during training makes it inclined to output either a complete and accurate answer span or no answer at all, as opposed to a partially correct answer span.
+
+	As presented in Table~\ref{tab:answer_counts}, $\text{AUG}_{eree}$ indeed predicted a higher number of empty answers compared to TASE and LIQUID, while achieving relatively higher Overlap F1 scores on non-empty predictions.
+Specifically, when equipped with $\text{BERT}_{base}$ as the encoder, $\text{AUG}_{eree}$ obtained an F1 score of 0.7976 on non-empty answer predictions, whereas TASE and LIQUID scored 0.7964 and 0.7909, respectively.
+With $\text{RoBERTa}_{base}$, $\text{AUG}_{eree}$ achieved an Overlap F1 score of 0.8414, surpassing TASE and LIQUID, which scored 0.8404 and 0.8357, respectively.
+Additionally, it is worth noting that $\text{AUG}_{eree}$ consistently predicted more empty answers, whether using BERT or RoBERTa.
+
+	These findings lend support to our conjecture that the introduction of entity knowledge leads to a slight reduction in the model's Overlap F1 scores.
+This suggests that utilizing LLM as a knowledge source to linearize entity information from LLM text and integrate it into the original context empowers the model to acquire greater entity knowledge, thereby exhibiting a preference for more accurate and complete answer spans, or simply providing no answer.
+
+		\begin{table*}[width=\textwidth,cols=9,pos=h]  % 
+		\caption{The statistics of answers span predicted by $\text{AUG}_{eree}$ and baselines} 
+		\label{tab:answer_counts}
+		\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccccc}
+			\toprule
+			\multirow{2}{*}{\textbf{ }} & \multicolumn{3}{c}{$\text{BERT}_{base}$} & \multicolumn{3}{c}{$\text{RoBERTa}_{base}$}  \\
+			\cline{2-7} 
+			\addlinespace
+			& TASE\((\%)\) & LIQUID\((\%)\) & $\text{AUG}_{eree}$\((\%)\) & TASE\((\%)\) & LIQUID\((\%)\) & $\text{AUG}_{eree}$\((\%)\) \\
+			\midrule
+			empty predictions counts   & 0.0245 & 0.0214 & \textbf{0.0643} & 0.0061 & 0.0153 & \textbf{0.0291} \\ 
+			non-empty Overlap f1  & 0.7964 & 0.7909 & \textbf{0.7976} & 0.8404 & 0.8357 & \textbf{0.8414} \\
+			\bottomrule
+		\end{tabular*}
+		%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
+		\end{table*}
 
@@
 \subsubsection{\textit{Discussion}}
-	Besides, Table~\ref{tab:bertall} and Table~\ref{tab:robertaall} also discuss the performance of different augmentation integrated strategies, including the results-bagging methods whose outputs are voting results of $\text{AUG}_{c}$, $\text{AUG}_{eree}$ as well as LIQUID, and the input-fusion model $\text{AUG}_{ceree}$ who injects all kinds of information above into input contexts.
+	Table~\ref{tab:bertall} and Table~\ref{tab:robertaall} discuss the performance of different augmentation integrated strategies, including the results-bagging methods whose outputs are voting results of $\text{AUG}_{c}$, $\text{AUG}_{eree}$ as well as LIQUID, and the input-fusion model $\text{AUG}_{ceree}$ who injects all kinds of information above into input contexts.
 
@@
 And its weak performance on overlap f1 also reveals complete entities preference of this information injection approach.
-	z
-	In addition, we	categorized the data in MultispanQA into DESC, NUM, ENTYS in terms of answer types, and compared the performance of each of the model mentioned above in each breakdown category.
-Specifically,  Table~\ref{tab:bertsub} and Table~\ref{tab:robertasub} present the results backed by  $\text{BERT}_{base}$ and $\text{RoBERTa}_{base}$, respectively.
-As shown in Tables~\ref{tab:bertsub},Table~\ref{tab:robertasub}, our proposed models display superior performance in DESC and ENTYS categories answer extraction, which to some extent indicates the enhancement of models' knowledge at entity and description levels.
 
-	\textcolor{red}{please supplements new overlap calculation method in tase-zh}
+	Furthermore, we stratified the data within MultispanQA according to answer types, specifically categorizing them into DESC, NUM, and ENTYS.
+We subsequently conducted a comparative analysis of model performance within each of these subcategories.
+In particular, the results are presented in Tables~\ref{tab:bertsub} and Table~\ref{tab:robertasub}, supported by $\text{BERT}_{base}$ and $\text{RoBERTa}_{base}$, respectively.
+	As indicated in Tables~\ref{tab:bertsub} and~\ref{tab:robertasub}, our proposed models exhibit superior performance in terms of EM F1 scores for all categorizing.
+However, they demonstrate suboptimal performance in terms of overlap F1 scores.
 

### 2023-10-16 paper.tex
Add files via upload

@@
 \label{sec:related}
+In this section, we briefly summarize previous works that are relevant to extractive reading comprehension
+(RC) datasets and various modeling approaches employed for extractive RC tasks.
+\subsection{Multi-Span RC Datasets}
+The complete answer to a real-world user question could consist of multiple text spans. 
+Furthermore, a user question can even have multiple intents, where the answer to each intent is composed of one or more spans. 
+We refer to the datasets focus on such multi-span questions as multi-span RC datasets.
+Natural Question~\citep{DBLP:journals/tacl/KwiatkowskiPRCP19} and Quoref~\citep{DBLP:conf/emnlp/DasigiLMSG19} both contain multi-span questions. 
+The Natural Question dataset incorporates real anonymized queries to the Google search engine. 
+Quoref is used to validate models with the ability to resolve co-reference among entities. %, which is not for general capability validation of models.
+However, the proportion of multi-span answers in Natural Question and Quoref is relatively low, around 2\% and 10\% respectively. 
+The DROP~\citep{DBLP:conf/naacl/DuaWDSS019} dataset which consists of complex questions on history and football games, requires discrete reasoning over the content of contexts, including  co-reference resolution and arithmetic operations, such as addition, sorting and counting.
+Although the questions could be multi-span, the answer spans are almost exclusively semantically homogeneous and related to numeric values. 
+MASH-QA~\citep{DBLP:conf/aaai/PangLGXSC19} is a domain-specific dataset that extends the answer space to general text types in the healthcare domain.
+Recently, \cite{li2022multispanqa} propose the MultiSpanQA dataset, which consists of open-domain multi-span questions.
+The MultiSpanQA dataset is derived from Natural Question, whose questions are real queries issued to the Google search engine.
+Each question is associated with a context extracted from a retrieved Wikipedia page.  
+MultiSpanQA also has an expanded variant by introducing single-span and unanswerable questions, namely MultiSpanQA (expand).
+
+\subsection{Neural Models for RC}
+Research in reading comprehension grows rapidly, and many successful neural-based RC models have been proposed in this area. 
+%As discussed in \secref{sec:related_dataset}, the extractive RC datasets support to cast RC as answer extraction task.
+Typically, neural  models~\citep{DBLP:conf/aaai/PangLGXSC19,DBLP:conf/iclr/Wang017a,DBLP:conf/iclr/XiongZS17} for RC are composed of two components, a context encoder and an answer decoder. 
+The context encoder is used to encode the information of questions, contexts and their interactions in-between.
+Then, the answer decoder aims to generate the answer texts based on outputs of the context encoder.
+To make the answer decoder compatible with the answer extraction task, 
+Pointer Network~\citep{DBLP:conf/nips/VinyalsFJ15} model has been adopted to
+% tackle the problem that 
+%generates answer texts from contexts. 
+copy tokens from the given contexts as answers~\citep{DBLP:conf/acl/KadlecSBK16,DBLP:conf/emnlp/TrischlerYYBSS16}.
+\cite{DBLP:conf/iclr/Wang017a} proposed a boundary model, which utilized Pointer Network to predict the start and end indices for an answer span.
+%\ZY{single token - single span - multispan}
+%Boundary Model
+\cite{DBLP:conf/iclr/SeoKFH17} proposed an alternative way for the implementation of answer decoder, that built neural position classifiers upon the encoder outputs, predicting the start and end indices of the answer span in the context.
+
+% neural layer unifies the components of encoder and decoder together that 
+Recently, the RC models upgrade the context encoder using pre-trained language models (PrLMs)~\citep{radford2018improving,kenton2019bert,liu2019roberta,lee2020biobert,gu2021domain} 
+%such as GPT~\citep{radford2018improving}, BERT~\citep{kenton2019bert} and RoBERTa~\citep{liu2019roberta}
+, benefiting from the invention of Transformer~\citep{vaswani2017attention} blocks.
+%Benefiting from nowadays pretrained language models (PrLMs) based on Transformer~\cite{vaswani2017attention} blocks, recent RC models upgrades the context encoder using PrLMs such as BERT. 
+%the context encoder and answer decoder can be unified into a standard algorithm that utilize PrLMs such as BERT to encode inputs, then predict the start position and end position for the answer span.
+\cite{DBLP:conf/naacl/DevlinCLT19}  proposed a standard extractive model for  single-span RC that utilizes BERT to encode inputs, then builds position classifiers to predict where the answer span starts and ends.
+However, the answer decoder, whether implemented with Pointer Network or position classifiers, predicts start and end position independently, thus can not distinguish the different answer spans properly.
+%Pang et al. proposed HAS-QA~\cite{} which built the conditional pointer network and aggregators to model multiple answer spans.
+~\cite{DBLP:conf/emnlp/ZhuAJ0R20} proposed MultiCo which used a contextualized sentence selection method to capture the relevance among multiple sentence-based answer spans in order to form an answer with multiple sentences.
+%However, such single-span extractive model is not suitable for multi-span RC task which can be formulated as multi-span extraction.
+These models are not well adapted to multi-span RC which can be formulated as more flexible task of multi-span extraction where each span can be a word, phrase, sentence or any continuous string of text.
+
+%the start position and end position of the answer span. 
+%PrLMs unify the context encoder and answer decoder as a standard algorithm, that  
+%\subsubsection{Single-span Models}
+%~\citep{yoon2022,DBLP:journals/corr/abs-2302-01691} 
+Extracting a variable number of spans from an input text can be commonly cast as a sequence tagging problem.
+\cite{segal2020simple} proposed using a sequence tagging model for multi-span extraction, which predicts whether each token is part of an answer.
+\cite{yoon2022} employed a similar sequence tagging approach to address extractive question answering~\citep{DBLP:journals/bmcbi/NaseemDKK22}  in the biomedical domain.
+\cite{li2022multispanqa} also adopted the tagging model architecture, integrating two sub-tasks: predicting the number of spans to extract and annotating the answer structure within their proposed dataset to capture global information.
+ADRAV~\citep{hu2023biomedical} proposed a dynamic routing and answer voting method to further make full use of the hidden layer knowledge of pre-trained models.
+More recently, LIQUID~\citep{lee2023liquid} was introduced to  automatically generate list-style QA pairs from unlabeled corpora.
+LIQUID extracted named entities from the summarized text as candidate answers and incorporated synthetic data in the tagging model.
+These methods harness the extensive factual knowledge embedded in powerful contextualized encoders (PrLMs) or synthesized data that resolves around named entities. 
+As a result, they have demonstrated promising performance in extracting  multi-span answers, particularly for factoid questions where the answers correspond entities.
+%Benefiting from the rich factual knowledge implied in the powerful contextualized encoders (PrLMs) or synthesized data centered around name entities, these methods have achieved promising performance on multi-span answer extraction, especially for factoid questions where the answers are entities.
+%These methods have been achieved promising performance on multi-span answer extraction, especially for factoid questions whose answers are entities, benefiting from the rich factoid knowledge implied in the powerful context encoder like PrLMs.
+However, these methods do not take into account the information of span boundaries in terms of the questions, and thus have very limited capabilities of precisely drawing a description answer. 
+%However, for these methodswhich are implied in the powerful context encoder like PrLMs, they are failed to care span boundaries .
+Compared to these approaches, TOAST incorporates the semantic and syntactic information of span boundaries by explicitly modeling the implicit neighboring transitions in-between the adjacent tokens or words, which benefits the span boundary identification.
+
+\subsection{Interaction with LLMs}
 

### 2023-10-22 paper.tex
init

--- 2023-10-11 paper.tex
@@
 
-\documentclass[a4paper,fleqn,twocolumn]{cas-dc}
+\documentclass[a4paper,fleqn]{cas-dc}
 
@@
 %\usepackage[numbers]{natbib}
-\usepackage[authoryear]{natbib}
+%\usepackage[authoryear]{natbib}
 %\usepackage[authoryear,longnamesfirst]{natbib}
@@
 \usepackage{xeCJK}
-%
-
-%\setCJKmainfont{STKaiti}
+\setCJKmainfont{STKaiti}
 
@@
 \begin{document}
-%	\begin{multicols}{2}
 \let\WriteBookmarks\relax
@@
 % Short title
-\shorttitle{Empowering Multi-Span Question Answering with Expansive Information Injection using Large Language Models}
+\shorttitle{A Token-based Transition-Aware Joint Framework for Multi-Span Question Answering}
 
@@
 % % Here goes the abstract
-\maketitle
-
 \begin{abstract}
@@
 
+Let's cite a paper~\cite{DBLP:conf/aaai/PangLGXSC19}.
+
 In summary, the main contributions in this paper are as follows:
@@
 	\item We employs a automatic data augmentation framework using Large Language Model \((LLM)\) as a knowledge source and a extra content supplement to linearize relevant information and possible continuation from LLM as texts, then inject them into original contexts.
+
 	\item We develop a series of prompt templates designed for interacting with ChatGPT to acquire comprehensive explanations of numerous entities.
 These templates ensure that the formats of the responses provided by ChatGPT are highly parseable and well-structured.
-	\item We propose a new calculation method for the overlap F1 score in multi-span QA task to alleviate the issue of lower scores in situations where the model decomposes the answer into multiple complete spans while the answer spans are still overall correct.The adjusted metrics provides a more accurate reflection of the model’s performance in handling complex multi-span answers.
 
+	\item We propose a new calculation method for the overlap F1 score in multi-span QA task.
+This method can alleviate the issue of lower scores in situations where the model decomposes the answer into multiple complete spans, but the answer’s spans are still entirely correct.
+This approach provides a more accurate reflection of the model’s performance in handling complex multi-span answers.
 \end{itemize}
@@
 
-	\begin{figure*}[h]
+	\begin{figure}[h]
 	\centering
-	\includegraphics[width=18cm]{overview.png}
+	\includegraphics[width=14.0cm]{overview.png}
 	\caption{An overview of our automatic information augmentation framework.
@@
 	\label{fig:overview}
-	\end{figure*}
+	\end{figure}
 
@@
 The main reasons for these shortcomings can be categorized into three aspects:
-
-	\textbf{Ambiguous Words}: The real world is replete with words that have a single form but multiple meanings, which heavily depend on the context.
-For instance, the word ``Cameron" could refer to a famous director or a former British Prime Minister, depending on the context.
+	\begin{itemize}
+		\item Ambiguous Words: The real world is replete with words that have a single form but multiple meanings, which heavily depend on the context.
+For instance, the word "Cameron" could refer to a famous director or a former British Prime Minister, depending on the context.
 The specific meanings of such words often appear infrequently in training corpora, making them difficult to learn.
-
-	\textbf{Numerical Values}: In contrast to ambiguous words, numerical values have a single meaning but can be represented in various forms.
+		\item Numerical Values: In contrast to ambiguous words, numerical values have a single meaning but can be represented in various forms.
 For example, "22.5 billion years" can also be expressed as "cosmic years".
-
-	\textbf{Multi-span Answers}: In extractive multi-span question answering tasks, the model needs to grasp the overall relationship of multi-span answers in the context, such as parallelism and progression.These challenges require the model to possess a high level of comprehensive understanding ability and knowledge about language and the world.
+		\item Multi-span Answers: In extractive multi-span question answering tasks, the model needs to grasp the overall relationship of multi-span answers in the context, such as parallelism and progression.
+		These challenges require the model to possess a high level of comprehensive understanding ability and knowledge about language and the world.
+	\end{itemize}
 
@@
 Thus, we use GPT-3.5-turbo to generate entity annotations, entity association analysis, and content continuation for each question-answering paragraph as auxiliary information for the model:
-
-	\textbf{Context Supplementary}: By inserting explanations of entities in the form of annotations after the main entities or concept words in the question and paragraph, this method helps the model capture the actual meaning of ambiguous words in specific contexts.
+	\begin{itemize}
+		\item Context Supplementary: By inserting explanations of entities in the form of annotations after the main entities or concept words in the question and paragraph, this method helps the model capture the actual meaning of ambiguous words in specific contexts.
 It provides direct information prompts for low-frequency meanings or low-frequency words, achieving entity or concept alignment in the question-answering system.
-
-	\textbf{Context Enrichment}: By integrating entity association analysis and content continuation with the original question-answering text to form new paragraphs based on knowledge enhancement, this method captures the inherent associations between words or entity concepts with the same meaning but different forms.
+		\item Context Enrichment: By integrating entity association analysis and content continuation with the original question-answering text to form new paragraphs based on knowledge enhancement, this method captures the inherent associations between words or entity concepts with the same meaning but different forms.
 On one hand, it parses the logical relationships between other entities using entity relationship analysis.
 On the other hand, it extends the original paragraph information using content continuation, introducing more external knowledge while helping the model understand the overall content direction of the paragraph, thereby enhancing the model's comprehension ability.
+	\end{itemize}
 
@@
 \label{sec:prompt_construction}
-	\begin{figure*}[h]
+	\begin{figure}[h]
 		\centering
@@
 		\label{fig:prompt_template}
-	\end{figure*}
-
-	The quality and format of the content produced by LLMs depends greatly on the prompts.
-Hence, it is necessary to clarify the format and content requirements of the outputs in advance, and to refine the templates that meet the expectations through extensive evaluation.
-	For entity relationship parsing and textual continuation, it would be better to ensured that the the output is a natural paragraph, to facilitate the automatic splicing of the enriched knowledge with the initial paragraphs,which is consistent with encoder's natural input format.
-	Regarding knowledge of entity explanation, the inserted knowledge fusion method requires a parsable and structured outputs for automatic recognition and segmentation of entities and their explanations in post-processing, as well as inserting explanation behind the description of matched entity in initial context.
-
-	Concretely, by clearly specifying the form and requirements in the prompts, especially for entity relationship parsing and contextual continuation, which need to be formulated in the form of natural statements, the targeted enhanced knowledge can be obtained more easily.
-	Furthermore, to obtain well-structured results for complex model interactions, like entity explanations, we utilize a set of corresponding hint templates to construct the process, which has proven to be useful for interactions that require semi-structured answers through verification.
-
-	Eventually, the template is piloted to clarify any ambiguous requirements in the template to confirm an accurate understanding of the LLMs (e.g., adding at the end of the prompt, ``Please return the answer in the following form, being careful not to repeat it: \textbackslash n\textbackslash nA is .....")  In addition, to avoid omission or confusion of requirements due to the length of the prompt text, specific principles should be reiterate in a separate paragraph.
+	\end{figure}
 
 \subsection{Information Injection}
-
-	To incorporate enhanced knowledge into the original data (comprising questions and paragraphs) pertaining to entity interpretation, a methodology involving the insertion of explanations is employed.
-Specifically, the process begins with the automated script parsing of entity interpretation data.
-This script, on one hand, utilizes regular expressions to analyze the structure of the majority of sentences, while on the other hand, for a limited subset of sentences that deviate from the template specifications, employs Spacy's Semantic Dependency Analysis model to identify entities and their corresponding interpretations.
-
-	Upon obtaining the ``Entity-Entity Interpretation" knowledge base for each question-and-answer data, a subsequent scan of the original context is conducted.
-For each entity that exists in the dataset's library of entities and their explanations, the corresponding explanation is inserted immediately following the entity, enclosed within parentheses.
-This meticulous approach ensures that the augmented text, enriched with knowledge, retains its natural sentence or paragraph flow.
-For instance, a resulting sentence might appear as follows: ``How long does it take for the Milky Way (Milky Way: The galaxy that contains our Solar System and is home to billions of stars.) to rotate?"
-
 \label{sec:information_injection}
-	\begin{figure*}[h]
+\begin{figure}[h]
 	\centering
@@
 	\label{fig:entity_insertion}
-	\end{figure*}
+\end{figure}
 
-	For the incorporation of enhanced knowledge related to entity relationship analysis and content continuation, a method of random slicing and concatenation based on length ratios is employed to infuse the augmented knowledge into the original paragraphs.
-Initially, the ratio of the average length of the augmented knowledge text to that of the original paragraph is calculated.
-Subsequently, at the model's input layer, the original input data is segmented into text fragments of length of \textit{512 * average original length / (average original length + average augmented text length)}, and the augmented text is also segmented into text fragments of length of  \textit{512 * average augmented text length / (average original length + average augmented text length)}.
-Then, random selections of augmented text fragments are made and concatenated into the middle of each original text fragment.
-Finally, this concatenated longer text is fed into the model in a sliding manner to ensure comprehensive interaction between the original data and the augmented data at lower layers of the model, as illustrated in Figure~\ref{fig:random_concatenate}.
-
-\begin{figure*}[h]
+\begin{figure}[h]
 	\centering
@@
 	\label{fig:random_concatenate}
-\end{figure*}
+\end{figure}
 
@@
 \label{sec:information_integration}
-	In addition to the aforementioned three types of information, we seek more valuable enhanced information by requesting summaries for each question-context pair from Large Language Models (LLMs).
-We then extract entities mentioned in the summaries to capture those highly relevant to the core context.
-Moreover, recognizing the intrinsic connection between entity explanation and entity relationship parsing, we categorize them as complementary information for context enrichment, with context continuation serving as supplementary information.
-This approach aims to augment the model's internal text-parsing knowledge with external world knowledge through enhanced information.
-
-	To further investigate the efficacy of multi-information integration, leveraging enhanced information derived from Large Language Models (LLMs), we employ two distinct approaches to combine entity knowledge and context continuity.
-The first approach involves the incorporation of all information within the original context, with each type of information undergoing individualized knowledge injection.
-The second approach, referred to as "bagging," treats models trained on diverse information sources as voters.
-For each query, we employ all model predictions for token-level BIO labeling within the context, determining the final prediction through a majority vote.
-In cases of tie-breaking, we prioritize the logits' magnitude to ascertain the ultimate prediction.
 
@@
 
-	\begin{table*}[width=\textwidth,cols=9,pos=h]  % 
+	\begin{table}[width=\textwidth,cols=9,pos=h]  % 
 		\caption{Approach performance on complete MultiSpanQA valid set based on $\text{BERT}_{base}$.} 
 		\label{tab:bertall}
-		\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccccc}
+		\begin{tabular*}{\textwidth}{p{1.5cm}cccccccc}
 			\toprule
@@
 			$\text{AUG}_{ereec}$ & 62.90          & 61.02        & 64.89          & 76.72         & 78.56          & 74.97         \\
-			Bagging & 64.44 & 61.63 & 67.50 & 79.5 & 80.49 & 78.57 \\
+			Bagging & 64.44          & 61.63        & 67.50          & 79.52         & 80.49          & 78.57         \\
 			\bottomrule
@@
 		%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
-	\end{table*}
+	\end{table}
 
-	\begin{table*}[width=\textwidth,cols=8,pos=h]  
+	\begin{table}[width=\textwidth,cols=8,pos=h]  
 		\caption{Approach performance on complete MultiSpanQA valid set based on $\text{RoBERTa}_{base}$.} 
 		\label{tab:robertaall}
-		\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccccc}
+		\begin{tabular*}{\textwidth}{p{1.5cm}ccccccc}
 			\toprule
@@
 		%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
-	\end{table*}
+	\end{table}
 	Table~\ref{tab:bertall} and Table~\ref{tab:robertaall} illustrate the performance comparison between the proposed approaches, $\text{AUG}_{c}$ and $\text{AUG}_{eree}$, and several strong baselines, including the previous state-of-the-art model LIQUID.
@@
 
-	\begin{table*}[ht]
+	\begin{table}[ht]
 		\caption{Model performance on complete MultiSpanQA valid Subset with different answer types based on $\text{BERT}_{base}$.}
 		\label{tab:bertsub}
-		\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccccc}
+		\begin{tabular*}{\textwidth}{cp{1.5cm}ccccccc}
 			\toprule
@@
 		\end{tabular*}
-	\end{table*}
+	\end{table}
 
-	\begin{table*}[ht]
+	\begin{table}[ht]
 		\caption{Model performance on complete MultiSpanQA valid Subset with different answer types based on $\text{RoBERTa}_{base}$.}
 		\label{tab:robertasub}
-		\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccccc}
+		\begin{tabular*}{\textwidth}{cp{1.5cm}ccccccc}
 			\toprule
@@
 		\end{tabular*}
-	\end{table*}
+	\end{table}
 
@@
 
-\begin{table*}[H] 
+\begin{table}[width=.6\textwidth,cols=8,pos=h]
 	\caption{Ablations of $\text{AUG}_{c}$ on different proportion for information concatenation, based on $\text{BERT}_{base}$.} 
 	\label{tab:different_ratio_bert}
-	\newcolumntype{C}{>{\centering\arraybackslash}X}
-	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccccc}
+	\begin{tabular*}{\tblwidth}{cccccccc}
+%	\begin{tabularx}{\textwidth}{p{1.7cm}ccccccc}
 		\toprule
@@
 	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
-\end{table*}
-
-\begin{table*}[H] 
-	\caption{Ablations of $\text{AUG}_{c}$ on different proportion for information concatenation, based on $\text{RoBERTa}_{base}$.} 
-	\label{tab:different_ratio_roberta}
-	\newcolumntype{C}{>{\centering\arraybackslash}X}
-	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccccc}
-		\toprule
-		\multirow{2}{*}{\textbf{Proportion}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match}  \\
-		\cline{2-7} 
-		\addlinespace
-		& F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
-		\midrule
-		0.90 & 58.13 & 56.92 & 59.39 & 71.70 & 73.49 & 69.98 \\ 
-		0.70 & 66.97 & 65.42 & 68.60 & 80.05 & 80.80 & 79.32 \\
-		0.50 & 68.94 & 67.23 & 70.75 & 82.43 & 83.23 & 81.64 \\
-		0.40 & 68.95 & 66.11 & 71.06 & 83.71 & 83.71 & 81.71 \\
-		0.10 & 69.80 & 66.47 & 73.47 & 84.23 & 83.49 & 84.99 \\
-		0.86 & 70.35 & 67.35 & 73.63 & 84.06 & 83.38 & 84.76 \\
-		\bottomrule
-	\end{tabular*}      
-	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
-\end{table*}
+\end{table}
 
@@
 \bibliography{refs}
-%\end{multicols}
 \end{document}

### 2024-01-12 experiments.tex
x

--- 2023-10-16 paper.tex
@@
-% !TeX program = xelatex 
-%% 
-%% Copyright 2019-2021 Elsevier Ltd
-%% 
-%% This file is part of the 'CAS Bundle'.
-%% --------------------------------------
-%% 
-%% It may be distributed under the conditions of the LaTeX Project Public
-%% License, either version 1.2 of this license or (at your option) any
-%% later version.  The latest version of this license is in
-%%    http://www.latex-project.org/lppl.txt
-%% and version 1.2 or later is part of all distributions of LaTeX
-%% version 1999/12/01 or later.
-%% 
-%% The list of all files belonging to the 'CAS Bundle' is
-%% given in the file `manifest.txt'.
-%% 
-%% Template article for cas-dc documentclass for 
-%% double column output.
-
-\documentclass[a4paper,fleqn,twocolumn]{cas-dc}
-
-% If the frontmatter runs over more than one page
-% use the longmktitle option.
-
-%\documentclass[a4paper,fleqn,longmktitle]{cas-dc}
-
-%\usepackage[numbers]{natbib}
-%\usepackage[authoryear]{natbib}
-\usepackage[authoryear,longnamesfirst]{natbib}
-
-%\usepackage[numbers]{natbib}
-\usepackage[authoryear]{natbib}
-%\usepackage[authoryear,longnamesfirst]{natbib}
-\usepackage{dsfont}
-\usepackage{array}
-\usepackage{float}
-\usepackage{placeins}
-\usepackage{makecell} % add by shuyun
-%\usepackage[utf8]{inputenc}
-\usepackage{lineno,hyperref}
-\usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage[small]{caption}
-\usepackage{subcaption}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{multicol}
-\usepackage{diagbox}
-\usepackage{mathrsfs}
-\usepackage{color}
-\usepackage{booktabs}
-\usepackage{soul}
-\usepackage{mathspec}
-\usepackage{xeCJK}
-%
-
-%\setCJKmainfont{STKaiti}
-
-%\setCJKmainfont[Mapping=tex-text]{STKaiti}
-\usepackage[ruled, linesnumbered, vlined]{algorithm2e}
-
-%\linenumbers
-%%%Author macros
-\def\tsc#1{\csdef{#1}{\textsc{\lowercase{#1}}\xspace}}
-\tsc{WGM}
-\tsc{QE}
-
-\newcommand{\1}[1]{\mathds{1}\left[#1\right]}
-\renewcommand{\floatpagefraction}{0.8}
-
-\newcommand{\secref}[1]{Section \ref{#1}}
-\newcommand{\figref}[1]{Figure \ref{#1}}
-\newcommand{\eqnref}[1]{Eq. (\ref{#1})}
-\newcommand{\exref}[1]{Example \ref{#1}}
-\newcommand{\algoref}[1]{Algorithm \ref{#1}}
-\newcommand{\tableref}[1]{Table \ref{#1}}
-\newcommand{\socvec}{SocVec}
-\newcommand{\argmin}{\operatornamewithlimits{argmin}}
-\newcommand{\argmax}{\operatornamewithlimits{argmax}}
-\newtheorem{example}{Example}
-\newtheorem{lemma}{Lemma}
-\newtheorem{definition}{Definition}
-\newcommand{\cut}[1]{}
-\newcommand{\ZY}[1]{\textcolor{red}{Zhiyi: #1}}
-
-\begin{document}
-%	\begin{multicols}{2}
-\let\WriteBookmarks\relax
-\def\floatpagepagefraction{1}
-\def\textpagefraction{.001}
-
-% Short title
-\shorttitle{Empowering Multi-Span Question Answering with Expansive Information Injection using Large Language Models}
-
-% Short author
-\shortauthors{Z. Luo et al.}
-
-% Main title of the paper
-\title{Empowering Multi-Span Question Answering with Expansive Information Injection using Large Language Models}
-
-\author{Zhiyi Luo}[type=editor,auid=000,bioid=1,orcid=0000-0002-2206-1926]
-%\cormark[1]
-\ead{luozhiyi@zstu.edu.cn}
-\ead[url]{http://zhiyiluo.site}
-%\credit{Conceptualization of this study, Methodology, Software}
-
-\author{Yingying Zhang}
-\ead{272831920@qq.com}
-
-\author{Shuyun Luo}
-\ead{shuyunluo@zstu.edu.cn}
-\cormark[1]
-\cortext[mycorrespondingauthor]{Corresponding author}
-
-\address[mymainaddress]{School of Computer Science and Technology and the Key Laboratory of Intelligent Textile and Flexible Interconnection of Zhejiang Province, Zhejiang Sci-Tech University}
-\address[mysecondaryaddress]{No. 928, No. 2 street, Baiyang street, Qiantang New District, Hangzhou 310018, China}
-
-%\Title{Empowering Multi-Span Question Answering with Expansive Information Injection using Large Language Models}
-%
-%% MDPI internal command: Title for citation in the left column
-%\TitleCitation{Title}
-%
-%% Author Orchid ID: enter ID or remove command
-%\newcommand{\orcidauthorA}{0000-0002-2206-1926} % Add \orcidA{} behind the author's name
-%%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name
-%
-%
-%% Authors, for the paper (add full first names)
-%\Author{Zhiyi Luo $^{1}$\orcidA{}, Yingying Zhang$^{1}$ and Shuyun Luo $^{1,}$*}
-%
-%%\longauthorlist{yes}
-%
-%% MDPI internal command: Authors, for metadata in PDF
-%\AuthorNames{Zhiyi Luo, Yingying Zhang and Shuyun Luo}
-%
-%% MDPI internal command: Authors, for citation in the left column
-%\AuthorCitation{Luo, Z.; Zhang, Y.; Luo, S.}
-%% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.
-%
-%% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
-%\address{%
-%$^{1}$ \quad School of Computer Science and Technology and the Key Laboratory of Intelligent Textile and Flexible Interconnection of Zhejiang Province, Zhejiang Sci-Tech University, Hangzhou, China; luozhiyi@zstu.edu.cn
-%%$^{2}$ \quad Affiliation 2; e-mail@e-mail.com
-%}
-%
-%% Contact information of the corresponding author
-%\corres{Correspondence: shuyunluo@zstu.edu.cn;}
-
-% Current address and/or shared authorship
-%\firstnote{Current address: Affiliation 3.} 
-%\secondnote{These authors contributed equally to this work.}
-% The commands \thirdnote{} till \eighthnote{} are available for further notes
-
-%\simplesumm{} % Simple summary
-
-%\conference{} % An extended version of a conference paper
-
-% % Here goes the abstract
-\maketitle
-
-\begin{abstract}
-	Multi-span question answering has gained prominence as it aligns more closely with real-world user requirements compared to single-span question answering.
-The utilization of pretrained language models has shown promise in improving multi-span question answering, particularly for factoid questions that necessitate entity-based answers.
-However, existing methods tend to overlook critical information regarding answer span boundaries, resulting in limited accuracy when generating descriptive answers.
-To address this limitation, we propose TOAST, a novel joint learning framework specialized in token-based neighboring transitions that capture answer span boundaries through adjacent word relations.
-Our approach extracts high-quality multi-span answers and is general-purpose, applicable to both alphabet languages like English and logographic languages like Chinese.
-Furthermore, we introduce CLEAN, a comprehensive open-domain Chinese multi-span question answering dataset, which includes a substantial number of descriptive questions.
-	Extensive experiments demonstrate the superior performance of TOAST over previous top-performing QA models in terms of both EM F1 and overlapped F1 scores.
-Specifically, the TOAST models, leveraging  $\text{BERT}_{base}$ and $\text{RoBERTa}_{base}$, achieve substantial  improvements in EM F1 scores, with increments of 3.03/2.13, 4.82/3.73, and 16.26/11.53, across three publicly available datasets, respectively.
-\end{abstract}
-
-% Keywords
-\begin{keywords}
-	Reading comprehension \sep Multi-span question answering \sep  Pretrained language models \sep Multitask learning  \sep Chinese datasets 
-\end{keywords}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Introduction}
-\label{sec:intro}
-
-In summary, the main contributions in this paper are as follows:
-\begin{itemize}
-	\item We employs a automatic data augmentation framework using Large Language Model \((LLM)\) as a knowledge source and a extra content supplement to linearize relevant information and possible continuation from LLM as texts, then inject them into original contexts.
-	\item We develop a series of prompt templates designed for interacting with ChatGPT to acquire comprehensive explanations of numerous entities.
-These templates ensure that the formats of the responses provided by ChatGPT are highly parseable and well-structured.
-
-\end{itemize}
-
-%The introduction should briefly place the study in a broad context and highlight why it is important.
-It should define the purpose of the work and its significance.
-The current state of the research field should be reviewed carefully and key publications cited.
-Please highlight controversial and diverging hypotheses when necessary.
-Finally, briefly mention the main aim of the work and highlight the principal conclusions.
-As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research.
-Citing a journal paper \cite{ref-journal}.
-Now citing a book reference \cite{ref-book1,ref-book2} or other reference types \cite{ref-unpublish,ref-communication,ref-proceeding}.
-Please use the command \citep{ref-thesis,ref-url} for the following MDPI journals, which use author--date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, Journal of Intelligence, Journalism and Media, JRFM, Languages, Laws, Religions, Risks, Social Sciences, Literature.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Related Work}
-\label{sec:related}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Our Approach}
-
-	\begin{figure*}[h]
-	\centering
-	\includegraphics[width=18cm]{overview.png}
-	\caption{An overview of our automatic information augmentation framework.
-\textbf{(a) Step 1}: Interact with ChatGPT to Get Auxiliary Information.
-\textbf{(b) Step 2}: Distilling the Information and Injecting Them into Context \textbf{(c) Step 3}: Input the Augmented Context into Tagging Model}
-	\label{fig:overview}
-	\end{figure*}
-
-%\unskip
-	Existing extractive multi-span question answering models exhibit subpar performance in handling ambiguous words, complex proper nouns (such as film and song titles), numerical values, and long descriptive answers.
-The main reasons for these shortcomings can be categorized into three aspects:
-
-	\textbf{Ambiguous Words}: The real world is replete with words that have a single form but multiple meanings, which heavily depend on the context.
-For instance, the word ``Cameron" could refer to a famous director or a former British Prime Minister, depending on the context.
-The specific meanings of such words often appear infrequently in training corpora, making them difficult to learn.
-
-	\textbf{Numerical Values}: In contrast to ambiguous words, numerical values have a single meaning but can be represented in various forms.
-For example, "22.5 billion years" can also be expressed as "cosmic years".
-
-	\textbf{Multi-span Answers}: In extractive multi-span question answering tasks, the model needs to grasp the overall relationship of multi-span answers in the context, such as parallelism and progression.These challenges require the model to possess a high level of comprehensive understanding ability and knowledge about language and the world.
-
-	Leveraging large language models to parse question-answering data and inject auxiliary knowledge into the model can promote the integration of the model's latent world knowledge and specific domain knowledge in the paragraph, thereby enhancing the model's performance.
-Thus, we use GPT-3.5-turbo to generate entity annotations, entity association analysis, and content continuation for each question-answering paragraph as auxiliary information for the model:
-
-	\textbf{Context Supplementary}: By inserting explanations of entities in the form of annotations after the main entities or concept words in the question and paragraph, this method helps the model capture the actual meaning of ambiguous words in specific contexts.
-It provides direct information prompts for low-frequency meanings or low-frequency words, achieving entity or concept alignment in the question-answering system.
-
-	\textbf{Context Enrichment}: By integrating entity association analysis and content continuation with the original question-answering text to form new paragraphs based on knowledge enhancement, this method captures the inherent associations between words or entity concepts with the same meaning but different forms.
-On one hand, it parses the logical relationships between other entities using entity relationship analysis.
-On the other hand, it extends the original paragraph information using content continuation, introducing more external knowledge while helping the model understand the overall content direction of the paragraph, thereby enhancing the model's comprehension ability.
-
-	Overall,we design an automated knowledge enhancement method for multi-span question answering tasks, which interacts with large language models based on templates.
-This method is applicable to all question answering models or frameworks.
-It is universally applicable to any other downstream tasks that contain paragraph data, without the need for any complex calculations.
-In the following sections, we will provide a detailed introduction to each specific module of this process.
-
-\subsection{Construction of Prompt Template}
-	\label{sec:prompt_construction}
-	\begin{figure*}[h]
-		\centering
-		\includegraphics[width=14.5cm]{Prompts_construction.png}
-		\caption{Prompt Templates and it's Construction}
-		\label{fig:prompt_template}
-	\end{figure*}
-
-	The quality and format of the content produced by LLMs depends greatly on the prompts.
-Hence, it is necessary to clarify the format and content requirements of the outputs in advance, and to refine the templates that meet the expectations through extensive evaluation.
-	For entity relationship parsing and textual continuation, it would be better to ensured that the the output is a natural paragraph, to facilitate the automatic splicing of the enriched knowledge with the initial paragraphs,which is consistent with encoder's natural input format.
-	Regarding knowledge of entity explanation, the inserted knowledge fusion method requires a parsable and structured outputs for automatic recognition and segmentation of entities and their explanations in post-processing, as well as inserting explanation behind the description of matched entity in initial context.
-
-	Concretely, by clearly specifying the form and requirements in the prompts, especially for entity relationship parsing and contextual continuation, which need to be formulated in the form of natural statements, the targeted enhanced knowledge can be obtained more easily.
-	Furthermore, to obtain well-structured results for complex model interactions, like entity explanations, we utilize a set of corresponding hint templates to construct the process, which has proven to be useful for interactions that require semi-structured answers through verification.
-
-	Eventually, the template is piloted to clarify any ambiguous requirements in the template to confirm an accurate understanding of the LLMs (e.g., adding at the end of the prompt, ``Please return the answer in the following form, being careful not to repeat it: \textbackslash n\textbackslash nA is .....")  In addition, to avoid omission or confusion of requirements due to the length of the prompt text, specific principles should be reiterate in a separate paragraph.
-
-\subsection{Information Injection}
-
-	To incorporate enhanced knowledge into the original data (comprising questions and paragraphs) pertaining to entity interpretation, a methodology involving the insertion of explanations is employed.
-Specifically, the process begins with the automated script parsing of entity interpretation data.
-This script, on one hand, utilizes regular expressions to analyze the structure of the majority of sentences, while on the other hand, for a limited subset of sentences that deviate from the template specifications, employs Spacy's Semantic Dependency Analysis model to identify entities and their corresponding interpretations.
-
-	Upon obtaining the ``Entity-Entity Interpretation" knowledge base for each question-and-answer data, a subsequent scan of the original context is conducted.
-For each entity that exists in the dataset's library of entities and their explanations, the corresponding explanation is inserted immediately following the entity, enclosed within parentheses.
-This meticulous approach ensures that the augmented text, enriched with knowledge, retains its natural sentence or paragraph flow.
-For instance, a resulting sentence might appear as follows: ``How long does it take for the Milky Way (Milky Way: The galaxy that contains our Solar System and is home to billions of stars.) to rotate?"
-
-	\label{sec:information_injection}
-	\begin{figure*}[h]
-		\centering
-		\includegraphics[width=10cm]{EntityInsert.png}
-		\caption{The Process of Inserting Entity Explanation into Context}
-		\label{fig:entity_insertion}
-	\end{figure*}
-
-	For the incorporation of enhanced knowledge related to entity relationship analysis and content continuation, a method of random slicing and concatenation based on length ratios is employed to infuse the augmented knowledge into the original paragraphs.
-Initially, the ratio of the average length of the augmented knowledge text to that of the original paragraph is calculated.
-Subsequently, at the model's input layer, the original input data is segmented into text fragments of length of \textit{512 * average original length / (average original length + average augmented text length)}, and the augmented text is also segmented into text fragments of length of  \textit{512 * average augmented text length / (average original length + average augmented text length)}.
-Then, random selections of augmented text fragments are made and concatenated into the middle of each original text fragment.
-Finally, this concatenated longer text is fed into the model in a sliding manner to ensure comprehensive interaction between the original data and the augmented data at lower layers of the model, as illustrated in Figure~\ref{fig:random_concatenate}.
-
-\begin{figure*}[h]
-	\centering
-	\includegraphics[width=10cm]{RandomConcat.png}
-	\caption{The Process of Concatenation of Original Context and Auxiliary Information}
-	\label{fig:random_concatenate}
-\end{figure*}
-
-\subsection{Information Integration}
-\label{sec:information_integration}
-	In addition to the aforementioned three types of information, we seek more valuable enhanced information by requesting summaries for each question-context pair from Large Language Models (LLMs).
-We then extract entities mentioned in the summaries to capture those highly relevant to the core context.
-Moreover, recognizing the intrinsic connection between entity explanation and entity relationship parsing, we categorize them as complementary information for context enrichment, with context continuation serving as supplementary information.
-This approach aims to augment the model's internal text-parsing knowledge with external world knowledge through enhanced information.
-
-	To further investigate the efficacy of multi-information integration, leveraging enhanced information derived from Large Language Models (LLMs), we employ two distinct approaches to combine entity knowledge and context continuity.
-The first approach involves the incorporation of all information within the original context, with each type of information undergoing individualized knowledge injection.
-The second approach, referred to as "bagging," treats models trained on diverse information sources as voters.
-For each query, we employ all model predictions for token-level BIO labeling within the context, determining the final prediction through a majority vote.
-In cases of tie-breaking, we prioritize the logits' magnitude to ascertain the ultimate prediction.
-
 \section{Experiments}
@@
 %
-%\section{Conclusion}
-
-%All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, etc.
-
-%\section{Discussion}
-%
-%Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses.
-The findings and their implications should be discussed in the broadest context possible.
-Future research directions may also be highlighted.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Conclusions}
-%
-%This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace{6pt}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-%\supplementary{The following supporting information can be downloaded at:  \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.}
-
-% Only for journal Methods and Protocols:
-% If you wish to submit a video article, please do so with any other supplementary material.
-% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.
-A supporting video article is available at doi: link.}
-
-% Only for journal Hardware:
-% If you wish to submit a video article, please do so with any other supplementary material.
-% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.\vspace{6pt}\\
-%\begin{tabularx}{\textwidth}{lll}
-%\toprule
-%\textbf{Name} & \textbf{Type} & \textbf{Description} \\
-%\midrule
-%S1 & Python script (.py) & Script of python source code used in XX \\
-%S2 & Text (.txt) & Script of modelling code used to make Figure X \\
-%S3 & Text (.txt) & Raw data from experiment X \\
-%S4 & Video (.mp4) & Video demonstrating the hardware in use \\
-%... & ... & ... \\
-%\bottomrule
-%\end{tabularx}
-%}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided.
-The following statements should be used ``Conceptualization, X.X.
-and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y.
-and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing---original draft preparation, X.X.; writing---review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y.
-All authors have read and agreed to the published version of the manuscript.'', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation.
-Authorship must be limited to those who have contributed substantially to the work~reported.}
-
-%=====================================
-% References, variant A: external bibliography
-%=====================================
-%\bibliography{your_external_BibTeX_file}
-
-\section*{Acknowledgements}
-This research was supported by the Natural Science Foundation of Zhejiang Province, China (Grant No.
-LQ22F020027), Fundamental Research Funds of Zhejiang Sci-Tech University (Grant No.
-23232138-Y), Liaoning Provincial Natural Science Foundation of China (Grant No.
-2022-KF-21-01) and the Key Research and Development Program of Zhejiang Province, China (Grant No.
-2023C01041 and 2022C01079).
-
-\bibliographystyle{cas-model2-names}
-% 
-\bibliography{refs}
-%\end{multicols}
-\end{document}

### 2024-01-12 intro.tex
x

--- 2023-10-22 paper.tex
@@
-% !TeX program = xelatex 
-%% 
-%% Copyright 2019-2021 Elsevier Ltd
-%% 
-%% This file is part of the 'CAS Bundle'.
-%% --------------------------------------
-%% 
-%% It may be distributed under the conditions of the LaTeX Project Public
-%% License, either version 1.2 of this license or (at your option) any
-%% later version.  The latest version of this license is in
-%%    http://www.latex-project.org/lppl.txt
-%% and version 1.2 or later is part of all distributions of LaTeX
-%% version 1999/12/01 or later.
-%% 
-%% The list of all files belonging to the 'CAS Bundle' is
-%% given in the file `manifest.txt'.
-%% 
-%% Template article for cas-dc documentclass for 
-%% double column output.
-
-\documentclass[a4paper,fleqn]{cas-dc}
-
-% If the frontmatter runs over more than one page
-% use the longmktitle option.
-
-%\documentclass[a4paper,fleqn,longmktitle]{cas-dc}
-
-%\usepackage[numbers]{natbib}
-%\usepackage[authoryear]{natbib}
-\usepackage[authoryear,longnamesfirst]{natbib}
-
-%\usepackage[numbers]{natbib}
-%\usepackage[authoryear]{natbib}
-%\usepackage[authoryear,longnamesfirst]{natbib}
-\usepackage{dsfont}
-\usepackage{array}
-\usepackage{float}
-\usepackage{placeins}
-\usepackage{makecell} % add by shuyun
-%\usepackage[utf8]{inputenc}
-\usepackage{lineno,hyperref}
-\usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage[small]{caption}
-\usepackage{subcaption}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{multicol}
-\usepackage{diagbox}
-\usepackage{mathrsfs}
-\usepackage{color}
-\usepackage{booktabs}
-\usepackage{soul}
-\usepackage{mathspec}
-\usepackage{xeCJK}
-\setCJKmainfont{STKaiti}
-
-%\setCJKmainfont[Mapping=tex-text]{STKaiti}
-\usepackage[ruled, linesnumbered, vlined]{algorithm2e}
-
-%\linenumbers
-%%%Author macros
-\def\tsc#1{\csdef{#1}{\textsc{\lowercase{#1}}\xspace}}
-\tsc{WGM}
-\tsc{QE}
-
-\newcommand{\1}[1]{\mathds{1}\left[#1\right]}
-\renewcommand{\floatpagefraction}{0.8}
-
-\newcommand{\secref}[1]{Section \ref{#1}}
-\newcommand{\figref}[1]{Figure \ref{#1}}
-\newcommand{\eqnref}[1]{Eq. (\ref{#1})}
-\newcommand{\exref}[1]{Example \ref{#1}}
-\newcommand{\algoref}[1]{Algorithm \ref{#1}}
-\newcommand{\tableref}[1]{Table \ref{#1}}
-\newcommand{\socvec}{SocVec}
-\newcommand{\argmin}{\operatornamewithlimits{argmin}}
-\newcommand{\argmax}{\operatornamewithlimits{argmax}}
-\newtheorem{example}{Example}
-\newtheorem{lemma}{Lemma}
-\newtheorem{definition}{Definition}
-\newcommand{\cut}[1]{}
-\newcommand{\ZY}[1]{\textcolor{red}{Zhiyi: #1}}
-
-\begin{document}
-\let\WriteBookmarks\relax
-\def\floatpagepagefraction{1}
-\def\textpagefraction{.001}
-
-% Short title
-\shorttitle{A Token-based Transition-Aware Joint Framework for Multi-Span Question Answering}
-
-% Short author
-\shortauthors{Z. Luo et al.}
-
-% Main title of the paper
-\title{Empowering Multi-Span Question Answering with Expansive Information Injection using Large Language Models}
-
-\author{Zhiyi Luo}[type=editor,auid=000,bioid=1,orcid=0000-0002-2206-1926]
-%\cormark[1]
-\ead{luozhiyi@zstu.edu.cn}
-\ead[url]{http://zhiyiluo.site}
-%\credit{Conceptualization of this study, Methodology, Software}
-
-\author{Yingying Zhang}
-\ead{272831920@qq.com}
-
-\author{Shuyun Luo}
-\ead{shuyunluo@zstu.edu.cn}
-\cormark[1]
-\cortext[mycorrespondingauthor]{Corresponding author}
-
-\address[mymainaddress]{School of Computer Science and Technology and the Key Laboratory of Intelligent Textile and Flexible Interconnection of Zhejiang Province, Zhejiang Sci-Tech University}
-\address[mysecondaryaddress]{No. 928, No. 2 street, Baiyang street, Qiantang New District, Hangzhou 310018, China}
-
-%\Title{Empowering Multi-Span Question Answering with Expansive Information Injection using Large Language Models}
-%
-%% MDPI internal command: Title for citation in the left column
-%\TitleCitation{Title}
-%
-%% Author Orchid ID: enter ID or remove command
-%\newcommand{\orcidauthorA}{0000-0002-2206-1926} % Add \orcidA{} behind the author's name
-%%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name
-%
-%
-%% Authors, for the paper (add full first names)
-%\Author{Zhiyi Luo $^{1}$\orcidA{}, Yingying Zhang$^{1}$ and Shuyun Luo $^{1,}$*}
-%
-%%\longauthorlist{yes}
-%
-%% MDPI internal command: Authors, for metadata in PDF
-%\AuthorNames{Zhiyi Luo, Yingying Zhang and Shuyun Luo}
-%
-%% MDPI internal command: Authors, for citation in the left column
-%\AuthorCitation{Luo, Z.; Zhang, Y.; Luo, S.}
-%% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.
-%
-%% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
-%\address{%
-%$^{1}$ \quad School of Computer Science and Technology and the Key Laboratory of Intelligent Textile and Flexible Interconnection of Zhejiang Province, Zhejiang Sci-Tech University, Hangzhou, China; luozhiyi@zstu.edu.cn
-%%$^{2}$ \quad Affiliation 2; e-mail@e-mail.com
-%}
-%
-%% Contact information of the corresponding author
-%\corres{Correspondence: shuyunluo@zstu.edu.cn;}
-
-% Current address and/or shared authorship
-%\firstnote{Current address: Affiliation 3.} 
-%\secondnote{These authors contributed equally to this work.}
-% The commands \thirdnote{} till \eighthnote{} are available for further notes
-
-%\simplesumm{} % Simple summary
-
-%\conference{} % An extended version of a conference paper
-
-% % Here goes the abstract
-\begin{abstract}
-	Multi-span question answering has gained prominence as it aligns more closely with real-world user requirements compared to single-span question answering.
-The utilization of pretrained language models has shown promise in improving multi-span question answering, particularly for factoid questions that necessitate entity-based answers.
-However, existing methods tend to overlook critical information regarding answer span boundaries, resulting in limited accuracy when generating descriptive answers.
-To address this limitation, we propose TOAST, a novel joint learning framework specialized in token-based neighboring transitions that capture answer span boundaries through adjacent word relations.
-Our approach extracts high-quality multi-span answers and is general-purpose, applicable to both alphabet languages like English and logographic languages like Chinese.
-Furthermore, we introduce CLEAN, a comprehensive open-domain Chinese multi-span question answering dataset, which includes a substantial number of descriptive questions.
-	Extensive experiments demonstrate the superior performance of TOAST over previous top-performing QA models in terms of both EM F1 and overlapped F1 scores.
-Specifically, the TOAST models, leveraging  $\text{BERT}_{base}$ and $\text{RoBERTa}_{base}$, achieve substantial  improvements in EM F1 scores, with increments of 3.03/2.13, 4.82/3.73, and 16.26/11.53, across three publicly available datasets, respectively.
-\end{abstract}
-
-% Keywords
-\begin{keywords}
-	Reading comprehension \sep Multi-span question answering \sep  Pretrained language models \sep Multitask learning  \sep Chinese datasets 
-\end{keywords}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Introduction}
@@
 	\item We employs a automatic data augmentation framework using Large Language Model \((LLM)\) as a knowledge source and a extra content supplement to linearize relevant information and possible continuation from LLM as texts, then inject them into original contexts.
-
 	\item We develop a series of prompt templates designed for interacting with ChatGPT to acquire comprehensive explanations of numerous entities.
@@
 
-	\item We propose a new calculation method for the overlap F1 score in multi-span QA task.
-This method can alleviate the issue of lower scores in situations where the model decomposes the answer into multiple complete spans, but the answer’s spans are still entirely correct.
-This approach provides a more accurate reflection of the model’s performance in handling complex multi-span answers.
 \end{itemize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Related Work}
-\label{sec:related}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Our Approach}
-
-	\begin{figure}[h]
-	\centering
-	\includegraphics[width=14.0cm]{overview.png}
-	\caption{An overview of our automatic information augmentation framework.
-\textbf{(a) Step 1}: Interact with ChatGPT to Get Auxiliary Information.
-\textbf{(b) Step 2}: Distilling the Information and Injecting Them into Context \textbf{(c) Step 3}: Input the Augmented Context into Tagging Model}
-	\label{fig:overview}
-	\end{figure}
-
-%\unskip
-	Existing extractive multi-span question answering models exhibit subpar performance in handling ambiguous words, complex proper nouns (such as film and song titles), numerical values, and long descriptive answers.
-The main reasons for these shortcomings can be categorized into three aspects:
-	\begin{itemize}
-		\item Ambiguous Words: The real world is replete with words that have a single form but multiple meanings, which heavily depend on the context.
-For instance, the word "Cameron" could refer to a famous director or a former British Prime Minister, depending on the context.
-The specific meanings of such words often appear infrequently in training corpora, making them difficult to learn.
-		\item Numerical Values: In contrast to ambiguous words, numerical values have a single meaning but can be represented in various forms.
-For example, "22.5 billion years" can also be expressed as "cosmic years".
-		\item Multi-span Answers: In extractive multi-span question answering tasks, the model needs to grasp the overall relationship of multi-span answers in the context, such as parallelism and progression.
-		These challenges require the model to possess a high level of comprehensive understanding ability and knowledge about language and the world.
-	\end{itemize}
-
-	Leveraging large language models to parse question-answering data and inject auxiliary knowledge into the model can promote the integration of the model's latent world knowledge and specific domain knowledge in the paragraph, thereby enhancing the model's performance.
-Thus, we use GPT-3.5-turbo to generate entity annotations, entity association analysis, and content continuation for each question-answering paragraph as auxiliary information for the model:
-	\begin{itemize}
-		\item Context Supplementary: By inserting explanations of entities in the form of annotations after the main entities or concept words in the question and paragraph, this method helps the model capture the actual meaning of ambiguous words in specific contexts.
-It provides direct information prompts for low-frequency meanings or low-frequency words, achieving entity or concept alignment in the question-answering system.
-		\item Context Enrichment: By integrating entity association analysis and content continuation with the original question-answering text to form new paragraphs based on knowledge enhancement, this method captures the inherent associations between words or entity concepts with the same meaning but different forms.
-On one hand, it parses the logical relationships between other entities using entity relationship analysis.
-On the other hand, it extends the original paragraph information using content continuation, introducing more external knowledge while helping the model understand the overall content direction of the paragraph, thereby enhancing the model's comprehension ability.
-	\end{itemize}
-
-	Overall,we design an automated knowledge enhancement method for multi-span question answering tasks, which interacts with large language models based on templates.
-This method is applicable to all question answering models or frameworks.
-It is universally applicable to any other downstream tasks that contain paragraph data, without the need for any complex calculations.
-In the following sections, we will provide a detailed introduction to each specific module of this process.
-
-\subsection{Construction of Prompt Template}
-\label{sec:prompt_construction}
-	\begin{figure}[h]
-		\centering
-		\includegraphics[width=14.5cm]{Prompts_construction.png}
-		\caption{Prompt Templates and it's Construction}
-		\label{fig:prompt_template}
-	\end{figure}
-
-\subsection{Information Injection}
-\label{sec:information_injection}
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=10cm]{EntityInsert.png}
-	\caption{The Process of Inserting Entity Explanation into Context}
-	\label{fig:entity_insertion}
-\end{figure}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=10cm]{RandomConcat.png}
-	\caption{The Process of Concatenation of Original Context and Auxiliary Information}
-	\label{fig:random_concatenate}
-\end{figure}
-
-\subsection{Information Integration}
-\label{sec:information_integration}
-
-\section{Experiments}
-In this section, we compare our information augmentation approach with multiple strong baseline on multi-span question answering.
-We first introduce the datasets and experiment setup, then show the experimental results and analysis for different model.
-
-\subsection{Evaluation Dataset}
-\label{sec:datasets}
-	 We conducted experiments on MultiSpanQA(Li et al., 2022), a recently introduced Reading Comprehension dataset designed for multi-span question answering.
-This dataset comprises 6.5K multi-span examples in which the questions represent user queries issued to the Google search engine, and the contexts are extracted from the English Wikipedia.
-It's worth noting that there is a expand variant of MultiSpanQA known as MultispanQA(expand), which intakes single-span and answerable questions.
-However, we did not perform a comparison with the expanded dataset due to its relatively lower proportion of multi-span QA pairs.
-
-\subsection{Experimental Setup}
-	For all competing models and our model, we use the HuggingFace implementation of $\text{BERT}_{base}$ or $\text{RoBERTa}_{base}$ as the \textit{encoder} with $\textit{max\_len}$ = 512.
-We set the initial learning rate as $3 \times 10^{-5}$ and  $\textit{batch\_size}$ = 4, and use the BERTAdam optimizer with a weight decay of 0.01.
-Our approach does not involve tuning the parameters on the validation set.
-Instead, we rely on the model checkpoints obtained after 5 epochs.
-Next, we introduce the comparison model and evaluation metrics in our experiments.
-
-	\subsubsection{\textit{Model Under Comparison}}
-	\label{sec:baselines}
-	We introduce two comstracting models approaches to multi-span answer extraction : \textbf{TASE} (Segal et al., 2020) and \textbf{LIQUID}(Lee et al., 2023).
-TASE utilizes a tag-based span extraction model which identifies multi-span answers though the assigning a tag to every input token with BIO tagging scheme.
-On the other hand, LIQUID serves as a framework for generating multi-span QA datasets to improve model performance.
-
-	To enhance the context with auxiliary information, we employ two distinct   approaches: \textbf{$\text{AUG}_{c}$} and \textbf{$\text{AUG}_{eree}$}, where \textbf{AUG} is our automatic data augmentation framework,and the suffix indicates which kind of information is injected into the context.
-\textbf{$\text{AUG}_{C}$} enriches the context with continue writing, while \textbf{$\text{AUG}_{EREE}$} supplements context with entities information including explanation and relationship analysis.
-	Specifically, we leverage ChatGPT as a knowledge source to linearize the relevant information from large language models.
-in texts format and seamlessly integrate into the original contexts, thus reinforces the information of model inputs.
-
-	\subsubsection{\textit{Evaluation Metrics}}
-	\label{sec:metrics}
-	We use two automatic metrics for evaluation: Exact Match and Overlap F1 score.
-	\begin{itemize}
-		\item \textbf{Exact Match}. An exact match occurs when a predicted span fully matches one of the ground-truth
-		answer spans. We calculate the micro-average precision, recall and f1 score for the extract match
-		metric.
-
-		\item \textbf{Overlap F1 score}. Overlap F1 score is the macro-average f1 score, where the f1 score for each
-		example is computed by treating the prediction and gold as a bag of tokens.
-	\end{itemize}
-
-\subsection{Experimental Results and Analysis}
-	In this section, we compare $\text{AUG}$ with all competing models described above quantitatively.
-
-	\subsubsection{\textit{Comparison Results}}
-	We evaluate our model as well as baselines 
-	\(( Section ~\ref{sec:baselines} )\) on the development splits of multi-span datasets \(( Section  ~\ref{sec:datasets})\) using automatic metrics \(( Section ~\ref{sec:datasets})\).
-The comparison results are shown in Table \ref{tab:bertall}, Table \ref{tab:robertaall}.
-
-	\begin{table}[width=\textwidth,cols=9,pos=h]  % 
-		\caption{Approach performance on complete MultiSpanQA valid set based on $\text{BERT}_{base}$.} 
-		\label{tab:bertall}
-		\begin{tabular*}{\textwidth}{p{1.5cm}cccccccc}
-			\toprule
-			\multirow{2}{*}{\textbf{Model}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match}  \\
-			\cline{2-7} 
-			\addlinespace
-			& F\((\%)\)           & P\((\%)\)          & R\((\%)\)           & F\((\%)\)          & P\((\%)\)           & R\((\%)\)           \\
-			\midrule
-			TASE   & 60.28         & 55.59         & 65.83         & 78.16         & 78.27         & 78.06         \\ 
-			LIQUID & 61.44         & 58.39         & 64.84         & 78.56         & 78.65         & 78.46         \\
-			$\text{AUG}_{c}$ & 63.05         & 58.51         & 68.34         & 79.42         & 78.70         & 80.14         \\
-			$\text{AUG}_{eree}$  & 63.93          & 60.22         & 68.13          & 77.50         & 77.07          & 77.94         \\
-			$\text{AUG}_{ereec}$ & 62.90          & 61.02        & 64.89          & 76.72         & 78.56          & 74.97         \\
-			Bagging & 64.44          & 61.63        & 67.50          & 79.52         & 80.49          & 78.57         \\
-			\bottomrule
-		\end{tabular*}
-		%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
-	\end{table}
-
-	\begin{table}[width=\textwidth,cols=8,pos=h]  
-		\caption{Approach performance on complete MultiSpanQA valid set based on $\text{RoBERTa}_{base}$.} 
-		\label{tab:robertaall}
-		\begin{tabular*}{\textwidth}{p{1.5cm}ccccccc}
-			\toprule
-			\multirow{2}{*}{\textbf{Model}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match}  \\
-			\cline{2-7} 
-			\addlinespace
-			& F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
-			\midrule
-			TASE & 68.00 & 65.06 & 71.22 & 83.13 & 83.05 & 83.22 \\ 
-			LIQUID & 68.33 & 66.68 & 70.07 & 82.71 & 82.45 & 82.98 \\
-			$\text{AUG}_{c}$ & 70.35 & 67.35 & 73.63 & 84.06 & 83.38 & 84.76 \\
-			$\text{AUG}_{eree}$ & 69.15 & 67.81 & 70.54 & 82.85 & 83.90 & 81.83 \\
-			$\text{AUG}_{ereec}$ & 70.44 & 67.83 & 73.26 & 82.80 & 82.45 & 83.15 \\
-			Bagging & 70.86 & 69.03 & 72.79 & 84.82 & 85.53 & 84.12 \\
-			\bottomrule
-		\end{tabular*}      
-		%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
-	\end{table}
-	Table~\ref{tab:bertall} and Table~\ref{tab:robertaall} illustrate the performance comparison between the proposed approaches, $\text{AUG}_{c}$ and $\text{AUG}_{eree}$, and several strong baselines, including the previous state-of-the-art model LIQUID.
-These comparisons are conducted using both the $\text{BERT}_{base}$ and $\text{RoBERTa}_{base}$ encoders, and regard multi-span question answering as a \textit{BIO} sequence tagging task to predict each token whether it is a part or begin of an answer.
-	Notably,$\text{AUG}_{c}$ exhibit superior performance across the evaluate dataset on all metrics.
-However, on Partial Match scores, $\text{AUG}_{eree}$ demonstrates slightly lower performance compared to TASE, and especially lower than LIQUID when employing the $\text{BERT}_{base}$ encoder.
-	Importantly, the performance of $\text{AUG}_{c}$ consistently outperforms LIQUID and TASE on all metrics and encoders, irrespective of the encoder setting.
-	These results demonstrate the effectiveness of our proposed framework, as well as the efficacy of the information augmentation strategy.
-
-	To be more specific, Table~\ref{tab:bertall} shows comparisons of metrics among all competing models 100 backed by $\text{BERT}_{base}$.
-We can see that our proposed framework, AUG, consistently outperforms all other baselines across multispanQA dataset.
-Backed by $\text{BERT}_{base}$, $\text{AUG}_{c}$ achieves EM and Overlap F1 scores of 63.05 and 79.42, respectively.
-Moreover, when equipped with entities’ information,  $\text{AUG}_{eree}$ achieves even higher EM F1 scores of 63.93 but relatively lower Overlap F1 of 77.50 than baselines on the same encoder.
-These results showcase substantial improvements over the previous state-of-the-art model, LIQUID, with EM F1 score enhancements ranging from 1.61 to 2.49 percents across validation datasets.
-
-	Additionally, when utilizing $\text{RoBERTa}_{base}$ instead of $\text{BERT}_{base}$, $\text{AUG}_{c}$ achieves EM and Overlap F1 scores of 70.35 and 84.06 respectively on the same datasets.
-These scores represent EM and Overlap F1 improvements of 2.02 and 0.93 compared to the previous setup.
-For  $\text{AUG}_{eree}$, the EM F1 score represents an enhancement of 0.82, with the EM and Overlap F1 values of 69.16 and 82.85 respectively.
-Notably, the partial metrics also indicate lower values compared to TASE and LIQUID, in line with the result supported by $\text{BERT}_{base}$.
-This is because augmenting the model with entity information, including definition and relationship knowledge, strengthens its ability to capture and understand entity concepts, which leads the model to prefer complete entity spans as answers rather than partial entity span, and therefore a decrease in the partial recall and ultimately a lower partial F1 scores and a higher EM F1.
-
-	Totally, the result, displayed in Table~\ref{tab:robertaall} demonstrates the same trends to Table~\ref{tab:bertall}.
-And the outcome highlights robustness in effectively generalizing across different datasets without requiring hyperparameter re-tuning.
-
-\subsubsection{\textit{Discussion}}
-	Besides, Table~\ref{tab:bertall} and Table~\ref{tab:robertaall} also discuss the performance of different augmentation integrated strategies, including the results-bagging methods whose outputs are voting results of $\text{AUG}_{c}$, $\text{AUG}_{eree}$ as well as LIQUID, and the input-fusion model $\text{AUG}_{ceree}$ who injects all kinds of information above into input contexts.
-
-	In detail, with EM f1 scores of 62.90 and 64.44 in Table~\ref{tab:bertall} and 70.44 and 70.86 in Table~\ref{tab:robertaall}, both the $\text{AUG}_{ceree}$ and Bagging methods consistently surpass TASE and LIQUID, which exhibits robust effectiveness of information injection strategies.
-However, there is a little decrease caused by fusing all auxiliary information when contrast with single information augmentation strategies and the bagging method.
-This may be due to the likelihood that incorporating all of the augmentation information into the model inputs will confuse the model by introducing excessive auxiliary knowledge and underrepresented original context proportion.
-Therefore it may be more useful that adding limit information into context, and using result-bagging method, a multi-model voting to bringing all information into model with an indirect way.
-
-	From the Partial Match perspective, $\text{AUG}_{ceree}$ and the Bagging method achieve 76.72 and 79.52 in Table~\ref{tab:bertall}, and 82.80 and 84.82 in Table~\ref{tab:robertaall}.
-In accordance with Exact Match metrics, Bagging demonstrate a overall superior performance.
-Meanwhile overlap f1 score of $\text{AUG}_{eree}$ is inferior to TASE but superior to LIQUID ,with relatively higher precision and relativelv higher recall, which  is comparable to all single augmented models such as $\text{AUG}_{eree}$.
-And its weak performance on overlap f1 also reveals complete entities preference of this information injection approach.
-	z
-	In addition, we	categorized the data in MultispanQA into DESC, NUM, ENTYS in terms of answer types, and compared the performance of each of the model mentioned above in each breakdown category.
-Specifically,  Table~\ref{tab:bertsub} and Table~\ref{tab:robertasub} present the results backed by  $\text{BERT}_{base}$ and $\text{RoBERTa}_{base}$, respectively.
-As shown in Tables~\ref{tab:bertsub},Table~\ref{tab:robertasub}, our proposed models display superior performance in DESC and ENTYS categories answer extraction, which to some extent indicates the enhancement of models' knowledge at entity and description levels.
-
-	\textcolor{red}{please supplements new overlap calculation method in tase-zh}
-
-	\begin{table}[ht]
-		\caption{Model performance on complete MultiSpanQA valid Subset with different answer types based on $\text{BERT}_{base}$.}
-		\label{tab:bertsub}
-		\begin{tabular*}{\textwidth}{cp{1.5cm}ccccccc}
-			\toprule
-			\multirow{2}{*}{\textbf{Type}} & \multirow{2}{*}{\textbf{Model}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match} \\
-			\cmidrule{3-8} 
-			& & F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
-			\midrule
-			\multirow{6}{*}{DESC} & TASE & 32.76 & 27.33 & 40.87 & 64.46 & 68.61 & 60.79 \\ 
-			& LIQUID & 36.69 & 31.10 & 44.71 & 66.05 & 65.95 & 66.15 \\
-			& $\text{AUG}_{c}$ & 38.74 & 32.89 & 47.12 & 68.31 & 70.32 & 66.42 \\
-			& $\text{AUG}_{eree}$ & 44.69 & 40.71 & 49.52 & 63.12 & 67.16 & 59.53 \\
-			& $\text{AUG}_{ereec}$ & 40.63 & 38.30 & 43.27 & 64.25 & 71.15 & 58.57 \\
-			& Bagging & 39.91 & 36.69 & 43.75 & 66.70 & 73.68 & 60.93 \\
-			\midrule
-			\multirow{6}{*}{NUM} & TASE & 33.33 & 30.23 & 37.14 & 60.98 & 71.99 & 52.89 \\ 
-			& LIQUID & 34.33 & 31.25 & 38.10 & 60.68 & 68.15 & 54.69 \\
-			& $\text{AUG}_{c}$ & 35.96 & 33.33 & 39.05 & 64.47 & 71.56 & 58.65 \\
-			& $\text{AUG}_{eree}$ & 36.20 & 34.48 & 38.10 & 59.02 & 65.63 & 53.62 \\
-			& $\text{AUG}_{ereec}$ & 36.71 & 37.25 & 36.19 & 57.09 & 69.04 & 48.67 \\
-			& Bagging & 35.94 & 34.82 & 37.14 & 60.73 & 71.15 & 52.97 \\
-			\midrule
-			\multirow{6}{*}{ENTYS} & TASE & 66.30 & 62.21 & 70.96 & 81.16 & 80.37 & 81.96 \\ 
-			& LIQUID & 67.17 & 65.25 & 69.21 & 81.66 & 81.69 & 81.63 \\
-			& $\text{AUG}_{c}$ & 68.47 & 64.44 & 73.03 & 81.93 & 80.57 & 83.34 \\
-			& $\text{AUG}_{eree}$ & 68.36 & 64.64 & 72.53 & 80.55 & 79.21 & 81.93 \\
-			& $\text{AUG}_{ereec}$ & 67.54 & 65.60 & 69.59 & 79.49 & 80.16 & 78.83 \\
-			& Bagging & 69.65 & 66.94 & 72.59 & 82.31 & 82.07 & 82.55 \\
-			\bottomrule
-		\end{tabular*}
-	\end{table}
-
-	\begin{table}[ht]
-		\caption{Model performance on complete MultiSpanQA valid Subset with different answer types based on $\text{RoBERTa}_{base}$.}
-		\label{tab:robertasub}
-		\begin{tabular*}{\textwidth}{cp{1.5cm}ccccccc}
-			\toprule
-			\multirow{2}{*}{\textbf{Type}} & \multirow{2}{*}{\textbf{Model}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match} \\
-			\cmidrule{3-8} 
-			& & F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
-			\midrule
-			\multirow{6}{*}{DESC} & TASE & 45.53 & 40.84 & 51.44 & 75.44 & 76.61 & 74.31 \\ 
-			& LIQUID & 48.68 & 44.76 & 53.37 & 73.27 & 71.57 & 75.04 \\
-			& $\text{AUG}_{c}$ & 49.02 & 44.66 & 54.33 & 76.33 & 77.85 & 74.86 \\
-			& $\text{AUG}_{eree}$ & 50.99 & 46.96 & 55.77 & 76.87 & 78.07 & 75.71 \\
-			& $\text{AUG}_{ereec}$ & 49.24 & 44.71 & 54.81 & 71.87 & 73.03 & 70.74 \\
-			& Bagging & 47.70 & 43.78 & 52.40 & 77.43 & 80.63 & 74.47 \\
-			\midrule
-			\multirow{6}{*}{NUM} & TASE & 46.23 & 45.79 & 46.67 & 71.89 & 78.42 & 66.36 \\ 
-			& LIQUID & 40.19 & 39.45 & 40.95 & 67.56 & 72.28 & 63.42 \\
-			& $\text{AUG}_{c}$ & 50.69 & 49.11 & 52.38 & 72.86 & 80.22 & 66.74 \\
-			& $\text{AUG}_{eree}$ & 42.40 & 41.07 & 43.81 & 66.67 & 73.51 & 61.00 \\
-			& $\text{AUG}_{ereec}$ & 45.58 & 44.55 & 46.67 & 65.86 & 73.19 & 59.87 \\
-			& Bagging & 44.65 & 43.64 & 45.71 & 70.11 & 78.49 & 63.35 \\
-			\midrule
-			\multirow{6}{*}{ENTYS} & TASE & 72.57 & 69.94 & 75.41 & 84.90 & 84.32 & 85.48 \\ 
-			& LIQUID & 72.95 & 71.77 & 74.16 & 85.02 & 84.75 & 85.29 \\
-			& $\text{AUG}_{c}$ & 74.59 & 71.87 & 77.53 & 85.79 & 84.40 & 87.23 \\
-			& $\text{AUG}_{eree}$ & 73.50 & 72.81 & 74.22 & 84.74 & 85.49 & 83.99 \\
-			& $\text{AUG}_{ereec}$ & 75.04 & 72.81 & 77.41 & 85.37 & 84.46 & 86.29 \\
-			& Bagging & 75.85 & 74.52 & 77.22 & 86.73 & 86.73 & 86.74 \\
-			\bottomrule
-		\end{tabular*}
-	\end{table}
-
-\subsubsection{\textit{Ablation Experiment}}
-	At the end of this section, we conducted ablations on our approach to confirm the effectiveness of selecting the information injection proportion.
-For each QA data, we randomly split the original context and the auxiliary text, then concatenated them into a final augmented context with a specific proportion to ensure that the new input length meets $\textit{max\_len}$, which has a crucial impact on our approach.
-In practice, we determined the final text splicing ratio by calculating the ratio of the average length of the source text to the added information, which for the $\text{AUG}_{c}$ is 0.86.
-
-	Specifically, Table~\ref{tab:different_ratio_bert} and Table~\ref{tab:different_ratio_roberta} displays $\text{AUG}_{c}$'s performance with differential proportion to concatenate original contexts and continuation, on complete MultispanQA valid set,backed by $\text{BERT}_{base}$ and $\text{RoBERTa}_{base}$ respectively.
-We choose five proportions for information integration, which determine how much auxiliary information would be inject into each overflowed text segment.
-The results presented in tables indicate that using the ratio of their average lengths as the proportion of the overflow text composed of original text and auxiliary information is an effective approach.
-In detail, $\text{AUG}_{c}$,equipping with $\text{BERT}_{base}$, achieves an Exact Match F1 scores improvements of at least 4.57 compared to other proportions and an overlap F1 scores improvements of at least 2.07.
-In line with Table~\ref{tab:different_ratio_bert}, when $\text{AUG}_{c}$ equips with $\text{Roberta}_{base}$, it achieves an improvement of Exact Match F1 scores of 0.55 but an decrease of Overlap F1 scores of 0.17.
-
-\begin{table}[width=.6\textwidth,cols=8,pos=h]
-	\caption{Ablations of $\text{AUG}_{c}$ on different proportion for information concatenation, based on $\text{BERT}_{base}$.} 
-	\label{tab:different_ratio_bert}
-	\begin{tabular*}{\tblwidth}{cccccccc}
-%	\begin{tabularx}{\textwidth}{p{1.7cm}ccccccc}
-		\toprule
-		\multirow{2}{*}{\textbf{Proportion}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match}  \\
-		\cline{2-7} 
-		\addlinespace
-		& F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
-		\midrule
-		0.90 & 58.55 & 57.69 & 59.44 & 71.88 & 74.30 & 69.61 \\ 
-		0.70 & 61.70 & 59.03 & 64.63 & 76.58 & 77.84 & 75.36 \\
-		0.50 & 61.22 & 57.37 & 65.62 & 77.38 & 77.61 & 77.16 \\
-		0.40 & 61.36 & 56.50 & 67.13 & 78.26 & 77.57 & 78.96 \\
-		0.10 & 61.41 & 56.36 & 67.45 & 78.94 & 78.45 & 79.44 \\
-		0.14 & 63.05 & 58.51 & 68.34 & 79.42 & 78.70 & 80.14 \\
-		\bottomrule
-	\end{tabular*}
-	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
-\end{table}
-
-%\begin{table}[H] 
-%	\caption{Ablations of $\text{AUG}_{c}$ on different proportion for information concatenation, based on $\text{BERT}_{base}$.} 
-%	\label{tab:different_ratio_roberta}
-%	\newcolumntype{C}{>{\centering\arraybackslash}X}
-%	\begin{tabularx}{\textwidth}{p{1.7cm}CCCCCCC}
-%		\toprule
-%		\multirow{2}{*}{\textbf{Proportion}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match}  \\
-%		\cline{2-7} 
-%		\addlinespace
-%		& F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
-%		\midrule
-%		0.90 & 58.13 & 56.92 & 59.39 & 71.70 & 73.49 & 69.98 \\ 
-%		0.70 & 66.97 & 65.42 & 68.60 & 80.05 & 80.80 & 79.32 \\
-%		0.50 & 68.94 & 67.23 & 70.75 & 82.43 & 83.23 & 81.64 \\
-%		0.40 & 68.95 & 66.11 & 71.06 & 83.71 & 83.71 & 81.71 \\
-%		0.10 & 69.80 & 66.47 & 73.47 & 84.23 & 83.49 & 84.99 \\
-%		0.86 & 70.35 & 67.35 & 73.63 & 84.06 & 83.38 & 84.76 \\
-%		\bottomrule
-%	\end{tabularx}      
-%	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
-%\end{table}
-%
-%\section{Conclusion}
-
-%All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, etc.
-
-%\section{Discussion}
-%
-%Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses.
-The findings and their implications should be discussed in the broadest context possible.
-Future research directions may also be highlighted.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Conclusions}
-%
-%This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace{6pt}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-%\supplementary{The following supporting information can be downloaded at:  \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.}
-
-% Only for journal Methods and Protocols:
-% If you wish to submit a video article, please do so with any other supplementary material.
-% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.
-A supporting video article is available at doi: link.}
-
-% Only for journal Hardware:
-% If you wish to submit a video article, please do so with any other supplementary material.
-% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.\vspace{6pt}\\
-%\begin{tabularx}{\textwidth}{lll}
-%\toprule
-%\textbf{Name} & \textbf{Type} & \textbf{Description} \\
-%\midrule
-%S1 & Python script (.py) & Script of python source code used in XX \\
-%S2 & Text (.txt) & Script of modelling code used to make Figure X \\
-%S3 & Text (.txt) & Raw data from experiment X \\
-%S4 & Video (.mp4) & Video demonstrating the hardware in use \\
-%... & ... & ... \\
-%\bottomrule
-%\end{tabularx}
-%}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided.
-The following statements should be used ``Conceptualization, X.X.
-and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y.
-and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing---original draft preparation, X.X.; writing---review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y.
-All authors have read and agreed to the published version of the manuscript.'', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation.
-Authorship must be limited to those who have contributed substantially to the work~reported.}
-
-%=====================================
-% References, variant A: external bibliography
-%=====================================
-%\bibliography{your_external_BibTeX_file}
-
-\section*{Acknowledgements}
-This research was supported by the Natural Science Foundation of Zhejiang Province, China (Grant No.
-LQ22F020027), Fundamental Research Funds of Zhejiang Sci-Tech University (Grant No.
-23232138-Y), Liaoning Provincial Natural Science Foundation of China (Grant No.
-2022-KF-21-01) and the Key Research and Development Program of Zhejiang Province, China (Grant No.
-2023C01041 and 2022C01079).
-
-\bibliographystyle{cas-model2-names}
-% 
-\bibliography{refs}
-\end{document}

### 2024-01-12 method.tex
x

--- 2023-10-16 paper.tex
@@
-% !TeX program = xelatex 
-%% 
-%% Copyright 2019-2021 Elsevier Ltd
-%% 
-%% This file is part of the 'CAS Bundle'.
-%% --------------------------------------
-%% 
-%% It may be distributed under the conditions of the LaTeX Project Public
-%% License, either version 1.2 of this license or (at your option) any
-%% later version.  The latest version of this license is in
-%%    http://www.latex-project.org/lppl.txt
-%% and version 1.2 or later is part of all distributions of LaTeX
-%% version 1999/12/01 or later.
-%% 
-%% The list of all files belonging to the 'CAS Bundle' is
-%% given in the file `manifest.txt'.
-%% 
-%% Template article for cas-dc documentclass for 
-%% double column output.
-
-\documentclass[a4paper,fleqn,twocolumn]{cas-dc}
-
-% If the frontmatter runs over more than one page
-% use the longmktitle option.
-
-%\documentclass[a4paper,fleqn,longmktitle]{cas-dc}
-
-%\usepackage[numbers]{natbib}
-%\usepackage[authoryear]{natbib}
-\usepackage[authoryear,longnamesfirst]{natbib}
-
-%\usepackage[numbers]{natbib}
-\usepackage[authoryear]{natbib}
-%\usepackage[authoryear,longnamesfirst]{natbib}
-\usepackage{dsfont}
-\usepackage{array}
-\usepackage{float}
-\usepackage{placeins}
-\usepackage{makecell} % add by shuyun
-%\usepackage[utf8]{inputenc}
-\usepackage{lineno,hyperref}
-\usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage[small]{caption}
-\usepackage{subcaption}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{multicol}
-\usepackage{diagbox}
-\usepackage{mathrsfs}
-\usepackage{color}
-\usepackage{booktabs}
-\usepackage{soul}
-\usepackage{mathspec}
-\usepackage{xeCJK}
-%
-
-%\setCJKmainfont{STKaiti}
-
-%\setCJKmainfont[Mapping=tex-text]{STKaiti}
-\usepackage[ruled, linesnumbered, vlined]{algorithm2e}
-
-%\linenumbers
-%%%Author macros
-\def\tsc#1{\csdef{#1}{\textsc{\lowercase{#1}}\xspace}}
-\tsc{WGM}
-\tsc{QE}
-
-\newcommand{\1}[1]{\mathds{1}\left[#1\right]}
-\renewcommand{\floatpagefraction}{0.8}
-
-\newcommand{\secref}[1]{Section \ref{#1}}
-\newcommand{\figref}[1]{Figure \ref{#1}}
-\newcommand{\eqnref}[1]{Eq. (\ref{#1})}
-\newcommand{\exref}[1]{Example \ref{#1}}
-\newcommand{\algoref}[1]{Algorithm \ref{#1}}
-\newcommand{\tableref}[1]{Table \ref{#1}}
-\newcommand{\socvec}{SocVec}
-\newcommand{\argmin}{\operatornamewithlimits{argmin}}
-\newcommand{\argmax}{\operatornamewithlimits{argmax}}
-\newtheorem{example}{Example}
-\newtheorem{lemma}{Lemma}
-\newtheorem{definition}{Definition}
-\newcommand{\cut}[1]{}
-\newcommand{\ZY}[1]{\textcolor{red}{Zhiyi: #1}}
-
-\begin{document}
-%	\begin{multicols}{2}
-\let\WriteBookmarks\relax
-\def\floatpagepagefraction{1}
-\def\textpagefraction{.001}
-
-% Short title
-\shorttitle{Empowering Multi-Span Question Answering with Expansive Information Injection using Large Language Models}
-
-% Short author
-\shortauthors{Z. Luo et al.}
-
-% Main title of the paper
-\title{Empowering Multi-Span Question Answering with Expansive Information Injection using Large Language Models}
-
-\author{Zhiyi Luo}[type=editor,auid=000,bioid=1,orcid=0000-0002-2206-1926]
-%\cormark[1]
-\ead{luozhiyi@zstu.edu.cn}
-\ead[url]{http://zhiyiluo.site}
-%\credit{Conceptualization of this study, Methodology, Software}
-
-\author{Yingying Zhang}
-\ead{272831920@qq.com}
-
-\author{Shuyun Luo}
-\ead{shuyunluo@zstu.edu.cn}
-\cormark[1]
-\cortext[mycorrespondingauthor]{Corresponding author}
-
-\address[mymainaddress]{School of Computer Science and Technology and the Key Laboratory of Intelligent Textile and Flexible Interconnection of Zhejiang Province, Zhejiang Sci-Tech University}
-\address[mysecondaryaddress]{No. 928, No. 2 street, Baiyang street, Qiantang New District, Hangzhou 310018, China}
-
-%\Title{Empowering Multi-Span Question Answering with Expansive Information Injection using Large Language Models}
-%
-%% MDPI internal command: Title for citation in the left column
-%\TitleCitation{Title}
-%
-%% Author Orchid ID: enter ID or remove command
-%\newcommand{\orcidauthorA}{0000-0002-2206-1926} % Add \orcidA{} behind the author's name
-%%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name
-%
-%
-%% Authors, for the paper (add full first names)
-%\Author{Zhiyi Luo $^{1}$\orcidA{}, Yingying Zhang$^{1}$ and Shuyun Luo $^{1,}$*}
-%
-%%\longauthorlist{yes}
-%
-%% MDPI internal command: Authors, for metadata in PDF
-%\AuthorNames{Zhiyi Luo, Yingying Zhang and Shuyun Luo}
-%
-%% MDPI internal command: Authors, for citation in the left column
-%\AuthorCitation{Luo, Z.; Zhang, Y.; Luo, S.}
-%% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.
-%
-%% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
-%\address{%
-%$^{1}$ \quad School of Computer Science and Technology and the Key Laboratory of Intelligent Textile and Flexible Interconnection of Zhejiang Province, Zhejiang Sci-Tech University, Hangzhou, China; luozhiyi@zstu.edu.cn
-%%$^{2}$ \quad Affiliation 2; e-mail@e-mail.com
-%}
-%
-%% Contact information of the corresponding author
-%\corres{Correspondence: shuyunluo@zstu.edu.cn;}
-
-% Current address and/or shared authorship
-%\firstnote{Current address: Affiliation 3.} 
-%\secondnote{These authors contributed equally to this work.}
-% The commands \thirdnote{} till \eighthnote{} are available for further notes
-
-%\simplesumm{} % Simple summary
-
-%\conference{} % An extended version of a conference paper
-
-% % Here goes the abstract
-\maketitle
-
-\begin{abstract}
-	Multi-span question answering has gained prominence as it aligns more closely with real-world user requirements compared to single-span question answering.
-The utilization of pretrained language models has shown promise in improving multi-span question answering, particularly for factoid questions that necessitate entity-based answers.
-However, existing methods tend to overlook critical information regarding answer span boundaries, resulting in limited accuracy when generating descriptive answers.
-To address this limitation, we propose TOAST, a novel joint learning framework specialized in token-based neighboring transitions that capture answer span boundaries through adjacent word relations.
-Our approach extracts high-quality multi-span answers and is general-purpose, applicable to both alphabet languages like English and logographic languages like Chinese.
-Furthermore, we introduce CLEAN, a comprehensive open-domain Chinese multi-span question answering dataset, which includes a substantial number of descriptive questions.
-	Extensive experiments demonstrate the superior performance of TOAST over previous top-performing QA models in terms of both EM F1 and overlapped F1 scores.
-Specifically, the TOAST models, leveraging  $\text{BERT}_{base}$ and $\text{RoBERTa}_{base}$, achieve substantial  improvements in EM F1 scores, with increments of 3.03/2.13, 4.82/3.73, and 16.26/11.53, across three publicly available datasets, respectively.
-\end{abstract}
-
-% Keywords
-\begin{keywords}
-	Reading comprehension \sep Multi-span question answering \sep  Pretrained language models \sep Multitask learning  \sep Chinese datasets 
-\end{keywords}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Introduction}
-\label{sec:intro}
-
-In summary, the main contributions in this paper are as follows:
-\begin{itemize}
-	\item We employs a automatic data augmentation framework using Large Language Model \((LLM)\) as a knowledge source and a extra content supplement to linearize relevant information and possible continuation from LLM as texts, then inject them into original contexts.
-	\item We develop a series of prompt templates designed for interacting with ChatGPT to acquire comprehensive explanations of numerous entities.
-These templates ensure that the formats of the responses provided by ChatGPT are highly parseable and well-structured.
-
-\end{itemize}
-
-%The introduction should briefly place the study in a broad context and highlight why it is important.
-It should define the purpose of the work and its significance.
-The current state of the research field should be reviewed carefully and key publications cited.
-Please highlight controversial and diverging hypotheses when necessary.
-Finally, briefly mention the main aim of the work and highlight the principal conclusions.
-As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research.
-Citing a journal paper \cite{ref-journal}.
-Now citing a book reference \cite{ref-book1,ref-book2} or other reference types \cite{ref-unpublish,ref-communication,ref-proceeding}.
-Please use the command \citep{ref-thesis,ref-url} for the following MDPI journals, which use author--date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, Journal of Intelligence, Journalism and Media, JRFM, Languages, Laws, Religions, Risks, Social Sciences, Literature.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Related Work}
-\label{sec:related}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Our Approach}
@@
 In cases of tie-breaking, we prioritize the logits' magnitude to ascertain the ultimate prediction.
-
-\section{Experiments}
-In this section, we compare our information augmentation approach with multiple strong baseline on multi-span question answering.
-We first introduce the datasets and experiment setup, then show the experimental results and analysis for different model.
-
-\subsection{Evaluation Dataset}
-\label{sec:datasets}
-	 We conducted experiments on MultiSpanQA(Li et al., 2022), a recently introduced Reading Comprehension dataset designed for multi-span question answering.
-This dataset comprises 6.5K multi-span examples in which the questions represent user queries issued to the Google search engine, and the contexts are extracted from the English Wikipedia.
-It's worth noting that there is a expand variant of MultiSpanQA known as MultispanQA(expand), which intakes single-span and answerable questions.
-However, we did not perform a comparison with the expanded dataset due to its relatively lower proportion of multi-span QA pairs.
-
-\subsection{Experimental Setup}
-	For all competing models and our model, we use the HuggingFace implementation of $\text{BERT}_{base}$ or $\text{RoBERTa}_{base}$ as the \textit{encoder} with $\textit{max\_len}$ = 512.
-We set the initial learning rate as $3 \times 10^{-5}$ and  $\textit{batch\_size}$ = 4, and use the BERTAdam optimizer with a weight decay of 0.01.
-Our approach does not involve tuning the parameters on the validation set.
-Instead, we rely on the model checkpoints obtained after 5 epochs.
-Next, we introduce the comparison model and evaluation metrics in our experiments.
-
-	\subsubsection{\textit{Model Under Comparison}}
-	\label{sec:baselines}
-	We introduce two comstracting models approaches to multi-span answer extraction : \textbf{TASE} (Segal et al., 2020) and \textbf{LIQUID}(Lee et al., 2023).
-TASE utilizes a tag-based span extraction model which identifies multi-span answers though the assigning a tag to every input token with BIO tagging scheme.
-On the other hand, LIQUID serves as a framework for generating multi-span QA datasets to improve model performance.
-
-	To enhance the context with auxiliary information, we employ two distinct   approaches: \textbf{$\text{AUG}_{c}$} and \textbf{$\text{AUG}_{eree}$}, where \textbf{AUG} is our automatic data augmentation framework,and the suffix indicates which kind of information is injected into the context.
-\textbf{$\text{AUG}_{C}$} enriches the context with continue writing, while \textbf{$\text{AUG}_{EREE}$} supplements context with entities information including explanation and relationship analysis.
-	Specifically, we leverage ChatGPT as a knowledge source to linearize the relevant information from large language models.
-in texts format and seamlessly integrate into the original contexts, thus reinforces the information of model inputs.
-
-	\subsubsection{\textit{Evaluation Metrics}}
-	\label{sec:metrics}
-	We use two automatic metrics for evaluation: Exact Match and Overlap F1 score.
-	\begin{itemize}
-		\item \textbf{Exact Match}. An exact match occurs when a predicted span fully matches one of the ground-truth
-		answer spans. We calculate the micro-average precision, recall and f1 score for the extract match
-		metric.
-
-		\item \textbf{Overlap F1 score}. Overlap F1 score is the macro-average f1 score, where the f1 score for each
-		example is computed by treating the prediction and gold as a bag of tokens.
-	\end{itemize}
-
-\subsection{Experimental Results and Analysis}
-	In this section, we compare $\text{AUG}$ with all competing models described above quantitatively.
-
-	\subsubsection{\textit{Comparison Results}}
-	We evaluate our model as well as baselines 
-	\(( Section ~\ref{sec:baselines} )\) on the development splits of multi-span datasets \(( Section  ~\ref{sec:datasets})\) using automatic metrics \(( Section ~\ref{sec:datasets})\).
-The comparison results are shown in Table \ref{tab:bertall}, Table \ref{tab:robertaall}.
-
-	\begin{table*}[width=\textwidth,cols=9,pos=h]  % 
-		\caption{Approach performance on complete MultiSpanQA valid set based on $\text{BERT}_{base}$.} 
-		\label{tab:bertall}
-		\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccccc}
-			\toprule
-			\multirow{2}{*}{\textbf{Model}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match}  \\
-			\cline{2-7} 
-			\addlinespace
-			& F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
-			\midrule
-			TASE   & 60.28 & 55.59 & 65.83 & 78.16 & 78.27 & 78.06 \\ 
-			LIQUID & 61.44 & 58.39 & 64.84 & 78.56 & 78.65 & 78.46 \\
-			$\text{AUG}_{c}$ & 63.05 & 58.51 & 68.34 & 79.42 & 78.70 & 80.14 \\
-			$\text{AUG}_{eree}$  & 63.93 & 60.22 & 68.13 & 77.50 & 77.07 & 77.94 \\
-			$\text{AUG}_{ereec}$ & 62.90  & 61.02 & 64.89 & 76.72 & 78.56 & 74.97 \\
-			Bagging & 64.44 & 61.63 & 67.50 & 79.5 & 80.49 & 78.57 \\
-			\bottomrule
-		\end{tabular*}
-		%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
-	\end{table*}
-
-	\begin{table*}[width=\textwidth,cols=8,pos=h]  
-		\caption{Approach performance on complete MultiSpanQA valid set based on $\text{RoBERTa}_{base}$.} 
-		\label{tab:robertaall}
-		\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccccc}
-			\toprule
-			\multirow{2}{*}{\textbf{Model}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match}  \\
-			\cline{2-7} 
-			\addlinespace
-			& F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
-			\midrule
-			TASE & 68.00 & 65.06 & 71.22 & 83.13 & 83.05 & 83.22 \\ 
-			LIQUID & 68.33 & 66.68 & 70.07 & 82.71 & 82.45 & 82.98 \\
-			$\text{AUG}_{c}$ & 70.35 & 67.35 & 73.63 & 84.06 & 83.38 & 84.76 \\
-			$\text{AUG}_{eree}$ & 69.15 & 67.81 & 70.54 & 82.85 & 83.90 & 81.83 \\
-			$\text{AUG}_{ereec}$ & 70.44 & 67.83 & 73.26 & 82.80 & 82.45 & 83.15 \\
-			Bagging & 70.86 & 69.03 & 72.79 & 84.82 & 85.53 & 84.12 \\
-			\bottomrule
-		\end{tabular*}      
-		%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
-	\end{table*}
-	Table~\ref{tab:bertall} and Table~\ref{tab:robertaall} illustrate the performance comparison between the proposed approaches, $\text{AUG}_{c}$ and $\text{AUG}_{eree}$, and several strong baselines, including the previous state-of-the-art model LIQUID.
-These comparisons are conducted using both the $\text{BERT}_{base}$ and $\text{RoBERTa}_{base}$ encoders, and regard multi-span question answering as a \textit{BIO} sequence tagging task to predict each token whether it is a part or begin of an answer.
-	Notably,$\text{AUG}_{c}$ exhibit superior performance across the evaluate dataset on all metrics.
-However, on Partial Match scores, $\text{AUG}_{eree}$ demonstrates slightly lower performance compared to TASE, and especially lower than LIQUID when employing the $\text{BERT}_{base}$ encoder.
-	Importantly, the performance of $\text{AUG}_{c}$ consistently outperforms LIQUID and TASE on all metrics and encoders, irrespective of the encoder setting.
-	These results demonstrate the effectiveness of our proposed framework, as well as the efficacy of the information augmentation strategy.
-
-	To be more specific, Table~\ref{tab:bertall} shows comparisons of metrics among all competing models 100 backed by $\text{BERT}_{base}$.
-We can see that our proposed framework, AUG, consistently outperforms all other baselines across multispanQA dataset.
-Backed by $\text{BERT}_{base}$, $\text{AUG}_{c}$ achieves EM and Overlap F1 scores of 63.05 and 79.42, respectively.
-Moreover, when equipped with entities’ information,  $\text{AUG}_{eree}$ achieves even higher EM F1 scores of 63.93 but relatively lower Overlap F1 of 77.50 than baselines on the same encoder.
-These results showcase substantial improvements over the previous state-of-the-art model, LIQUID, with EM F1 score enhancements ranging from 1.61 to 2.49 percents across validation datasets.
-
-	Additionally, when utilizing $\text{RoBERTa}_{base}$ instead of $\text{BERT}_{base}$, $\text{AUG}_{c}$ achieves EM and Overlap F1 scores of 70.35 and 84.06 respectively on the same datasets.
-These scores represent EM and Overlap F1 improvements of 2.02 and 0.93 compared to the previous setup.
-For  $\text{AUG}_{eree}$, the EM F1 score represents an enhancement of 0.82, with the EM and Overlap F1 values of 69.16 and 82.85 respectively.
-Notably, the partial metrics also indicate lower values compared to TASE and LIQUID, in line with the result supported by $\text{BERT}_{base}$.
-This is because augmenting the model with entity information, including definition and relationship knowledge, strengthens its ability to capture and understand entity concepts, which leads the model to prefer complete entity spans or empty span set as answers rather than partial entity span, and therefore a decrease in the partial recall and ultimately a lower partial F1 scores and a higher EM F1.
-
-	To further substantiate our explanation for the suboptimal performance of our model on the Overlap F1 metric, we conducted a detailed examination of the predictions made by $\text{AUG}_{eree}$ and two baseline models on the validation dataset.
-In essence, we tallied the instances where these models predicted empty answers and recalculated their Overlap F1 scores on non-empty predictions.
-This allowed us to investigate whether the $\text{AUG}_{eree}$ model aligns with our hypothesis, which posits that its extensive learning of entity knowledge during training makes it inclined to output either a complete and accurate answer span or no answer at all, as opposed to a partially correct answer span.
-
-	As presented in Table~\ref{tab:answer_counts}, $\text{AUG}_{eree}$ indeed predicted a higher number of empty answers compared to TASE and LIQUID, while achieving relatively higher Overlap F1 scores on non-empty predictions.
-Specifically, when equipped with $\text{BERT}_{base}$ as the encoder, $\text{AUG}_{eree}$ obtained an F1 score of 0.7976 on non-empty answer predictions, whereas TASE and LIQUID scored 0.7964 and 0.7909, respectively.
-With $\text{RoBERTa}_{base}$, $\text{AUG}_{eree}$ achieved an Overlap F1 score of 0.8414, surpassing TASE and LIQUID, which scored 0.8404 and 0.8357, respectively.
-Additionally, it is worth noting that $\text{AUG}_{eree}$ consistently predicted more empty answers, whether using BERT or RoBERTa.
-
-	These findings lend support to our conjecture that the introduction of entity knowledge leads to a slight reduction in the model's Overlap F1 scores.
-This suggests that utilizing LLM as a knowledge source to linearize entity information from LLM text and integrate it into the original context empowers the model to acquire greater entity knowledge, thereby exhibiting a preference for more accurate and complete answer spans, or simply providing no answer.
-
-		\begin{table*}[width=\textwidth,cols=9,pos=h]  % 
-		\caption{The statistics of answers span predicted by $\text{AUG}_{eree}$ and baselines} 
-		\label{tab:answer_counts}
-		\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccccc}
-			\toprule
-			\multirow{2}{*}{\textbf{ }} & \multicolumn{3}{c}{$\text{BERT}_{base}$} & \multicolumn{3}{c}{$\text{RoBERTa}_{base}$}  \\
-			\cline{2-7} 
-			\addlinespace
-			& TASE\((\%)\) & LIQUID\((\%)\) & $\text{AUG}_{eree}$\((\%)\) & TASE\((\%)\) & LIQUID\((\%)\) & $\text{AUG}_{eree}$\((\%)\) \\
-			\midrule
-			empty predictions counts   & 0.0245 & 0.0214 & \textbf{0.0643} & 0.0061 & 0.0153 & \textbf{0.0291} \\ 
-			non-empty Overlap f1  & 0.7964 & 0.7909 & \textbf{0.7976} & 0.8404 & 0.8357 & \textbf{0.8414} \\
-			\bottomrule
-		\end{tabular*}
-		%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
-		\end{table*}
-
-	Totally, the result, displayed in Table~\ref{tab:robertaall} demonstrates the same trends to Table~\ref{tab:bertall}.
-And the outcome highlights robustness in effectively generalizing across different datasets without requiring hyperparameter re-tuning.
-
-\subsubsection{\textit{Discussion}}
-	Table~\ref{tab:bertall} and Table~\ref{tab:robertaall} discuss the performance of different augmentation integrated strategies, including the results-bagging methods whose outputs are voting results of $\text{AUG}_{c}$, $\text{AUG}_{eree}$ as well as LIQUID, and the input-fusion model $\text{AUG}_{ceree}$ who injects all kinds of information above into input contexts.
-
-	In detail, with EM f1 scores of 62.90 and 64.44 in Table~\ref{tab:bertall} and 70.44 and 70.86 in Table~\ref{tab:robertaall}, both the $\text{AUG}_{ceree}$ and Bagging methods consistently surpass TASE and LIQUID, which exhibits robust effectiveness of information injection strategies.
-However, there is a little decrease caused by fusing all auxiliary information when contrast with single information augmentation strategies and the bagging method.
-This may be due to the likelihood that incorporating all of the augmentation information into the model inputs will confuse the model by introducing excessive auxiliary knowledge and underrepresented original context proportion.
-Therefore it may be more useful that adding limit information into context, and using result-bagging method, a multi-model voting to bringing all information into model with an indirect way.
-
-	From the Partial Match perspective, $\text{AUG}_{ceree}$ and the Bagging method achieve 76.72 and 79.52 in Table~\ref{tab:bertall}, and 82.80 and 84.82 in Table~\ref{tab:robertaall}.
-In accordance with Exact Match metrics, Bagging demonstrate a overall superior performance.
-Meanwhile overlap f1 score of $\text{AUG}_{eree}$ is inferior to TASE but superior to LIQUID ,with relatively higher precision and relativelv higher recall, which  is comparable to all single augmented models such as $\text{AUG}_{eree}$.
-And its weak performance on overlap f1 also reveals complete entities preference of this information injection approach.
-
-	Furthermore, we stratified the data within MultispanQA according to answer types, specifically categorizing them into DESC, NUM, and ENTYS.
-We subsequently conducted a comparative analysis of model performance within each of these subcategories.
-In particular, the results are presented in Tables~\ref{tab:bertsub} and Table~\ref{tab:robertasub}, supported by $\text{BERT}_{base}$ and $\text{RoBERTa}_{base}$, respectively.
-	As indicated in Tables~\ref{tab:bertsub} and~\ref{tab:robertasub}, our proposed models exhibit superior performance in terms of EM F1 scores for all categorizing.
-However, they demonstrate suboptimal performance in terms of overlap F1 scores.
-
-	\begin{table*}[ht]
-		\caption{Model performance on complete MultiSpanQA valid Subset with different answer types based on $\text{BERT}_{base}$.}
-		\label{tab:bertsub}
-		\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccccc}
-			\toprule
-			\multirow{2}{*}{\textbf{Type}} & \multirow{2}{*}{\textbf{Model}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match} \\
-			\cmidrule{3-8} 
-			& & F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
-			\midrule
-			\multirow{6}{*}{DESC} & TASE & 32.76 & 27.33 & 40.87 & 64.46 & 68.61 & 60.79 \\ 
-			& LIQUID & 36.69 & 31.10 & 44.71 & 66.05 & 65.95 & 66.15 \\
-			& $\text{AUG}_{c}$ & 38.74 & 32.89 & 47.12 & 68.31 & 70.32 & 66.42 \\
-			& $\text{AUG}_{eree}$ & 44.69 & 40.71 & 49.52 & 63.12 & 67.16 & 59.53 \\
-			& $\text{AUG}_{ereec}$ & 40.63 & 38.30 & 43.27 & 64.25 & 71.15 & 58.57 \\
-			& Bagging & 39.91 & 36.69 & 43.75 & 66.70 & 73.68 & 60.93 \\
-			\midrule
-			\multirow{6}{*}{NUM} & TASE & 33.33 & 30.23 & 37.14 & 60.98 & 71.99 & 52.89 \\ 
-			& LIQUID & 34.33 & 31.25 & 38.10 & 60.68 & 68.15 & 54.69 \\
-			& $\text{AUG}_{c}$ & 35.96 & 33.33 & 39.05 & 64.47 & 71.56 & 58.65 \\
-			& $\text{AUG}_{eree}$ & 36.20 & 34.48 & 38.10 & 59.02 & 65.63 & 53.62 \\
-			& $\text{AUG}_{ereec}$ & 36.71 & 37.25 & 36.19 & 57.09 & 69.04 & 48.67 \\
-			& Bagging & 35.94 & 34.82 & 37.14 & 60.73 & 71.15 & 52.97 \\
-			\midrule
-			\multirow{6}{*}{ENTYS} & TASE & 66.30 & 62.21 & 70.96 & 81.16 & 80.37 & 81.96 \\ 
-			& LIQUID & 67.17 & 65.25 & 69.21 & 81.66 & 81.69 & 81.63 \\
-			& $\text{AUG}_{c}$ & 68.47 & 64.44 & 73.03 & 81.93 & 80.57 & 83.34 \\
-			& $\text{AUG}_{eree}$ & 68.36 & 64.64 & 72.53 & 80.55 & 79.21 & 81.93 \\
-			& $\text{AUG}_{ereec}$ & 67.54 & 65.60 & 69.59 & 79.49 & 80.16 & 78.83 \\
-			& Bagging & 69.65 & 66.94 & 72.59 & 82.31 & 82.07 & 82.55 \\
-			\bottomrule
-		\end{tabular*}
-	\end{table*}
-
-	\begin{table*}[ht]
-		\caption{Model performance on complete MultiSpanQA valid Subset with different answer types based on $\text{RoBERTa}_{base}$.}
-		\label{tab:robertasub}
-		\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccccc}
-			\toprule
-			\multirow{2}{*}{\textbf{Type}} & \multirow{2}{*}{\textbf{Model}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match} \\
-			\cmidrule{3-8} 
-			& & F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
-			\midrule
-			\multirow{6}{*}{DESC} & TASE & 45.53 & 40.84 & 51.44 & 75.44 & 76.61 & 74.31 \\ 
-			& LIQUID & 48.68 & 44.76 & 53.37 & 73.27 & 71.57 & 75.04 \\
-			& $\text{AUG}_{c}$ & 49.02 & 44.66 & 54.33 & 76.33 & 77.85 & 74.86 \\
-			& $\text{AUG}_{eree}$ & 50.99 & 46.96 & 55.77 & 76.87 & 78.07 & 75.71 \\
-			& $\text{AUG}_{ereec}$ & 49.24 & 44.71 & 54.81 & 71.87 & 73.03 & 70.74 \\
-			& Bagging & 47.70 & 43.78 & 52.40 & 77.43 & 80.63 & 74.47 \\
-			\midrule
-			\multirow{6}{*}{NUM} & TASE & 46.23 & 45.79 & 46.67 & 71.89 & 78.42 & 66.36 \\ 
-			& LIQUID & 40.19 & 39.45 & 40.95 & 67.56 & 72.28 & 63.42 \\
-			& $\text{AUG}_{c}$ & 50.69 & 49.11 & 52.38 & 72.86 & 80.22 & 66.74 \\
-			& $\text{AUG}_{eree}$ & 42.40 & 41.07 & 43.81 & 66.67 & 73.51 & 61.00 \\
-			& $\text{AUG}_{ereec}$ & 45.58 & 44.55 & 46.67 & 65.86 & 73.19 & 59.87 \\
-			& Bagging & 44.65 & 43.64 & 45.71 & 70.11 & 78.49 & 63.35 \\
-			\midrule
-			\multirow{6}{*}{ENTYS} & TASE & 72.57 & 69.94 & 75.41 & 84.90 & 84.32 & 85.48 \\ 
-			& LIQUID & 72.95 & 71.77 & 74.16 & 85.02 & 84.75 & 85.29 \\
-			& $\text{AUG}_{c}$ & 74.59 & 71.87 & 77.53 & 85.79 & 84.40 & 87.23 \\
-			& $\text{AUG}_{eree}$ & 73.50 & 72.81 & 74.22 & 84.74 & 85.49 & 83.99 \\
-			& $\text{AUG}_{ereec}$ & 75.04 & 72.81 & 77.41 & 85.37 & 84.46 & 86.29 \\
-			& Bagging & 75.85 & 74.52 & 77.22 & 86.73 & 86.73 & 86.74 \\
-			\bottomrule
-		\end{tabular*}
-	\end{table*}
-
-\subsubsection{\textit{Ablation Experiment}}
-	At the end of this section, we conducted ablations on our approach to confirm the effectiveness of selecting the information injection proportion.
-For each QA data, we randomly split the original context and the auxiliary text, then concatenated them into a final augmented context with a specific proportion to ensure that the new input length meets $\textit{max\_len}$, which has a crucial impact on our approach.
-In practice, we determined the final text splicing ratio by calculating the ratio of the average length of the source text to the added information, which for the $\text{AUG}_{c}$ is 0.86.
-
-	Specifically, Table~\ref{tab:different_ratio_bert} and Table~\ref{tab:different_ratio_roberta} displays $\text{AUG}_{c}$'s performance with differential proportion to concatenate original contexts and continuation, on complete MultispanQA valid set,backed by $\text{BERT}_{base}$ and $\text{RoBERTa}_{base}$ respectively.
-We choose five proportions for information integration, which determine how much auxiliary information would be inject into each overflowed text segment.
-The results presented in tables indicate that using the ratio of their average lengths as the proportion of the overflow text composed of original text and auxiliary information is an effective approach.
-In detail, $\text{AUG}_{c}$,equipping with $\text{BERT}_{base}$, achieves an Exact Match F1 scores improvements of at least 4.57 compared to other proportions and an overlap F1 scores improvements of at least 2.07.
-In line with Table~\ref{tab:different_ratio_bert}, when $\text{AUG}_{c}$ equips with $\text{Roberta}_{base}$, it achieves an improvement of Exact Match F1 scores of 0.55 but an decrease of Overlap F1 scores of 0.17.
-
-\begin{table*}[H] 
-	\caption{Ablations of $\text{AUG}_{c}$ on different proportion for information concatenation, based on $\text{BERT}_{base}$.} 
-	\label{tab:different_ratio_bert}
-	\newcolumntype{C}{>{\centering\arraybackslash}X}
-	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccccc}
-		\toprule
-		\multirow{2}{*}{\textbf{Proportion}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match}  \\
-		\cline{2-7} 
-		\addlinespace
-		& F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
-		\midrule
-		0.90 & 58.55 & 57.69 & 59.44 & 71.88 & 74.30 & 69.61 \\ 
-		0.70 & 61.70 & 59.03 & 64.63 & 76.58 & 77.84 & 75.36 \\
-		0.50 & 61.22 & 57.37 & 65.62 & 77.38 & 77.61 & 77.16 \\
-		0.40 & 61.36 & 56.50 & 67.13 & 78.26 & 77.57 & 78.96 \\
-		0.10 & 61.41 & 56.36 & 67.45 & 78.94 & 78.45 & 79.44 \\
-		0.14 & 63.05 & 58.51 & 68.34 & 79.42 & 78.70 & 80.14 \\
-		\bottomrule
-	\end{tabular*}      
-	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
-\end{table*}
-
-\begin{table*}[H] 
-	\caption{Ablations of $\text{AUG}_{c}$ on different proportion for information concatenation, based on $\text{RoBERTa}_{base}$.} 
-	\label{tab:different_ratio_roberta}
-	\newcolumntype{C}{>{\centering\arraybackslash}X}
-	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccccc}
-		\toprule
-		\multirow{2}{*}{\textbf{Proportion}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match}  \\
-		\cline{2-7} 
-		\addlinespace
-		& F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
-		\midrule
-		0.90 & 58.13 & 56.92 & 59.39 & 71.70 & 73.49 & 69.98 \\ 
-		0.70 & 66.97 & 65.42 & 68.60 & 80.05 & 80.80 & 79.32 \\
-		0.50 & 68.94 & 67.23 & 70.75 & 82.43 & 83.23 & 81.64 \\
-		0.40 & 68.95 & 66.11 & 71.06 & 83.71 & 83.71 & 81.71 \\
-		0.10 & 69.80 & 66.47 & 73.47 & 84.23 & 83.49 & 84.99 \\
-		0.86 & 70.35 & 67.35 & 73.63 & 84.06 & 83.38 & 84.76 \\
-		\bottomrule
-	\end{tabular*}      
-	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
-\end{table*}
-
-%\begin{table}[H] 
-%	\caption{Ablations of $\text{AUG}_{c}$ on different proportion for information concatenation, based on $\text{BERT}_{base}$.} 
-%	\label{tab:different_ratio_roberta}
-%	\newcolumntype{C}{>{\centering\arraybackslash}X}
-%	\begin{tabularx}{\textwidth}{p{1.7cm}CCCCCCC}
-%		\toprule
-%		\multirow{2}{*}{\textbf{Proportion}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match}  \\
-%		\cline{2-7} 
-%		\addlinespace
-%		& F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
-%		\midrule
-%		0.90 & 58.13 & 56.92 & 59.39 & 71.70 & 73.49 & 69.98 \\ 
-%		0.70 & 66.97 & 65.42 & 68.60 & 80.05 & 80.80 & 79.32 \\
-%		0.50 & 68.94 & 67.23 & 70.75 & 82.43 & 83.23 & 81.64 \\
-%		0.40 & 68.95 & 66.11 & 71.06 & 83.71 & 83.71 & 81.71 \\
-%		0.10 & 69.80 & 66.47 & 73.47 & 84.23 & 83.49 & 84.99 \\
-%		0.86 & 70.35 & 67.35 & 73.63 & 84.06 & 83.38 & 84.76 \\
-%		\bottomrule
-%	\end{tabularx}      
-%	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
-%\end{table}
-%
-%\section{Conclusion}
-
-%All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, etc.
-
-%\section{Discussion}
-%
-%Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses.
-The findings and their implications should be discussed in the broadest context possible.
-Future research directions may also be highlighted.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Conclusions}
-%
-%This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\vspace{6pt}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-%\supplementary{The following supporting information can be downloaded at:  \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.}
-
-% Only for journal Methods and Protocols:
-% If you wish to submit a video article, please do so with any other supplementary material.
-% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.
-A supporting video article is available at doi: link.}
-
-% Only for journal Hardware:
-% If you wish to submit a video article, please do so with any other supplementary material.
-% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.\vspace{6pt}\\
-%\begin{tabularx}{\textwidth}{lll}
-%\toprule
-%\textbf{Name} & \textbf{Type} & \textbf{Description} \\
-%\midrule
-%S1 & Python script (.py) & Script of python source code used in XX \\
-%S2 & Text (.txt) & Script of modelling code used to make Figure X \\
-%S3 & Text (.txt) & Raw data from experiment X \\
-%S4 & Video (.mp4) & Video demonstrating the hardware in use \\
-%... & ... & ... \\
-%\bottomrule
-%\end{tabularx}
-%}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided.
-The following statements should be used ``Conceptualization, X.X.
-and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y.
-and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing---original draft preparation, X.X.; writing---review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y.
-All authors have read and agreed to the published version of the manuscript.'', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation.
-Authorship must be limited to those who have contributed substantially to the work~reported.}
-
-%=====================================
-% References, variant A: external bibliography
-%=====================================
-%\bibliography{your_external_BibTeX_file}
-
-\section*{Acknowledgements}
-This research was supported by the Natural Science Foundation of Zhejiang Province, China (Grant No.
-LQ22F020027), Fundamental Research Funds of Zhejiang Sci-Tech University (Grant No.
-23232138-Y), Liaoning Provincial Natural Science Foundation of China (Grant No.
-2022-KF-21-01) and the Key Research and Development Program of Zhejiang Province, China (Grant No.
-2023C01041 and 2022C01079).
-
-\bibliographystyle{cas-model2-names}
-% 
-\bibliography{refs}
-%\end{multicols}
-\end{document}

### 2024-01-12 paper.tex
x

@@
 \usepackage{xeCJK}
-\setCJKmainfont{STKaiti}
+%
+
+%\setCJKmainfont{STKaiti}
 
@@
 \begin{document}
+%	\begin{multicols}{2}
 \let\WriteBookmarks\relax
@@
 \author{Zhiyi Luo}[type=editor,auid=000,bioid=1,orcid=0000-0002-2206-1926]
-%\cormark[1]
 \ead{luozhiyi@zstu.edu.cn}
@@
 
+\author{Ying Zhao}
+\ead{272831920@qq.com}
+
 \author{Shuyun Luo}
+\cormark[1]
+\cortext[mycorrespondingauthor]{Corresponding author}
 \ead{shuyunluo@zstu.edu.cn}
@@
 \cortext[mycorrespondingauthor]{Corresponding author}
+
+\author{Wentao Lv}
+\ead{272831920@qq.com}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\input{intro}
+\input{related}
+\input{method}
+\input{experiments}
+\input{conclusion}
 
-\section{Introduction}
-\label{sec:intro}
-
-Let's cite a paper~\cite{DBLP:conf/aaai/PangLGXSC19}.
-
-In summary, the main contributions in this paper are as follows:
-\begin{itemize}
-	\item We employs a automatic data augmentation framework using Large Language Model \((LLM)\) as a knowledge source and a extra content supplement to linearize relevant information and possible continuation from LLM as texts, then inject them into original contexts.
-
-	\item We develop a series of prompt templates designed for interacting with ChatGPT to acquire comprehensive explanations of numerous entities.
-These templates ensure that the formats of the responses provided by ChatGPT are highly parseable and well-structured.
-
-	\item We propose a new calculation method for the overlap F1 score in multi-span QA task.
-This method can alleviate the issue of lower scores in situations where the model decomposes the answer into multiple complete spans, but the answer’s spans are still entirely correct.
-This approach provides a more accurate reflection of the model’s performance in handling complex multi-span answers.
-\end{itemize}
-
-%The introduction should briefly place the study in a broad context and highlight why it is important.
-It should define the purpose of the work and its significance.
-The current state of the research field should be reviewed carefully and key publications cited.
-Please highlight controversial and diverging hypotheses when necessary.
-Finally, briefly mention the main aim of the work and highlight the principal conclusions.
-As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research.
-Citing a journal paper \cite{ref-journal}.
-Now citing a book reference \cite{ref-book1,ref-book2} or other reference types \cite{ref-unpublish,ref-communication,ref-proceeding}.
-Please use the command \citep{ref-thesis,ref-url} for the following MDPI journals, which use author--date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, Journal of Intelligence, Journalism and Media, JRFM, Languages, Laws, Religions, Risks, Social Sciences, Literature.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Related Work}
-\label{sec:related}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Our Approach}
-
-	\begin{figure}[h]
-	\centering
-	\includegraphics[width=14.0cm]{overview.png}
-	\caption{An overview of our automatic information augmentation framework.
-\textbf{(a) Step 1}: Interact with ChatGPT to Get Auxiliary Information.
-\textbf{(b) Step 2}: Distilling the Information and Injecting Them into Context \textbf{(c) Step 3}: Input the Augmented Context into Tagging Model}
-	\label{fig:overview}
-	\end{figure}
-
-%\unskip
-	Existing extractive multi-span question answering models exhibit subpar performance in handling ambiguous words, complex proper nouns (such as film and song titles), numerical values, and long descriptive answers.
-The main reasons for these shortcomings can be categorized into three aspects:
-	\begin{itemize}
-		\item Ambiguous Words: The real world is replete with words that have a single form but multiple meanings, which heavily depend on the context.
-For instance, the word "Cameron" could refer to a famous director or a former British Prime Minister, depending on the context.
-The specific meanings of such words often appear infrequently in training corpora, making them difficult to learn.
-		\item Numerical Values: In contrast to ambiguous words, numerical values have a single meaning but can be represented in various forms.
-For example, "22.5 billion years" can also be expressed as "cosmic years".
-		\item Multi-span Answers: In extractive multi-span question answering tasks, the model needs to grasp the overall relationship of multi-span answers in the context, such as parallelism and progression.
-		These challenges require the model to possess a high level of comprehensive understanding ability and knowledge about language and the world.
-	\end{itemize}
-
-	Leveraging large language models to parse question-answering data and inject auxiliary knowledge into the model can promote the integration of the model's latent world knowledge and specific domain knowledge in the paragraph, thereby enhancing the model's performance.
-Thus, we use GPT-3.5-turbo to generate entity annotations, entity association analysis, and content continuation for each question-answering paragraph as auxiliary information for the model:
-	\begin{itemize}
-		\item Context Supplementary: By inserting explanations of entities in the form of annotations after the main entities or concept words in the question and paragraph, this method helps the model capture the actual meaning of ambiguous words in specific contexts.
-It provides direct information prompts for low-frequency meanings or low-frequency words, achieving entity or concept alignment in the question-answering system.
-		\item Context Enrichment: By integrating entity association analysis and content continuation with the original question-answering text to form new paragraphs based on knowledge enhancement, this method captures the inherent associations between words or entity concepts with the same meaning but different forms.
-On one hand, it parses the logical relationships between other entities using entity relationship analysis.
-On the other hand, it extends the original paragraph information using content continuation, introducing more external knowledge while helping the model understand the overall content direction of the paragraph, thereby enhancing the model's comprehension ability.
-	\end{itemize}
-
-	Overall,we design an automated knowledge enhancement method for multi-span question answering tasks, which interacts with large language models based on templates.
-This method is applicable to all question answering models or frameworks.
-It is universally applicable to any other downstream tasks that contain paragraph data, without the need for any complex calculations.
-In the following sections, we will provide a detailed introduction to each specific module of this process.
-
-\subsection{Construction of Prompt Template}
-\label{sec:prompt_construction}
-	\begin{figure}[h]
-		\centering
-		\includegraphics[width=14.5cm]{Prompts_construction.png}
-		\caption{Prompt Templates and it's Construction}
-		\label{fig:prompt_template}
-	\end{figure}
-
-\subsection{Information Injection}
-\label{sec:information_injection}
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=10cm]{EntityInsert.png}
-	\caption{The Process of Inserting Entity Explanation into Context}
-	\label{fig:entity_insertion}
-\end{figure}
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=10cm]{RandomConcat.png}
-	\caption{The Process of Concatenation of Original Context and Auxiliary Information}
-	\label{fig:random_concatenate}
-\end{figure}
-
-\subsection{Information Integration}
-\label{sec:information_integration}
-
-\section{Experiments}
-In this section, we compare our information augmentation approach with multiple strong baseline on multi-span question answering.
-We first introduce the datasets and experiment setup, then show the experimental results and analysis for different model.
-
-\subsection{Evaluation Dataset}
-\label{sec:datasets}
-	 We conducted experiments on MultiSpanQA(Li et al., 2022), a recently introduced Reading Comprehension dataset designed for multi-span question answering.
-This dataset comprises 6.5K multi-span examples in which the questions represent user queries issued to the Google search engine, and the contexts are extracted from the English Wikipedia.
-It's worth noting that there is a expand variant of MultiSpanQA known as MultispanQA(expand), which intakes single-span and answerable questions.
-However, we did not perform a comparison with the expanded dataset due to its relatively lower proportion of multi-span QA pairs.
-
-\subsection{Experimental Setup}
-	For all competing models and our model, we use the HuggingFace implementation of $\text{BERT}_{base}$ or $\text{RoBERTa}_{base}$ as the \textit{encoder} with $\textit{max\_len}$ = 512.
-We set the initial learning rate as $3 \times 10^{-5}$ and  $\textit{batch\_size}$ = 4, and use the BERTAdam optimizer with a weight decay of 0.01.
-Our approach does not involve tuning the parameters on the validation set.
-Instead, we rely on the model checkpoints obtained after 5 epochs.
-Next, we introduce the comparison model and evaluation metrics in our experiments.
-
-	\subsubsection{\textit{Model Under Comparison}}
-	\label{sec:baselines}
-	We introduce two comstracting models approaches to multi-span answer extraction : \textbf{TASE} (Segal et al., 2020) and \textbf{LIQUID}(Lee et al., 2023).
-TASE utilizes a tag-based span extraction model which identifies multi-span answers though the assigning a tag to every input token with BIO tagging scheme.
-On the other hand, LIQUID serves as a framework for generating multi-span QA datasets to improve model performance.
-
-	To enhance the context with auxiliary information, we employ two distinct   approaches: \textbf{$\text{AUG}_{c}$} and \textbf{$\text{AUG}_{eree}$}, where \textbf{AUG} is our automatic data augmentation framework,and the suffix indicates which kind of information is injected into the context.
-\textbf{$\text{AUG}_{C}$} enriches the context with continue writing, while \textbf{$\text{AUG}_{EREE}$} supplements context with entities information including explanation and relationship analysis.
-	Specifically, we leverage ChatGPT as a knowledge source to linearize the relevant information from large language models.
-in texts format and seamlessly integrate into the original contexts, thus reinforces the information of model inputs.
-
-	\subsubsection{\textit{Evaluation Metrics}}
-	\label{sec:metrics}
-	We use two automatic metrics for evaluation: Exact Match and Overlap F1 score.
-	\begin{itemize}
-		\item \textbf{Exact Match}. An exact match occurs when a predicted span fully matches one of the ground-truth
-		answer spans. We calculate the micro-average precision, recall and f1 score for the extract match
-		metric.
-
-		\item \textbf{Overlap F1 score}. Overlap F1 score is the macro-average f1 score, where the f1 score for each
-		example is computed by treating the prediction and gold as a bag of tokens.
-	\end{itemize}
-
-\subsection{Experimental Results and Analysis}
-	In this section, we compare $\text{AUG}$ with all competing models described above quantitatively.
-
-	\subsubsection{\textit{Comparison Results}}
-	We evaluate our model as well as baselines 
-	\(( Section ~\ref{sec:baselines} )\) on the development splits of multi-span datasets \(( Section  ~\ref{sec:datasets})\) using automatic metrics \(( Section ~\ref{sec:datasets})\).
-The comparison results are shown in Table \ref{tab:bertall}, Table \ref{tab:robertaall}.
-
-	\begin{table}[width=\textwidth,cols=9,pos=h]  % 
-		\caption{Approach performance on complete MultiSpanQA valid set based on $\text{BERT}_{base}$.} 
-		\label{tab:bertall}
-		\begin{tabular*}{\textwidth}{p{1.5cm}cccccccc}
-			\toprule
-			\multirow{2}{*}{\textbf{Model}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match}  \\
-			\cline{2-7} 
-			\addlinespace
-			& F\((\%)\)           & P\((\%)\)          & R\((\%)\)           & F\((\%)\)          & P\((\%)\)           & R\((\%)\)           \\
-			\midrule
-			TASE   & 60.28         & 55.59         & 65.83         & 78.16         & 78.27         & 78.06         \\ 
-			LIQUID & 61.44         & 58.39         & 64.84         & 78.56         & 78.65         & 78.46         \\
-			$\text{AUG}_{c}$ & 63.05         & 58.51         & 68.34         & 79.42         & 78.70         & 80.14         \\
-			$\text{AUG}_{eree}$  & 63.93          & 60.22         & 68.13          & 77.50         & 77.07          & 77.94         \\
-			$\text{AUG}_{ereec}$ & 62.90          & 61.02        & 64.89          & 76.72         & 78.56          & 74.97         \\
-			Bagging & 64.44          & 61.63        & 67.50          & 79.52         & 80.49          & 78.57         \\
-			\bottomrule
-		\end{tabular*}
-		%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
-	\end{table}
-
-	\begin{table}[width=\textwidth,cols=8,pos=h]  
-		\caption{Approach performance on complete MultiSpanQA valid set based on $\text{RoBERTa}_{base}$.} 
-		\label{tab:robertaall}
-		\begin{tabular*}{\textwidth}{p{1.5cm}ccccccc}
-			\toprule
-			\multirow{2}{*}{\textbf{Model}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match}  \\
-			\cline{2-7} 
-			\addlinespace
-			& F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
-			\midrule
-			TASE & 68.00 & 65.06 & 71.22 & 83.13 & 83.05 & 83.22 \\ 
-			LIQUID & 68.33 & 66.68 & 70.07 & 82.71 & 82.45 & 82.98 \\
-			$\text{AUG}_{c}$ & 70.35 & 67.35 & 73.63 & 84.06 & 83.38 & 84.76 \\
-			$\text{AUG}_{eree}$ & 69.15 & 67.81 & 70.54 & 82.85 & 83.90 & 81.83 \\
-			$\text{AUG}_{ereec}$ & 70.44 & 67.83 & 73.26 & 82.80 & 82.45 & 83.15 \\
-			Bagging & 70.86 & 69.03 & 72.79 & 84.82 & 85.53 & 84.12 \\
-			\bottomrule
-		\end{tabular*}      
-		%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
-	\end{table}
-	Table~\ref{tab:bertall} and Table~\ref{tab:robertaall} illustrate the performance comparison between the proposed approaches, $\text{AUG}_{c}$ and $\text{AUG}_{eree}$, and several strong baselines, including the previous state-of-the-art model LIQUID.
-These comparisons are conducted using both the $\text{BERT}_{base}$ and $\text{RoBERTa}_{base}$ encoders, and regard multi-span question answering as a \textit{BIO} sequence tagging task to predict each token whether it is a part or begin of an answer.
-	Notably,$\text{AUG}_{c}$ exhibit superior performance across the evaluate dataset on all metrics.
-However, on Partial Match scores, $\text{AUG}_{eree}$ demonstrates slightly lower performance compared to TASE, and especially lower than LIQUID when employing the $\text{BERT}_{base}$ encoder.
-	Importantly, the performance of $\text{AUG}_{c}$ consistently outperforms LIQUID and TASE on all metrics and encoders, irrespective of the encoder setting.
-	These results demonstrate the effectiveness of our proposed framework, as well as the efficacy of the information augmentation strategy.
-
-	To be more specific, Table~\ref{tab:bertall} shows comparisons of metrics among all competing models 100 backed by $\text{BERT}_{base}$.
-We can see that our proposed framework, AUG, consistently outperforms all other baselines across multispanQA dataset.
-Backed by $\text{BERT}_{base}$, $\text{AUG}_{c}$ achieves EM and Overlap F1 scores of 63.05 and 79.42, respectively.
-Moreover, when equipped with entities’ information,  $\text{AUG}_{eree}$ achieves even higher EM F1 scores of 63.93 but relatively lower Overlap F1 of 77.50 than baselines on the same encoder.
-These results showcase substantial improvements over the previous state-of-the-art model, LIQUID, with EM F1 score enhancements ranging from 1.61 to 2.49 percents across validation datasets.
-
-	Additionally, when utilizing $\text{RoBERTa}_{base}$ instead of $\text{BERT}_{base}$, $\text{AUG}_{c}$ achieves EM and Overlap F1 scores of 70.35 and 84.06 respectively on the same datasets.
-These scores represent EM and Overlap F1 improvements of 2.02 and 0.93 compared to the previous setup.
-For  $\text{AUG}_{eree}$, the EM F1 score represents an enhancement of 0.82, with the EM and Overlap F1 values of 69.16 and 82.85 respectively.
-Notably, the partial metrics also indicate lower values compared to TASE and LIQUID, in line with the result supported by $\text{BERT}_{base}$.
-This is because augmenting the model with entity information, including definition and relationship knowledge, strengthens its ability to capture and understand entity concepts, which leads the model to prefer complete entity spans as answers rather than partial entity span, and therefore a decrease in the partial recall and ultimately a lower partial F1 scores and a higher EM F1.
-
-	Totally, the result, displayed in Table~\ref{tab:robertaall} demonstrates the same trends to Table~\ref{tab:bertall}.
-And the outcome highlights robustness in effectively generalizing across different datasets without requiring hyperparameter re-tuning.
-
-\subsubsection{\textit{Discussion}}
-	Besides, Table~\ref{tab:bertall} and Table~\ref{tab:robertaall} also discuss the performance of different augmentation integrated strategies, including the results-bagging methods whose outputs are voting results of $\text{AUG}_{c}$, $\text{AUG}_{eree}$ as well as LIQUID, and the input-fusion model $\text{AUG}_{ceree}$ who injects all kinds of information above into input contexts.
-
-	In detail, with EM f1 scores of 62.90 and 64.44 in Table~\ref{tab:bertall} and 70.44 and 70.86 in Table~\ref{tab:robertaall}, both the $\text{AUG}_{ceree}$ and Bagging methods consistently surpass TASE and LIQUID, which exhibits robust effectiveness of information injection strategies.
-However, there is a little decrease caused by fusing all auxiliary information when contrast with single information augmentation strategies and the bagging method.
-This may be due to the likelihood that incorporating all of the augmentation information into the model inputs will confuse the model by introducing excessive auxiliary knowledge and underrepresented original context proportion.
-Therefore it may be more useful that adding limit information into context, and using result-bagging method, a multi-model voting to bringing all information into model with an indirect way.
-
-	From the Partial Match perspective, $\text{AUG}_{ceree}$ and the Bagging method achieve 76.72 and 79.52 in Table~\ref{tab:bertall}, and 82.80 and 84.82 in Table~\ref{tab:robertaall}.
-In accordance with Exact Match metrics, Bagging demonstrate a overall superior performance.
-Meanwhile overlap f1 score of $\text{AUG}_{eree}$ is inferior to TASE but superior to LIQUID ,with relatively higher precision and relativelv higher recall, which  is comparable to all single augmented models such as $\text{AUG}_{eree}$.
-And its weak performance on overlap f1 also reveals complete entities preference of this information injection approach.
-	z
-	In addition, we	categorized the data in MultispanQA into DESC, NUM, ENTYS in terms of answer types, and compared the performance of each of the model mentioned above in each breakdown category.
-Specifically,  Table~\ref{tab:bertsub} and Table~\ref{tab:robertasub} present the results backed by  $\text{BERT}_{base}$ and $\text{RoBERTa}_{base}$, respectively.
-As shown in Tables~\ref{tab:bertsub},Table~\ref{tab:robertasub}, our proposed models display superior performance in DESC and ENTYS categories answer extraction, which to some extent indicates the enhancement of models' knowledge at entity and description levels.
-
-	\textcolor{red}{please supplements new overlap calculation method in tase-zh}
-
-	\begin{table}[ht]
-		\caption{Model performance on complete MultiSpanQA valid Subset with different answer types based on $\text{BERT}_{base}$.}
-		\label{tab:bertsub}
-		\begin{tabular*}{\textwidth}{cp{1.5cm}ccccccc}
-			\toprule
-			\multirow{2}{*}{\textbf{Type}} & \multirow{2}{*}{\textbf{Model}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match} \\
-			\cmidrule{3-8} 
-			& & F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
-			\midrule
-			\multirow{6}{*}{DESC} & TASE & 32.76 & 27.33 & 40.87 & 64.46 & 68.61 & 60.79 \\ 
-			& LIQUID & 36.69 & 31.10 & 44.71 & 66.05 & 65.95 & 66.15 \\
-			& $\text{AUG}_{c}$ & 38.74 & 32.89 & 47.12 & 68.31 & 70.32 & 66.42 \\
-			& $\text{AUG}_{eree}$ & 44.69 & 40.71 & 49.52 & 63.12 & 67.16 & 59.53 \\
-			& $\text{AUG}_{ereec}$ & 40.63 & 38.30 & 43.27 & 64.25 & 71.15 & 58.57 \\
-			& Bagging & 39.91 & 36.69 & 43.75 & 66.70 & 73.68 & 60.93 \\
-			\midrule
-			\multirow{6}{*}{NUM} & TASE & 33.33 & 30.23 & 37.14 & 60.98 & 71.99 & 52.89 \\ 
-			& LIQUID & 34.33 & 31.25 & 38.10 & 60.68 & 68.15 & 54.69 \\
-			& $\text{AUG}_{c}$ & 35.96 & 33.33 & 39.05 & 64.47 & 71.56 & 58.65 \\
-			& $\text{AUG}_{eree}$ & 36.20 & 34.48 & 38.10 & 59.02 & 65.63 & 53.62 \\
-			& $\text{AUG}_{ereec}$ & 36.71 & 37.25 & 36.19 & 57.09 & 69.04 & 48.67 \\
-			& Bagging & 35.94 & 34.82 & 37.14 & 60.73 & 71.15 & 52.97 \\
-			\midrule
-			\multirow{6}{*}{ENTYS} & TASE & 66.30 & 62.21 & 70.96 & 81.16 & 80.37 & 81.96 \\ 
-			& LIQUID & 67.17 & 65.25 & 69.21 & 81.66 & 81.69 & 81.63 \\
-			& $\text{AUG}_{c}$ & 68.47 & 64.44 & 73.03 & 81.93 & 80.57 & 83.34 \\
-			& $\text{AUG}_{eree}$ & 68.36 & 64.64 & 72.53 & 80.55 & 79.21 & 81.93 \\
-			& $\text{AUG}_{ereec}$ & 67.54 & 65.60 & 69.59 & 79.49 & 80.16 & 78.83 \\
-			& Bagging & 69.65 & 66.94 & 72.59 & 82.31 & 82.07 & 82.55 \\
-			\bottomrule
-		\end{tabular*}
-	\end{table}
-
-	\begin{table}[ht]
-		\caption{Model performance on complete MultiSpanQA valid Subset with different answer types based on $\text{RoBERTa}_{base}$.}
-		\label{tab:robertasub}
-		\begin{tabular*}{\textwidth}{cp{1.5cm}ccccccc}
-			\toprule
-			\multirow{2}{*}{\textbf{Type}} & \multirow{2}{*}{\textbf{Model}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match} \\
-			\cmidrule{3-8} 
-			& & F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
-			\midrule
-			\multirow{6}{*}{DESC} & TASE & 45.53 & 40.84 & 51.44 & 75.44 & 76.61 & 74.31 \\ 
-			& LIQUID & 48.68 & 44.76 & 53.37 & 73.27 & 71.57 & 75.04 \\
-			& $\text{AUG}_{c}$ & 49.02 & 44.66 & 54.33 & 76.33 & 77.85 & 74.86 \\
-			& $\text{AUG}_{eree}$ & 50.99 & 46.96 & 55.77 & 76.87 & 78.07 & 75.71 \\
-			& $\text{AUG}_{ereec}$ & 49.24 & 44.71 & 54.81 & 71.87 & 73.03 & 70.74 \\
-			& Bagging & 47.70 & 43.78 & 52.40 & 77.43 & 80.63 & 74.47 \\
-			\midrule
-			\multirow{6}{*}{NUM} & TASE & 46.23 & 45.79 & 46.67 & 71.89 & 78.42 & 66.36 \\ 
-			& LIQUID & 40.19 & 39.45 & 40.95 & 67.56 & 72.28 & 63.42 \\
-			& $\text{AUG}_{c}$ & 50.69 & 49.11 & 52.38 & 72.86 & 80.22 & 66.74 \\
-			& $\text{AUG}_{eree}$ & 42.40 & 41.07 & 43.81 & 66.67 & 73.51 & 61.00 \\
-			& $\text{AUG}_{ereec}$ & 45.58 & 44.55 & 46.67 & 65.86 & 73.19 & 59.87 \\
-			& Bagging & 44.65 & 43.64 & 45.71 & 70.11 & 78.49 & 63.35 \\
-			\midrule
-			\multirow{6}{*}{ENTYS} & TASE & 72.57 & 69.94 & 75.41 & 84.90 & 84.32 & 85.48 \\ 
-			& LIQUID & 72.95 & 71.77 & 74.16 & 85.02 & 84.75 & 85.29 \\
-			& $\text{AUG}_{c}$ & 74.59 & 71.87 & 77.53 & 85.79 & 84.40 & 87.23 \\
-			& $\text{AUG}_{eree}$ & 73.50 & 72.81 & 74.22 & 84.74 & 85.49 & 83.99 \\
-			& $\text{AUG}_{ereec}$ & 75.04 & 72.81 & 77.41 & 85.37 & 84.46 & 86.29 \\
-			& Bagging & 75.85 & 74.52 & 77.22 & 86.73 & 86.73 & 86.74 \\
-			\bottomrule
-		\end{tabular*}
-	\end{table}
-
-\subsubsection{\textit{Ablation Experiment}}
-	At the end of this section, we conducted ablations on our approach to confirm the effectiveness of selecting the information injection proportion.
-For each QA data, we randomly split the original context and the auxiliary text, then concatenated them into a final augmented context with a specific proportion to ensure that the new input length meets $\textit{max\_len}$, which has a crucial impact on our approach.
-In practice, we determined the final text splicing ratio by calculating the ratio of the average length of the source text to the added information, which for the $\text{AUG}_{c}$ is 0.86.
-
-	Specifically, Table~\ref{tab:different_ratio_bert} and Table~\ref{tab:different_ratio_roberta} displays $\text{AUG}_{c}$'s performance with differential proportion to concatenate original contexts and continuation, on complete MultispanQA valid set,backed by $\text{BERT}_{base}$ and $\text{RoBERTa}_{base}$ respectively.
-We choose five proportions for information integration, which determine how much auxiliary information would be inject into each overflowed text segment.
-The results presented in tables indicate that using the ratio of their average lengths as the proportion of the overflow text composed of original text and auxiliary information is an effective approach.
-In detail, $\text{AUG}_{c}$,equipping with $\text{BERT}_{base}$, achieves an Exact Match F1 scores improvements of at least 4.57 compared to other proportions and an overlap F1 scores improvements of at least 2.07.
-In line with Table~\ref{tab:different_ratio_bert}, when $\text{AUG}_{c}$ equips with $\text{Roberta}_{base}$, it achieves an improvement of Exact Match F1 scores of 0.55 but an decrease of Overlap F1 scores of 0.17.
-
-\begin{table}[width=.6\textwidth,cols=8,pos=h]
-	\caption{Ablations of $\text{AUG}_{c}$ on different proportion for information concatenation, based on $\text{BERT}_{base}$.} 
-	\label{tab:different_ratio_bert}
-	\begin{tabular*}{\tblwidth}{cccccccc}
-%	\begin{tabularx}{\textwidth}{p{1.7cm}ccccccc}
-		\toprule
-		\multirow{2}{*}{\textbf{Proportion}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match}  \\
-		\cline{2-7} 
-		\addlinespace
-		& F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
-		\midrule
-		0.90 & 58.55 & 57.69 & 59.44 & 71.88 & 74.30 & 69.61 \\ 
-		0.70 & 61.70 & 59.03 & 64.63 & 76.58 & 77.84 & 75.36 \\
-		0.50 & 61.22 & 57.37 & 65.62 & 77.38 & 77.61 & 77.16 \\
-		0.40 & 61.36 & 56.50 & 67.13 & 78.26 & 77.57 & 78.96 \\
-		0.10 & 61.41 & 56.36 & 67.45 & 78.94 & 78.45 & 79.44 \\
-		0.14 & 63.05 & 58.51 & 68.34 & 79.42 & 78.70 & 80.14 \\
-		\bottomrule
-	\end{tabular*}
-	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
-\end{table}
-
-%\begin{table}[H] 
-%	\caption{Ablations of $\text{AUG}_{c}$ on different proportion for information concatenation, based on $\text{BERT}_{base}$.} 
-%	\label{tab:different_ratio_roberta}
-%	\newcolumntype{C}{>{\centering\arraybackslash}X}
-%	\begin{tabularx}{\textwidth}{p{1.7cm}CCCCCCC}
-%		\toprule
-%		\multirow{2}{*}{\textbf{Proportion}} & \multicolumn{3}{c}{Exact Match} & \multicolumn{3}{c}{Partial Match}  \\
-%		\cline{2-7} 
-%		\addlinespace
-%		& F\((\%)\) & P\((\%)\) & R\((\%)\) & F\((\%)\) & P\((\%)\) & R\((\%)\) \\
-%		\midrule
-%		0.90 & 58.13 & 56.92 & 59.39 & 71.70 & 73.49 & 69.98 \\ 
-%		0.70 & 66.97 & 65.42 & 68.60 & 80.05 & 80.80 & 79.32 \\
-%		0.50 & 68.94 & 67.23 & 70.75 & 82.43 & 83.23 & 81.64 \\
-%		0.40 & 68.95 & 66.11 & 71.06 & 83.71 & 83.71 & 81.71 \\
-%		0.10 & 69.80 & 66.47 & 73.47 & 84.23 & 83.49 & 84.99 \\
-%		0.86 & 70.35 & 67.35 & 73.63 & 84.06 & 83.38 & 84.76 \\
-%		\bottomrule
-%	\end{tabularx}      
-%	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
-%\end{table}
-%
-%\section{Conclusion}
-
-%All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, etc.
-
-%\section{Discussion}
-%
-%Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses.
-The findings and their implications should be discussed in the broadest context possible.
-Future research directions may also be highlighted.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Conclusions}
-%
-%This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \vspace{6pt}
@@
 \bibliography{refs}
+%\end{multicols}
 \end{document}

### 2024-01-12 related.tex
x

--- 2023-10-01 manuscript.tex
@@
-%% 
-%% Copyright 2019-2021 Elsevier Ltd
-%% 
-%% This file is part of the 'CAS Bundle'.
-%% --------------------------------------
-%% 
-%% It may be distributed under the conditions of the LaTeX Project Public
-%% License, either version 1.2 of this license or (at your option) any
-%% later version.  The latest version of this license is in
-%%    http://www.latex-project.org/lppl.txt
-%% and version 1.2 or later is part of all distributions of LaTeX
-%% version 1999/12/01 or later.
-%% 
-%% The list of all files belonging to the 'CAS Bundle' is
-%% given in the file `manifest.txt'.
-%% 
-%% Template article for cas-sc documentclass for 
-%% single column output.
-
-\documentclass[a4paper]{cas-sc}
-
-% If the frontmatter runs over more than one page
-% use the longmktitle option.
-
-%\documentclass[a4paper,fleqn,longmktitle]{cas-sc}
-
-%\usepackage[numbers]{natbib}
-\usepackage[authoryear]{natbib}
-%\usepackage[authoryear,longnamesfirst]{natbib}
-\usepackage{dsfont}
-\usepackage{array}
-\usepackage{float}
-\usepackage{placeins}
-\usepackage{makecell} % add by shuyun
-%\usepackage[utf8]{inputenc}
-\usepackage{lineno,hyperref}
-\usepackage{amsmath}
-\usepackage{graphicx}
-\usepackage[small]{caption}
-\usepackage{subcaption}
-\usepackage{array}
-\usepackage{multirow}
-\usepackage{multicol}
-\usepackage{diagbox}
-\usepackage{mathrsfs}
-\usepackage{color}
-\usepackage{booktabs}
-\usepackage{soul}
-\usepackage{mathspec}
-\usepackage{xeCJK}
-\setCJKmainfont{STKaiti}
-
-%\setCJKmainfont[Mapping=tex-text]{STKaiti}
-\usepackage[ruled, linesnumbered, vlined]{algorithm2e}
-
-%\linenumbers
-
-%%%Author macros
-\def\tsc#1{\csdef{#1}{\textsc{\lowercase{#1}}\xspace}}
-\tsc{WGM}
-\tsc{QE}
-%%%
-
-% Uncomment and use as if needed
-%\newtheorem{theorem}{Theorem}
-%\newtheorem{lemma}[theorem]{Lemma}
-%\newdefinition{rmk}{Remark}
-%\newproof{pf}{Proof}
-%\newproof{pot}{Proof of Theorem \ref{thm}}
-
-\newcommand{\1}[1]{\mathds{1}\left[#1\right]}
-\renewcommand{\floatpagefraction}{0.8}
-
-\newcommand{\secref}[1]{Section \ref{#1}}
-\newcommand{\figref}[1]{Figure \ref{#1}}
-\newcommand{\eqnref}[1]{Eq. (\ref{#1})}
-\newcommand{\exref}[1]{Example \ref{#1}}
-\newcommand{\algoref}[1]{Algorithm \ref{#1}}
-\newcommand{\tableref}[1]{Table \ref{#1}}
-\newcommand{\socvec}{SocVec}
-\newcommand{\argmin}{\operatornamewithlimits{argmin}}
-\newcommand{\argmax}{\operatornamewithlimits{argmax}}
-\newtheorem{example}{Example}
-\newtheorem{lemma}{Lemma}
-\newtheorem{definition}{Definition}
-\newcommand{\cut}[1]{}
-\newcommand{\ZY}[1]{\textcolor{red}{Zhiyi: #1}}
-
-\begin{document}
-	\let\WriteBookmarks\relax
-	\def\floatpagepagefraction{1}
-	\def\textpagefraction{.001}
-
-	% Short title
-	\shorttitle{A Token-based Transition-Aware Joint Framework for Multi-Span Question Answering}
-
-	% Short author
-	\shortauthors{Z. Luo et al.}
-
-	% Main title of the paper
-	\title{A Token-based Transition-Aware Joint Framework for Multi-Span Question Answering}
-
-	\author{Zhiyi Luo}[type=editor,auid=000,bioid=1,orcid=0000-0002-2206-1926]
-	%\cormark[1]
-	\ead{luozhiyi@zstu.edu.cn}
-	\ead[url]{http://zhiyiluo.site}
-	%\credit{Conceptualization of this study, Methodology, Software}
-
-	\author{Yingying Zhang}
-	\ead{272831920@qq.com}
-
-	\author{Shuyun Luo}
-	\ead{shuyunluo@zstu.edu.cn}
-	\cormark[1]
-	\cortext[mycorrespondingauthor]{Corresponding author}
-
-	\address[mymainaddress]{School of Computer Science and Technology and the Key Laboratory of Intelligent Textile and Flexible Interconnection of Zhejiang Province, Zhejiang Sci-Tech University}
-	\address[mysecondaryaddress]{No. 928, No. 2 street, Baiyang street, Qiantang New District, Hangzhou 310018, China}
-
-	% % Here goes the abstract
-	\begin{abstract}
-		Multi-span question answering has gained prominence as it aligns more closely with real-world user requirements compared to single-span question answering.
-The utilization of pretrained language models has shown promise in improving multi-span question answering, particularly for factoid questions that necessitate entity-based answers.
-However, existing methods tend to overlook critical information regarding answer span boundaries, resulting in limited accuracy when generating descriptive answers.
-To address this limitation, we propose TOAST, a novel joint learning framework specialized in token-based neighboring transitions that capture answer span boundaries through adjacent word relations.
-Our approach extracts high-quality multi-span answers and is general-purpose, applicable to both alphabet languages like English and logographic languages like Chinese.
-Furthermore, we introduce CLEAN, a comprehensive open-domain Chinese multi-span question answering dataset, which includes a substantial number of descriptive questions.
-		Extensive experiments demonstrate the superior performance of TOAST over previous top-performing QA models in terms of both EM F1 and overlapped F1 scores.
-Specifically, the TOAST models, leveraging  $\text{BERT}_{base}$ and $\text{RoBERTa}_{base}$, achieve substantial  improvements in EM F1 scores, with increments of 3.03/2.13, 4.82/3.73, and 16.26/11.53, across three publicly available datasets, respectively.
-
-	\end{abstract}
-	% 
-	% Use if graphical abstract is present
-	%\begin{graphicalabstract}
-	%\includegraphics{}
-	%\end{graphicalabstract}
-	% 
-	% Research highlights
-	%\begin{highlights}
-	%\item The paper proposes a novel joint learning framework called TOAST, which specializes in token-based neighboring transitions to capture the boundary information of answer spans through adjacent word relations for multi-span question answering.
-	%\item TOAST extracts high-quality multi-span answers and is general-purpose, applicable to both alphabet languages like English and logographic languages like Chinese.
-	%\item The paper creates a new Chinese reading comprehension dataset, consisting of both single-span and multi-span answers, with a broad-coverage of types of open-domain questions and demonstrates that incorporating the span boundary information via the awareness of adjacent word relations improves strong baselines on three multi-span question answering datasets.
-	%\end{highlights}
-
-	% Keywords
-	% Each keyword is seperated by \sep
-	\begin{keywords}
-		Reading comprehension \sep Multi-span question answering \sep  Pretrained language models \sep Multitask learning  \sep Chinese datasets 
-	\end{keywords}
-	%Reading comprehension \sep
-	%\sep Neural networks
-	% \keywords{multi-span question answering, reading comprehension, chinese datasets, joint learning, neural networks}
-	\maketitle
-
-%	\input{intro}
-\section{Introduction}
-\label{sec:introduction}
-
-Extractive question answering, also commonly referred as the task of reading comprehension, which aims to answer a user's question by finding short text segments (i.e., {\em spans}) from the given context, has been actively studied and achieved rapid progress in recent years.
-Benefiting from the sophisticated industrial search engines and the vast amount of text collections on the web, 
-high-quality contexts relevant to the user questions can be effectively retrieved to construct the datasets.
-As a result, the answers directly drawn from the high-quality contexts are expressive enough.
-Hence, existing datasets and models~\citep{DBLP:conf/emnlp/DasigiLMSG19,li2022multispanqa,lee2023liquid,DBLP:journals/ipm/Liu0GC23}, cast reading comprehension as an \emph{extractive} task that is easy to learn.
-
-Most previous work~\citep{rajpurkar2016squad,rajpurkar2018know,yang2018hotpotqa,zaheer2020big} restricts the answer extracted from the context to a single text span 
-which can only satisfy limited real-world open-domain questions. 
-For example, as shown in \tableref{tab:intro} (the left example), the complete answer to a question could consist of a series of non-contiguous spans, 
-or even the question itself could have multiple intents, 
-where the answer to each intent is composed of one or more spans drawn from the input.
-Hence, the models of multi-span question answering have significant utility to users. 
-Recently, ~\cite{segal2020simple} cast the multi-span extraction as a sequence tagging task, 
-predicting whether each token is part of an answer. 
-~\cite{li2022multispanqa} captured the global information by integrating two sub-tasks of predicting the number of spans to extract and the answer structure annotated in their proposed dataset. 
-Benefiting from nowadays pretrained models (e.g., BERT~\citep{kenton2019bert}, RoBERTa~\citep{liu2019roberta}), 
-the above neural approaches 
-have achieved promising performance on answer span extraction,  
-especially for factoid questions where the expected answers are \emph{entities} (e.g., \emph{Person} and \emph{Location}).
-
-However, existing systems fail to carefully consider span boundaries according to the information need of the question, 
-and thus have very limited capabilities of 
-precisely drawing a \emph{description} answer, for example, 
-the answer spans of ``饮食护理(diet and care)'' and  ``适当地带它们出去运动一下(take them out for some exercises)''
-as shown in \tableref{tab:intro}, from the input.
-Moreover,  in the construction of existing datasets, 
-user question candidates are constrained 
-by the organization way of the document collection 
-where the relevant contexts are retrieved from. 
-For example, Wikipedia, the most widely used document collection 
-for context retrieval, organizes articles using entities.
-The problem is that a \emph{semantic gap} exists between the real context of what users want to ask and the entity-based articles (i.e. single Wiki page). 
-Backed by the document collection of Wikipedia, 
-existing datasets include most types of the factoid questions,
-whereas they exclude many questions that can not be answered from a single 
-article of an entity.
-% =====  draw a figure here ====
-\begin{table}[width=\textwidth,cols=4,pos=h]
-	%	\centering
-	\caption{Examples of questions and answers.}
-	\begin{tabular*}{\tblwidth}{c|c|c} \hline
-		Dataset   & CLEAN   &  MultiSpanQA \\ \hline
-		Question  &  {\makecell[l]{
-				如何养好约克夏犬?
-				\\ (How to raise a Yorkshire terrier?)}} & Who wrote the song if you could see me now? \\ \hline
-		Context  & {\makecell[l]{想要养好约克夏对于它们的{\color{blue}饮食护理}都要做好，\\
-				由于它们所需的运动量并不是特别大，所以一般\\
-				在家里就可以，不过还是要{\color{blue}适当地带它们出去运}\\
-				{\color{blue}动一下}，这样它们能够生长的更好。\\
-				(...
-				must do a good job in their {\color{blue}diet and care.}\\
-				... but it is still necessary to
-				{\color{blue}take them out for}\\
-				{\color{blue}some exercise} so that they can grow better.)}} 
-		&  {\makecell[l]{
-				``If You Could See Me Now'' is a 1946 jazz\\
-				standard, composed by {\color{blue}Tadd Dameron}. He\\
-				wrote it especially for vocalist Sarah\\
-				Vaughan, a frequent collaborator. Lyrics\\
-				were written by {\color{blue}Carl Sigman} and it became\\
-				one of her signature songs, inducted into\\
-				the Grammy Hall of Fame in 1998.}}
-		\\ \hline
-		Answer & {\makecell[l]{Segment1:饮食护理(diet and care)\\Segment2:适当地带它们出去运动一下\\(take them out for some exercise)}} &
-		{\makecell[l]{Segment1: Tadd Dameron\\
-				Segment2: Carl Sigman}}\\ \hline
-	\end{tabular*}
-	\label{tab:intro}
-\end{table}
-
-Following the above observations, we in this paper propose a novel approach to explicitly model the implicit \emph{neighboring transitions} 
-via the adjacent word (or token) relations, 
-which are both semantically and syntactically informative for span boundaries identification. 
-This approach captures the intuition that the span boundary is produced in-between adjacent words. 
-We indicate neighboring transitions in-between
-as five types of relations.
-Then, we jointly learn the sequence tagging task 
-together with the  adjacent word relation classification task 
-evolved from the span boundary identification, 
-considering whether each token is part of an answer 
-and which span each token belongs to accordingly. 
-With the awareness of adjacent word relations, 
-we incorporate the information of span boundaries in a multi-task learning manner.
-Furthermore, in order to ameliorate the observed limitation of previous datasets, 
-which including more real-world open-domain questions, 
-we create a new dataset (in Chinese) in a more natural manner, 
-extracting question-context pairs from a large-scale knowledge Q\&A sharing platform (i.e., BaiduZhidao\footnote{https://zhidao.baidu.com/}) instead of Wikipedia.
-
-In summary, the main contributions in this paper are as follows:
-\begin{itemize}
-	\item We create a new reading comprehension dataset named CLEAN~\footnote{We intend to make CLEAN 1.0 dataset publicly avaiable at http://zhiyiluo.site/misc/clean\_v1.0\_sample.json for future work in this research area.} that consists of both single-span and multi-span answers, covering a wide range of open-domain question topics.
-	CLEAN overcomes the constraints imposed by previous datasets by incorporating carefully crafted long answers as contexts, effectively bridging the semantic gap with the insights provided by respondents.
-	\item We propose a novel approach for multi-span reading comprehension,  where we explore implicit neighboring transitions using adjacent word relations, effectively capturing both semantic and syntactic information pertaining to the boundaries of answer spans.
-
-	\item We demonstrate that incorporating the span boundary information via the awareness of adjacent word relations improves strong baselines on three multi-span question answering datasets (both English and Chinese).
-\end{itemize}
-
-%	\input{method}
-%\section{Tasks and Datasets}
-\section{Preliminary}
-\label{sec:preliminary}
-% 1.30  10:20 - 13:00  0.5页
-In this section, we present the problem statement and then introduce the datasets. 
-%\subsection{Task}
-%\label{sec:tasks}
-%Information retrieval based question answering (IR-based QA) systems consist of two components: \emph{retriever}  and  \emph{reader}. 
-%The reading comprehension (RC) task focuses more on building the \emph{reader} model since the construction of the RC dataset already utilizes the \emph{retriever} component  explicitly or implicitly.
-%Thus, we formulate the problem of multi-span question answering as a task of multi-span extraction on the basis of the RC datasets.
-The objective of the task is to extract one or more answer spans based on the input question and context.
-\subsection{Problem Statement}
-\label{sec:problem}
-We formulate the problem of multi-span question answering as a task of multi-span extraction on the basis of the reading comprehension (RC) datasets.
-The objective of the task is to extract one or more answer spans based on the input question and context.
-
-Formally, given an input question represented as a sequence of words 
-$q=(q_1, q_2, ..., q_n) \in \mathcal{V}$, and an input context $c$, associating to $q$, 
-which is also represented as a sequence of words $c=(c_1, c_2, ..., c_m)\in \mathcal{V}$, where $\mathcal{V}$ refers to the vocabulary, 
-the objective of the system is to extract one or more spans as the answer $a$, 
-say $l$ spans, $a = [a_1, a_2, ..., a_l]$ from the context $c$,
-where the $i$-th span $a_i$ is a sequence of words $a_i=(c_{i_s}, c_{i_s+1}, ..., c_{i_e})$, 
-ranging from the start position $i_s$ to its end position $i_e$.
-Note that the extracted answer spans should be neither duplicated nor overlap with each other.
-That means, for any $i, j$ where $i$ < $j$, $i_e < j_s$ holds.
-%Following previous studies, we regard the problem as a sequence tagging task.
-%We also build an auxiliary task incorporating token-based transition knowledge to capture 
-%the information of span boundaries, and jointly learn the sequence tagging task as well as the transition classification task.
-
-Evaluation are exact match and partial match with any of the reference answer strings after minor normalization such as lowercasing, following evaluation scripts from~\cite{li2022multispanqa}.
-
-\subsection{Datasets}
-\label{sec:predata}
-In this work, we conduct the experiments on three RC datasets, ranging from two English datasets and one proposed Chinese dataset for multi-span question answering.
-
-The latest dataset, MultiSpanQA, focus on multi-span questions, which is derived from Natural Question (NQ) ~\citep{DBLP:journals/tacl/KwiatkowskiPRCP19}, a large-scale open domain QA dataset.
-It also has an expanded variant by introducing single-span and unanswerable questions, namely MultiSpanQA (expand).
-
-In MultiSpanQA and MultiSpanQA (expand), the questions are derived from real queries issued to the Google search engine.
-Each question is paired with a context extracted from a retrieved Wikipedia page.
-However, it is important to acknowledge that Wikipedia pages are structured around entities, which may not fully align with the intentions of real-world open-domain questions, especially those that are non-factoid in nature.
-This entity-centric organization of Wikipedia pages introduces a semantic gap between the content and the intended meaning of real-world open-domain questions.
-As a result, existing RC datasets like MultiSpanQA are limited to questions  that primarily revolve around entities, allowing for the extraction of concise spans from a single Wikipedia page as answers.
-Moreover, there is a noticeable scarcity of publicly available open-domain multi-span QA datasets in the Chinese language.
-Although recently proposed CMQA~\citep{DBLP:conf/coling/JuWZZ0022} is one such dataset, it primarily focuses on a new task of conditional question answering, which may not directly address the requirements of traditional question answering scenarios.
-
-To ameliorate these limitations, we create a more realistic and challenging dataset, utilizing a large-scale Chinese online knowledge Q\&A sharing platform (i.e.
-BaiduZhidao) which is full of open-domain questions with crafted long answers from  public users.
-Over the course of two decades of crowd-sourcing efforts, the shared questions have covered  a broad range of subjects, including people, celestial bodies, flora and fauna, landmarks, etc.
-Firstly, we conduct a random crawl of one million questions across 29 popular subjects in the open domain.
-Next, we employ two key strategies to increase the proportion of multi-span answers relative to single-span answers: 1) selectively choosing questions that contain  keywords such as \emph{如何/怎样}(e.g.
-\emph{how}) or \emph{哪些}(e.g.\emph{ what/which ones}), as these types of questions typically require multipart descriptions; and 2) translating all the crawled questions into English and specifically targeting questions featuring plural nouns.
-Note that, a question may have a number of long answers created by different users, and we only consider those with more than 3 likes as potential candidates.
-Then, our annotators are educated to pick up high-quality contexts from the candidate answers for each question and identify one or more answer spans within the context that can effectively answer the given question.
-Finally, we obtain a diverse collection of multi-span answers in various formats.
-
-In our proposed \textbf{C}hinese mu\textbf{L}ti-span qu\textbf{E}stion \textbf{AN}swering (or CLEAN) dataset, the context consists of meticulously constructed long answers that effectively bridge the semantic gap with the insights provided by respondents.
-This approach ensures that the question intents are appropriately addressed and breaks the constraints imposed by  previous datasets in terms of question selection.
-Table 1 (left) presents a specific example from the CLEAN dataset, where the question is obtained from BaiduZhidao, and the context is selected from the original long answers associated with that question.
-To make our dataset more general, as well as considering the versatility of questions, unlike MultiSpanQA, we only annotate the span of answer without the structure of the answer.
-
-\section{Our Framework}
-\label{sec:framework}
-% 1.30  导言 15:00 - 15:30  0.2页
-In this section, we first introduce a basic neural framework for multi-span question answering based on pretrained language models, which involves casting multi-span extraction as a sequence tagging task.
-We then propose a novel model called \textbf{TO}ken-b\textbf{AS}ed \textbf{T}ransition-aware
-(TOAST) for multi-span question answering that incorporates joint learning.
-
-%In this section, we first introduce the basic neural framework on the basis of 
-%pretrained models, casting multi-span extraction as a sequence tagging task.
-%We then propose a novel joint learning 
-%\textbf{TO}ken-b\textbf{AS}ed \textbf{T}ransition-aware 
-%(or TOAST) model
-%for multi-span question answering.
-
-The architecture of TOAST is depicted in \figref{fig:toast}.
-The \emph{Transition Identification} module demonstrates how span boundary identification can be transferred to a token-based transition classification task, while the  \emph{Transition Incorporation} module explains how we incorporate semantic and syntactic knowledge in adjacent word relations to improve the informativeness of the extraction.
-In addition to the sequence tagging task (Task 1 in \figref{fig:toast}), TOAST also includes an auxiliary task of transition classification (Task 2 in \figref{fig:toast}).
-We therefore present a multi-task learning strategy for TOAST.
-Finally, we present the joint decoding step, which leverages outputs from multiple tasks to improve performance.
-
-\begin{figure*}[thb!]
-	%	\small
-	\centering
-	\includegraphics[width=0.9\columnwidth]{framework.png}
-	\caption{An illustration of TOAST framework architecture.}
-	\label{fig:toast}
-\end{figure*}
-%at the inference time.
-\subsection{A BERT-based Sequence Tagging Model}
-\label{sec:basic}
-Extracting a variable number of spans from an input text can be
-commonly cast as a sequence tagging problem, 
-which is suitable for answer extraction of multi-span questions.
-Following the observation of ~\cite{li2022multispanqa}, 
-we adopt the BIO
-tagging scheme to mark answer spans in the context 
-where words are tagged as either part of the answer (\textbf{B}egin, \textbf{I}nside) or not (\textbf{O}ther). 
-Formally, BIO tagging scheme is represented by a tag set $\mathcal{T}=\{$ B, I, O$\}$.
-
-\subsubsection{Encoder}
-First, we encode the question and context with a pretrained 
-language model, such as BERT and RoBERTa.
-Generally, the encoder takes in the input text and encodes it into 
-a series of contextualized hidden representations.
-Specifically, the BERT-style encoder takes in a
-$[CLS] $ token, followed by
-the concatenation of a question $q=(q_1, q_2, ..., q_n)$ and its context $c=(c_1, c_2, ..., c_m)$ with $[SEP]$  token,
-as the input sequence $([CLS], q_1, q_2, ..., q_n, $ $[SEP], $ $c_1, c_2, ..., c_m)$.
-We use $x=(x_1, x_2, ..., x_L)$ as a more concise notation of the above sequence, 
-where $L$ refers to the length of the input, 
-that $L=n+m+2$ when ignoring padding tokens.
-Then we send it through neural layers of the encoder to finally obtain hidden representations 
-$\mathbf{H}=\left[\mathbf{h}_1, \mathbf{h}_2, ..., \mathbf{h}_{L}\right] 
-\in \mathbb{R}^{L\times d_h}$,
-where $d_h$ denotes the hidden-layer size, and $\mathbf{h}_i$ represents the hidden representation of the $i$-th input token. 
-In the next step, output representations are sent into 
-an FFN (Feed Forward Neural Network) layer, 
-and computed the output logits as 
-$\mathbf{O}_{tag}=FFN(\mathbf{H})\in\mathbb{R}^{L\times |\mathcal{T}|}$ for token-level tag prediction,  
-where $\mathcal{T}$ denotes the tag set we described above.
-
-\subsubsection{Training \& Decoding}
-The task of token-level tag prediction that aims to assign a specific tag $t_i$ from the set $\mathcal{T}$ to each token $x_i$ in the input sequence $x$, is inherently a classification problem.
-In this regard,  we employ the widely adopted cross-entropy loss, which aggregates the negative logarithm of the predicted probability for the correct tag across all tokens in the training set.
-This loss penalizes the model heavily for confident yet incorrect predictions, prompting the model to adjust its parameters and minimize the loss.
-To optimize the answer span tagging model, we compute the cross-entropy loss, say $L_{tag}$, as follows:
-\begin{equation}\label{eq:tag_loss}
-	\centering
-	%	\widetilde{
-	L_{tag}=-\sum_{x\in D}\sum_{i=1}^{L(x)} \log (p(t_i | x_{i})) ,
-\end{equation}
-where $D$ is the training set, and $L(x)$ is the input length of $x$. 
-At the decoding step, we predict the tag $\hat{t}_i$ for token $x_i$ as follows:
-\begin{equation}\label{eq:ti1}
-	\hat{t}_i=\argmax_{t\in \mathcal{T}} p(t | x_i).
-\end{equation}
-Then, we extract a successive sequence of 
-B- and I-tagged tokens as an answer span. 
-For example, the input sequence of context ``a b c d e f'' tagged as ``O B I O B O'' can be decoded into two 
-answer spans of ``b c'' and ``e'' respectively. 
-Note that we do a post-processing step to tag``O'' for all input tokens except for those from the context, 
-which means we only draw answer spans from the input context.
-
-\subsection{Token-based Transition Awareness}
-\label{sec:aware}
-One limitation of the baseline framework is that 
-it often breaks a complete answer span into 
-many meaningless splits, 
-which is especially serious for those description answer spans.
-This reflects that the model lacks specific knowledge to indicate span boundaries accurately. 
-A context or long answer for a multi-span question contains a variable number of answer spans corresponding to one or more user intents. 
-Therefore, semantic meanings and syntactic patterns transit quickly  
-across words (or tokens), the minimal text unit.
-Following the above observation, 
-we propose a novel approach to capture such token-based neighboring transitions, 
-then come up with an auxiliary task and  joint learning strategy to incorporate such knowledge into our framework.
-
-\subsubsection{Transition Identification}
-In our approach, neighboring transitions are represented as five types of \emph{relations} in-between adjacent words by exploring whether a span transition happens across the adjacent words. 
-More specifically, for each adjacent word pair in the input, say $x_{i-1}$ and $x_{i}$, 
-8 possible tagging cases exist under the BIO tagging scheme,
-denoted as ($t_{i-1}$, $t_{i}$), where $t_{i}\in \mathcal{T}$ is the ground truth tag of $x_i$.
-As shown in \tableref{tab:relation}, 
-we summarize five relations in-between adjacent words $(x_{i-1}, x_{i})$ according to their tags $(t_{i-1}, t_{i})$, each of which corresponds to a type of span transition. 
-For example, an inter-span transition (defined as \emph{Inter} relation) happens when an adjacent word pair is tagged as (B, B) or (I, B), which means $x_{i-1}$ and $x_{i}$ are both part of the answer while belong to two consecutive but different answer spans.
-The relation of \emph{NONE} indicates that there is no span transition in-between $x_{i-1}$ and $x_{i}$.
-Note that $x_{i}$ could be either a context word (e.g., $c_i$) or a question word (e.g., $q_i$) as well as a special token (e.g., [CLS] and [SEP].
-The NONE relation holds if any word in $(x_{i-1}, x_{i})$ is a non-context word or both $x_{i-1}$ and $x_{i}$ are context words, but neither is part of the answer.
-To further illustrate the types of relations, we provide an example from the MSQA dataset in~\tableref{tab:relation}. 
-The question ``When are the Winter Olympics and where are they'' has two intents: querying the time and location of the Winter Olympics.
-The  \textit{Inter} relation between the terms ``2018'' and ``in'' indicates a semantic transition from time to location.
-By exploring every neighboring transition modeled by the defined set of relations between adjacent words, our approach effectively captures semantically and syntactically span-based transitions.
-Next, we present how to encode span-transition knowledge via adjacent word relations in \tableref{tab:relation} and incorporate such knowledge into our framework.
-
-\begin{table}[width=\textwidth,cols=4,pos=h]
-	\centering
-	% 	\begin{center}
-	\caption{The definition of adjacent word relations.}
-	\label{tab:relation}
-	% 	\begin{tabular}{lcc}
-	\begin{tabular*}{\tblwidth}{lllc}%{@{}LCC@{}}
-		\hline 
-		Tag Pair  ~$(t_{i-1}, t_{i})$ 
-		& Span Transition &  Relation Name &  MSQA Example \\
-		\hline
-		(O, O)
-		&  NONE &  NONE  &   \raisebox{-0.3\totalheight}{\includegraphics[width=0.51\textwidth]{relation_a}} \\
-		(O, B) 
-		&  Other $\rightarrow$ Span1 &   In relation & \raisebox{-0.4\totalheight}{~~~~~~~~~~~~~~~~~\includegraphics[width=0.4\textwidth]{relation_b}} \\
-		(B, I), (I, I)  
-		& Span1 $\rightarrow$ Span1 &  Intra relation & \raisebox{-0.5\totalheight}{\includegraphics[width=0.51\textwidth]{relation_c}}  \\
-		(B, B), (I, B)  
-		& Span1 $\rightarrow$ Span2 &  Inter relation & \raisebox{-0.6\totalheight}{~~~~~~~~~~~~~~~~~~~~~~\includegraphics[width=0.4\textwidth]{relation_d}} \\
-		(B, O), (I, O) 
-		& Span1 $\rightarrow$ Other  &  Out relation &
-		% \raisebox{-0.5\totalheight}{Span 1: between 9 and 25 February 2018 \\ Span 2: in Pyeongchang County , Gangwon Province , South Korea} \\
-		\raisebox{-0.5\totalheight}{\includegraphics[width=0.51\textwidth]{relation_e}} 
-		\\
-		% 		\raisebox{-0.5\totalheight}{\includegraphics[width=0.6\textwidth]{relation_e}} \\
-		\hline
-	\end{tabular*}
-	%\end{center}
-\end{table}
-
-\subsubsection{Transition Incorporation}
-After transition identification, each adjacent word pair $(x_{i-1}, x_{i})$ has been associated with a relation $r_i \in \mathcal{R}$, where $\mathcal{R}$ is the set of adjacent word relations.
-As defined in  \tableref{tab:relation}, $\mathcal{R} = \{NONE, In, Intra, Inter, Out\}$.
-Then, we equip our model with
-token-based transition knowledge though relational transformations.
-More specifically, for each $(x_{i-1}, r_i, x_i)$ triple, 
-that $r_i$ associates to a relational matrix $\mathbf{W}^{r_i}\in \mathbb{R}^{d_h\times 2d_h}$,
-we compute the enhanced contextualized representation of $x_i$
-with the awareness of span transitions as follows: 
-\begin{equation}\label{eq:matrix}
-	\mathbf{u_i}=\mathbf{W}^{r_i} \left[ \mathbf{h}_{i-1}; \mathbf{h}_i \right], 
-\end{equation}
-where $\mathbf{h_i}$ is the output representation of token $x_i$ 
-from the encoder described in \secref{sec:basic}, 
-$\mathbf{u_i}$ is its enhanced representation, 
-%and $[\mathbf{h}_{i-1}; \mathbf{h}_i]$ denotes the concatenation of $\mathbf{h}_{i-1}$ and $\mathbf{h}_i$.
-and $[;]$ is vector concatenation across row.
-Then, we send the enhanced representations $\mathbf{U} = [\mathbf{u}_1, \mathbf{u}_2, ..., \mathbf{u}_L] \in \mathbb{R}^{L\times d_h}$ into a FNN layer and compute the output logits as:
-\begin{equation}\label{eq:enhanced}
-	\mathbf{\widetilde{O}}_{tag}=FNN(\mathbf{U})\in \mathbb{R}^{L\times|\mathcal{T}|},
-\end{equation}
-where $[, ]$ is vector concatenation aross column, and 
-the implicit multiplicaiton is matrix multiplication.
-We make up a fake token $x_0$ as the prior word of $x_1$, that $(x_0, NONE, x_1)$ holds, and $\mathbf{h}_0$ is set to be a vector full of zeros.
-Hence, each input token $x_i$ can be paired with its prior token $x_{i-1}$ as an adjacent word pair indicating with a relation $r_i$, where $i$ ranges from $1$ to $L$.
-
-We argue that the awareness of span-based transition which intuitively modeled by adjacent word relations bring extra information for span identification%both semantically and syntactically
-, thus facilitate the multi-span extraction task.
-The proposed incorporation method is natural and straightforward, 
-and we will demonstrate its effectiveness in our experiments
-(See \secref{sec:experiments}).
-
-\subsection{Multi-task Learning}
-\label{sec:multitask}
-To aware the knowledge of span-based transition, 
-we need to construct a series of relations $(r_1, r_2, ..., r_L)$ from the input sequence $(x_1, x_2, ..., x_L)$, where $r_i$ indicates the adjacent word relation in-between the adjacent word pair $(x_{i-1}, x_i)$.
-%At the training step, 
-For the training data, each input token $x_i$ is annotated with a ground truth tag $t_i$, thus we can draw relation $r_i$  from the tag pair $(t_{i-1}, t_i)$ according to \tableref{tab:relation}.
-While it is not true for the test data, 
-we can not harvest accurate adjacent word relations directly.
-Thus, on the basis of previous sequence tagging model, 
-we build a multi-task learning framework by introducing an auxiliary task of token-based transition classification.
-This relation classifier of the auxiliary task shares the BERT-style encoder with previous tagging model with a new, unshared FNN layer upon. The output logits of relation classifier are computed as: 
-\begin{equation}\label{eq:aux_logits}
-	%	\widetilde{
-	\mathbf{O}_{rel}=FNN([ \mathbf{H}_{prev}; \mathbf{H} ]) \in \mathbb{R}^{L \times |\mathcal{R}|},
-\end{equation}
-where $\mathbf{H}_{prev}=[\mathbf{h}_0, \mathbf{h}_1, ..., \mathbf{h}_{L-1}]\in \mathbb{R}^{L\times d_h}$ denotes representations of the prior token sequence $(x_0, x_1, ..., x_{L-1})$ with respect to the input sequnce $(x_1, x_2, ..., x_L)$.
-For the auxiliary task, we use cross-entropy loss to train the relation classifier, which reflects the awareness of span-based transition. 
-More specifically, the above loss $L_{rel}$ is computed as:
-\begin{equation}\label{eq:rel_loss}
-	%	\widetilde{
-	L_{rel}=- \sum_{x\in D}\sum_{i=1}^{L(x)} \log (p(r_i | x_{i-1}, x_{i})) ,
-\end{equation}
-where $D$ refers to the training data, and $L(x)$ denotes the length of input sequence $x$. 
-To jointly learn shared parameters in the encoder as well as leverage the representation of token-based transition knowledge, we use a combinartorial loss as follows:
-\begin{equation}\label{eq:loss}
-	%	\widetilde{
-	%	L= L_{tag} + \lambda L_{rel}.  %,
-	L = L_{tag} + L_{rel}.  %,
-\end{equation}
-
-In summary, 
-the strategy of our multi-task learning framework is that, 
-given an input sequence, we first predict the token-based transitions in each position, 
-then leverage the predicted transitions to calculate the enhanced token representation following \eqnref{eq:enhanced}, 
-finally optimize the proposed combinartorial loss in \eqnref{eq:loss} to update joint model parameters together.
-
-\subsection{Decoding}
-\label{sec:decoding}
-Next, we present two decoding strategies for our joint framework.
-As described above, we jointly train two tasks (i.
-e, sequence tagging and transition classification) in our framework, then predict the adjacent token-based transitions and the token tags respectively.
-Intuitively,  
-we can decode the answer spans from tags predicted by the enhanced sequence tagging model of our framework directly, 
-similar to the decoding algorithm described in \secref{sec:basic}.
-Formally, we decode tag $\hat{t}_i$ of $x_i$ as follows:
-\begin{equation}\label{eq:t_i1}
-	\hat{t}_i = \argmax_{t\in \mathcal{T}} p(t | x_i, \mathcal{M}_{tag}),
-\end{equation}
-where $\mathcal{M}_{tag}$ represents the token-based transition aware tagging model (see \secref{sec:aware}). 
-As we will see in \secref{sec:experiments}, this enhanced tagging model outperforms the baseline model marginally.
-
-While the predicted tags implicitly incorporate the knowledge of token-based transitions, we propose to explicitly combine the predictions from the enhanced tagging model $\mathcal{M}_{tag}$ with those from the transition classifier $\mathcal{M}_{rel}$ at decoding time.
-We score the potential tag $t$ of a token $x_i$, considering not only $x_i$ but also its prior token $x_{i-1}$ through the predicted transition $r_i$ in-between.
-
-To be more specific, we jointly decode the tag $t_i$ of $x_i$ as  follows:
-\begin{equation}\label{eq:t_i}
-	\hat{t}_i = \argmax_{t\in \mathcal{T}} \widetilde{S}(t | x_{i-1}, x_i, \hat{t}_{i-1}, \mathcal{M}_{joint}),
-\end{equation}
-where $\widetilde{S}$ denotes the scoring function that intakes the predicted transition between $x_{i-1}$ and $x_i$.
-Therefore, $\widetilde{S}(t  | x_{i-1}, x_i, \hat{t}_{i-1}, \mathcal{M}_{joint})$ is computed as: 
-\begin{equation}\label{eq:decoding}
-	\begin{split}
-		\widetilde{S}(& t | x_{i-1}, x_i, \hat{t}_{i-1},  \mathcal{M}_{joint})  = S(t|x_i, \mathcal{M}_{tag}) +  S(\hat{r}_i | x_{i-1}, x_i, \hat{t}_{i-1}, t, \mathcal{M}_{rel})\\
-		& = S(t|x_i, \mathcal{M}_{tag}) + \mathds{1}(\hat{t}_{i-1} \in \text{First}(\hat{r}_i)) S({\hat{r}_i}| x_i, x_{i-1}, \mathcal{M}_{rel})^{\frac{1}{2}}\cdot \mathds{1}(t \in \text{Second}(\hat{r}_i)) S({\hat{r}_i}| x_i, x_{i-1}, \mathcal{M}_{rel})^{\frac{1}{2}}\\
-		& = S(t|x_i, \mathcal{M}_{tag}) + \mathds{1}(\hat{t}_{i-1} \in \text{First}(\hat{r}_i)) \cdot \mathds{1}(t \in \text{Second}(\hat{r}_i)) \cdot  S({\hat{r}_i}| x_i, x_{i-1}, \mathcal{M}_{rel}),
-	\end{split}
-\end{equation}
-where $S$ refers to the probability score, $\mathds{1}$ denotes the indicator function, $\text{First}(r)$ represents 
-a set of tags consisting of the distinct first elements of all tag pairs mapped from $r$ according to \tableref{tab:relation}, and $\text{Second}$ operates like $\text{First}$ except that $\text{Second}$ collects the second elements.
-For example, \emph{Inter} can be mapped into two kinds of tag pairs (B, B) and (B, I), then 
-$\text{First}(\emph{\text{Inter}})$ is the set $\{\text{B}\}$ and   $\text{Second}(\emph{\text{Inter}})$ is the set $\{\text{B}, \text{I}\}$.
-Note that, $\hat{r}_i$ in \eqnref{eq:decoding} is the optimal transition relation predicted by $\mathcal{M}_{tag}$ which is computed as: 
-\begin{equation}\label{eq:r_i}
-	\hat{r}_i = \argmax_{r_i\in \mathcal{R}} p(r_i | x_{i-1}, x_i, \mathcal{M}_{rel}).
-\end{equation}
-
-%	\input{experiments}
-\section{Experiments}
-\label{sec:experiments} %preamble 16:10 - 16:40
-In this section, we compare TOAST with multiple strong baselines on multi-span question answering. 
-We first introduce the datasets and experimental setup, 
-then show the experimental results and analysis for different models.
-
-%To show the generalization ability of TOAST
-
-\subsection{Dataset Description} 
-\label{sec:dataset}
-% 17:30 - 20:00  0.4页 
-% MultiSpanQA  MultiSpanQA (expanded)  0.2页
-We conduct the experiments  on three RC datasets, including
-two English datasets, namely MultiSpanQA and its variant MultiSpanQA (expand), as well as one Chinese dataset, namely CLEAN (ours).
-\tableref{tab:datasets} shows an overview statistics of those datasets.
-To examine the performance of different models on various question types, 
-we categorize the samples into two types: \emph{description} and \emph{entity}, 
-based on the expected answer type. \tableref{tab:answer_types} illustrates the breakdown of these types along with an example for each answer type class.
-Note that, MSQA is short for MultiSpanQA, and MSQA-Exp is short for the expansion of MultiSpanQA.
-
-%\subsubsection*{QUOREF}
-%%%%%%%%
-%Quoref~\cite{DBLP:conf/emnlp/DasigiLMSG19} contains over 21K examples, where each example is a triple of (question, context, answer). 
-%The contexts consist of 4.7K paragraphs  from English Wikipedia, from each paragraph a number of questions requiring coreferential reasoning are derived.
-Quoref contains both single-span and multi-span questions, whose answers are spans and sets of spans, respectively.
-%%%%%%%%%%%%%
-%4.7K paragraphs where the answer to a single-span question is a single span, and the answer to a multi-span question is a set of spans. English Wikipedia. 
-%Quoref, an earlier RC dataset which contains multi-span questions models the answers 
-\subsubsection*{MultiSpanQA} 
-MultiSpanQA~\citep{li2022multispanqa}, a recently proposed dataset for multi-span question answering, consists of 6.5K multi-span examples, where the questions are user queries issued to Google search engine and the contexts are extracted from English Wikipedia.
-\subsubsection*{MultiSpanQA (expand)}
-MultiSpanQA(expand)~\citep{li2022multispanqa}, an expanded variant of MultiSpanQA, intakes single-span and unanswerable questions, and consists of 19K examples in total.
-\subsubsection*{CLEAN}
-We propose CLEAN harvesting from a Chinese online knowledge Q\&A sharing platform (i.e., BaiduZhidao), 
-which consists of 9,063 examples in total, including over 4.2K multi-span examples. 
-CLEAN contains 3,077 distinct open-domain user questions, and each question is annotated with a number of contexts from its associated long answers.
-To be more specific, we recruit three annotators to extract answer spans from given contexts, and retained only those examples that achieved a Fleiss' Kappa score greater than 0.5.
-Our results indicate a high level of inner-annotator agreement, with a Fleiss' Kappa score of 0.739, suggesting that the annotations are consistent and reliable.
-
-\begin{table}[width=.7\textwidth,cols=4,pos=h]
-	\caption{Dataset statistics.}
-	\label{tab:datasets}
-	\begin{tabular*}{\tblwidth}{lccc}
-		\toprule
-		Dataset 
-		& Language &  \#Examples & \#Multi-span Examples \\
-		\hline
-		% 		QUOREF~\cite{DBLP:conf/emnlp/DasigiLMSG19}
-		% 		&  English &  21,817  & 2,207 \\
-		MSQA~\cite{li2022multispanqa}
-		&  English  & 6,536   & 6,536  \\
-		MSQAExp~\cite{li2022multispanqa}
-		&  English  & 19,608   & 6,536  \\
-		CLEAN (ours)
-		& Chinese &  9,063  & 4,204  \\
-		\bottomrule
-	\end{tabular*}
-\end{table}
-
-\begin{table}[width=.7\textwidth,cols=4,pos=h]
-	\caption{Proportion and examples of answer types in MSQA and CLEAN Datasets.}
-	\label{tab:answer_types}
-	\begin{tabular*}{\tblwidth}{llcp{8cm}}
-		\toprule
-		\textbf{Dataset} & \textbf{Answer Type} & \textbf{\%} & \textbf{Example} \\
-		\midrule
-		\multirow{3}{*}{MSQA} & Description & 16.40 & \emph{other gases} \\
-		& Entity & 76.30 & \emph{Vermont} \\
-		& \emph{Numeric} & 7.30 & \emph{9,677 ft} \\
-		\midrule
-		\multirow{3}{*}{CLEAN} & Description & 76.54 & \emph{长满了尖锐的刺 (full of sharp thorns)} \\
-		& Entity & 18.00 & \emph{北京市 (Beijing)}  \\
-		& Numeric & 5.46 & \emph{1006万人 (10.06 million people)} \\
-		\bottomrule
-	\end{tabular*}
-\end{table}
-
-%Our results demonstrate a high level of inner-annotator agreement, as indicated by a Fleiss' Kappa score of 0.739.
-This high score strengthens the validity of subsequent analyses, as it suggests that the annotations are consistent and reliable.
-%Our results demonstrate a high level of inner-annotator agreement, as indicated by a Fleiss' Kappa score of 0.739 suggesting that the annotations are consistent and reliable. 
-%We  ask 3 annotators to extract answer spans from contexts, and remain those examples with Fleiss Kappa greater than 0.5.
-Finally, CLEAN demonstrates a high level of inner-annotator agreement, as evidenced by a Fleiss' Kappa score of 0.739.
-%Te sample 208 examples from  CLEAN The inner-annotator agreement of each   \ZY{加一个一致性}
-% 弄一个数据集的表格 解释 QUAREF, MultiSpanQA, CLEAN的区别
-% 分别给出例子
-
-%\example{xx}
-% CLEAN 总共有9063条数据 即(question, context, answers) triples
-% 其中包括3077个unique的questions 平均每个问题有 9063/3077个有效回答
-% 4204 个multi-span examples
-% 1588 个multi-span questions
-% \begin{table}[h]
-%	\caption{Proportion and examples of answer types in MSQA and CLEAN.}
-%	\label{tab:answer_types}
-%	\begin{tabular*}{\tblwidth}{lcc}
-%		\toprule
-%		Answer type 
-%		& \% &  Example  \\
-%		\hline
-%		MSQA
-%		&  English  & 6,536   & 6,536  \\
-%		MSQAExp~\cite{li2022multispanqa}
-%		&  English  & 19,608   & 6,536  \\
-%		CLEAN (ours)
-%		& Chinese &  9,063  & 4,204  \\
-%		\bottomrule
-%	\end{tabular*}
-%\end{table}
-
-\subsection{Experimental Setup}
-\label{sec:setup}
-% 22:00 - 22:30 preamble 
-For all competing models and our models, we use the HuggingFace implementation of $\text{BERT}_{base}$ or $\text{RoBERTa}_{base}$ as the \emph{encoder} with $max\_len=512$. 
-Specifically, for TOAST models, we initialize the learning rate to $3e-5$ and set the batch size to $32$, then use the BERTAdam optimizer with a weight decay of 0.01. 
-Our approach does not involve tuning the parameters on the validation set. Instead, we rely on using the model checkpoints obtained after 50 epochs.
-As for the other competing models, we follow the configurations as originally reported  in~\citep{segal2020simple,li2022multispanqa,lee2023liquid} accordingly. 
-%with a linear warm-up at first 200 steps.
-Next, we introduce the comparison models and the evaluation metrics in our experiments. 
-\subsubsection{Models Under Comparison}
-\label{sec:baselines}
-% 6:00 - 8:00  0.4页
-We introduce four competing models for multi-span answer extraction.
-These are \textbf{SSE}~\citep{DBLP:conf/naacl/DevlinCLT19}, \textbf{TASE}~\citep{segal2020simple}, \textbf{SNP-TASE}~\citep{li2022multispanqa} and \textbf{LIQUID}~\citep{lee2023liquid}.
-
-\textbf{SSE} is a traditional single-span extraction  model which formulates the answer extraction task by span labeling, i.e., identifying in the context a span (a continuous string of text) that constitutes an answer.
-SSE builds a learnable linear layer upon the encoder which is used to predict the start and end position of the span.
-We adapt SSE for multi-span question answering, that considers the first span of a multi-span answer as the ground truth at the training step.
-
-\textbf{TASE} is a tag-based span extraction model which identifies the multi-span answer by assigning a tag to every input token with BIO tagging scheme.
-Following~\cite{li2022multispanqa}, we build a strong baseline upon TASE, integrating with span number prediction and structure prediction, namely \textbf{SNP-TASE}.
-
-The most recent framework, \textbf{LIQUID}~\citep{lee2023liquid}, employs question generation as a form of data augmentation to enhance answer extraction performance, differing from the conventional emphasis on the exploration of model architectures.
-
-According to the different strategies of decoding,
-we propose two models, $\textbf{TOAST}_{tag}$ and $\textbf{TOAST}_{joint}$, on the basis of our framework, where
-\textbf{TOAST} is our joint learning framework, and the respective suffix designates the module from which predictions are used at decoding step.
-$\textbf{TOAST}_{tag}$ predicts a tag for every token using the predictions of $\mathcal{M}_{tag}$ (see \eqnref{eq:t_i1}), while $\textbf{TOAST}_{joint}$  leverages predictions from both $\mathcal{M}_{tag}$ and $\mathcal{M}_{rel}$ explicitly (see \eqnref{eq:t_i}).
-%\begin{itemize}
-%	\item[] \textbf{TOAST} 
-%\end{itemize}
-\subsubsection{Evaluation Metrics}
-\label{sec:metrics}
-% 9:30 - 11:30  0.4页
-% 人工判断标准   因为
-We evaluate the performance of our methods by automatic metrics and human evaluation.
-% Exact Match
-
-\textbf{Automatic Metrics.}  We use two automatic metrics for evaluation: Exact Match and F1 score. 
-%The exact match metric  and F1 score.
-Following Segal et al.~\cite{segal2020simple} and Li et al.~\cite{li2022multispanqa}, we use Exact Match (EM) on question-level and span-level as well as Partial Match (PM) scores as the automatic metrics for multi-span question answering evaluation.
-\begin{itemize}
-	\item \textbf{Exact Match}.
-An exact match occurs when a predicted span fully matches one of the ground-truth answer spans.
-We calculate the micro-average precision, recall and f1 score for the extract match metric.
-	%	For each example, we iterate over  the predicted spans given by the model for evaluation, and an exact match occurs when the predicted span exactly matches one of the ground-truth spans for that example.
-	\item \textbf{Overlap F1 score}. Overlap F1 score is the macro-average f1 score, where the f1 score for each example is computed by treating the prediction and gold as a bag of tokens.
-\end{itemize}
-The exact match shows the quality of predictions straightforwardly.
-However, counting the number of exact matches makes the score discrete and coarse.
-Besides, it penalizes the partial matched prediction too much.
-The overlap F1 score considers the overlap between the prediction and gold and thus can be used as a complementary metric to the exact match metric.
-%\textbf{Exact Match} 
-%
-%\textbf{Partial Match}
-% F1 score 
-%In QA, it's computed over the individual words in the prediction against those in the True Answer.
-The number of shared words between the prediction and the truth is the basis of the F1 score: precision is the ratio of the number of shared words to the total number of words in the prediction, and recall is the ratio of the number of shared words to the total number of words in the ground truth.
-%https://github.com/eladsegal/tag-based-multi-span-extraction/blob/master/predictions/quoref_predictions.jsonl
-
-\textbf{Human Evaluation.} We randomly select 50 samples from each dataset and average the scores of two human annotators who are proficient in English and Chinese.
-%We ask annotators to give a score on each predicted span of one sample, ranging from 1 to 5, then average the scores of each span as the final score of this sample.
-%We ask the annotators to score each predicted span for a sample on a five-scale scores, ranging from 1 to 5, according to its quality, and then average the scores for each span as the final score for that sample.
-We ask the annotators to score each sample under 3 span-level aspects (completeness, correctness and distinctness) and the overall quality:
-\begin{itemize}
-	\item \textbf{Completeness} is to measure the semantic completeness of a given predicted span. If the span expresses the meaning completely, it will receive a high rate on the completeness.
-	\item \textbf{Correctness} is to measure the content correctness of a given predicted span. If the span answers the user question correctly, it will receive a high rate on the correctness.
-	\item \textbf{Distinctness} is to measure the content distinctness of a given predicted span against other predictions.
-If the span distinguishes from others semantically, it will receive a high rate on the distinctness.
-	\item \textbf{Overall} is to measure the overall quality of the predictions from a model for each sample.
-\end{itemize}
-For a given sample, each aspect is judged as a five-scale scores, 
-ranging from 1 (Poor) to 5 (Excellent) depending on its quality.
-For each span-level aspect, we score every predicted span and then average the scores across all predicated spans for evaluation.
-In addition, for each sample we use the averaged overall scores from three annotators to present the overall quality of the predictions of that sample.
-%For a given sample and aspect, we score each predicted span on a five-scale scores, ranging from 1 to 5, according to its quality, and then average the scores of all predicted spans respectively to evaluate that sample on the given aspect.
-
-% 整几个方面
-
-%For each sample, we ask an annotator scores for each predicted span with three-scale 
-\subsection{Experimental Results and Analysis}
-\label{sec:evaluation}
-% 13:00 - 17:00 做各种实验
-% encoder: RoBERTa large
-In this section, we compare TOAST with all competing models described above both quantitatively and qualitatively.
-
-\subsubsection{Comparison Results}
-\label{sec:comparison}
-We evaluate our model as well as baselines (\secref{sec:baselines}) on the development splits of four datasets (\secref{sec:dataset}) using both automatic metrics and human evaluation metrics (\secref{sec:metrics}).
-The comparison results are shown in \tableref{tab:exact_match} (exact match), \tableref{tab:overlapped} (overlap) and \figref{fig:human_eval} (human evaluation).
-
-\begin{table}[width=\textwidth,cols=4,pos=h]
-	%	\centering
-	\caption{The Exact Match results for all competing models, including micro-average precision (P), recall (R) and f1 score (F1). }
-	\label{tab:exact_match}
-	\begin{tabular*}{\tblwidth}{@{}p{2.2cm}p{1.0cm}p{1.0cm}p{1.0cm}cp{1.0cm}p{1.0cm}p{1.0cm}cp{1.0cm}p{1.0cm}p{1.0cm}@{}}
-		\toprule[0.3mm]
-		\multicolumn{1}{l}{}  & \multicolumn{3}{c}{MSQA}  & \multicolumn{1}{l}{}  & \multicolumn{3}{c}{MSQA-Exp} & \multicolumn{1}{l}{} & \multicolumn{3}{c}{CLEAN} \\ 
-		\cline{2-4} \cline{6-8} \cline{10-12}
-		%		\midrule
-		\addlinespace
-		& P(\%)  & R(\%)  & F1(\%)  &  ~& P(\%)    & R(\%)   & F1(\%)  & ~ & P(\%)   & R(\%)  & F1(\%)  \\
-		%		\cline{2-4} \cline{6-8} \cline{10-12}
-		%		\midrule
-		\toprule[0.3mm]
-		$\left[\text{BERT}_{base}\right]$ & & & & & & & & & \\ \midrule
-		SSE              & 52.53 & 17.95  & 26.76  & & 32.21    & 19.61   & 24.38  &  & 22.02   & 21.19  & 21.60  \\
-		TASE                 & 54.16  & 63.63  & 58.52  & & 51.01    & 59.12   & 54.77  &  & 28.73   & 49.39  & 36.33  \\
-		SNP-TASE              & 58.12  & 60.50 & 59.28 &  & 58.32   & 60.34 & 59.31  & & -   & -  & -  \\
-		LIQUID  & 55.67  &66.24  & 60.50 &  & 55.56   & 61.49  & 58.37 &  & 41.04  & 47.95  & 44.23 \\
-		$\text{TOAST}_{tag}$           & 60.10  & 66.61  & 63.19  &  & 59.47    & 61.98   &  60.70  &  & 57.95   & 62.31  & 60.05  \\
-		$\text{TOAST}_{joint}$          & \textbf{60.55}  & \textbf{66.82}  & \textbf{63.53}  & & \textbf{60.97}    & \textbf{65.57}   & \textbf{63.19}   & &  \textbf{58.48}  & \textbf{62.64}   & \textbf{60.49}  \\
-		%		\midrule
-		\toprule[0.3mm]
-		%		\toprule
-		$\left[\text{RoBERTa}_{base}\right]$  & & & &  & & & & & & & \\ \midrule
-		SSE                & 55.13  & 18.84  & 
-		28.08  & & 33.18    & 20.20   & 25.12  &  & 23.41   & 22.74  & 23.07  \\
-		TASE                  & 63.91  & 69.13  & 66.42  & & 64.17    &  68.20   & 66.12  &  & 33.62   & 51.05  & 40.54  \\
-		SNP-TASE             & 61.43  & 67.30  & 64.23  & & 32.85    & 22.41   & 26.64  &  & -   & -  & -  \\
-		LIQUID  & 66.14  & 72.16  & 69.02 & & 63.80    & 66.21   & 64.98  &  & 47.75   & 56.20  & 51.63  \\
-		$\text{TOAST}_{tag}$    & 68.15   & 73.57  &  70.76  & & 66.90   & 68.23   & 67.56  &  & 61.04   & 64.32  & 62.64  \\
-		$\text{TOAST}_{joint}$         &\textbf{68.61}  & \textbf{73.89}  & \textbf{71.15} &  & \textbf{68.41 } & \textbf{69.01}   & \textbf{68.71}  & & \textbf{61.86}  & \textbf{64.52}  & \textbf{63.16}  \\ \bottomrule
-	\end{tabular*}
-\end{table}
-
-\begin{table}[width=\textwidth,cols=4,pos=h]
-	%	\centering
-	\caption{The Overlapped results for all competing models, including macro-average precision (P), recall (R) and f1 score (F1). }
-	\label{tab:overlapped}
-	\begin{tabular*}{\tblwidth}{@{}p{2.2cm}p{1.0cm}p{1.0cm}p{1.0cm}cp{1.0cm}p{1.0cm}p{1.0cm}cp{1.0cm}p{1.0cm}p{1.0cm}@{}}
-		\toprule[0.3mm]
-		\multicolumn{1}{l}{}  & \multicolumn{3}{c}{MSQA}  & \multicolumn{1}{l}{}  & \multicolumn{3}{c}{MSQA-Exp} & \multicolumn{1}{l}{} & \multicolumn{3}{c}{CLEAN} \\ 
-		\cline{2-4} \cline{6-8} \cline{10-12}
-		\addlinespace
-		& P(\%)  & R(\%)  & F1(\%)  &  ~& P(\%)    & R(\%)   & F1(\%)  & ~ & P(\%)   & R(\%)  & F1(\%)  \\
-		\toprule
-		$\left[\text{BERT}_{base}\right]$ & & & & & & & & & \\ \midrule
-		SSE                   & 72.44  &48.05 & 57.77 & & 46.23    & 42.02   & 44.03  & & 65.90   & 67.19  & 66.54  \\
-		TASE                  & 77.34 & 77.25  & 77.30 & & 70.39   & 70.03   & 70.21  & & 67.48   & 74.02  & 70.60  \\
-		SNP-TASE           &  79.56  & 73.23 & 73.23  & & 74.05    & 68.06   & 70.47 &   & -   & -  & - \\
-		LIQUID   & 78.60 & 79.80 & 79.20  & & 72.65  & 71.91  & 72.29 &  & 70.91  & 67.82  & 69.33  \\
-		$\text{TOAST}_{tag}$          & 79.48 &  78.78  &  79.12 &  & 73.47    & 71.37   & 72.40 &  & \textbf{82.32}   & 79.41  & 80.84  \\
-		$\text{TOAST}_{joint}$        & \textbf{79.88}& \textbf{79.72}  & \textbf{79.80}  & & \textbf{78.49}    & \textbf{76.87}   & \textbf{77.65}   & & 82.16   & \textbf{79.83}  & \textbf{80.98}  \\ 
-		%		\midrule
-		\toprule[0.25mm]
-		$\left[\text{RoBERTa}_{base}\right]$ & & & & & & & & & & & \\ \midrule
-		SSE              & 75.65  & 49.25  & 59.66  & & 48.53    &  43.48   & 45.87   & & 66.24  & 67.25  & 66.74 \\
-		TASE                & 82.56    & 81.73   & 82.14  & & 78.94    & \textbf{78.81  } & 78.88 &  & 70.81  & 75.68  & 73.16  \\
-		SNP-TASE              & 80.72  & 79.83  & 80.27  & & 47.79    & 27.10   & 34.59   & & -   & -  & -  \\
-		LIQUID  & 80.90  & 81.50  & 81.20  & &  78.31   & 76.14  & 77.21  & & 75.60  & 74.96  &  75.28  \\
-		$\text{TOAST}_{tag}$            & 83.76  & 84.27  & 84.01  & & 79.64   & 77.72   & 78.67  & & 83.77   & 80.58  & 82.15  \\
-		$\text{TOAST}_{joint}$    & \textbf{84.06}  & \textbf{84.40}  & \textbf{84.23}  & & \textbf{80.65}    & 78.47  & \textbf{79.54}  & & \textbf{83.81}  & \textbf{80.79}  & \textbf{82.27}  \\ 
-		\bottomrule[0.25mm]
-	\end{tabular*}
-\end{table}
-
-\tableref{tab:exact_match} and \tableref{tab:overlapped} illustrate the performance comparison between the proposed models, $\text{TOAST}_{tag}$ and $\text{TOAST}_{joint}$, and  several strong baselines, including the previous state-of-the-art model LIQUID.
-These comparisons are conducted using both the $\text{BERT}_{base}$  and $\text{RoBERTa}_{base}$ encoders.
-Notably, $\text{TOAST}_{tag}$ exhibits superior performance in EM F1 across all three datasets.
-However, when employing the $\text{BERT}_{base}$ encoder on the MSQA dataset, $\text{TOAST}_{tag}$ demonstrates slightly lower performance in overlapped F1 compared to LIQUID.
-Importantly, the performance of $\text{TOAST}_{joint}$ consistently outperforms LIQUID on all three datasets, irrespective of the encoder setting.
-These results demonstrate the effectiveness of our proposed framework, as well as the efficacy of the joint decoding strategy.
-%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%
-%dev_precision: 65.31 | dev_recall: 71.22 | dev_f1 = 68.14| dev_macro_precision = 83.38| dev_macro_recall = 82.80| dev_macro_avg_f1 = 83.09
-To be more specific, \tableref{tab:exact_match} shows the comparisons of exact match scores among all competing models.
-We can see that our proposed framework, TOAST, consistently outperforms all other baselines across multiple multi-span question answering datasets.
-Backed by $\text{BERT}_{base}$,    $\text{TOAST}_{tag}$ achieves EM F1 scores of 63.19 and, 60.70 and 60.05 on the datasets of MSQA, MSQA-Exp and CLEAN, respectively.
-Moreover, when equipped with the joint decoding strategy, $\text{TOAST}_{joint}$ achieves even higher EM F1 scores of 63.53 and, 63.19 and 60.49 on the same datasets.
-These results showcase substantial improvements over the previous state-of-the-art model, LIQUID, with EM F1 score enhancements ranging from 3.03 to 16.26 across various datasets.
-Additionally, when utilizing $\text{RoBERTa}_{base}$ instead of  $\text{BERT}_{base}$, $\text{TOAST}_{joint}$ 
-achieves EM F1 scores of 71.15, 68.68 and 63.16 on the respective datasets. These scores represent EM F1 improvements of 7.62, 5.49 and 2.67 compared to the previous setup.
-
-The overlapped F1 results shown in \tableref{tab:overlapped} demonstrate similar trends to the EM F1 results.
-In comparison to the state-of-the-art (SOTA) model LIQUID, $\text{TOAST}_{joint}$ achieves improvements in overlapped F1 scores.
-Specifically, when using  $\text{BERT}_{base}$, the improvements are 0.6, 5.36,  11.65 on the MSQA, MSQA-Exp and CLEAN datasets, respectively.
-Similarly, when employing $\text{RoBERTa}_{base}$, the improvements of 3.03, 2.33, and 6.99 are observed on the same datasets.
-When augmenting TOAST with joint decoding, we observed further performance  improvements on both BERT-based and RoBERTa-based encoders.
-This outcome highlights the effectiveness of the joint decoding strategy, which explicitly combines predictions from multitask modules.
-%Moreover, our proposed model demonstrates robustness in effectively generalizing across different datasets without requiring hyperparameter re-tuning. 
-%In contrast, SNP-TASE faces challenges in achieving such generalization.
-%While SNP-TASE demonstrates satisfactory performance when utilizing the $\text{BERT}_{base}$ encoder, its effectiveness significantly declines when transitioning to the $\text{RoBERTa}_{base}$ encoder.
-%\textcolor{blue}{
-Moreover, our proposed model demonstrates robustness in effectively generalizing across different datasets without requiring hyperparameter re-tuning.
-In contrast, SNP-TASE faces challenge in achieving such generalization.
-While SNP-TASE demonstrates satisfactory performance when utilizing the $\text{RoBERTa}_{base}$ encoder on MSQA dataset, its effectiveness significantly declines when transitioning to MSQA-Exp dataset with the same hyperparameter configuration.
-Specifically, SNP-TASE achieves an EM F1 score of approximately 27, which is considerably lower compared to other competing models.
-These results suggest the potential need for hyperparameter re-tuning when applying the SNP-TASE model to different datasets.
-To ensure a fair comparison with other competing models that did not undergo this re-tuning process, we report the raw results of the SNP-TASE model without any adjustments.
-%}
-
-% 
-%As shown in \tableref{tab:exact_match} and \tableref{tab:overlapped},
-%when utilizing the $\text{BERT}_{base}$ encoder, $\text{TOAST}_{tag}$ demonstrates superior performance compared to the previous state-of-the-art model, LIQUID, across all three datasets. 
-%However, with the $\text{RoBERTa}_{base}$ encoder, $\text{TOAST}_{tag}$ exhibits slightly lower performance than LIQUID.
-It is worth nothing that the performance of $\text{TOAST}_{joint}$ surpasses that of  LIQUID on all three datasets, consistently outperforming it across both the $\text{BERT}_{base}$ and $\text{RoBERTa}_{base}$ encoder settings, which shows the effectiveness of our proposed framework as well as of joint decoding strategy.
-
-% 1. joint decoding 策略有效
-% 2. 我们最好的模型比之前SOTA提高了xx xx xx
-% 
-%We can see that our proposed framework TOAST  outperforms all the other baselines on all multi-span question answering datasets, except Quoref, under both automatic metrics and human evaluation metrics.
-
-%%%%%%%%%%%%
-
-%%%%%%%%%%
-%Our proposed framework, TOAST, exhibits superior performance compared to all other baselines across multiple multi-span question answering datasets, with the exception of Quoref, as demonstrated by both automatic metrics and human evaluation.
-This discrepancy can potentially be attributed to the Quoref dataset's emphasis on evaluating coreference resolution capabilities.
-%Additionally, when augmenting TOAST with joint decoding, referred to as $\text{TOAST}_{joint}$, we observed further improvements in performance on both BERT-based and RoBERTa-based encoders.
-This outcome highlights the effectiveness of the joint decoding strategy, which explicitly combines predictions from multitask modules.
-%%%%%%%%%%%%%%%
-%In addition, $\text{TOAST}_{joint}$, the TOAST framework equipped with joint decoding, outperforms vanilla TOAST on both BERT-based and RoBERTa-based encoders
-%by xx percent
-%,  showing the effectiveness of the joint decoding strategy that explicitly combines the predictions from multitask modules.
-
-%%%%%%%%%%%%%%%%%%%%Table 6
-%\begin{table}[bth!]
-%	\centering
-%	\caption{The human evaluation results for all competing models, including the span-level evaluation (completeness, correctness, distinctness), and the question-level evaluation (overall quality). }
-%	\label{tab:human}
-%	\begin{tabular*}{\tblwidth}{@{}lcccccccccccc@{}}
-%		\toprule
-%		\multicolumn{1}{l}{} & \multicolumn{3}{c}{Span-level Evaluation} & \multicolumn{1}{c}{Question-level Evaluation} \\ \midrule
-%		& Completeness (1-5)   & Correctness (1-5) & Distinctness (1-5) & Overall (1-5)  \\
-%		\midrule
-%		SSE                  & 00.00   & 00.00   & 00.00  & 00.00  \\
-%		TASE                 & 00.00   & 00.00   & 00.00  & 00.00  \\
-%		SNP-TASE             & 00.00   & 00.00   & 00.00  & 00.00 \\
-%		LIQUID             & -   & -   & -  & - \\
-%		$\text{TOAST}_{tag}$          & 00.00   & 00.00   & 00.00  & 00.00  \\
-%		$\text{TOAST}_{joint}$        & 00.00   & 00.00   & 00.00  & 00.00  \\ \bottomrule
-%	\end{tabular*}
-%\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%
-
-In addition, \figref{fig:human_eval} presents the comparison results of human evaluation on the overall quality of the complete answer, as well as three aspects at the span-level: completeness, correctness and distinctness.
-Specifically, \figref{fig:bert_msqa}  and \figref{fig:roberta_msqa} illustrate the comparisons on the MSQA dataset using $\text{BERT}_{base}$ and $\text{RoBERTa}_{base}$, respectively.
-Similarly, \figref{fig:bert_clean} and \figref{fig:roberta_clean} depict the comparisons on the CLEAN dataset.
-As shown in \figref{fig:human_eval}, the competing models demonstrate superior performance in terms of \emph{completeness} and \emph{distinctness} when extracting spans from the MSQA dataset compared to the CLEAN dataset.
-This observation can be attributed to the prevalence of entity-type questions in the MSQA dataset (see \tableref{tab:answer_types}), which are typically shorter and relatively easier to extract completely using tagging models.
-
-\begin{figure*}[!ht]
-	\centering
-	\begin{subfigure}{.49\textwidth}
-		\centering
-		\includegraphics[width=0.99\linewidth]{bert_msqa}
-		\caption{Comparisons on MSQA based on $\text{BERT}_{base}$}
-		\label{fig:bert_msqa}
-	\end{subfigure}%
-	\begin{subfigure}{.49\textwidth}
-		\centering
-		\includegraphics[width=0.99\linewidth]{roberta_msqa}
-		\caption{Comparisons on MSQA based on $\text{RoBERTa}_{base}$}
-		\label{fig:roberta_msqa}
-	\end{subfigure}%
-
-	\begin{subfigure}{.49\textwidth}
-		\centering
-		\includegraphics[width=0.99\linewidth]{bert_clean}
-		\caption{Comparisons on CLEAN based on $\text{BERT}_{base}$}
-		\label{fig:bert_clean}
-	\end{subfigure}%
-	\begin{subfigure}{.49\textwidth}
-		\centering
-		\includegraphics[width=0.99\linewidth]{roberta_clean}
-		\caption{Comparisons on CLEAN based on $\text{RoBERTa}_{base}$}
-		\label{fig:roberta_clean}
-	\end{subfigure}%
-
-	\caption{Human evaluations on MSQA and CLEAN datasets. }
-	\label{fig:human_eval}
-\end{figure*}
-
-Our proposed models, $\text{TOAST}_{tag}$ and $\text{TOAST}_{joint}$, demonstrate an overall superior performance in the human evaluation.
-Specifically, concerning the MSQA dataset, TOAST outperforms the strong baselines TASE and LIQUID in terms of the span correctness and the overall answer quality (see \figref{fig:bert_msqa} and \figref{fig:roberta_msqa}).
-However, it shows a slight decline in the completeness and distinctiveness aspects of spans when using $\text{RoBERTa}_{base}$ (see  \figref{fig:roberta_msqa}).
-We observe that the LIQUID model tends to extract keywords from reference spans of the description type, leading to the fragmentation of answer spans into multiple shorter spans, such as single-word nouns.
-While these shorter spans are more likely to achieve enhanced completeness and distinctiveness at the span level, but this does not necessarily imply that LIQUID is more effective.
-In fact, $\text{TOAST}_{joint}$ consistently outperforms them in terms of span correctness and the overall quality.
-On the other hand, in the comparison of different models on the CLEAN dataset,
-the TOAST models demonstrate marginal improvements across all aspects  compared to the competing models. 
-%This is because that most of questions in CLEAN dataset are description type (see Table 4). 
-Specifically, the $\text{TOAST}_{joint}$ model using $\text{RoBERTa}_{base}$ achieves the highest overall score of 4.34 (ranging from 1 to 5), representing a 0.56 score improvement over the TASE model.
-Similarly, the $\text{TOAST}_{joint}$ model using $\text{BERT}_{base}$ achieves an overall score of 4.3 which demonstrates a 0.46 score improvement  over the TASE model.
-At the span level, $\text{TOAST}_{joint}$ using $\text{RoBERTa}_{base}$ exhibit enhancements of 0.64, 0.52, and 0.54 scores of in terms of completeness, distinctness and correctness, respectively.
-Additionally, $\text{TOAST}_{joint}$ using  $\text{BERT}_{base}$ demonstrates improvements of 0.26, 0.2, and 0.38 scores in these respective aspects.
-
-\subsubsection{Case Studies}
-\label{sec:case}
-Next, we perform case studies to examine the impact of our proposed methods on answer extraction. 
-The case studies utilize running examples from the MSQA and CLEAN datasets, which are presented in \tableref{tab:msqa_case} and \tableref{tab:clean_case}, respectively. 
-In the context, the gold answer spans are annotated in blue color to facilitate identification.
-
-\begin{table}[width=\textwidth,cols=3,pos=h]
-	\small
-	\caption{The case studies from the MSQA dataset.}
-	\label{tab:msqa_case}
-	\begin{tabular}{p{21em}|c|cp{22em}}
-		\hline
-		\multicolumn{1}{c|}{Example} & Model & Extracted Answer \\ 
-		\hline
-		\multirow{5}{*}[2pt]{\begin{tabular}{@{}p{21em}@{}}
-				\textbf{Question}: what is the proximal attachment of the flexor carpi ulnaris in humans \\
-				\textbf{Context}: The flexor carpi ulnaris muscle (or FCU) is a muscle of the human forearm that acts to flex and adduct (medial deviation) the hand.
-The flexor carpi ulnaris muscle arises from two heads, the {\color{blue}humeral} and {\color{blue}ulnar} heads, which are connected by a tendinous arch beneath which the ulnar nerve and artery pass.
-\\
-				\textbf{Gold Answer}: 
-				[``{\color{blue}humeral}'', ``{\color{blue}ulnar}'']
-		\end{tabular}}
-		&SSE &  \begin{tabular}{p{22.5em}} \vskip -1mm 
-			[``{\color{blue} humeral} and {\color{blue} ulnar} , connected by a tendinous arch''] \vskip -1mm
-		\end{tabular} \\
-		\cline{2-3}
-		& TASE & \begin{tabular}{p{22.5em}} 
-			\vskip -1mm	
-			[``medial deviation'', ``the hand''] \vskip -1mm
-		\end{tabular} \\
-		\cline{2-3}
-		& LIQUID & \begin{tabular}{p{22.5em}} \vskip -1mm
-			[``flex'', ``medial deviation'', ``the hand'', ``tendinous''] \vskip -1mm
-		\end{tabular}  \\
-		\cline{2-3}
-		& $\text{TOAST}_{tag}$ & \begin{tabular}{p{22.5em}}  \vskip -1mm 
-			[``hand'', ``{\color{blue}humeral}'', ``{\color{blue}ulnar}'']  \vskip -1mm
-		\end{tabular} \\
-		\cline{2-3}
-		& $\text{TOAST}_{joint}$ & \begin{tabular}{p{22.5em}} \vskip -1mm
-			[``{\color{blue}humeral}'', ``{\color{blue}ulnar}''] \vskip -1mm
-		\end{tabular} \\
-		\cline{2-3}
-		\hline
-		\multirow{5}{*}[2pt]{\begin{tabular}{@{}p{21em}@{}}
-				\textbf{Question}: popular styles of music in the middle ages \\ 
-				\textbf{Context}: Medieval music consists of songs , instrumental pieces ...
-Medieval music was an era of Western music, including {\color{blue}liturgical music} (also known as sacred) used for the church, and {\color{blue} secular music}, non-religious music.
-Medieval music includes solely vocal music, such as {\color{blue} Gregorian chant} and {\color{blue} choral music} (music for a group of singers), solely instrumental music ...
-practice era , a period of shared music writing practices ...
-\\
-				\textbf{Gold Answer}: 
-				[``{\color{blue}liturgical music}'', ``{\color{blue}secular music}'', ``{\color{blue}Gregorian chant}'', ``{\color{blue}choral music}'']
-		\end{tabular}}
-		&SSE &  \begin{tabular}{p{22.5em}} \vskip -1mm 
-			[``{\color{blue} Gregorian chant} and {\color{blue} choral music}''] \vskip -1mm
-		\end{tabular} \\
-		\cline{2-3}
-		& TASE & \begin{tabular}{p{22.5em}} 
-			\vskip -1mm	
-			[``{\color{blue}secular music}'', ``{\color{blue}Gregorian chant}'', ``{\color{blue}choral music}'', ``Baroque'', ``Classical music'', ``Romantic music'']  
-			\vskip -1mm
-		\end{tabular} \\
-		\cline{2-3}
-		& LIQUID & \begin{tabular}{p{22.5em}} \vskip -1mm
-			[``Baroque'', ``Classical music'', ``Romantic''] \vskip -1mm
-		\end{tabular}  \\
-		\cline{2-3}
-		& $\text{TOAST}_{tag}$ & \begin{tabular}{p{22.5em}}  \vskip -1mm 
-			[``{\color{blue}liturgical music}'', ``{\color{blue}secular music}'', ``{\color{blue}Gregorian chant}'', ``{\color{blue}choral music}'']
-			\vskip -1mm
-		\end{tabular} \\
-		\cline{2-3}
-		& $\text{TOAST}_{joint}$ & \begin{tabular}{p{22.5em}} \vskip -1mm [``{\color{blue}liturgical music}'', ``{\color{blue}secular music}'', ``{\color{blue}Gregorian chant}'', ``{\color{blue}choral music}'']
-			\vskip -1mm
-		\end{tabular} \\
-		\cline{2-3}
-		\hline
-		\multirow{5}{*}[6pt]{\begin{tabular}{@{}p{21em}@{}}
-				\textbf{Question}: how long does it take for the milky way to rotate \\
-				\textbf{Context}: The galactic year, also known as a cosmic year, is the duration of time required for the Sun to orbit once around the center of the Milky Way Galaxy.
-Estimates of the length of one orbit range from 225 to 250 million terrestrial years.
-The Solar System is traveling at an average speed of 828,000 km / h (230 km / s) or 514,000 mph (143 mi / s) within its trajectory around the galactic center, a speed at which an object could circumnavigate the Earth 's equator in 2 minutes and 54 seconds; ...
-\\
-				\textbf{Gold Answer}: 
-				%				[``{\color{blue}galactic year}'', ``{\color{blue}cosmic year}''] 
-				Unanswerable \vskip 2mm
-		\end{tabular}}
-		&SSE &  \begin{tabular}{p{22.5em}} \vskip -1mm 
-			[``2 minutes and 54 seconds''] \vskip -1mm
-		\end{tabular} \\
-		\cline{2-3}
-		& TASE & \begin{tabular}{p{22.5em}} 
-			\vskip -1mm	
-			[``galactic year'', ``million'', ``years'', ``km / h'', ``514,000 mph'', ``2 minutes and 54 seconds''] \vskip -1mm
-		\end{tabular} \\
-		\cline{2-3}
-		& LIQUID & \begin{tabular}{p{22.5em}} \vskip -1mm
-			[``828,000 km / h'', ``514,000 mph (143 mi / s)'', ``2 minutes and 54 seconds''] \vskip -1mm
-		\end{tabular}  \\
-		\cline{2-3}
-		& $\text{TOAST}_{tag}$ & \begin{tabular}{p{22.5em}}  \vskip -1mm 
-			[``828,000 km / h'', ``514,000 mph (143 mi / s) '', ``2 minutes and 54 seconds'']  \vskip -1mm
-		\end{tabular} \\
-		\cline{2-3}
-		& $\text{TOAST}_{joint}$ & \begin{tabular}{p{22.5em}} \vskip -1mm
-			[``828,000 km / h'', ``514,000 mph (143 mi / s) '', ``2 minutes and 54 seconds''] \vskip -1mm
-		\end{tabular} \\
-		\cline{2-3}
-		\hline
-	\end{tabular}
-\end{table}
-
-\begin{table}[width=\textwidth,cols=4,pos=htp]	\caption{The case studies from the CLEAN dataset.}
-	\label{tab:clean_case}
-	\begin{tabular}{p{23em}|c|cp{20em}}
-		\hline
-		\multicolumn{1}{c|}{Example} & Model & Extracted Answer \\ 
-		\hline
-		\multirow{5}{*}[-2pt]{\begin{tabular}{@{}p{22em}@{}}
-				\textbf{Question}: 甘肃省哪些城市经济比较发达 \\ (Which cities in Gansu Province have relatively developed economies) \\
-				\vskip -1mm
-				\textbf{Context}: 论GDP人均，{\color{blue}嘉峪关}，{\color{blue}金昌} \\ \quad \quad \quad \quad ~论GDP总量{\color{blue}兰州} ，{\color{blue}庆阳} \\ (In terms of per capita GDP, {\color{blue}Jiayuguan} and {\color{blue}Jinchang}.
-In terms of total GDP, {\color{blue}Lanzhou} and {\color{blue}Qingyang}.) \\
-				\vskip -1mm
-				\textbf{Gold Answer}: 
-				[``{\color{blue}嘉峪关}'', ``{\color{blue}金昌}'', ``{\color{blue}兰州}'', ``{\color{blue}庆阳}'']  \vskip -1mm \quad \\
-		\end{tabular}}
-		&SSE &  \begin{tabular}{p{19em}} \vskip -1mm 
-			[``{\color{blue}嘉峪关}，{\color{blue}金昌}''] \vskip -1mm
-		\end{tabular} \\
-		\cline{2-3}
-		& TASE & \begin{tabular}{p{19em}} 
-			\vskip -1mm	
-			[``{\color{blue}兰州}''，``{\color{blue}庆阳}'']  \vskip -1mm
-		\end{tabular} \\
-		\cline{2-3}
-		&LIQUID &  \begin{tabular}{p{19em}} \vskip -1mm 
-			[``{\color{blue}嘉峪关}，{\color{blue}金昌}''] \vskip -1mm
-		\end{tabular} \\
-		\cline{2-3}
-		& $\text{TOAST}_{tag}$ & \begin{tabular}{p{19em}}  \vskip -1mm 
-			[``{\color{blue}嘉峪关}'', ``{\color{blue}金昌}'', ``{\color{blue}兰州}'', ``{\color{blue}庆阳}'']  \vskip -1mm
-		\end{tabular} \\
-		\cline{2-3}
-		& $\text{TOAST}_{joint}$ & \begin{tabular}{p{19em}} \vskip -1mm
-			[``{\color{blue}嘉峪关}'', ``{\color{blue}金昌}'', ``{\color{blue}兰州}'', ``{\color{blue}庆阳}''] \vskip -1mm
-		\end{tabular} \\
-		\cline{2-3}
-		\hline
-		\multirow{5}{*}[-2pt]{\begin{tabular}{@{}p{22em}@{}}
-				\vskip -4mm
-				\textbf{Question}: 细菌和古细菌有什么区别\\ (What are the differences between bacteria and archaea)  \\
-				\vskip -1mm
-				\textbf{Context}: 在细胞结构和代谢上，古菌在很多方面接近其它原核生物 ...
-{\color{blue}古菌}还具有一些其它特征。与大多数细菌不同，它们{\color{blue}只有一层细胞膜而缺少肽聚糖细胞壁}。而且，绝大多数{\color{blue}细菌和真核生物的细胞膜中的脂类主要由甘油酯组成}，而{\color{blue}古菌的膜脂由甘油醚构成} ...
-\\ (In terms of cellular structure and metabolism, ...
-{\color{blue}Archaea} also possess some other characteristics.
-Unlike most bacteria, they {\color{blue}only have a single layer of cell membrane and lack peptidogly can cell walls}.
-Additionally, while the cell membranes of most {\color{blue}bacteria and eukaryotes are predominantly composed of glycerol esters}, {\color{blue}the membrane lipids of archaea are composed of glycerol ethers}...) \\
-				\vskip -1mm
-				\textbf{Gold Answer}: 
-				[``{\color{blue}古菌}'', ``{\color{blue}只有一层细胞膜而缺少肽聚糖细胞壁}'', ``{\color{blue}细菌和真核生物的细胞膜中的脂类主要由甘油酯 组成}'', ``{\color{blue}古菌的膜脂由甘油醚构成}'']
-		\end{tabular}}
-		&SSE &  \begin{tabular}{p{19em}} \vskip -1mm 
-			[``在细胞结构和代谢上，古菌在很多方面接近其它原核生物 ...'']\vskip -0.1mm
-		\end{tabular} \\ 
-		\cline{2-3}
-		& TASE & \begin{tabular}{p{19em}} 
-			\vskip -0.1mm	
-			[``大多数细菌'', ``同'', ``它们'', ``{\color{blue}只有一层细胞膜而缺少肽聚糖细胞壁}'', ``绝大多数细菌和真核生物'', ``{\color{blue}细胞膜中}'', ``{\color{blue}脂类主要由甘油酯组成}，而{\color{blue}古菌} '', ``{\color{blue}膜脂由甘油醚构成}'']
-			\vskip -0.1mm
-		\end{tabular} \\
-		\cline{2-3}
-		&LIQUID &  \begin{tabular}{p{19em}} \vskip -0.5mm 
-			[``{\color{blue}只有一层细胞膜而缺少肽聚糖细胞壁}，{\color{blue}绝大多数细菌和真核生物的细胞膜中的脂类主要由甘油酯组成},{\color{blue}而古菌的膜脂由甘油醚构成}''] \vskip -0.1mm
-		\end{tabular} \\
-		\cline{2-3}
-		& $\text{TOAST}_{tag}$ & \begin{tabular}{p{19em}}  \vskip -0.5mm 
-			[``{\color{blue}只有一层细胞膜而缺少肽聚糖细胞壁}'', ``{\color{blue}细菌和真核生物的细胞膜中的脂类主要由甘油酯组成}'', ``{\color{blue}古菌的膜脂由甘油醚构成}'']
-			\vskip -0.1mm
-		\end{tabular} \\
-		\cline{2-3}
-		& $\text{TOAST}_{joint}$ & \begin{tabular}{p{19em}} \vskip -1mm [``{\color{blue}只有一层细胞膜而缺少肽聚糖细胞壁}'', ``{\color{blue}细菌和真核生物的细胞膜中的脂类主要由甘油酯组成}'', ``{\color{blue}古菌的膜脂由甘油醚构成}'']
-			\vskip -0.3mm
-		\end{tabular} \\
-		\cline{2-3}
-		\hline
-		\multirow{5}{*}[-2pt]{\begin{tabular}{@{}p{22em}@{}}
-				\vskip -1mm
-				\textbf{Question}: 宿州学院的特色专业是什么\\ (What are the characteristic majors of Suzhou University)  \\
-				\vskip -1mm
-				\textbf{Context}: {\color{blue}会计}或{\color{blue}英语}吧，西校区{\color{blue}人力资源管理}，{\color{blue}地理科学}不错\\ ({\color{blue}Accounting} or {\color{blue}English}, {\color{blue}human resource management} at West Campus, good in {\color{blue}geography science}) \\
-				\vskip -1mm
-				\textbf{Gold Answer}: 
-				[``{\color{blue}会计}'', ``{\color{blue}英语}'', ``{\color{blue}人力资源管理}'', ``{\color{blue}地理科学}'']
-		\end{tabular}}
-		&SSE &  \begin{tabular}{p{19em}} \vskip -1mm 
-			[``{\color{blue}会计}或{\color{blue}英语}''] \vskip -0.5mm
-		\end{tabular} \\
-		\cline{2-3}
-		& TASE & \begin{tabular}{p{19em}} 
-			\vskip -0.5mm	
-			[``{\color{blue}会计}或{\color{blue}英语}'', ``人'',``{\color{blue}管理}'' ,`` 地'',`` 科学'']
-			\vskip -0.01mm
-		\end{tabular} \\
-		\cline{2-3}
-		&LIQUID &  \begin{tabular}{p{19em}}
-			\vskip -1mm 
-			[``{\color{blue}会计}或{\color{blue}英语}''] \vskip -0.5mm
-		\end{tabular} \\
-		\cline{2-3}
-		& $\text{TOAST}_{tag}$ & \begin{tabular}{p{19em}}  \vskip -1mm 
-			[``{\color{blue}会计}'',``{\color{blue}英语}'', ``人'']
-			\vskip -0.5mm
-		\end{tabular} \\
-		\cline{2-3}
-		& $\text{TOAST}_{joint}$ & \begin{tabular}{p{19em}} \vskip -1mm [``{\color{blue}会计}'', ``人'']
-			\vskip -0.5mm
-		\end{tabular} \\
-		\cline{2-3}
-		\hline
-	\end{tabular}
-\end{table}
-
-In \tableref{tab:msqa_case}, the first example inquires about the proximal attachment of the flexor carpi ulnaris.
-TASE and LIQUID primarily focus on the flexion  and adduction functions of the flexor carpi ulnaris muscle.
-In constract, TOAST models accurately identify that the muscle originates from the humeral and ulnar heads, which are its true proximal attachments.
-The second example explores the prevalent music styles during the Middle Ages.
-TASE and LIQUID mistakenly categorize the style of composers (e.g.
-Baroque) as  music styles, whereas TOAST models correctly identify all popular music styles.
-These cases exemplify the effectiveness of TOAST in comprehending the query intention and semantics of the associated context. 
-The third example, which seeks to determine the duration of the Milky Way's rotation, presents a failure case for TOAST.
-The given context introduces the concept of a galactic year as a measure of time for Milky Way rotation.
-However, the provided information is insufficient to answer the question.
-Instead of refusing to answer, we observe that the TASE model extracts the concept of a "galactic year," albeit with multiple broken spans.
-Both LIQUID and TOAST models extract information related to the traveling speed of the Solar System and the time it takes to circumnavigate the Earth's equator at this speed, which pertain to the Solar System rather than the Milky Way.
-Thus, TOAST and other competing models may struggle to handle cases with intricate semantic relations.
-
-Likewise, the examples in \tableref{tab:clean_case} from the CLEAN dataset demonstrate similar trends.
-TOAST models excel in accurately and comprehensively extracting description answers from the given contexts.
-For instance, in the second example from \tableref{tab:clean_case}, the TASE model tends to fragment the description answer into multiple incomplete spans, whereas TOAST models capture the boundary information of the long description span, thus precisely extracting the entire answer span.
-The running examples from both datasets emphasize the effectiveness of the proposed model.
-
-%	\input{related}
 \section{Related Work}
 \label{sec:related}
-In this section, we briefly summarize previous works that are relevant to extractive reading comprehension (RC) datasets and various modeling approaches employed for extractive RC tasks.
-\subsection{Extractive RC Datasets}
-\label{sec:related_dataset}
-\subsubsection{Single-Span RC Datasets}
-Most existing RC datasets, such as SQuAD~\citep{rajpurkar2016squad}, SQuAD2.0~\citep{rajpurkar2018know}, SearchQA~\citep{DBLP:journals/corr/DunnSHGCC17}, HotpotQA~\citep{yang2018hotpotqa}, TriviaQA~\citep{DBLP:conf/acl/JoshiCWZ17} and QuAC~\citep{DBLP:conf/emnlp/ChoiHIYYCLZ18}, contain only single-span questions whose answers are limited to a single text span from the provided context, referred as single-span RC datasets.
-SQuAD consists of passages from Wikipedia as contexts and associated questions whose answers are spans from the passage.
-SQuAD 2.0 expands SQuAD by adding some questions that are designed to be unanswerable.
-HotpotQA dataset extends the answer context from single passage to multiple passages.
-Since the RC datasets like SQuAD or HotpotQA are built by having humans read a given context, write questions and choose a specific answer span, the annotators may tend to make use of words from the answer text which potentially makes  their questions easier to answer.
-To address this concern, one possible solution is to create datasets where questions are not specifically designed with a context in mind. 
-The TriviaQA dataset consists of questions authored by trivia enthusiasts, while the QuAC dataset prevents the annotators (who also serve as questioners) from seeing the full context.
-However, all of these RC datasets primarily focus on single-span questions, which does not align with the distribution of real-world user questions. 
-\subsubsection{Multi-Span RC Datasets}
+In this section, we briefly summarize previous works that are relevant to extractive reading comprehension
+(RC) datasets and various modeling approaches employed for extractive RC tasks.
+\subsection{Multi-Span RC Datasets}
 The complete answer to a real-world user question could consist of multiple text spans. 
@@
 
-The above datasets are all in English.
-The TyDi QA dataset~\citep{DBLP:journals/tacl/ClarkPNCGCK20} offers question-answer pairs in 11 typologically diverse languages, including Arabic, Bengali, Kiswahili, Russian and Thai.
-The various languages in the dataset bring up new challenges such as morphological variation and word segmentation.
-To address the scarcity of Arabic datasets for the RC task, the QRCD dataset~\citep{DBLP:journals/ipm/MalhasE22} provides valuable resources. 
-Additionally, the CMQA dataset~\citep{DBLP:conf/coling/JuWZZ0022} introduces a new annotate scheme that labels both fine-grained answers and conditions  as well as the hierarchical relations in-between.
-% requires models to extract  conditions and hierarchical relations for multi-span answers. 
-CMQA is the first public multi-span QA dataset in Chinese, 
-however it formulates a new task of conditional question answering.
-%However, the multi-span Chinese RC datasets 
-To ameliorate the situation of the lack of Chinese multi-span RC datasets, we propose a Chinese multi-span question answering dataset (CLEAN), which consists of multi-span questions in open domain and supports to cast RC as answer extraction task.
-
-%Dasigi et al. propose Quoref~\cite{DBLP:conf/emnlp/DasigiLMSG19}
-
-%\subsection{Neural-based RC Models}
 \subsection{Neural Models for RC}
-\label{sec:related_models}
 Research in reading comprehension grows rapidly, and many successful neural-based RC models have been proposed in this area. 
@@
 
-%	\input{conclusion}
-\section{Implications}
-Our main aim in this study is to address the problem of multi-span question answering, that has widespread implications for real-life applications such as virtual assistants.
-Although existing reading comprehension (RC) datasets and models have demonstrated effectiveness in answering factoid questions, they encounter difficulties when it comes to handling the complexities inherent in descriptive questions.
-
-We propose the TOAST framework, which is designed for the extraction of multi-span answers, and complement it with a newly created RC dataset named CLEAN that encompasses a significant number of descriptive questions.
-In \secref{sec:evaluation}, we demonstrate the effectiveness of the components integrated within TOAST.
-A key insight in the extraction of multi-span answers lies in the value placed on boundary knowledge, particularly through token-based neighboring transitions.
-To capture this information, we employ an auxiliary task that incorporates token-based transition knowledge, enabling us to jointly learn the sequence tagging task and the transition classification task.
-Additionally, we further demonstrate the usefulness of the joint decoding strategy in TOAST, which not only implicitly integrates neighboring transition knowledge but also explicitly combines predictions from the enhanced tagging model.
-
-\section{Conclusion}
-\label{sec:conclusion}
-In this paper, we propose a joint learning framework named TOAST, which specializes in token-based neighboring transitions to capture the boundary information of answer spans through adjacent word relations for multi-span question answering.
-Our approach extracts high-quality multi-span answers and is applicable to both alphabet languages like English and logographic languages like Chinese.
-Furthermore, we introduce an open-domain Chinese multi-span question answering dataset, named CLEAN, that incorporates crafted long answers as contexts.
-CLEAN effectively bridges the semantic gap by leveraging insights from public contributors, addressing the limitation of existing datasets.
-Results show that TOAST is more effective than a number of other strong baselines across three publicly available datasets.
-
-	\section*{Acknowledgements}
-	This research was supported by the Natural Science Foundation of Zhejiang Province, China (Grant No.
-LQ22F020027), Fundamental Research Funds of Zhejiang Sci-Tech University (Grant No.
-23232138-Y), Liaoning Provincial Natural Science Foundation of China (Grant No.
-2022-KF-21-01) and the Key Research and Development Program of Zhejiang Province, China (Grant No.
-2023C01041 and 2022C01079).
-
-	\bibliographystyle{cas-model2-names}
-	% 
-	\bibliography{refs}
-\end{document}
+\subsection{Interaction with LLMs}

### 2024-01-15 related.tex
dev

@@
+<<<<<<< HEAD
+
 \section{Related Work}
 \label{sec:related}
-In this section, we briefly summarize previous works that are relevant to extractive reading comprehension
-(RC) datasets and various modeling approaches employed for extractive RC tasks.
-\subsection{Multi-Span RC Datasets}
-The complete answer to a real-world user question could consist of multiple text spans. 
-Furthermore, a user question can even have multiple intents, where the answer to each intent is composed of one or more spans. 
-We refer to the datasets focus on such multi-span questions as multi-span RC datasets.
-Natural Question~\citep{DBLP:journals/tacl/KwiatkowskiPRCP19} and Quoref~\citep{DBLP:conf/emnlp/DasigiLMSG19} both contain multi-span questions. 
-The Natural Question dataset incorporates real anonymized queries to the Google search engine. 
-Quoref is used to validate models with the ability to resolve co-reference among entities. %, which is not for general capability validation of models.
-However, the proportion of multi-span answers in Natural Question and Quoref is relatively low, around 2\% and 10\% respectively. 
-The DROP~\citep{DBLP:conf/naacl/DuaWDSS019} dataset which consists of complex questions on history and football games, requires discrete reasoning over the content of contexts, including  co-reference resolution and arithmetic operations, such as addition, sorting and counting.
-Although the questions could be multi-span, the answer spans are almost exclusively semantically homogeneous and related to numeric values. 
-MASH-QA~\citep{DBLP:conf/aaai/PangLGXSC19} is a domain-specific dataset that extends the answer space to general text types in the healthcare domain.
-Recently, \cite{li2022multispanqa} propose the MultiSpanQA dataset, which consists of open-domain multi-span questions.
-The MultiSpanQA dataset is derived from Natural Question, whose questions are real queries issued to the Google search engine.
-Each question is associated with a context extracted from a retrieved Wikipedia page.  
-MultiSpanQA also has an expanded variant by introducing single-span and unanswerable questions, namely MultiSpanQA (expand).
+In this section, we briefly summarize previous work on how Large Language Models (LLMs) such as the GPT series can be utilized as sources of knowledge and content generators to enhance and enrich text data in various application scenarios.
+\subsection{Interaction with LLMs}
+Large Language Models (LLMs) are powerful natural language processing models in the field of deep learning, 
+characterized by their massive parameter scale and outstanding capabilities in understanding and generating natural language text. 
+Recent research has highlighted the extraction of relevant knowledge from LLMs, especially in domains lacking proper coverage in knowledge bases~\citep{fang2021leveraging}. 
+The application of large language models has expanded from the field of knowledge extraction to text data augmentation. 
+GPT3Mix~\citep{yoo2021gpt3mix} has proposed a method that utilizes large language models to generate new text samples, thereby enhancing the performance of machine learning models.
+AugGPT~\citep{dai2023auggpt} enhances natural language processing tasks in situations with limited data by interacting with ChatGPT to generate new textual data, further advancing text data augmentation.
+In the realm of common sense reasoning,~\citep{liu2021generated,liu2022rainier} suggests that performance in common sense question answering can be effectively improved through prompt generation and reinforcement learning.
+Additionally, LLMs excel in generating contextual information, demonstrating the ability to create rich, 
+relevant contexts based on given inputs, as validated in studies such as those by~\citep{yu2022generate}. 
+The collaborative effect of iterative retrieval and generation further boosts the performance of LLMs~\citep{shao2023enhancing}. 
+However, a limitation in current research is the insufficient interpretation of entities.Our study addresses this gap by interacting with ChatGPT, 
+leveraging its powerful generative capabilities to design a series of prompt templates for obtaining more comprehensive entity interpretations.
+
+In the research domain of question-answering systems, ~\citep{huang2023enhancing} improves the context learning ability of models in multi-span question-answering tasks through the introduction of answer feedback mechanisms.
+Comparisons between ChatGPT and traditional knowledge base question-answering models explore its potential as an alternative to traditional KBQA tasks~\citep{tan2023can}, 
+investigating differences in providing single versus multiple answers in various contexts within reading comprehension tasks~\citep{zhang2023many}. 
+Considering the limitations of LLMs in handling factual information, ~\citep{ren2023investigating} utilizes retrieval-enhanced techniques to enhance the model's understanding and response capabilities to fact-based queries.
+Finally, ~\citep{wei2023zero} showcase a new approach to zero-shot information extraction through interaction with ChatGPT, 
+while~\citep{liu2023once} explore the enhancement of content-based recommendation systems by combining open-source and closed-source language models. 
+These studies not only demonstrate the innovation and advantages of LLMs across various domains but also provide profound insights into future research directions. 
+However, the response structures generated by LLMs in these studies are not standardized. 
+To address this, our prompt template design aims to ensure that the responses from ChatGPT are easily parsed and processed, enhancing the structured nature of the responses. 
+Additionally, dealing with ambiguity and ambiguity is another challenge. 
+Through the integration of LLM knowledge sources, our framework aims to provide clearer, more detailed information to better address semantic complexities.
 

### 2024-01-15 related.tex
minor
Add files via upload

@@
 ADRAV~\citep{hu2023biomedical} proposed a dynamic routing and answer voting method to further make full use of the hidden layer knowledge of pre-trained models.
-More recently, LIQUID~\citep{lee2023liquid} was introduced to  automatically generate list-style QA pairs from unlabeled corpora.
-LIQUID extracted named entities from the summarized text as candidate answers and incorporated synthetic data in the tagging model.
-These methods harness the extensive factual knowledge embedded in powerful contextualized encoders (PrLMs) or synthesized data that resolves around named entities. 
-As a result, they have demonstrated promising performance in extracting  multi-span answers, particularly for factoid questions where the answers correspond entities.
-%Benefiting from the rich factual knowledge implied in the powerful contextualized encoders (PrLMs) or synthesized data centered around name entities, these methods have achieved promising performance on multi-span answer extraction, especially for factoid questions where the answers are entities.
-%These methods have been achieved promising performance on multi-span answer extraction, especially for factoid questions whose answers are entities, benefiting from the rich factoid knowledge implied in the powerful context encoder like PrLMs.
-However, these methods do not take into account the information of span boundaries in terms of the questions, and thus have very limited capabilities of precisely drawing a description answer. 
-%However, for these methodswhich are implied in the powerful context encoder like PrLMs, they are failed to care span boundaries .
-Compared to these approaches, TOAST incorporates the semantic and syntactic information of span boundaries by explicitly modeling the implicit neighboring transitions in-between the adjacent tokens or words, which benefits the span boundary identification.
+
+More recently, SpanQualifier improves Multi-Span Reading Comprehension (MSRC) by explicitly representing spans and modeling interactions within and between them.
+Iterative Extractor introduces a classification method for MSRC instances, prompting exploration of strategies to maximize different paradigms' advantages in capturing key information and modeling relationships between questions and context.
+While these methods leverage powerful context encoders (PrLMs) with good multi-span answer extraction performance, they fall short in fully harnessing external knowledge, limiting their text comprehension abilities.
+LIQUID was designed to automatically generate list-style QA pairs from unlabeled corpora, using named entities from summarized text as candidate answers and incorporating synthetic data in the tagging model.
+However, its focus on list QA data narrows the scope of knowledge and lacks specificity, reducing efficiency.
+In contrast, AUG significantly advances the field by efficiently enhancing model training.
+It achieves this by leveraging interactions with a large language model to acquire contextually relevant knowledge directly tied to the data, which can be seamlessly incorporated into the finetuning.
 

### 2024-01-16 related.tex
Add files via upload

@@
 
-More recently, SpanQualifier improves Multi-Span Reading Comprehension (MSRC) by explicitly representing spans and modeling interactions within and between them.
-Iterative Extractor introduces a classification method for MSRC instances, prompting exploration of strategies to maximize different paradigms' advantages in capturing key information and modeling relationships between questions and context.
+More recently, SpanQualifier~\cite{huang2023qualifier} improves Multi-Span Reading Comprehension (MSRC) by explicitly representing spans and modeling interactions within and between them.
+Iterative Extractor~\cite{zhang2023many} introduces a classification method for MSRC instances, prompting exploration of strategies to maximize different paradigms' advantages in capturing key information and modeling relationships between questions and context.
 While these methods leverage powerful context encoders (PrLMs) with good multi-span answer extraction performance, they fall short in fully harnessing external knowledge, limiting their text comprehension abilities.
-LIQUID was designed to automatically generate list-style QA pairs from unlabeled corpora, using named entities from summarized text as candidate answers and incorporating synthetic data in the tagging model.
+LIQUID~\cite{lee2023liquid} was designed to automatically generate list-style QA pairs from unlabeled corpora, using named entities from summarized text as candidate answers and incorporating synthetic data in the tagging model.
 However, its focus on list QA data narrows the scope of knowledge and lacks specificity, reducing efficiency.

### 2024-01-16 related.tex
提交本地related_work rc修改
dev

@@
 \subsection{Interaction with LLMs}
-Large Language Models (LLMs) are powerful natural language processing models in the field of deep learning, 
-characterized by their massive parameter scale and outstanding capabilities in understanding and generating natural language text. 
-Recent research has highlighted the extraction of relevant knowledge from LLMs, especially in domains lacking proper coverage in knowledge bases~\citep{fang2021leveraging}. 
-The application of large language models has expanded from the field of knowledge extraction to text data augmentation. 
-GPT3Mix~\citep{yoo2021gpt3mix} has proposed a method that utilizes large language models to generate new text samples, thereby enhancing the performance of machine learning models.
-AugGPT~\citep{dai2023auggpt} enhances natural language processing tasks in situations with limited data by interacting with ChatGPT to generate new textual data, further advancing text data augmentation.
-In the realm of common sense reasoning,~\citep{liu2021generated,liu2022rainier} suggests that performance in common sense question answering can be effectively improved through prompt generation and reinforcement learning.
-Additionally, LLMs excel in generating contextual information, demonstrating the ability to create rich, 
-relevant contexts based on given inputs, as validated in studies such as those by~\citep{yu2022generate}. 
-The collaborative effect of iterative retrieval and generation further boosts the performance of LLMs~\citep{shao2023enhancing}. 
-However, a limitation in current research is the insufficient interpretation of entities.Our study addresses this gap by interacting with ChatGPT, 
-leveraging its powerful generative capabilities to design a series of prompt templates for obtaining more comprehensive entity interpretations.
+Recent research emphasizes the significance of extracting knowledge from Large Language Models (LLMs) in domains characterized by limited knowledge base coverage~\citep{fang2021leveraging}.
+GPT3Mix~\citep{yoo2021gpt3mix} extends the utility of LLMs to text data augmentation, thereby elevating the performance of machine learning models. 
+AugGPT~\citep{dai2023auggpt} further contributes to natural language processing tasks in scenarios with constrained data by generating new textual data through interactions with ChatGPT.
 
-In the research domain of question-answering systems, ~\citep{huang2023enhancing} improves the context learning ability of models in multi-span question-answering tasks through the introduction of answer feedback mechanisms.
-Comparisons between ChatGPT and traditional knowledge base question-answering models explore its potential as an alternative to traditional KBQA tasks~\citep{tan2023can}, 
-investigating differences in providing single versus multiple answers in various contexts within reading comprehension tasks~\citep{zhang2023many}. 
-Considering the limitations of LLMs in handling factual information, ~\citep{ren2023investigating} utilizes retrieval-enhanced techniques to enhance the model's understanding and response capabilities to fact-based queries.
-Finally, ~\citep{wei2023zero} showcase a new approach to zero-shot information extraction through interaction with ChatGPT, 
-while~\citep{liu2023once} explore the enhancement of content-based recommendation systems by combining open-source and closed-source language models. 
-These studies not only demonstrate the innovation and advantages of LLMs across various domains but also provide profound insights into future research directions. 
-However, the response structures generated by LLMs in these studies are not standardized. 
-To address this, our prompt template design aims to ensure that the responses from ChatGPT are easily parsed and processed, enhancing the structured nature of the responses. 
-Additionally, dealing with ambiguity and ambiguity is another challenge. 
-Through the integration of LLM knowledge sources, our framework aims to provide clearer, more detailed information to better address semantic complexities.
+In the realm of common-sense reasoning, the effectiveness of prompt generation and reinforcement learning has been demonstrated in enhancing question-answering performance ~\citep{liu2021generated,liu2022rainier}.
+LLMs excel in the generation of contextual information ~\citep{yu2022generate}, 
+and the collaborative impact of iterative retrieval and generation amplifies overall LLM performance~\citep{shao2023enhancing}.
+
+Within question-answering systems, ~\citep{huang2023enhancing} improve model context learning in multi-span tasks through answer feedback mechanisms. 
+Comparative analyses between ChatGPT and traditional knowledge base question-answering models explore its potential as an alternative~\citep{tan2023can}. 
+In addressing LLM limitations in handling factual information, ~\citep{ren2023investigating} employ retrieval-enhanced techniques to enhance the model's understanding of fact-based queries.
+
+~\citep{wei2023zero} showcase zero-shot information extraction through ChatGPT interaction, 
+while~\citep{wei2023zero} explore enhancing content-based recommendation systems by combining open-source and closed-source language models. 
+Collectively, these studies highlight LLM innovation across diverse domains, offering valuable insights for future research.
+
+However, challenges persist, including non-standardized response structures and ambiguity. 
+Our research focuses on designing a set of templates for interacting with ChatGPT, encompassing entity interpretation, entity relationship analysis, rewriting, and summary information for each task. 
+Additionally, we introduce a knowledge injection method to directly incorporate knowledge generated by large models into training texts, thereby enhancing task performance. 
+This approach aims to provide a structured and comprehensive framework for leveraging LLMs in various applications.
 

### 2024-01-16 related.tex
修改related work

@@
-<<<<<<< HEAD
-
 \section{Related Work}
 \label{sec:related}
-In this section, we briefly summarize previous work on how Large Language Models (LLMs) such as the GPT series can be utilized as sources of knowledge and content generators to enhance and enrich text data in various application scenarios.
+This section briefly covers past research on employing Large Language Models (LLMs) like GPT for knowledge enhancement in diverse applications, emphasizing different approaches in extractive Reading Comprehension (RC) tasks.
+
 \subsection{Interaction with LLMs}
@@
 
-More recently, SpanQualifier~\cite{huang2023qualifier} improves Multi-Span Reading Comprehension (MSRC) by explicitly representing spans and modeling interactions within and between them.
-Iterative Extractor~\cite{zhang2023many} introduces a classification method for MSRC instances, prompting exploration of strategies to maximize different paradigms' advantages in capturing key information and modeling relationships between questions and context.
+More recently, SpanQualifier~\citep{huang2023qualifier} improves Multi-Span Reading Comprehension (MSRC) by explicitly representing spans and modeling interactions within and between them.
+Iterative Extractor~\citep{zhang2023many} introduces a classification method for MSRC instances, prompting exploration of strategies to maximize different paradigms' advantages in capturing key information and modeling relationships between questions and context.
 While these methods leverage powerful context encoders (PrLMs) with good multi-span answer extraction performance, they fall short in fully harnessing external knowledge, limiting their text comprehension abilities.
-LIQUID~\cite{lee2023liquid} was designed to automatically generate list-style QA pairs from unlabeled corpora, using named entities from summarized text as candidate answers and incorporating synthetic data in the tagging model.
+LIQUID~\citep{lee2023liquid} was designed to automatically generate list-style QA pairs from unlabeled corpora, using named entities from summarized text as candidate answers and incorporating synthetic data in the tagging model.
 However, its focus on list QA data narrows the scope of knowledge and lacks specificity, reducing efficiency.
@@
 It achieves this by leveraging interactions with a large language model to acquire contextually relevant knowledge directly tied to the data, which can be seamlessly incorporated into the finetuning.
-
-\subsection{Interaction with LLMs}

### 2024-03-21 experiments.tex
add metrics

@@
 		$\text{AUG}_{ereec}$ & 62.90  & 61.02 & 64.89 & 76.72 & 78.56 & 74.97 \\
-		Bagging & 64.44 & 61.63 & 67.50 & 79.5 & 80.49 & 78.57 \\
+		$\text{Bagging}_{eeerc}$ & 63.63  & 61.53 & 65.88 & 78.24 & 80.00 & 76.56 \\
+		$\text{Bagging}_{eeerc+liquid}$ & 64.44 & 61.63 & 67.50 & 79.5 & 80.49 & 78.57 \\
 		\bottomrule
@@
 		$\text{AUG}_{ereec}$ & 70.44 & 67.83 & 73.26 & 82.80 & 82.45 & 83.15 \\
-		Bagging & 70.86 & 69.03 & 72.79 & 84.82 & 85.53 & 84.12 \\
+		$\text{Bagging}_{eeerc}$ & 70.48  & 69.11 & 71.90 & 84.28 & 85.61 & 83.00 \\
+		$\text{Bagging}_{eeerc+liquid}$ & 70.86 & 69.03 & 72.79 & 84.82 & 85.53 & 84.12 \\
 		\bottomrule
@@
 
-\begin{table*}[width=\textwidth,cols=9,pos=h]  % 
-	\caption{The statistics of answers span predicted by $\text{AUG}_{eree}$ and baselines} 
-	\label{tab:answer_counts}
-	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lccccccc}
+\begin{table}[htbp]
+	\caption{The statistics of answers span predicted by $\text{AUG}{eree}$, $\text{AUG}{ereec}$ and baselines}
+	\label{tab:answer_counts_vertical}
+	\centering
+	\begin{tabular}{lcc}
 		\toprule
-		\multirow{2}{*}{\textbf{ }} & \multicolumn{3}{c}{$\text{BERT}_{base}$} & \multicolumn{3}{c}{$\text{RoBERTa}_{base}$}  \\
-		\cline{2-7} 
-		\addlinespace
-		& TASE\((\%)\) & LIQUID\((\%)\) & $\text{AUG}_{eree}$\((\%)\) & TASE\((\%)\) & LIQUID\((\%)\) & $\text{AUG}_{eree}$\((\%)\) \\
+		\textbf{Category} & \textbf{BERT} & \textbf{RoBERTa} \\
 		\midrule
-		empty predictions counts   & 0.0245 & 0.0214 & \textbf{0.0643} & 0.0061 & 0.0153 & \textbf{0.0291} \\ 
-		non-empty Overlap f1  & 0.7964 & 0.7909 & \textbf{0.7976} & 0.8404 & 0.8357 & \textbf{0.8414} \\
+		\multicolumn{3}{l}{\textbf{TASE}} \\
+		\hspace{5mm} empty preds & 2.45 & 0.61 \\
+		\hspace{5mm} non-empty pmf1 & 79.64 & 84.04 \\
+		\multicolumn{3}{l}{\textbf{LIQUID)}} \\
+		\hspace{5mm} empty preds & 2.14 & 1.53 \\
+		\hspace{5mm} non-empty pmf1 & 79.09 & 83.57 \\
+		\multicolumn{3}{l}{$\textbf{AUG}{eree}$ } \\
+		\hspace{5mm} empty preds & \textbf{6.43} & \textbf{2.91} \\
+		\hspace{5mm} non-empty pmf1 & \textbf{79.76} & \textbf{84.14} \\
+		\multicolumn{3}{l}{$\textbf{AUG}{ereec}$ } \\
+		\hspace{5mm} empty preds & \textbf{7.96} & \textbf{3.22} \\
+		\hspace{5mm} non-empty pmf1 & \textbf{80.20} & \textbf{83.78} \\
 		\bottomrule
-	\end{tabular*}
-	%	\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
-\end{table*}
+	\end{tabular}
+\end{table}
 
@@
 		& $\text{AUG}_{ereec}$ & 40.63 & 38.30 & 43.27 & 64.25 & 71.15 & 58.57 \\
-		& Bagging & 39.91 & 36.69 & 43.75 & 66.70 & 73.68 & 60.93 \\
+		& $\text{Bagging}_{eeerc}$ & 39.19  & 36.86 & 41.83 & 64.46 & 75.12 & 56.45 \\
+		& $\text{Bagging}_{eeerc+liquid}$  & 39.91 & 36.69 & 43.75 & 66.70 & 73.68 & 60.93 \\
 		\midrule
@@
 		& $\text{AUG}_{ereec}$ & 36.71 & 37.25 & 36.19 & 57.09 & 69.04 & 48.67 \\
-		& Bagging & 35.94 & 34.82 & 37.14 & 60.73 & 71.15 & 52.97 \\
+		& $\text{Bagging}_{eeerc}$ & 35.58 & 35.92 & 35.24 & 58.62  & 68.09 & 51.46 \\
+		& $\text{Bagging}_{eeerc+liquid}$  & 35.94 & 34.82 & 37.14 & 60.73 & 71.15 & 52.97 \\
 		\midrule
@@
 		& $\text{AUG}_{ereec}$ & 67.54 & 65.60 & 69.59 & 79.49 & 80.16 & 78.83 \\
-		& Bagging & 69.65 & 66.94 & 72.59 & 82.31 & 82.07 & 82.55 \\
+		& $\text{Bagging}_{eeerc}$ & 68.68  & 66.49 & 71.03 & 81.11 & 81.39 & 80.83 \\
+		& $\text{Bagging}_{eeerc+liquid}$ & 69.65 & 66.94 & 72.59 & 82.31 & 82.07 & 82.55 \\
 		\bottomrule
@@
 		& $\text{AUG}_{ereec}$ & 49.24 & 44.71 & 54.81 & 71.87 & 73.03 & 70.74 \\
-		& Bagging & 47.70 & 43.78 & 52.40 & 77.43 & 80.63 & 74.47 \\
+		& $\text{Bagging}_{eeerc}$ & 51.54 & 47.56 & 56.25 & 78.20 & 80.04 & 76.44 \\
+		& $\text{Bagging}_{eeerc+liquid}$ & 47.70 & 43.78 & 52.40 & 77.43 & 80.63 & 74.47 \\
 		\midrule
@@
 		& $\text{AUG}_{ereec}$ & 45.58 & 44.55 & 46.67 & 65.86 & 73.19 & 59.87 \\
-		& Bagging & 44.65 & 43.64 & 45.71 & 70.11 & 78.49 & 63.35 \\
+		& $\text{Bagging}_{eeerc}$ & 43.32 & 41.96 & 44.76 & 68.57 & 76.54 & 62.11 \\
+		& $\text{Bagging}_{eeerc+liquid}$ & 44.65 & 43.64 & 45.71 & 70.11 & 78.49 & 63.35 \\
 		\midrule
@@
 		& $\text{AUG}_{ereec}$ & 75.04 & 72.81 & 77.41 & 85.37 & 84.46 & 86.29 \\
-		& Bagging & 75.85 & 74.52 & 77.22 & 86.73 & 86.73 & 86.74 \\
+		& $\text{Bagging}_{eeerc}$ & 74.97 & 74.23 & 75.72 & 86.14 & 87.07 & 87.06 \\
+		&$\text{Bagging}_{eeerc+liquid}$ & 75.85 & 74.52 & 77.22 & 86.73 & 86.73 & 86.74 \\
 		\bottomrule

### 2024-03-24 method.tex
update section 3.1 (method-framework)

@@
-\section{Our Approach}
-
+\section{Approach}
+\subsection{our framework}
 \begin{figure*}[h]
@@
 
-%\unskip
-Existing extractive multi-span question answering models exhibit subpar performance in handling ambiguous words, complex proper nouns (such as film and song titles), numerical values, and long descriptive answers.
-The main reasons for these shortcomings can be categorized into three aspects:
+ Given a question $Q_i \in Q = \{Q_1,...,Q_n\}$ and a context $C_i \in C = \{c_0,...,c_n\}$, where $C_i$ contains m tokens $c_0,..,c_m$, the objective of multi-span question answering is to identify a set of answer spans $A_i = \{a_0,...,a_s\}$ within the context.
+Here, each answer span $a_j \in A_i$ is represented as $a_j = c_{s_l},...,c_{e_l}$, where $s_l$ and $e_l$ denote the start and end positions of the l-th answer span, respectively.
+ Following the observation of~\cite{li2022multispanqa}, We adopt the BIO tagging scheme to mark answer spans in the context where words are tagged as either part of the answer(\textbf{B}egin, \textbf{I}nside) or not (\textbf{O}ther).
+Formally, BIO tagging scheme is represented by a tag set $\tau = \{B, I, O\}$.
 
-\textbf{Ambiguous Words}: The real world is replete with words that have a single form but multiple meanings, which heavily depend on the context.
-For instance, the word ``Cameron" could refer to a famous director or a former British Prime Minister, depending on the context.
-The specific meanings of such words often appear infrequently in training corpora, making them difficult to learn.
+ Intuitively, large language models (LLMs) can serve as supplementary sources of external knowledge, compensating for the restricted semantic comprehension and limited information perception inherent in pre-trained language models).
+ We then propose a novel \textbf{G}enerative \textbf{I}nformation \textbf{A}ugme\textbf{NT}ation framework (GIANT) for multi-span question answering.
+ GIANT employs a plug-and-play strategy to integrate the knowledge from large language models into the input layer of tagging models, built upon pre-trained language models.
 
-\textbf{Numerical Values}: In contrast to ambiguous words, numerical values have a single meaning but can be represented in various forms.
-For example, "22.5 billion years" can also be expressed as "cosmic years".
+ The overview of GIANT is depicted as \figref{fig:overview}.
+ This process comprises the following steps:
+ \textbf{1)Prompting}: constructing instruction templates to leverage language models for generating diversified data, involving entity elucidation, entity relationships, content continuation, and summarization.
+ \textbf{2)Generating}: the large language model generating new knowledge based on the designed prompts.
+ \textbf{3)Updating}: filtering the generated data, and combine it with metadata in different forms.
+ \textbf{4)Training}: employing the knowledge-enhanced data to train a tagging model.
 
-\textbf{Multi-span Answers}: In extractive multi-span question answering tasks, the model needs to grasp the overall relationship of multi-span answers in the context, such as parallelism and progression.These challenges require the model to possess a high level of comprehensive understanding ability and knowledge about language and the world.
+ Consider $Gen(\cdot)$ as a generative large language model, and let $Inj(\cdot)$ function as a mapping that takes the generated content $K_i$ and context $C_i$, producing the augmented context $\tilde{C_i}$.
+$P(\cdot)$ represents a mapping of the context $C$ onto instantiated instructions, while $Tag(\cdot)$ serves as a QA model, and $Filter(\cdot)$ denotes the sieving operation.
+ With these definitions, GIANT can be formulated as follows:
+ \begin{align*}
+ 	K_i &= Gen(C_i,P(C_i)) \tag{1}\\
+ 	\tilde{C_i} &= Inj(K_i,C_i) \tag{2}\\
+ 	A_i &= Tag(Q_i,~Filter(\tilde{C_i})) \tag{3}
+ \end{align*}
 
-Leveraging large language models to parse question-answering data and inject auxiliary knowledge into the model can promote the integration of the model's latent world knowledge and specific domain knowledge in the paragraph, thereby enhancing the model's performance.
-Thus, we use GPT-3.5-turbo to generate entity annotations, entity association analysis, and content continuation for each question-answering paragraph as auxiliary information for the model:
+ In the following section, we will explore how GIANT utilizes a large language model to generate knowledge.
+Subsequently, we will delve into the methods employed by GIANT to filter these knowledge, amalgamate them into meta-context, and orchestrate ensemble strategies to leverage these knowledge effectively.
 
-\textbf{Context Supplementary}: By inserting explanations of entities in the form of annotations after the main entities or concept words in the question and paragraph, this method helps the model capture the actual meaning of ambiguous words in specific contexts.
-It provides direct information prompts for low-frequency meanings or low-frequency words, achieving entity or concept alignment in the question-answering system.
-
-\textbf{Context Enrichment}: By integrating entity association analysis and content continuation with the original question-answering text to form new paragraphs based on knowledge enhancement, this method captures the inherent associations between words or entity concepts with the same meaning but different forms.
-On one hand, it parses the logical relationships between other entities using entity relationship analysis.
-On the other hand, it extends the original paragraph information using content continuation, introducing more external knowledge while helping the model understand the overall content direction of the paragraph, thereby enhancing the model's comprehension ability.
-
-Overall,we design an automated knowledge enhancement method for multi-span question answering tasks, which interacts with large language models based on templates.
-This method is applicable to all question answering models or frameworks.
-It is universally applicable to any other downstream tasks that contain paragraph data, without the need for any complex calculations.
-In the following sections, we will provide a detailed introduction to each specific module of this process.
-
-\subsection{Construction of Prompt Template}
+\textcolor{red}{提示的模板放在哪里描述比较好？}
 \label{sec:prompt_construction}
@@
 
-The quality and format of the content produced by LLMs depends greatly on the prompts.
-Hence, it is necessary to clarify the format and content requirements of the outputs in advance, and to refine the templates that meet the expectations through extensive evaluation.
-For entity relationship parsing and textual continuation, it would be better to ensured that the the output is a natural paragraph, to facilitate the automatic splicing of the enriched knowledge with the initial paragraphs,which is consistent with encoder's natural input format.
-Regarding knowledge of entity explanation, the inserted knowledge fusion method requires a parsable and structured outputs for automatic recognition and segmentation of entities and their explanations in post-processing, as well as inserting explanation behind the description of matched entity in initial context.
+\subsection{LLMs as Knowledge Source}
+ GIANT employs a large language model to generate augmented data from multiple perspectives, including named entity elucidation, entity relations, content summarization, and content continuation.
+ The perspectives of named entity elucidation and entity relations provide factual knowledge, with GIANT forming knowledge cues for the model by jointly injecting them into metadata. 
+ Summarization acts as a mechanism for information filtering, sieving and retaining entity interpretations to ensure augmentation efficiency. 
+ Content continuation introduces relevant external knowledge by extending contextual content.
 
-Concretely, by clearly specifying the form and requirements in the prompts, especially for entity relationship parsing and contextual continuation, which need to be formulated in the form of natural statements, the targeted enhanced knowledge can be obtained more easily.
-Furthermore, to obtain well-structured results for complex model interactions, like entity explanations, we utilize a set of corresponding hint templates to construct the process, which has proven to be useful for interactions that require semi-structured answers through verification.
+\subsubsection{LLMs as Named Entity Elucidator}
 
-Eventually, the template is piloted to clarify any ambiguous requirements in the template to confirm an accurate understanding of the LLMs (e.g., adding at the end of the prompt, ``Please return the answer in the following form, being careful not to repeat it: \textbackslash n\textbackslash nA is .....")  In addition, to avoid omission or confusion of requirements due to the length of the prompt text, specific principles should be reiterate in a separate paragraph.
-
-\subsection{Information Injection}
-
-To incorporate enhanced knowledge into the original data (comprising questions and paragraphs) pertaining to entity interpretation, a methodology involving the insertion of explanations is employed.
-Specifically, the process begins with the automated script parsing of entity interpretation data.
-This script, on one hand, utilizes regular expressions to analyze the structure of the majority of sentences, while on the other hand, for a limited subset of sentences that deviate from the template specifications, employs Spacy's Semantic Dependency Analysis model to identify entities and their corresponding interpretations.
-
-Upon obtaining the ``Entity-Entity Interpretation" knowledge base for each question-and-answer data, a subsequent scan of the original context is conducted.
-For each entity that exists in the dataset's library of entities and their explanations, the corresponding explanation is inserted immediately following the entity, enclosed within parentheses.
-This meticulous approach ensures that the augmented text, enriched with knowledge, retains its natural sentence or paragraph flow.
-For instance, a resulting sentence might appear as follows: ``How long does it take for the Milky Way (Milky Way: The galaxy that contains our Solar System and is home to billions of stars.) to rotate?"
+  The knowledge of named entity elucidation serves as a direct aid to the model in comprehending infrequent lexical items within its pre-training corpus, context-specific terminologies in fine-tuning data, and ambiguous conceptual nuances in real world.
+  Meanwhile, the inherent robustness of large language models, owing to their sophisticated language representation capabilities and vast training corpora, facilitates the provision of more precise and comprehensive entity delineations.
+  Therefore, GIANT utilizes large language models to generate entity definitions for each question-answer pair, employing a combined approach of regular expressions and semantic dependency analysis models (Spacy) to parse the generated text and then constructs a branch-oriented "entity-elucidation" knowledge base.
+  Ultimately, the obtained knowledge base is used to retrieve entity elucidations and insert them behind entities in the original context, enriching the original textual content.
 
@@
 \end{figure*}
-
-For the incorporation of enhanced knowledge related to entity relationship analysis and content continuation, a method of random slicing and concatenation based on length ratios is employed to infuse the augmented knowledge into the original paragraphs.
-Initially, the ratio of the average length of the augmented knowledge text to that of the original paragraph is calculated.
-Subsequently, at the model's input layer, the original input data is segmented into text fragments of length of \textit{512 * average original length / (average original length + average augmented text length)}, and the augmented text is also segmented into text fragments of length of  \textit{512 * average augmented text length / (average original length + average augmented text length)}.
-Then, random selections of augmented text fragments are made and concatenated into the middle of each original text fragment.
-Finally, this concatenated longer text is fed into the model in a sliding manner to ensure comprehensive interaction between the original data and the augmented data at lower layers of the model, as illustrated in Figure~\ref{fig:random_concatenate}.
 

### 2024-03-24 method.tex
update 3.2.1 llms as named entity elucidator

@@
 
- Given a question $Q_i \in Q = \{Q_1,...,Q_n\}$ and a context $C_i \in C = \{c_0,...,c_n\}$, where $C_i$ contains m tokens $c_0,..,c_m$, the objective of multi-span question answering is to identify a set of answer spans $A_i = \{a_0,...,a_s\}$ within the context.
+ Given a question $Q_i \in Q = \{Q_1,...,Q_n\}$ and a context $C_i \in C = \{C_0,...,C_n\}$, where $C_i$ contains m tokens $c_0,..,c_m$, the objective of multi-span question answering is to identify a set of answer spans $A_i = \{a_0,...,a_s\}$ within the context.
 Here, each answer span $a_j \in A_i$ is represented as $a_j = c_{s_l},...,c_{e_l}$, where $s_l$ and $e_l$ denote the start and end positions of the l-th answer span, respectively.
@@
 \subsection{LLMs as Knowledge Source}
- GIANT employs a large language model to generate augmented data from multiple perspectives, including named entity elucidation, entity relations, content summarization, and content continuation.
- The perspectives of named entity elucidation and entity relations provide factual knowledge, with GIANT forming knowledge cues for the model by jointly injecting them into metadata. 
- Summarization acts as a mechanism for information filtering, sieving and retaining entity interpretations to ensure augmentation efficiency. 
+ GIANT leverages a large language model as an external knowledge source, utilizing it to generate augmented data $K_i = \{E_i, S_i, R_i, F_i\}$ from multiple perspectives.
+Here, $E_i$ represents named entity elucidation, $R_i$ denotes entity relations, $S_i$ pertains to content swdsummarization, and $F_i$ encompasses content continuation.
+
+ Within these knowledge perspectives, named entity elucidation and entity relations provide factual knowledge, with GIANT synthesizing knowledge cues for the model by jointly injecting them into metadata.
+ Summarization acts as a mechanism for information filtering, sieving and retaining entity interpretations, thereby ensuring augmentation efficiency. 
  Content continuation introduces relevant external knowledge by extending contextual content.
@@
 \subsubsection{LLMs as Named Entity Elucidator}
+  The resolution of multi-span questions usually entails identifying named entities.
+This intricate task can be greatly improved by tapping into the specialized knowledge of named entities.
+This expertise directly aids the model in comprehending rare lexical items within its pre-training corpus and adapting to context-specific terminologies during fine-tuning.
 
-  The knowledge of named entity elucidation serves as a direct aid to the model in comprehending infrequent lexical items within its pre-training corpus, context-specific terminologies in fine-tuning data, and ambiguous conceptual nuances in real world.
-  Meanwhile, the inherent robustness of large language models, owing to their sophisticated language representation capabilities and vast training corpora, facilitates the provision of more precise and comprehensive entity delineations.
-  Therefore, GIANT utilizes large language models to generate entity definitions for each question-answer pair, employing a combined approach of regular expressions and semantic dependency analysis models (Spacy) to parse the generated text and then constructs a branch-oriented "entity-elucidation" knowledge base.
-  Ultimately, the obtained knowledge base is used to retrieve entity elucidations and insert them behind entities in the original context, enriching the original textual content.
+  While previous research has delved into entity knowledge either through training or direct application of fine-tuned NER models like spaCy and BERN2, these models have limitations stemming from their narrow training datasets and their tendency to solely provide extracted entities without contextualized meanings due to their inflexible design.
+  In comparison, generative large language models, endowed with advanced representation capabilities and abundant training data, present a promising avenue for achieving more precise and comprehensive entity delineations.
+
+  Accordingly, GIANT utilizes a large language model to generate entity elucidation $E_i = \{e_0,...,e_h\}$ for each context $C_i$, where $i=1,..,n$. 
+  Following this, it adopts a hybrid methodology integrating both regular expressions and semantic dependency analysis models, exemplified by spaCy, to parse the produced text.
+  This systematic procedure culminates in the establishment of a ``Entity-Elucidation'' knowledge base oriented towards the elucidation of entities. 
+  Furthermore, we seamlessly integrates the retrieved entity $e_t \in E_i$ mentioned within context $C_i$ by inserting its corresponding explanation immediately after the entity mention, significantly enriching the original text content while ensuring coherence and clarity are upheld.
 

### 2024-03-25 experiments.tex
add method 'llm as summarizer'

@@
 \subsection{Experimental Setup}
-For all competing models and our model, we use the HuggingFace implementation of $\text{BERT}_{base}$ or $\text{RoBERTa}_{base}$ as the \textit{encoder} with $\textit{max\_len}$ = 512.
+For all competing models and our model, we use the HuggingwadFace implementation of $\text{BERT}_{base}$ or $\text{RoBERTa}_{base}$ as the \textit{encoder} with $\textit{max\_len}$ = 512.
 We set the initial learning rate as $3 \times 10^{-5}$ and  $\textit{batch\_size}$ = 4, and use the BERTAdam optimizer with a weight decay of 0.01.

### 2024-03-25 method.tex
add method 'llm as summarizer'

@@
 
- Consider $Gen(\cdot)$ as a generative large language model, and let $Inj(\cdot)$ function as a mapping that takes the generated content $K_i$ and context $C_i$, producing the augmented context $\tilde{C_i}$.
-$P(\cdot)$ represents a mapping of the context $C$ onto instantiated instructions, while $Tag(\cdot)$ serves as a QA model, and $Filter(\cdot)$ denotes the sieving operation.
- With these definitions, GIANT can be formulated as follows:
- \begin{align*}
- 	K_i &= Gen(C_i,P(C_i)) \tag{1}\\
- 	\tilde{C_i} &= Inj(K_i,C_i) \tag{2}\\
- 	A_i &= Tag(Q_i,~Filter(\tilde{C_i})) \tag{3}
- \end{align*}
-
  In the following section, we will explore how GIANT utilizes a large language model to generate knowledge.
@@
  GIANT leverages a large language model as an external knowledge source, utilizing it to generate augmented data $K_i = \{E_i, S_i, R_i, F_i\}$ from multiple perspectives.
-Here, $E_i$ represents named entity elucidation, $R_i$ denotes entity relations, $S_i$ pertains to content swdsummarization, and $F_i$ encompasses content continuation.
+Here, $E_i$ represents named entity elucidation, $R_i$ denotes entity relations, $S_i$ pertains to content summarization, and $F_i$ encompasses content continuation.
 
@@
  Content continuation introduces relevant external knowledge by extending contextual content.
+
+\subsubsection{LLMs as Content Summerizer}
+ One of the pivotal factors in entity knowledge selection lies in ensuring that these entities exhibit semantic relevance within the specified context.
+The incorporation of disparate entity explanations and relationship analyses at the model's input layer may lead to the valueless augmentation of contexts, consequently impeding the model's learning.
+
+ Utilizing the potent capabilities of large language models, we employ them to succinctly summarize the context $C_i$ into $S_i$, followed by extracting entities-based factual knowledge from $S_i$.
+ By considering summarization as a knowledge filter, we can achieve information augmentation with greater efficiency.
 
@@
 
-  Accordingly, GIANT utilizes a large language model to generate entity elucidation $E_i = \{e_0,...,e_h\}$ for each context $C_i$, where $i=1,..,n$. 
+ GIANT utilizes a large language model to generate entity elucidation $E_i = \{e_0,...,e_h\}$ for each context $C_i$, where $i=1,..,n$. 
  Following this, it adopts a hybrid methodology integrating both regular expressions and semantic dependency analysis models, exemplified by spaCy, to parse the produced text.
  This systematic procedure culminates in the establishment of a ``Entity-Elucidation'' knowledge base oriented towards the elucidation of entities. 
-  Furthermore, we seamlessly integrates the retrieved entity $e_t \in E_i$ mentioned within context $C_i$ by inserting its corresponding explanation immediately after the entity mention, significantly enriching the original text content while ensuring coherence and clarity are upheld.
+ Furthermore, as \figref{fig:entity_insertion} presented, we seamlessly integrates the retrieved entity $e_t \in E_i$ mentioned within context $C_i$ by inserting its corresponding explanation immediately after the entity mention, significantly enriching the original text content while ensuring coherence and clarity are upheld.
 
-\label{sec:information_injection}
+\label{sec:LLMs as Named Entity Elucidator}
 \begin{figure*}[h]
@@
 
-\subsection{Information Integration}
+\subsubsection{Information Integration}
 \label{sec:information_integration}

### 2024-03-27 method.tex
add method llm as entity relationship extractor

@@
 \section{Approach}
-\subsection{our framework}
+\subsection{Our Framework}
 \begin{figure*}[h]
@@
  Within these knowledge perspectives, named entity elucidation and entity relations provide factual knowledge, with GIANT synthesizing knowledge cues for the model by jointly injecting them into metadata.
- Summarization acts as a mechanism for information filtering, sieving and retaining entity interpretations, thereby ensuring augmentation efficiency. 
+ Summarization acts as a mechanism for information filtering, sieving and retaining entity interpretations and analyses of entity relationship, thereby ensuring augmentation efficiency. 
  Content continuation introduces relevant external knowledge by extending contextual content.
@@
 \subsubsection{LLMs as Named Entity Elucidator}
+\label{sec:LLMs as Named Entity Elucidator}
  The resolution of multi-span questions usually entails identifying named entities.
@@
 
- GIANT utilizes a large language model to generate entity elucidation $E_i = \{e_0,...,e_h\}$ for each context $C_i$, where $i=1,..,n$. 
+ GIANT utilizes a large language model to generate entity elucidation $E_i$ represented as $\{e_0,...,e_h\}$, from summary $S_i$ ,from summaries $S_i$ within each context $C_i$, where $i$ ranges from 1 to $n$.
  Following this, it adopts a hybrid methodology integrating both regular expressions and semantic dependency analysis models, exemplified by spaCy, to parse the produced text.
@@
 
-\label{sec:LLMs as Named Entity Elucidator}
 \begin{figure*}[h]
@@
 
-\subsubsection{Information Integration}
-\label{sec:information_integration}
-In addition to the aforementioned three types of information, we seek more valuable enhanced information by requesting summaries for each question-context pair from Large Language Models (LLMs).
-We then extract entities mentioned in the summaries to capture those highly relevant to the core context.
-Moreover, recognizing the intrinsic connection between entity explanation and entity relationship parsing, we categorize them as complementary information for context enrichment, with context continuation serving as supplementary information.
-This approach aims to augment the model's internal text-parsing knowledge with external world knowledge through enhanced information.
+\subsubsection{LLMs as Entity Relationship Extractor}
+\label{sec:llm_as_relationship_extrator}
+ In addition to entity elucidation, understanding entity relations can also assist the model in untangling intricate logical relationships within complex context, thereby facilitating the clarification of interconnected concepts focused on the question-and-answering process.
+ With the robust language comprehension capabilities, contextual sensitivity, and extensive external knowledge, large language models can adeptly capture entity associations within extensive contents and transform this structured knowledge into natural language expressions, thus integrating factual knowledge into the model in textual form.
 
-To further investigate the efficacy of multi-information integration, leveraging enhanced information derived from Large Language Models (LLMs), we employ two distinct approaches to combine entity knowledge and context continuity.
-The first approach involves the incorporation of all information within the original context, with each type of information undergoing individualized knowledge injection.
-The second approach, referred to as "bagging," treats models trained on diverse information sources as voters.
-For each query, we employ all model predictions for token-level BIO labeling within the context, determining the final prediction through a majority vote.
-In cases of tie-breaking, we prioritize the logits' magnitude to ascertain the ultimate prediction.
+ After extracting the textual entity relationships $R_i$ from each context $C_i$ provided in the MSQA benchmark, we first calculate the ratio $r_l$, which is defined as the quotient of the cumulative length of the generated text $R_i$ and the total length of the original context $C_i$.
+ As depicted in Figure 2, we subsequently partition the enhanced text $R_i$ and the original context $C_i$ into several segments, denoted as $\tilde{R_i} = \{\hat{r_1}, \hat{r_2}, ..., \hat{r_w}\}$ and $\tilde{C_i} = \{\hat{t_1}, \hat{t_2}, ..., \hat{t_w}\}$, respectively.
+ After partitioning, the number of enhanced text segments $|\tilde{R_i}|$ equals the number of original context segments $|\tilde{C_i}|$, and the ratio of the length of each enhanced text segment $|t_i|$ to each original context segment $|c_i|$ is consistent with $r_l$.
+ Next, we maintain the order of the original context segments while shuffling the order of the enhanced text segments, represented as $R_i' = \{r_{\sigma(1)}, r_{\sigma(2)}, ..., r_{\sigma(m)}\}$, where $\sigma$ is a random permutation of the indices of the enhanced text segments.
+Then, we sequentially insert the shuffled enhanced text segments into the original text segments.
+This concatenation results in a new context $C' = \{c_1, r_{\sigma(1)}, c_2, r_{\sigma(2)}, ..., c_n, r_{\sigma(n)}\}$ enriched with relational knowledge.
+
+\subsubsection{LLMs as Content Continuator}
+\label{sec:llm_as_continuator}

### 2024-03-27 method.tex
add method llm as continuator

@@
 \label{sec:llm_as_relationship_extrator}
- In addition to entity elucidation, understanding entity relations can also assist the model in untangling intricate logical relationships within complex context, thereby facilitating the clarification of interconnected concepts focused on the question-and-answering process.
+ Besides, understanding entity relations can also assist the model in untangling intricate logical relationships within complex context, thereby facilitating the clarification of interconnected concepts focused on the question-and-answering process.
  With the robust language comprehension capabilities, contextual sensitivity, and extensive external knowledge, large language models can adeptly capture entity associations within extensive contents and transform this structured knowledge into natural language expressions, thus integrating factual knowledge into the model in textual form.
+ Moreover, since entity interpretation and entity relationships are both factual knowledge, they naturally exhibit consistency, thus leading to their integration while GIANT injecting multiple knowledge into original context.
 
- After extracting the textual entity relationships $R_i$ from each context $C_i$ provided in the MSQA benchmark, we first calculate the ratio $r_l$, which is defined as the quotient of the cumulative length of the generated text $R_i$ and the total length of the original context $C_i$.
- As depicted in Figure 2, we subsequently partition the enhanced text $R_i$ and the original context $C_i$ into several segments, denoted as $\tilde{R_i} = \{\hat{r_1}, \hat{r_2}, ..., \hat{r_w}\}$ and $\tilde{C_i} = \{\hat{t_1}, \hat{t_2}, ..., \hat{t_w}\}$, respectively.
+ After extracting the textual entity relationships $R_i$ from the summary $S_i$ of each context $C_i$, to maximize the interaction between context $C_i$ and relational knowledge $R_i$, we first calculate the ratio $r_l$, which is defined as the quotient of the cumulative length of the generated text $R_i$ and the total length of the original context $C_i$.
+ As depicted in \figref{fig:random_concatenate}, we subsequently partition the enhanced text $R_i$ and the original context $C_i$ into several segments, denoted as $\tilde{R_i} = \{\hat{r_1}, \hat{r_2}, ..., \hat{r_w}\}$ and $\tilde{C_i} = \{\hat{t_1}, \hat{t_2}, ..., \hat{t_w}\}$, respectively.
  After partitioning, the number of enhanced text segments $|\tilde{R_i}|$ equals the number of original context segments $|\tilde{C_i}|$, and the ratio of the length of each enhanced text segment $|t_i|$ to each original context segment $|c_i|$ is consistent with $r_l$.
@@
 \label{sec:llm_as_continuator}
+
+ In addition to extracting and organizing knowledge from given contexts, we can enhance contexts by introducing external knowledge through the expansion of textual content.
+By continuing to write the original context, we enrich its content and themes, indirectly providing knowledge cues to models, thereby enabling model to learn more task-relevant information during fine-tuning.
+
+ With extensive training data and parameters, large language models possess vast knowledge and domain backgrounds, exhibiting strong language expression capabilities and a deep understanding of context.
+Consequently, they can generate coherent and informative text extensions based on contexts.
+Such continuations not only improve text coherence but also enhance information content.
+
+ The method of injecting extension knowledge is similar to injecting entity relationships into the original context.
+It involves randomly slicing the content continuation and inserting segmented text pieces into the original text, facilitating full interaction between the original and enhanced texts, which results in further enriching the semantics and content of the text.

### 2024-03-30 method.tex
update method

@@
 \subsection{LLMs as Knowledge Source}
+\label{sec:llm_as_knowledge_source}
  GIANT leverages a large language model as an external knowledge source, utilizing it to generate augmented data $K_i = \{E_i, S_i, R_i, F_i\}$ from multiple perspectives.
@@
 It involves randomly slicing the content continuation and inserting segmented text pieces into the original text, facilitating full interaction between the original and enhanced texts, which results in further enriching the semantics and content of the text.
+
+\subsection{Knowledge Ensemble}
+\label{sec:knowledge_ensemble}
+ Various types of knowledge are closely interconnected.
+A deep understanding of one type of knowledge can facilitate comprehension across different types.
+For instance, grasping entity relationship analysis can significantly enhance entity interpretation.
+We have developed multiple strategies for combining knowledge, focusing on data ensemble and model ensemble.
+Our aim is to determine which combinations of knowledge yield better results and to improve overall effectiveness by optimizing knowledge organization methods.
+\subsubsection{Data Ensemble}
+\label{sec:data_ensemble}
+ From the data ensemble perspective, we concurrently integrate various forms of knowledge into the metadata at the input layer of the model, thus learning a comprehensive knowledge enhancement model.
+The methodology for integrating each type of knowledge into the metadata during knowledge fusion aligns with the approach detailed in \secref{sec:llm_as_knowledge_source} specific to that type of knowledge.
+Given that entity interpretation and entity relationship analysis data stem from content summaries, a logical amalgamation emerges between summaries and the knowledge derived from entity interpretation and entity relationship analysis.
+Furthermore, considering that entity relationships and entity interpretation inherently embody factual knowledge centered on entities, we amalgamate them directly, conceptualizing it as a synthesis of summaries, entity interpretation, and entity relationship analysis.
+Ultimately, we can integrate content continuation knowledge into this tripartite fusion.
+ Totally, we present two combinations of knowledge:
+ $(a)$ integrating entity interpretation and entity relationship analysis, both derived from summaries, to mutually supplement factual knowledge;
+ $(b)$ building upon $(a)$, incorporating content continuation knowledge.
+
+ Illustrating through the exemplar combination $(a)$, we elucidate our methodology for knowledge amalgamation:
+ \begin{enumerate}
+ 	\item \textbf{Integration of Entity Interpretation:} We first incorporate entity interpretation ($E_i$) immediately after the the entity mention within the original context $C_i$,with the result designated as $C_i'$.
+ 	\item \textbf{Refinement of Enhanced Text:} Employing a methodological approach encompassing slicing, shuffling, and strategic insertion, we imbue the enhanced text ($C_i'$), with  entity relationship analysis, thereby engendering an evolved iteration ($C_i''$).
+ 	\item \textbf{Model Augmentation:} Finally, the refined $C_i''$ is channeled into the model's input layer to learn a fusion model incorporating multiple forms of knowledge, which is utilized for both training and inference.
+ \end{enumerate}
+ Furthermore, for combination $(b)$, the process merely requires an additional step of inserting content continuation knowledge after step 2.
+All other procedures remain consistent with the exemplified approach, employing a injection method identical to that used for integrating entity relationship analysis $R_i$ data into entity-interpretation-enhanced context $C_i'$.
+
+\subsubsection{Model Ensemble}
+\label{sec:model_ensemble}

### 2024-03-31 method.tex
update method

@@
 \label{sec:model_ensemble}
+ From the model ensemble perspective, we first fine-tune multiple single-knowledge-enhanced question-answering models.
+During the prediction phase, each model performs token-based B/I/O classification on the context.
+Subsequently, for each token, we conduct a voting process on the prediction results from each model, selecting the category with the highest number of votes as the final classification result.
+In case of a tie, we compare the average probabilities of all categories provided by the models, and select the category with the higher average probability as the classification for the given token.
+
+ Overall, we applied the aforementioned integration methods to two combinations for research purposes:$(a)$ combining factual knowledge (entity interpretation, entity relationships) with content continuation to compare the effectiveness of model ensemble methods versus data ensembles methods in knowledge fusion; and $(b)$ combining factual knowledge, content continuation, and other data augmentation methods (such as LIQUID) to investigate the compatibility between the model and other data augmentation methods.
